### 2021-11-26 src/ms.tex
add text

% Define document class
\documentclass[twocolumn]{article}%{aastex631}

% Filler text
\usepackage{blindtext}

% Begin!
\begin{document}

% Title
\title{asdfasf}

% Author list
\author{Björn Biltzinger, Jochen Greiner, J. Michael Burgess, Thomas Siegert}

% Abstract with filler text
\begin{abstract}
  In the last years it has been shown, that it is needed to fit physical models to Gamma-Ray Burst (GRB) data to get more insights into their emission mechanism. For the energy range between ~ 10 keV to ~ 10 MeV Fermi/GBM has been the main instrument.... In this paper we show how we can add INTEGRAL/SPI to this analysis. INTEGRAL/SPI covers a similar energy range like Fermi/GBM and has a very good energy resolution of 2.2 keV at 1.3 MeV. Therefore INTEGRAL/SPI is an ideal instrument to precisely measure the curvature of the spectrum. In this work we present PySPI, a new analysis software we developed to analyze GRB data from SPI, and apply it to the GRB 120711A. We show that the GBM and the SPI data of this GRB can be fitted with a physical synchrotron model and that combining both, reduces the allowed parameter space.

\end{abstract}

% Main body with filler text
\section{Introduction}
Gamma-Ray Bursts (GRBs) are short transient bursts of gamma rays, with a typical active time range between a few ms and few hundred seconds for the prompt phase, which is mostly observed in X- and Gamma-Rays. After the prompt emission there is a long lasting afterglow phase when the ejecta interacts with the Inter Steallar Medium (ISM). Long GRBs ($\approx$> 2s) have been associated to the collapse of massive stars (cite), whereas short GRBs are believed to be caused by mergers of compact objects, like Neutron Stars (cite grb-gw). In both cases is commonly agreed on that the progenitor events of GRBs should produce jetted relativistic outflows, which consists of shells which results in internal shell collisions. But it is still highly debated what the exact emission mechanism of the Gamma-Rays is.

In the past, GRB data was often fitted with empirical function like the Band function (cite band). But in recent years it has been shown, that this approach can be misleading and that one should rather fit physical models directly to the data. An example for this is the so-called line-of-death for synchrotron emission, which states that synchrotron radiation can not be the emission mechanism, if fits with a Band function give a low energy power law slope larger than -2/3. (cite) have shown that this conclusion is not correct and that you can fit GRB spectral well with a physical synchrotron model even though the same spectra violate the line-of-death if fitted with a Band function.
The Gamma-Ray Burst Monitor (GBM) onboard of the Fermi satellite is often used to fit GRB data in the Gamma-Ray energy range. GBM is an all-sky instrument, that observes the whole sky, except the part that is occulted by the Earth at that time. It consists of 12 NaI and two BGO scintillator detectors that cover in total an energy range between 8 keV and 10 MeV. (cite)
%The problem with fitting empirical models to the data and using the individual parameters of these fits to construct constrains on the physics is that the
Another instrument that operates in a similar energy range The SPectrometer on INTEGRAL (SPI) is one of the instruments onboard of the INTErnational Gamma-Ray Astrophysics Laboratory (INTEGRAL) satellite, that was launched in 2002 and is still operating today. SPI is a coded mask instrument, which has a FOV of roughly ? sr and covers an energy range between 20 keV and 8 MeV. Due to the Germanium detectors it has a very good energy resolution of roughly 2.2 keV at 1.3 MeV, which allows the identification of fine features, like atomic decay lines. (cite) In the case of GRBs this excellent energy resolution could allow us to determine the curvature of the spectra with an unmet precision. This is the main motivation to use SPI in our analysis. Several works have used SPI data to fit GRB models (cite), but all of them fitted empirical models like the Band function. To allow us to fit physical models and to improve the analysis methods we developed PySPI, which will be explained in detail in \ref{pyspi}.

%The other instrument that we use in this work is the Gamma-Ray Burst Monitor (GBM) onboard of the Fermi satellite. GBM is an all-sky instrument, that observes the whole sky, except the part that is occulted by the Earth at that time. It consists of 12 NaI and two BGO scintillator detectors that cover in total an energy range between 8 keV and 10 MeV. (cite)

\section{Methods}
\subsection{PySPI}
\label{pyspi}
To fit the SPI data of GRBs, we developed a new python package PySPI (ref to JOSS?), which is an open source analysis tool. In the following we will summarize the main points of PySPI.

\subsubsection*{Background}

GRBs are transient sources with a typical duration only up to a few tens of seconds.
%Therefore we can use the time before and after the GRB signal, but within the same science window, as a background measurement.
%The background treatment we use, depends on two assumptions, namely that within one science window the background is stable and the pointing direction of SPI does not change.
%Due to the high orbit and pointing scheme of INTEGRAL both these assumptions are valid.
Therefore we can use the time intervals during a science window when the transient source is not active as an independent background measurement. Similar to other instruments that use spatially off-source observation as an independent background measurement. In the case of transients in SPI we have temporal off-source observation. From the background observations we construct the probability of the background model rates per energy channel from a poisson distribution, like given in equation \ref{eq:poisson_bkg}, where $b_{i}$ are the background rates per energy channel, $B_{i}$ are the detected counts in the off-source observation and $t_{b}$ is the exposure of the off-source observation.
\begin{equation}
	L(b_{i}|B_{i}, t_{b})=\frac{(t_{b} b_{i})^{B_{i}}}{B_{i}!}\cdot e^{-t_{b}*b_{i}}
  \label{eq:poisson_bkg}
\end{equation}
This will be used in the next paragraph to derive the total likelihood.
% add a lightcurve plot?

\subsubsection*{Likelihood}

With the defined background treatment, we can construct a Poisson likelihood with a Poisson measurement of background, like given in \ref{eq:likelihood_m_and_b}. Here $\theta$ summarizes all the parameters of the model, $D_{i}$ are the measured counts in the selected active time interval of the transient source, $m(\theta)_{i}$ are the predicted counts from the model evaluated at the parameters $\theta$ and $t_{d}$ is the exposure of the selected active time interval.

\begin{equation}
	L(\theta, b_{i}|D_{i}, B_{i},t_{d},t_{b}) = \frac{(t_{d}(m(\theta)_{i}+ b_{i}))^{D_{i}}}{D_{i}!}\cdot e^{-t_{d}*(m(\theta)+b_{i})} \frac{(t_{b} b_{i})^{B_{i}}}{B_{i}!}\cdot e^{-t_{b}*b_{i}}
  \label{eq:likelihood_m_and_b}
\end{equation}

Now we can marginalize over the parameters $b_{i}$, that we are not interested in, which leaves us with equation \ref{eq:likelihood_marg}.

\begin{equation}
	L(\theta|D_{i}, B_{i},t_{d},t_{b}) = \int_{0}^{\infty}\textrm{db}_{i}\frac{(t_{d}(m(\theta)_{i}+ b_{i}))^{D_{i}}}{D_{i}!}\cdot e^{-t_{d}*(m(\theta)+b_{i})} \frac{(t_{b} b_{i})^{B_{i}}}{B_{i}!}\cdot e^{-t_{b}*b_{i}}
  \label{eq:likelihood_marg}
\end{equation}

Because there is no easy analytical solution for this integral, one often uses a so-called profiled likelihood as an approximation. For the profiled likelihood we use the fact, that the derivative of the likelihood at its maximum should be zero. Therefore one can construct from $\frac{\textrm{dL}}{\textrm{db}_i}=0$ the background rates $b_{i, max}$ that maximize the likelihood for a given model $m(\theta)_{i}$ and observed counts. Solving $\frac{\textrm{dL}}{\textrm{db}_i}=0$ for b gives equation \ref{eq:bmax}.
\begin{equation}
	b_{i,max}=
  \label{eq:bmax}
\end{equation}

These values can then be substituted in the likelihood \ref{eq:likelihood_m_and_b} to eliminate the $b_{i}$ dependency. This approximation gives the exact solution for the maximum of the likelihood, for likelihood values close to the maximum the assumption is that most of the likelihood in the integrand in \ref{eq:likelihood_marg} is in a small area around $b_{i,max}$ and we can add a $\delta(b_{i}-b_{{i,max}})$. This assumption is used in many works (cite) and works very well as long as one does not have too few counts in the background observation (for a derivation see cite Giacomo derivation).

\subsubsection*{Response}

To convert a physical spectrum to a detected count spectrum, we need the response for a given source position. The response encapsulates all the information about the probability of a photon with a certain energy and origin to be detected in a certain energy channel of the detector. This includes for example information about partial energy deposition of the photon in the crystal and the process that transforms the deposited energy into an electronic signal, that SPI measures.
% distribution of how much energy a photon with a certain energy deposit in the crystal and what energy is in the end measured for this deposited energy.
In PySPI we use the official response files for Image Response Functions (IRFs) and Redistribution Matrix Files (RMFs) derived by Sturner 2003 (cite). The IRF files give the total effective area for three different interaction types:
\begin{itemize}
  \item Photo peak events
  \item Non photo peak events that first interact in the crystal
  \item Non photo peak events that first interact in passive material
\end{itemize}

These effective areas were calculated for 51 photon energies and on a 0.5 degree grid. For each of the three interaction type there is one RMF, to define the shape of the redistributed spectra, assuming that this shape does not depend on the detector or the incident angles of the photons.
The procedure to construct the response includes several simplification to keep the computational costs and storage space manageable (cite). This could of course affect every analysis done with SPI. Re-simulating the response without these simplifications could improve the scientific output of SPI, but would take a hugh amount of computational time, even today.

In PySPI we then interpolate the official response files to the user defined energy bins.

\subsubsection*{Electronic Noise}

Since shortly after the start of INTEGRAL, it is known that there are spurious events in the SPI data around 1.5 MeV. According to Roques (cite) these spurious events are photons with small energy (<100 keV) that get detected at a higher energy due to saturation of the ??? electronics by previous high energy deposition. It is also known, that these spurious events do not show up if one looks only at events with a detection also in the Pulse Shape Discriminator (PSD) electronics. This is because the PSD electronics has an low energy threshold of roughly 450 keV (the exact value has been changed a few times during the mission). Therefore only events that deposit more than this low energy threshold in the Germanium crystal can trigger this electronic, which eliminates the <100 keV events that are detected at the wrong energies by the AFEE electronics. In Fig. ? one can see that the feature at 1.5 MeV in the non-PSD events is nicely visible and is missing in the PSD events.

(add plot with electronic noise in sgl events and not in psd)

\subsubsection*{General Procedure}

In PySPI every Germanium detector is treated as an independent detector. The workflow during a fit is the following:
\begin{itemize}
  \item Sample model parameters
  \item Calculate model flux and Responses individually for all detectors for the source position
  \item Fold model with responses to get predicted model counts in all detectors
  \item Calculate log-likelihood for all detectors
  \item Sum these log-likelihoods to get the total log-likelihood of SPI
\end{itemize}
Then a sampling algorithm like emcee (cite) or multinest (cite) is used to iterate this procedure, in order to determine the posterior distributions.\\
This workflow is very similar, like for example for Fermi/GBM, because fundamentally instruments like INTEGRAL/SPI and Fermi/GBM are very similar. They both consist of individual detectors that have different responses for a given source position. In GBM this is due to the different pointing directions of the detectors and in SPI due to the different occultation by the mask. Therefore there is no reason to treat SPI specially, just because it is a coded mask instrument. The information the mask encodes into the data is automatically included by using the different responses for the detectors.

\subsubsection*{3ML plugin}

PySPI can construct a plugin for the Multi-Mission Maximum Likelihood framework (3ML). This allows without any further work to fit the SPI data together with the data from other instruments, like Fermi/GBM. For more informations about 3ML see (cite paper and documentation).

\subsubsection*{Open Source Software}

PySPI is an open source software, which is publicly available on GitHub. There is also a documentation, that shows how to use PySPI for other GRBs as well. (cite JOSS, link to repo, docs).

\subsection{Synchrotron Model}

We use pynchrotron (cite github) to calculate the spectrum from a physical, time dependent spectral model. This model was previously used to successfully fit many single pulse GRBs with GBM in cite syn paper. This paper also include a detailed description of the model. Here we only want to summarize the main points shortly.

The core of the model is the assumption of some generic acceleration mechanism, that constantly produces an electron spectrum with a power law shape $N(\gamma )\propto gamma^{-p}$ between $\gamma_{inj}$ and $\gamma_{max}$. These electrons are cooled via synchrotron cooling in a magnetic field and produce radiation in this process. The resulting photon spectrum is defined by five quantities:

\begin{enumerate}
	\item Magnetic field strength $B$
  \item Lower boundary of the injected electron spectrum $\gamma_{inj}$
  \item Upper boundary of the injected electron spectrum $\gamma_{max}$
  \item Slope of the injected electron spectrum $p$
  \item Characteristic Lorentz factor the electrons cool to $\gamma_{cool}$
\end{enumerate}

For more details about the model check (cite Syn paper).

\subsection{Model Checking}

To check if the fit of a model is a good description of the measured data is a very complicated topic and highly debated in the statistics community. Measurements like reduced $\chi^{2}$ assume that all the probability distributions in the problem are described as normal distributions, which is definitely not the case here, as for example the measurement process is a Poisson process. Therefore we decided to use Posterior Predictive Checks (PPCs), which use the posterior of the fit as well as the measurement process to simulate new data.

\begin{equation}
  \textrm{P}(y^{\textrm{sim}}|y^{\textrm{obs}}) = \int \textrm{P}(y^{\textrm{sim}}|\theta) \textrm{P}(\theta|y^{\textrm{obs}}) \mathrm{d}\theta
\end{equation}
\noindent
Here $y^{\textrm{obs}}$ are the observed data, $\textrm{P}(\theta|y^{\textrm{obs}})$ is the posterior distribution of the model parameters $\theta$ given the observed data, $\textrm{P}(y^{\textrm{sim}}|\theta)$ is the probability of new data given the parameters of the model and $y^{\textrm{sim}}$ are the simulated data. These simulated data are then compared to the observed data and allow for a visual check, whether the fit results together with the measuring process can reproduce the data. (cite paper for this)
\section{Analysis}

- GRB120711A seen by SPI and GBM
- bright multi pulse GRB with a precurser and a long emission period of ~ 100 seconds
- select ~ 10 seconds to avoid to much spectral evolution and response change for GBM
- Fit with OSA, PySPI and GBM (explain procedure...) with Band -> in agreement but PySPI>>OSA
- FIt OSA, PySPI and GBM with Synch -> in agreement but PySPI>>OSA
- Fit PySPI and GBM combined -> improvement on parameter space.

- Simulation?

\section{Conclusion}

- Possible to fit physical models to GRB data of SPI and get same parameters as GBM
- Combined fits reduce available parameter space
- PySPI can be used to fit all SPI GRBs in the future with different physical models to help distinguishing between them

\end{document}

### 2021-11-26 src/ms.tex
change template
add bmax
fix
move i

@@
 % Define document class
-\documentclass[twocolumn]{article}%{aastex631}
+\documentclass[modern]{aastex631}
 
@@
 \begin{equation}
-	L(b_{i}|B_{i}, t_{b})=\frac{(t_{b} b_{i})^{B_{i}}}{B_{i}!}\cdot e^{-t_{b}*b_{i}}
+	L(b_{i}|B_{i}, t_{b})=\frac{(t_{b} b_{i})^{B_{i}}}{B_{i}!}\cdot e^{-t_{b} b_{i}}
   \label{eq:poisson_bkg}
@@
 With the defined background treatment, we can construct a Poisson likelihood with a Poisson measurement of background, like given in \ref{eq:likelihood_m_and_b}.
-Here $\theta$ summarizes all the parameters of the model, $D_{i}$ are the measured counts in the selected active time interval of the transient source, $m(\theta)_{i}$ are the predicted counts from the model evaluated at the parameters $\theta$ and $t_{d}$ is the exposure of the selected active time interval.
+Here $\theta$ summarizes all the parameters of the model, $D_{i}$ are the measured counts in the selected active time interval of the transient source, $m_{i}(\theta)$ are the predicted counts from the model evaluated at the parameters $\theta$ and $t_{d}$ is the exposure of the selected active time interval.
 
 \begin{equation}
-	L(\theta, b_{i}|D_{i}, B_{i},t_{d},t_{b}) = \frac{(t_{d}(m(\theta)_{i}+ b_{i}))^{D_{i}}}{D_{i}!}\cdot e^{-t_{d}*(m(\theta)+b_{i})} \frac{(t_{b} b_{i})^{B_{i}}}{B_{i}!}\cdot e^{-t_{b}*b_{i}}
+	L(\theta, b_{i}|D_{i}, B_{i},t_{d},t_{b}) = \frac{(t_{d}(m_{i}(\theta)+ b_{i}))^{D_{i}}}{D_{i}!}\cdot e^{-t_{d}(m_{i}(\theta)+b_{i})} \frac{(t_{b} b_{i})^{B_{i}}}{B_{i}!}\cdot e^{-t_{b} b_{i}}
   \label{eq:likelihood_m_and_b}
@@
 \begin{equation}
-	L(\theta|D_{i}, B_{i},t_{d},t_{b}) = \int_{0}^{\infty}\textrm{db}_{i}\frac{(t_{d}(m(\theta)_{i}+ b_{i}))^{D_{i}}}{D_{i}!}\cdot e^{-t_{d}*(m(\theta)+b_{i})} \frac{(t_{b} b_{i})^{B_{i}}}{B_{i}!}\cdot e^{-t_{b}*b_{i}}
+	L(\theta|D_{i}, B_{i},t_{d},t_{b}) = \int_{0}^{\infty}\textrm{db}_{i}\frac{(t_{d}(m_{i}(\theta)+ b_{i}))^{D_{i}}}{D_{i}!}\cdot e^{-t_{d}(m_{i}(\theta)+b_{i})} \frac{(t_{b} b_{i})^{B_{i}}}{B_{i}!}\cdot e^{-t_{b}b_{i}}
   \label{eq:likelihood_marg}
@@
 \begin{equation}
-	b_{i,max}=
+	b_{i,max}(\theta)=\frac{1}{2(t_{b}+t_{d})}(B_{i}+D_{i}-m_{i}(\theta)}(t_{b}+t_{d})+\sqrt{(B_{i}+D_{i}+m_{i}(\theta)(t_{b}+t_{d}))^{2}-4m_{i}(\theta)D_{i}(t_{d}-t_{b})}
   \label{eq:bmax}

### 2021-11-26 src/figures/lightcurve.py
first real script

@@ -1,0 +1,22 @@
+from pyspi.utils.data_builder.time_series_builder import TimeSeriesBuilderSPI
+import numpy as np
+
+grb_time = "120711 024453" #(YYMMDD HHMMSS) - from GBM trigger time
+background_time_interval_1_spi = "-500--10"
+background_time_interval_2_spi = "150-1000"
+
+tsb_sgl = TimeSeriesBuilderSPI.from_spi_grb("SPIDet0",
+                                            0,
+                                            grb_time,
+                                            ebounds=np.linspace(20,8000,100),
+                                            sgl_type="both",
+                                            poly_order=0,
+                                            )
+
+tsb_sgl.set_background_interval(background_time_interval_1_spi,
+                                background_time_interval_2_spi,
+                                fit_poly=False
+                               )
+
+f = tsb_sgl.view_lightcurve(-300,500);
+f.savefig("lightcurve.pdf")

### 2021-11-26 src/ms.tex
bug fix
add fig to paper

@@
 Similar to other instruments that use spatially off-source observation as an independent background measurement.
-In the case of transients in SPI we have temporal off-source observation.
+In the case of transients in SPI we have temporal off-source observation (see Fig.
+\ref{fig:lightcurve}).
 From the background observations we construct the probability of the background model rates per energy channel from a poisson distribution, like given in equation \ref{eq:poisson_bkg}, where $b_{i}$ are the background rates per energy channel, $B_{i}$ are the detected counts in the off-source observation and $t_{b}$ is the exposure of the off-source observation.
@@
 This will be used in the next paragraph to derive the total likelihood.
+
+\begin{figure}
+    \begin{centering}
+        \includegraphics{figures/lightcurve.pdf}
+        \caption{Lightcurve for SPI detector 0 for GRB120711A. The transient source is clearly visible as well as the constant background for the time when the transient is not active.}
+        % This label tells showyourwork that the script `figures/mandelbrot.py'
+        % generates the PDF file included above
+        \label{fig:lightcurve}
+    \end{centering}
+\end{figure}
+
 % add a lightcurve plot?
@@
 \begin{equation}
-	b_{i,max}(\theta)=\frac{1}{2(t_{b}+t_{d})}(B_{i}+D_{i}-m_{i}(\theta)}(t_{b}+t_{d})+\sqrt{(B_{i}+D_{i}+m_{i}(\theta)(t_{b}+t_{d}))^{2}-4m_{i}(\theta)D_{i}(t_{d}-t_{b})}
+	b_{i,max}(\theta)=\frac{1}{2(t_{b}+t_{d})}(B_{i}+D_{i}-m_{i}(\theta)(t_{b}+t_{d})+\sqrt{(B_{i}+D_{i}+m_{i}(\theta)(t_{b}+t_{d}))^{2}-4m_{i}(\theta)D_{i}(t_{d}-t_{b})}
   \label{eq:bmax}

### 2021-11-26 src/figures/lightcurve.py
add style

@@ -1,6 +1,7 @@
 from pyspi.utils.data_builder.time_series_builder import TimeSeriesBuilderSPI
 import numpy as np
-
+import matplotlib.pyplot as plt
+plt.style.use("matplotlibrc")
 grb_time = "120711 024453" #(YYMMDD HHMMSS) - from GBM trigger time
 background_time_interval_1_spi = "-500--10"
 background_time_interval_2_spi = "150-1000"

### 2021-11-26 src/ms.tex
add electronic noise image

@@
 In Fig.
-?
-one can see that the feature at 1.5 MeV in the non-PSD events is nicely visible and is missing in the PSD events.
+\ref{fig:electronic} one can see that the feature at 1.5 MeV in the non-PSD events is nicely visible and is missing in the PSD events.
+Even though this problem is the most significant in the area around 1.5 MeV it is also important at lower energies >400 keV.
 
-(add plot with electronic noise in sgl events and not in psd)
+\begin{figure}
+    \begin{centering}
+        \includegraphics{figures/electronic_noise.pdf}
+        \caption{Count spectrum for detector 0 integrated over 1000 seconds. One can clearly see the feature in the Non-PSD events at 1.5 MeV that is not visible in the PSD events.}
+        % This label tells showyourwork that the script `figures/mandelbrot.py'
+        % generates the PDF file included above
+        \label{fig:electronic}
+    \end{centering}
+\end{figure}
 

### 2021-11-26 src/figures/electronic_noise.py

@@ -1,0 +1,43 @@
+from pyspi.utils.data_builder.time_series_builder import TimeSeriesBuilderSPI
+import numpy as np
+import matplotlib.pyplot as plt
+plt.style.use("matplotlibrc")
+color1 = "#544b3dff"
+color2 = "#340068ff"
+color3 = "#4cb944ff"
+color4 = "#4f7cacff"
+color5 = "#6d2e46ff"
+
+ebounds=np.geomspace(20,8000,100)
+grb_time = "120711 024453" #(YYMMDD HHMMSS) - from GBM trigger time
+
+tsb_psd = TimeSeriesBuilderSPI.from_spi_grb("SPIDet0",
+                                            0,
+                                            grb_time,
+                                            ebounds=ebounds,
+                                            sgl_type="psd",
+                                            poly_order=0,
+                                            )
+
+tsb_non_psd = TimeSeriesBuilderSPI.from_spi_grb("SPIDet0",
+                                            0,
+                                            grb_time,
+                                            ebounds=ebounds,
+                                            sgl_type="sgl",
+                                            poly_order=0,
+                                            )
+
+counts_psd = tsb_psd.time_series.count_per_channel_over_interval(-1000,0)
+counts_non_psd = tsb_non_psd.time_series.count_per_channel_over_interval(-1000,0)
+
+fig, ax = plt.subplots(1,1)
+ax.step(ebounds[1:], counts_psd, label="PSD events", color=color1)
+ax.step(ebounds[1:], counts_non_psd, label="Non-PSD events", color=color2)
+ax.fill_betweenx(np.linspace(0,np.max(counts_non_psd),10),1400, 1900, alpha=0.5, color=color3, label="Main Electronic Noise Region")
+ax.set_yscale("log")
+ax.set_xscale("log")
+ax.set_xlabel("Detected Energy [keV]")
+ax.set_ylabel("Counts")
+ax.legend()
+
+fig.savefig("electronic_noise.pdf")

### 2021-11-26 src/figures/lightcurve.py

@@ -2,6 +2,13 @@ from pyspi.utils.data_builder.time_series_builder import TimeSeriesBuilderSPI
 import numpy as np
 import matplotlib.pyplot as plt
 plt.style.use("matplotlibrc")
+
+color1 = "#544b3dff"
+color2 = "#340068ff"
+color3 = "#4cb944ff"
+color4 = "#4f7cacff"
+color5 = "#6d2e46ff"
+
 grb_time = "120711 024453" #(YYMMDD HHMMSS) - from GBM trigger time
 background_time_interval_1_spi = "-500--10"
 background_time_interval_2_spi = "150-1000"
@@ -20,4 +27,12 @@ tsb_sgl.set_background_interval(background_time_interval_1_spi,
                                )
 
 f = tsb_sgl.view_lightcurve(-300,500);
+
+axis = f.axes[0]
+
+axis.get_lines()[0].set_color(color1)
+axis.get_lines()[1].set_color(color2)
+axis.collections[0].set_color(color3)
+axis.collections[1].set_color(color3)
+axis.legend()
 f.savefig("lightcurve.pdf")

### 2021-11-29 src/ms.tex
change to aa style

@@
 % Define document class
-\documentclass[modern]{aastex631}
+\documentclass[twocolumn]{aa}
 
@@
 Long GRBs ($\approx$> 2s) have been associated to the collapse of massive stars (cite), whereas short GRBs are believed to be caused by mergers of compact objects, like Neutron Stars (cite grb-gw).
-In both cases is commonly agreed on that the progenitor events of GRBs should produce jetted relativistic outflows, which consists of shells which results in internal shell collisions.
+In both cases is commonly agreed on that the progenitor events of GRBs should produce jetted relativistic outflows, which consists of shells resulting in internal shell collisions.
 But it is still highly debated what the exact emission mechanism of the Gamma-Rays is.
@@
         \caption{Lightcurve for SPI detector 0 for GRB120711A. The transient source is clearly visible as well as the constant background for the time when the transient is not active.}
-        % This label tells showyourwork that the script `figures/mandelbrot.py'
-        % generates the PDF file included above
         \label{fig:lightcurve}
@@
         \caption{Count spectrum for detector 0 integrated over 1000 seconds. One can clearly see the feature in the Non-PSD events at 1.5 MeV that is not visible in the PSD events.}
-        % This label tells showyourwork that the script `figures/mandelbrot.py'
-        % generates the PDF file included above
         \label{fig:electronic}
@@
 
+\subsection{OSA}
+\label{OSA}
+
+As we are introducing a new analysis software in this work, we want to compare it to the existing analysis software, to check if the results are in agreement.
+Therefor we shortly summarize the official analysis tools for GRB analysis, which are part of the INTEGRAL Offline Scientific Analysis (OSA) software, here.
+
+Analyzing GRB data from SPI with the OSA tools is a multi step process.
+The first steps are selecting the science window with the GRB, the time intervals for active time and background time as well as the energy bins for the analysis.
+After that one can either find the location of the GRB with SPIROS or set it manually, if it is already known.
+The next steps concern the spectral fitting, which is done in a two step procedure, which will be called Photo Peak Fitting and Energy Redistribution Fitting hereafter.
+
+\subsubsection*{Photo Peak Fitting}
+
+The first step in the spectral fitting with OSA is to use only the photo peak response of the detectors. These responses depend on the source position
+
 \subsection{Synchrotron Model}
@@
 \subsection{Model Checking}
-
+\ref{PPC}
 To check if the fit of a model is a good description of the measured data is a very complicated topic and highly debated in the statistics community.
@@
 
-- GRB120711A seen by SPI and GBM
-- bright multi pulse GRB with a precurser and a long emission period of ~ 100 seconds
-- select ~ 10 seconds to avoid to much spectral evolution and response change for GBM
-- Fit with OSA, PySPI and GBM (explain procedure...) with Band -> in agreement but PySPI>>OSA
-- FIt OSA, PySPI and GBM with Synch -> in agreement but PySPI>>OSA
-- Fit PySPI and GBM combined -> improvement on parameter space.
+In this work we analyze GRB 120711A, which was a multi bright pulse GRB with a precursor and a long emission period of $\approx$100 seconds.
+It was detected by SPI and GBM.
+In this work we only look at one time slice with a duration of 10 seconds around the highest peak in the light curves (add light curve plot with SPI and GBM data).
 
-- Simulation?
+First we analyze the data from the two instruments independently with empirical and physical models, to check if the results for SPI and GBM are in agreement and show a comparison between the fit results with PySPI and the official software tools for GRB analysis within OSA.
+After that we fit the data simultaneously, to show that it can reduce the allowed parameter space significantly.
+
+All the fits in this section are done with 3ML and the Bayesian sampler algorithm MultiNest (cite) to create full posterior distributions.
+
+\subsection{Compare PySPI and OSA}
+
+We analyze the SPI data for the same time interval with PySPI and OSA, to check if the results are in agreement.
+The two methods are described in \ref{OSA} and \ref{pyspi}.
+This is done for a fit with an empirical model (Band function) and a fit with the physical synchrotron model.
+The resulting posterior distributions, displayed as corner plots, and the PPC plots (see \ref{PPC}) are shown in Fig.
+?
+- Fig.
+?.
+The posterior distributions show, that the results from the two analysis techniques are in agreement, but PySPI can constrain the parameters much better.
+
+(include figs for band function and syn. fits!)
+
+\subsection{Compare SPI and GBM}
+
+Next, we analyze the SPI data with PySPI and the GBM data with the GRB analysis within 3ML (cite a paper for this?).
+Again we do this for an empirical model and the physical synchrotron model.
+The fit results are shown in Fig.
+?
+- Fig.
+?.
+
+\subsection{Joint Fit of SPI and GBM}
+
+The final analysis is a joint fit with SPI and GBM. This
 

### 2021-11-29 src/ms.tex
aa style

@@
 % Title
-\title{asdfasf}
+\title{Fitting Synchrotron Models to Gamma Ray Burst data from INTEGRAL/SPI}
 
 % Author list
-\author{Björn Biltzinger, Jochen Greiner, J. Michael Burgess, Thomas Siegert}
-
+\author{Björn Biltzinger \inst{mpe}, Jochen Greiner \inst{mpe}, J. Michael Burgess \inst{mpe}, Thomas Siegert \inst{mpe}}
+\institute{Max-Planck-Institut fur extraterrestrische Physik, Giessenbachstrasse 1, D-85748 Garching, Germany \label{mpe}}
+\date{Received 18 December, 2019; accepted 22 May, 2020}
 % Abstract with filler text
-\begin{abstract}
+\abstract{
   In the last years it has been shown, that it is needed to fit physical models to Gamma-Ray Burst (GRB) data to get more insights into their emission mechanism.
@@
 We show that the GBM and the SPI data of this GRB can be fitted with a physical synchrotron model and that combining both, reduces the allowed parameter space.
+}
 
-\end{abstract}
+\keywords{ (stars:) gamma ray bursts -- methods: data analysis --
+  methods: statistical}
+
+\maketitle
 
@@
 
-The first step in the spectral fitting with OSA is to use only the photo peak response of the detectors. These responses depend on the source position
+The first step in the spectral fitting with OSA is to use only the photo peak response of the detectors.
+These responses depend on the source position, as this defines the absorption by the mask.
+With these responses and the different measured data in the individual SPI detectors, taking into account
 
@@
 \subsection{Model Checking}
-\ref{PPC}
+\label{PPC}
 To check if the fit of a model is a good description of the measured data is a very complicated topic and highly debated in the statistics community.

### 2021-11-29 src/ms.tex
edits

@@
 % Author list
-\author{Björn Biltzinger \inst{mpe}, Jochen Greiner \inst{mpe}, J. Michael Burgess \inst{mpe}, Thomas Siegert \inst{mpe}}
+\author{Björn Biltzinger \inst{1}, Jochen Greiner \inst{1}, J. Michael Burgess \inst{1}, Thomas Siegert \inst{1}}
 \institute{Max-Planck-Institut fur extraterrestrische Physik, Giessenbachstrasse 1, D-85748 Garching, Germany \label{mpe}}
 \date{Received 18 December, 2019; accepted 22 May, 2020}
+
+\label{firstpage}
 % Abstract with filler text
-\abstract{
+\abstract {
   In the last years it has been shown, that it is needed to fit physical models to Gamma-Ray Burst (GRB) data to get more insights into their emission mechanism.
@@
 Gamma-Ray Bursts (GRBs) are short transient bursts of gamma rays, with a typical active time range between a few ms and few hundred seconds for the prompt phase, which is mostly observed in X- and Gamma-Rays.
-After the prompt emission there is a long lasting afterglow phase when the ejecta interacts with the Inter Steallar Medium (ISM).
+After the prompt emission there is a long lasting afterglow phase when the ejecta interacts with the Inter Stellar Medium (ISM).
 Long GRBs ($\approx$> 2s) have been associated to the collapse of massive stars (cite), whereas short GRBs are believed to be caused by mergers of compact objects, like Neutron Stars (cite grb-gw).
-In both cases is commonly agreed on that the progenitor events of GRBs should produce jetted relativistic outflows, which consists of shells resulting in internal shell collisions.
+In both cases it is commonly agreed on, that the progenitor events of GRBs produce jetted relativistic outflows, which consists of several shells with different velocities, resulting in internal shell collisions.
 But it is still highly debated what the exact emission mechanism of the Gamma-Rays is.
@@
 An example for this is the so-called line-of-death for synchrotron emission, which states that synchrotron radiation can not be the emission mechanism, if fits with a Band function give a low energy power law slope larger than -2/3.
-(cite) have shown that this conclusion is not correct and that you can fit GRB spectral well with a physical synchrotron model even though the same spectra violate the line-of-death if fitted with a Band function.
+(cite) have shown that this conclusion is not correct and that you can fit GRB spectra well with a physical synchrotron model even though the same spectra violate the line-of-death if fitted with a Band function.
 The Gamma-Ray Burst Monitor (GBM) onboard of the Fermi satellite is often used to fit GRB data in the Gamma-Ray energy range.
@@
 %The problem with fitting empirical models to the data and using the individual parameters of these fits to construct constrains on the physics is that the
-Another instrument that operates in a similar energy range The SPectrometer on INTEGRAL (SPI) is one of the instruments onboard of the INTErnational Gamma-Ray Astrophysics Laboratory (INTEGRAL) satellite, that was launched in 2002 and is still operating today.
+Another instrument that operates in a similar energy range is the SPectrometer on INTEGRAL (SPI), which is one of the instruments onboard of the INTErnational Gamma-Ray Astrophysics Laboratory (INTEGRAL) satellite, that was launched in 2002 and is still operating today.
 SPI is a coded mask instrument, which has a FOV of roughly ?
@@
 This is the main motivation to use SPI in our analysis.
+
 Several works have used SPI data to fit GRB models (cite), but all of them fitted empirical models like the Band function.
@@
 %Due to the high orbit and pointing scheme of INTEGRAL both these assumptions are valid.
-Therefore we can use the time intervals during a science window when the transient source is not active as an independent background measurement.
+Therefore we can use the time intervals during a science window when the transient source is not active as an independent temporal off-source observation (see Fig.
+\ref{fig:lightcurve}).
 Similar to other instruments that use spatially off-source observation as an independent background measurement.
-In the case of transients in SPI we have temporal off-source observation (see Fig.
-\ref{fig:lightcurve}).
 From the background observations we construct the probability of the background model rates per energy channel from a poisson distribution, like given in equation \ref{eq:poisson_bkg}, where $b_{i}$ are the background rates per energy channel, $B_{i}$ are the detected counts in the off-source observation and $t_{b}$ is the exposure of the off-source observation.
@@
 \end{equation}
-This will be used in the next paragraph to derive the total likelihood.
+This expression will be used in the next paragraph to derive the total likelihood.
 
@@
 Because there is no easy analytical solution for this integral, one often uses a so-called profiled likelihood as an approximation.
-For the profiled likelihood we use the fact, that the derivative of the likelihood at its maximum should be zero.
-Therefore one can construct from $\frac{\textrm{dL}}{\textrm{db}_i}=0$ the background rates $b_{i, max}$ that maximize the likelihood for a given model $m(\theta)_{i}$ and observed counts.
+For the profiled likelihood we use the fact, that the derivative of the likelihood at its maximum is zero.
+Therefore one can construct from $\frac{\textrm{dL}}{\textrm{db}_i}=0$ the background rates $b_{i, max}$ that maximize the likelihood for a given model $m_{i}(\theta)$ and observed counts.
 Solving $\frac{\textrm{dL}}{\textrm{db}_i}=0$ for b gives equation \ref{eq:bmax}.
@@
 These values can then be substituted in the likelihood \ref{eq:likelihood_m_and_b} to eliminate the $b_{i}$ dependency.
-This approximation gives the exact solution for the maximum of the likelihood, for likelihood values close to the maximum the assumption is that most of the likelihood in the integrand in \ref{eq:likelihood_marg} is in a small area around $b_{i,max}$ and we can add a $\delta(b_{i}-b_{{i,max}})$.
+This approximation gives the exact solution for the maximum of the likelihood, for likelihood values close to the maximum the assumption is that most of the likelihood in the integrand in \ref{eq:likelihood_marg} is in a small area around $b_{i,max}$ and we can basically add a $\delta(b_{i}-b_{{i,max}})$.
 This assumption is used in many works (cite) and works very well as long as one does not have too few counts in the background observation (for a derivation see cite Giacomo derivation).
@@
 The response encapsulates all the information about the probability of a photon with a certain energy and origin to be detected in a certain energy channel of the detector.
-This includes for example information about partial energy deposition of the photon in the crystal and the process that transforms the deposited energy into an electronic signal, that SPI measures.
+This includes for example information about partial energy deposition of the photon in the crystal and the process that transforms the deposited energy into an electronic signal, that is measured in the end.
 % distribution of how much energy a photon with a certain energy deposit in the crystal and what energy is in the end measured for this deposited energy.
@@
 
-In PySPI we then interpolate the official response files to the user defined energy bins.
+In PySPI we then interpolate the official response files to the user defined energy bins and source positions.
 
@@
 Since shortly after the start of INTEGRAL, it is known that there are spurious events in the SPI data around 1.5 MeV.
-According to Roques (cite) these spurious events are photons with small energy (<100 keV) that get detected at a higher energy due to saturation of the ???
+According to (cite Roques) these spurious events are photons with small energy (<100 keV) that get detected at a higher energy due to saturation of the ???
 electronics by previous high energy deposition.
 It is also known, that these spurious events do not show up if one looks only at events with a detection also in the Pulse Shape Discriminator (PSD) electronics.
-This is because the PSD electronics has an low energy threshold of roughly 450 keV (the exact value has been changed a few times during the mission).
+The reason for this is that the PSD electronics has an low energy threshold of roughly 450 keV (the exact value has been changed a few times during the mission).
 Therefore only events that deposit more than this low energy threshold in the Germanium crystal can trigger this electronic, which eliminates the <100 keV events that are detected at the wrong energies by the AFEE electronics.
 In Fig.
-\ref{fig:electronic} one can see that the feature at 1.5 MeV in the non-PSD events is nicely visible and is missing in the PSD events.
+\ref{fig:electronic} one can see that the feature at 1.5 MeV is nicely visible in the non-PSD events but is missing in the PSD events.
 Even though this problem is the most significant in the area around 1.5 MeV it is also important at lower energies >400 keV.
@@
 
-In PySPI every Germanium detector is treated as an independent detector. The workflow during a fit is the following:
+In PySPI every Germanium detector is treated as an independent detector. The workflow during a fit step is the following:
 \begin{itemize}
   \item Sample model parameters
-  \item Calculate model flux and Responses individually for all detectors for the source position
+  \item Calculate model flux and responses individually for all detectors for the source position
   \item Fold model with responses to get predicted model counts in all detectors
@@
 \end{itemize}
-Then a sampling algorithm like emcee (cite) or multinest (cite) is used to iterate this procedure, in order to determine the posterior distributions.\\
+A sampling algorithm like emcee (cite) or multinest (cite) is used to iterate this procedure, in order to determine the posterior distributions.\\
 This workflow is very similar, like for example for Fermi/GBM, because fundamentally instruments like INTEGRAL/SPI and Fermi/GBM are very similar.
@@
 PySPI can construct a plugin for the Multi-Mission Maximum Likelihood framework (3ML).
-This allows without any further work to fit the SPI data together with the data from other instruments, like Fermi/GBM.
-For more informations about 3ML see (cite paper and documentation).
+This allows, without any further work, to fit the SPI data together with the data from other instruments, like Fermi/GBM.
+For more information about 3ML see (cite paper and documentation).
 
@@
 
-PySPI is an open source software, which is publicly available on GitHub. There is also a documentation, that shows how to use PySPI for other GRBs as well. (cite JOSS, link to repo, docs).
+PySPI is an open source software, which is publicly available on GitHub. There is also a documentation, that shows how to use it. (cite JOSS, link to repo, docs).
 
@@
 Analyzing GRB data from SPI with the OSA tools is a multi step process.
-The first steps are selecting the science window with the GRB, the time intervals for active time and background time as well as the energy bins for the analysis.
+The first steps are basic and cover selecting the science window with the GRB, the time intervals for active time and background time as well as the energy bins for the analysis.
 After that one can either find the location of the GRB with SPIROS or set it manually, if it is already known.
-The next steps concern the spectral fitting, which is done in a two step procedure, which will be called Photo Peak Fitting and Energy Redistribution Fitting hereafter.
+The next steps concern the spectral fitting, which is done in a two step procedure, which will be called 'Photo Peak Fitting' and 'Energy Redistribution Fitting' hereafter.
 
@@
 
-The first step in the spectral fitting with OSA is to use only the photo peak response of the detectors.
-These responses depend on the source position, as this defines the absorption by the mask.
-With these responses and the different measured data in the individual SPI detectors, taking into account
+The first step in the spectral fitting with OSA, is to use only the photo peak response of the detectors.
+These responses depend on the source position, as this defines for example the absorption by the mask.
+With these responses and the measured data in the individual SPI detectors, taking into account the different background rates, a photon flux is fitted individually per energy channel.
+These pseudo photon fluxes are not the final result, as up to this point energy dispersion and resolution was ignored.
+
+\subsubsection*{Energy Redistribution Fitting}
+
+The pseudo photon flux data points from the 'Photo Peak Fitting' step, which are no real data points anymore, are fitted with a photon model which gets folded through a correction response, that was created by OSA.
+This correction response depends on the source position and energy bins that are used and should account for energy dispersion as well as resolution.
+In this step the energy channels are fitted simultaneously, as it is impossible to incorporate energy dispersion in a way that fits every energy channel individually.
+This fitting can be done in different spectral fitting software like 3ML or XSPEC.
+In this work we always used 3ML.
 
@@
 
-We use pynchrotron (cite github) to calculate the spectrum from a physical, time dependent spectral model.
+We use pynchrotron (cite github) to calculate the spectrum from a physical, time dependent spectral synchrotron model.
 This model was previously used to successfully fit many single pulse GRBs with GBM in cite syn paper.
@@
 To check if the fit of a model is a good description of the measured data is a very complicated topic and highly debated in the statistics community.
-Measurements like reduced $\chi^{2}$ assume that all the probability distributions in the problem are described as normal distributions, which is definitely not the case here, as for example the measurement process is a Poisson process.
-Therefore we decided to use Posterior Predictive Checks (PPCs), which use the posterior of the fit as well as the measurement process to simulate new data.
+Measurements like reduced $\chi^{2}$ use many assumptions, like for example that all the probability distributions in the problem are described as normal distributions, which is definitely not the case here, as the measurement process is a Poisson process.
+Therefore we decided to use Posterior Predictive Checks (PPCs, see Eq.
+\ref{eq:ppc}), which use the full posterior of the fit as well as the measurement process to simulate new data and compare them to the observed data.
 
@@
   \textrm{P}(y^{\textrm{sim}}|y^{\textrm{obs}}) = \int \textrm{P}(y^{\textrm{sim}}|\theta) \textrm{P}(\theta|y^{\textrm{obs}}) \mathrm{d}\theta
+  \label{eq:ppc}
 \end{equation}
@@
 Here $y^{\textrm{obs}}$ are the observed data, $\textrm{P}(\theta|y^{\textrm{obs}})$ is the posterior distribution of the model parameters $\theta$ given the observed data, $\textrm{P}(y^{\textrm{sim}}|\theta)$ is the probability of new data given the parameters of the model and $y^{\textrm{sim}}$ are the simulated data.
-These simulated data are then compared to the observed data and allow for a visual check, whether the fit results together with the measuring process can reproduce the data.
+These simulated data are then compared to the observed data and allow for a visual check, whether the posterior distributions of the fit together with the measuring process can reproduce the data.
 (cite paper for this)
@@
 
-In this work we analyze GRB 120711A, which was a multi bright pulse GRB with a precursor and a long emission period of $\approx$100 seconds.
+In this work we analyze GRB 120711A, which was a bright, multi pulse GRB with a precursor and a long emission period of $\approx$100 seconds.
 It was detected by SPI and GBM.
@@
 
-First we analyze the data from the two instruments independently with empirical and physical models, to check if the results for SPI and GBM are in agreement and show a comparison between the fit results with PySPI and the official software tools for GRB analysis within OSA.
-After that we fit the data simultaneously, to show that it can reduce the allowed parameter space significantly.
+First we analyze the data from the two instruments independently with empirical and physical models, to check if the results for SPI and GBM are in agreement as well as show a comparison between the fit results with PySPI and the official software tools for GRB analysis within OSA.
+After that we fit the data of SPI and GBM simultaneously, to show that it can reduce the allowed parameter space significantly.
 
-All the fits in this section are done with 3ML and the Bayesian sampler algorithm MultiNest (cite) to create full posterior distributions.
+All the fits in this section are done with 3ML and the Bayesian sampler algorithm MultiNest (cite) to create full posterior distributions of the parameters.
 

### 2021-11-29 src/ms.tex
fix authors

@@
 % Title
-\title{Fitting Synchrotron Models to Gamma Ray Burst data from INTEGRAL/SPI}
+\title{Fitting Synchrotron Models to Gamma-Ray Burst Data from INTEGRAL/SPI}
 
 % Author list
-\author{Björn Biltzinger \inst{1}, Jochen Greiner \inst{1}, J. Michael Burgess \inst{1}, Thomas Siegert \inst{1}}
+\author{
+  Björn Biltzinger
+  \and
+  Jochen Greiner
+  \and
+  Michael Burgess
+  \and
+  Siegert
+}
+
 \institute{Max-Planck-Institut fur extraterrestrische Physik, Giessenbachstrasse 1, D-85748 Garching, Germany \label{mpe}}
@@
 \section{Introduction}
+
 Gamma-Ray Bursts (GRBs) are short transient bursts of gamma rays, with a typical active time range between a few ms and few hundred seconds for the prompt phase, which is mostly observed in X- and Gamma-Rays.

### 2021-11-29 src/figures/lightcurve.py
use correct PR for 3ML because this will be not merged soon...

@@ -31,7 +31,7 @@ f = tsb_sgl.view_lightcurve(-300,500);
 axis = f.axes[0]
 
 axis.get_lines()[0].set_color(color1)
-axis.get_lines()[1].set_color(color2)
+#axis.get_lines()[1].set_color(color2)
 axis.collections[0].set_color(color3)
 axis.collections[1].set_color(color3)
 axis.legend()

### 2021-11-29 src/ms.tex
text

@@
 As we are introducing a new analysis software in this work, we want to compare it to the existing analysis software, to check if the results are in agreement.
-Therefor we shortly summarize the official analysis tools for GRB analysis, which are part of the INTEGRAL Offline Scientific Analysis (OSA) software, here.
+Therefore we shortly summarize the official analysis tools for GRB analysis, which are part of the INTEGRAL Offline Scientific Analysis (OSA) software, here.
 

### 2021-11-29 src/figures/lightcurve.py

@@ -31,8 +31,9 @@ f = tsb_sgl.view_lightcurve(-300,500);
 axis = f.axes[0]
 
 axis.get_lines()[0].set_color(color1)
-#axis.get_lines()[1].set_color(color2)
 axis.collections[0].set_color(color3)
 axis.collections[1].set_color(color3)
+
 axis.legend()
+
 f.savefig("lightcurve.pdf")

### 2021-11-29 src/figures/lightcurve.py
try install

@@ -20,7 +20,6 @@ tsb_sgl = TimeSeriesBuilderSPI.from_spi_grb("SPIDet0",
                                             sgl_type="both",
                                             poly_order=0,
                                             )
-
 tsb_sgl.set_background_interval(background_time_interval_1_spi,
                                 background_time_interval_2_spi,
                                 fit_poly=False

### 2021-11-30 src/ms.tex
add ts figures

--- 2021-11-29 src/ms.tex
@@
 % Filler text
-\usepackage{blindtext}
-
+\usepackage{caption}
+\usepackage{subcaption}
 % Begin!
@@
 As we are introducing a new analysis software in this work, we want to compare it to the existing analysis software, to check if the results are in agreement.
-Therefor we shortly summarize the official analysis tools for GRB analysis, which are part of the INTEGRAL Offline Scientific Analysis (OSA) software, here.
+We shortly summarize the official analysis tools for GRB analysis, which are part of the INTEGRAL Offline Scientific Analysis (OSA) software.
+(https://ui.adsabs.harvard.edu/abs/2003A%26A...411L..53C/abstract)
 
-Analyzing GRB data from SPI with the OSA tools is a multi step process.
+Analyzing GRB data from SPI with the OSA tools is a multistep process.
 The first steps are basic and cover selecting the science window with the GRB, the time intervals for active time and background time as well as the energy bins for the analysis.
-After that one can either find the location of the GRB with SPIROS or set it manually, if it is already known.
-The next steps concern the spectral fitting, which is done in a two step procedure, which will be called 'Photo Peak Fitting' and 'Energy Redistribution Fitting' hereafter.
+After that one can either find the location of the GRB with SPIROS, i.e.
+an iterative source removal algorithm for SPI data, or set it manually, if it is already known.
+The next steps concern the spectral fitting, which is done in an other two-step procedure, which will be called 'Photo Peak Fitting' and 'Energy Redistribution Fitting' hereafter.
 
@@
 
-The first step in the spectral fitting with OSA, is to use only the photo peak response of the detectors.
+The first step in the spectral fitting with OSA is to use only the photo peak response of the detectors.
 These responses depend on the source position, as this defines for example the absorption by the mask.
 With these responses and the measured data in the individual SPI detectors, taking into account the different background rates, a photon flux is fitted individually per energy channel.
-These pseudo photon fluxes are not the final result, as up to this point energy dispersion and resolution was ignored.
+These pseudo photon fluxes are not the final result, as up to this point energy dispersion and detector energy resolution was ignored.
 
@@
 
-The pseudo photon flux data points from the 'Photo Peak Fitting' step, which are no real data points anymore, are fitted with a photon model which gets folded through a correction response, that was created by OSA.
+The pseudo photon flux data points from the 'Photo Peak Fitting' step, which are no real data points anymore, are fitted with a spectral photon flux model which is convolved with a correction response, which is also available through OSA.
 This correction response depends on the source position and energy bins that are used and should account for energy dispersion as well as resolution.
@@
 It was detected by SPI and GBM.
-In this work we only look at one time slice with a duration of 10 seconds around the highest peak in the light curves (add light curve plot with SPI and GBM data).
+In this work we only look at one time slice with a duration of 10 seconds around the highest peak in the light curves
+
+\begin{figure}
+  \begin{centering}
+    \begin{subfigure}[b]{1\textwidth}
+      \begin{centering}
+        \includegraphics{figures/spi_lightcurve_ts.pdf}
+        \caption{Light curve for SPI detector 0 and GRB120711A.}
+        \label{fig:ts_spi}
+      \end{centering}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{1\textwidth}
+      \begin{centering}
+        \includegraphics{figures/gbm_lightcurve_ts.pdf}
+        \caption{Light curve for GBM detector n2 and GRB120711A.}
+        \label{fig:ts_gbm}
+      \end{centering}
+    \end{subfigure}
+  \end{centering}
+\end{figure}
 

### 2021-11-30 src/figures/time_selection.py

@@ -1,0 +1,108 @@
+from pyspi.utils.data_builder.time_series_builder import TimeSeriesBuilderSPI
+from pyspi.utils.response.spi_response_data import ResponseDataRMF
+from pyspi.utils.response.spi_response import ResponseRMFGenerator
+from pyspi.utils.response.spi_drm import SPIDRM
+import numpy as np
+import matplotlib.pyplot as plt
+plt.style.use("matplotlibrc")
+
+color1 = "#544b3dff"
+color2 = "#340068ff"
+color3 = "#4cb944ff"
+color4 = "#4f7cacff"
+color5 = "#6d2e46ff"
+
+grb_time = "120711 024453" #(YYMMDD HHMMSS) - from GBM trigger time
+background_time_interval_1_spi = "-500--10"
+background_time_interval_2_spi = "150-1000"
+active_time = '65-73'
+det_spi = 0
+det_gbm = "n2"
+ebounds_spi = np.linspace(20,8000,100)
+ein = np.geomspace(20,8000,100)
+
+rsp_base = ResponseDataRMF.from_version(4)
+drm_gen = ResponseRMFGenerator.from_time(grb_time,  0,
+                                        ebounds_spi, ein,
+                                        rsp_base)
+
+sd = SPIDRM(drm_gen, 94.67830, -70.99905)
+
+tsb = TimeSeriesBuilderSPI.from_spi_grb("SPIDet0",
+                                            det_spi,
+                                            grb_time,
+                                            response=sd,
+                                            sgl_type="both",
+                                            )
+tsb.set_background_interval(background_time_interval_1_spi,
+                                background_time_interval_2_spi,
+                                fit_poly=False
+                               )
+tsb.set_active_time_interval(active_time)
+f_spi = tsb.view_lightcurve(-20,200,0.5)
+
+from threeML.utils.data_builders.time_series_builder import TimeSeriesBuilder
+from threeML import silence_warnings
+silence_warnings()
+# GBM Specific Input
+background_time_interval_1_gbm = "-30--10"
+background_time_interval_2_gbm = "150-200"
+
+# General Input
+active_time_gbm = '65-73'
+det = "n2"
+sls1 = []
[…]

### 2021-11-30 src/figures/time_selection.py
add data download

@@ -54,9 +54,12 @@ det = "n2"
 sls1 = []
 tss1 = []
 
-tte_file = "/home/bjorn/Downloads/glg_tte_{}_bn120711115_v00.fit".format(det)
-rsp2_file="/home/bjorn/Downloads/glg_cspec_{}_bn120711115_v00.rsp2".format(det)
-ts = TimeSeriesBuilder.from_gbm_tte('gbm{}'.format(det), tte_file, rsp2_file,poly_order=0)
+from threeML.utils.data_download.Fermi_GBM.download_GBM_data import download_GBM_trigger_data
+download_GBM_trigger_data("bn120711115", [det], ".")
+
+tte_file = "glg_tte_{}_bn120711115_v00.fit".format(det)
+rsp2_file="glg_cspec_{}_bn120711115_v00.rsp2".format(det)
+ts = TimeSeriesBuilder.from_gbm_tte('gbm{}'.format(det), tte_file, rsp2_file)
 ts.set_active_time_interval(active_time_gbm)
 ts.set_background_interval(background_time_interval_1_gbm,
                            background_time_interval_2_gbm,

### 2021-11-30 src/figures/time_selection.py
next try

@@ -55,10 +55,11 @@ sls1 = []
 tss1 = []
 
 from threeML.utils.data_download.Fermi_GBM.download_GBM_data import download_GBM_trigger_data
-download_GBM_trigger_data("bn120711115", [det], ".")
-
-tte_file = "glg_tte_{}_bn120711115_v00.fit".format(det)
-rsp2_file="glg_cspec_{}_bn120711115_v00.rsp2".format(det)
+download_GBM_trigger_data("bn120711115", [det], "/home/runner/")
+import os
+os.listdir("/home/runner/")
+tte_file = "/home/runner/glg_tte_{}_bn120711115_v00.fit".format(det)
+rsp2_file="/home/runner/glg_cspec_{}_bn120711115_v00.rsp2".format(det)
 ts = TimeSeriesBuilder.from_gbm_tte('gbm{}'.format(det), tte_file, rsp2_file)
 ts.set_active_time_interval(active_time_gbm)
 ts.set_background_interval(background_time_interval_1_gbm,

### 2021-11-30 src/figures/time_selection.py
try

@@ -57,7 +57,7 @@ tss1 = []
 from threeML.utils.data_download.Fermi_GBM.download_GBM_data import download_GBM_trigger_data
 download_GBM_trigger_data("bn120711115", [det], "/home/runner/")
 import os
-os.listdir("/home/runner/")
+print(os.listdir("/home/runner/"))
 tte_file = "/home/runner/glg_tte_{}_bn120711115_v00.fit".format(det)
 rsp2_file="/home/runner/glg_cspec_{}_bn120711115_v00.rsp2".format(det)
 ts = TimeSeriesBuilder.from_gbm_tte('gbm{}'.format(det), tte_file, rsp2_file)

### 2021-11-30 src/figures/time_selection.py
add .gz

@@ -58,7 +58,7 @@ from threeML.utils.data_download.Fermi_GBM.download_GBM_data import download_GBM
 download_GBM_trigger_data("bn120711115", [det], "/home/runner/")
 import os
 print(os.listdir("/home/runner/"))
-tte_file = "/home/runner/glg_tte_{}_bn120711115_v00.fit".format(det)
+tte_file = "/home/runner/glg_tte_{}_bn120711115_v00.fit.gz".format(det)
 rsp2_file="/home/runner/glg_cspec_{}_bn120711115_v00.rsp2".format(det)
 ts = TimeSeriesBuilder.from_gbm_tte('gbm{}'.format(det), tte_file, rsp2_file)
 ts.set_active_time_interval(active_time_gbm)

### 2021-11-30 src/figures/time_selection.py
change path

@@ -55,11 +55,9 @@ sls1 = []
 tss1 = []
 
 from threeML.utils.data_download.Fermi_GBM.download_GBM_data import download_GBM_trigger_data
-download_GBM_trigger_data("bn120711115", [det], "/home/runner/")
-import os
-print(os.listdir("/home/runner/"))
-tte_file = "/home/runner/glg_tte_{}_bn120711115_v00.fit.gz".format(det)
-rsp2_file="/home/runner/glg_cspec_{}_bn120711115_v00.rsp2".format(det)
+download_GBM_trigger_data("bn120711115", [det], ".")
+tte_file = "glg_tte_{}_bn120711115_v00.fit.gz".format(det)
+rsp2_file="glg_cspec_{}_bn120711115_v00.rsp2".format(det)
 ts = TimeSeriesBuilder.from_gbm_tte('gbm{}'.format(det), tte_file, rsp2_file)
 ts.set_active_time_interval(active_time_gbm)
 ts.set_background_interval(background_time_interval_1_gbm,

### 2021-12-02 src/ms.tex
fix figure
fix label name
add corner plot

@@
 In this work we present PySPI, a new analysis software we developed to analyze GRB data from SPI, and apply it to the GRB 120711A.
-We show that the GBM and the SPI data of this GRB can be fitted with a physical synchrotron model and that combining both, reduces the allowed parameter space.
+We show that PySPI improves the analysis of SPI data, for GRBs, compared to the official analysis software.
+Also we show that the GBM and the SPI data of this GRB can be fitted well with a physical synchrotron model and that combining both, reduces the allowed parameter space.
 }
@@
 Even though this problem is the most significant in the area around 1.5 MeV it is also important at lower energies >400 keV.
+In PySPI one can select the energy range in which only the PSD events should be used, to avoid including spurious events.
+To account for the larger dead time of the PSD electronics, an effective area correction can be either fix to 85 \% (cite) or treated as a free parameter in the fit.
 
@@
 \end{itemize}
-A sampling algorithm like emcee (cite) or multinest (cite) is used to iterate this procedure, in order to determine the posterior distributions.\\
-This workflow is very similar, like for example for Fermi/GBM, because fundamentally instruments like INTEGRAL/SPI and Fermi/GBM are very similar.
+A sampling algorithm like emcee (cite) or MultiNest (cite) is used to iterate this procedure, in order to determine the posterior distributions.\\
+This workflow is very similar, like for example for GBM, because fundamentally instruments like SPI and GBM are very similar.
 They both consist of individual detectors that have different responses for a given source position.
@@
   \begin{centering}
-    \begin{subfigure}[b]{1\textwidth}
-      \begin{centering}
-        \includegraphics{figures/spi_lightcurve_ts.pdf}
-        \caption{Light curve for SPI detector 0 and GRB120711A.}
-        \label{fig:ts_spi}
-      \end{centering}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{1\textwidth}
-      \begin{centering}
-        \includegraphics{figures/gbm_lightcurve_ts.pdf}
-        \caption{Light curve for GBM detector n2 and GRB120711A.}
-        \label{fig:ts_gbm}
-      \end{centering}
-    \end{subfigure}
+    \includegraphics[width=1\linewidth]{figures/spi_lightcurve_ts.pdf}
+    \includegraphics[width=1\linewidth]{figures/gbm_lightcurve_ts.pdf}
+    \label{fig:time_selection}
+    \caption{Light curve for GRB120711A.}
   \end{centering}
@@
 
+\begin{figure}
+  \begin{centering}
+    \includegraphics[width=1\linewidth]{figures/pyspi_vs_gbm_band.pdf}
+    \label{fig:corner_gb_pyspi_band}
+    \caption{Corner plot for the SPI fit with PySPI and the GBM fit. In this fit we used a Band function as spectral model.}
+  \end{centering}
+\end{figure}
+
 \subsection{Joint Fit of SPI and GBM}

### 2021-12-02 src/figures/corner_gbm_pyspi_band.py

@@ -1,0 +1,24 @@
+from chainconsumer import ChainConsumer
+import numpy as np
+
+
+def loadtxt2d(intext):
+        try:
+            return np.loadtxt(intext, ndmin=2)
+        except:
+            return np.loadtxt(intext)
+
+c = ChainConsumer()
+c.configure(plot_hists=False, kde=1.0)
+chain = loadtxt2d('./chains/PYSPI_BAND_post_equal_weights.dat')
+
+c.add_chain(chain[:,:4], parameters=['K', r'$\alpha$', r'$E_{peak}$', r'$\beta$'], name='PYSPI')
+
+chain = loadtxt2d('./chains/GBM_BAND_post_equal_weights.dat')
+
+c.add_chain(chain[:,:4], parameters=['K', r'$\alpha$', r'$E_{peak}$', r'$\beta$'], name='GBM')
+
+c.configure(plot_hists=False, kde=1.0, shade_alpha=0.5)
+
+c.plotter.plot(filename="pyspi_vs_gbm_band.pdf",
+               parameters=['K', r'$\alpha$', r'$E_{peak}$', r'$\beta$']);

### 2021-12-02 src/figures/corner_gbm_pyspi_band.py
add color

@@ -1,6 +1,12 @@
 from chainconsumer import ChainConsumer
 import numpy as np
+plt.style.use("matplotlibrc")
 
+color1 = "#544b3dff"
+color2 = "#340068ff"
+color3 = "#4cb944ff"
+color4 = "#4f7cacff"
+color5 = "#6d2e46ff"
 
 def loadtxt2d(intext):
         try:
@@ -12,11 +18,13 @@ c = ChainConsumer()
 c.configure(plot_hists=False, kde=1.0)
 chain = loadtxt2d('./chains/PYSPI_BAND_post_equal_weights.dat')
 
-c.add_chain(chain[:,:4], parameters=['K', r'$\alpha$', r'$E_{peak}$', r'$\beta$'], name='PYSPI')
+c.add_chain(chain[:,:4], parameters=['K', r'$\alpha$', r'$E_{peak}$', r'$\beta$'],
+            name='PYSPI', color=color1)
 
 chain = loadtxt2d('./chains/GBM_BAND_post_equal_weights.dat')
 
-c.add_chain(chain[:,:4], parameters=['K', r'$\alpha$', r'$E_{peak}$', r'$\beta$'], name='GBM')
+c.add_chain(chain[:,:4], parameters=['K', r'$\alpha$', r'$E_{peak}$', r'$\beta$'], name='GBM',
+            color=color2)
 
 c.configure(plot_hists=False, kde=1.0, shade_alpha=0.5)
 

### 2021-12-02 src/fit_scripts/band_fits.py
add folder for chains and fit_scripts

@@ -1,0 +1,191 @@
+from pyspi.utils.data_builder.time_series_builder import TimeSeriesBuilderSPI
+from pyspi.utils.response.spi_response_data import ResponseDataRMF
+from pyspi.utils.response.spi_response import ResponseRMFGenerator
+from pyspi.utils.response.spi_drm import SPIDRM
+from pyspi.utils.livedets import get_live_dets
+from pyspi.SPILike import SPILikeGRB
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+
+#### General Input #####
+
+grb_time = "120711 024453" #(YYMMDD HHMMSS) - from GBM trigger time
+background_time_interval_1_spi = "-500--10"
+background_time_interval_2_spi = "150-1000"
+background_time_interval_1_gbm = "-30--10"
+background_time_interval_2_gbm = "150-200"
+active_time = '65-73'
+ebounds = np.geomspace(25, 8000, 200)
+ebounds_sgl = ebounds[ebounds<400]
+ebounds_psd = ebounds[np.logical_and(ebounds>400, ebounds<2700)]
+ebounds_sgl2 = ebounds[ebounds>2700]
+ein = np.geomspace(20,8000,100)
+
+#### INIT PYSPI plugins #####
+rsp_base = ResponseDataRMF.from_version(4)
+spilikes_sgl = []
+spilikes_sgl2 = []
+spilikes_psd = []
+for d in get_live_dets(time=grb_time, event_types=["single"]):
+    drm_gen_sgl = ResponseRMFGenerator.from_time(grb_time,  d,
+                                            ebounds_sgl, ein,
+                                            rsp_base)
+
+    sd_sgl = SPIDRM(drm_gen_sgl, 94.67830, -70.99905)
+
+    tsb_sgl = TimeSeriesBuilderSPI.from_spi_grb(f"SPIDet{d}",
+                                                d,
+                                                grb_time,
+                                                response=sd_sgl,
+                                                sgl_type="both",
+                                                )
+    #tsb_sgl.set_active_time_interval(active_time)
+    tsb_sgl.set_background_interval(background_time_interval_1_spi,
+                                    background_time_interval_2_spi,
+                                    fit_poly=False
+                                   )
+    tsb_sgl.set_active_time_interval(active_time)
+    sl_sgl = tsb_sgl.to_spectrumlike(extract_measured_background=True)
+    spilikes_sgl.append(SPILikeGRB.from_spectrumlike(sl_sgl,
[…]

### 2021-12-02 src/figures/corner_gbm_pyspi_band.py
add matplotlib

@@ -1,5 +1,6 @@
 from chainconsumer import ChainConsumer
 import numpy as np
+import matplotlib.pyplot as plt
 plt.style.use("matplotlibrc")
 
 color1 = "#544b3dff"

### 2021-12-02 src/figures/corner_gbm_pyspi_band.py
remove ff in hex color

@@ -3,11 +3,11 @@ import numpy as np
 import matplotlib.pyplot as plt
 plt.style.use("matplotlibrc")
 
-color1 = "#544b3dff"
-color2 = "#340068ff"
-color3 = "#4cb944ff"
-color4 = "#4f7cacff"
-color5 = "#6d2e46ff"
+color1 = "#544b3d"
+color2 = "#340068"
+color3 = "#4cb944"
+color4 = "#4f7cac"
+color5 = "#6d2e46"
 
 def loadtxt2d(intext):
         try:

### 2021-12-02 src/figures/electronic.py

@@ -2,11 +2,11 @@ from pyspi.utils.data_builder.time_series_builder import TimeSeriesBuilderSPI
 import numpy as np
 import matplotlib.pyplot as plt
 plt.style.use("matplotlibrc")
-color1 = "#544b3dff"
-color2 = "#340068ff"
-color3 = "#4cb944ff"
-color4 = "#4f7cacff"
-color5 = "#6d2e46ff"
+color1 = "#544b3d"
+color2 = "#340068"
+color3 = "#4cb944"
+color4 = "#4f7cac"
+color5 = "#6d2e46"
 
 ebounds=np.geomspace(20,8000,100)
 grb_time = "120711 024453" #(YYMMDD HHMMSS) - from GBM trigger time

### 2021-12-02 src/figures/lightcurve.py

@@ -3,11 +3,11 @@ import numpy as np
 import matplotlib.pyplot as plt
 plt.style.use("matplotlibrc")
 
-color1 = "#544b3dff"
-color2 = "#340068ff"
-color3 = "#4cb944ff"
-color4 = "#4f7cacff"
-color5 = "#6d2e46ff"
+color1 = "#544b3d"
+color2 = "#340068"
+color3 = "#4cb944"
+color4 = "#4f7cac"
+color5 = "#6d2e46"
 
 grb_time = "120711 024453" #(YYMMDD HHMMSS) - from GBM trigger time
 background_time_interval_1_spi = "-500--10"

### 2021-12-02 src/figures/time_selection.py

@@ -6,11 +6,11 @@ import numpy as np
 import matplotlib.pyplot as plt
 plt.style.use("matplotlibrc")
 
-color1 = "#544b3dff"
-color2 = "#340068ff"
-color3 = "#4cb944ff"
-color4 = "#4f7cacff"
-color5 = "#6d2e46ff"
+color1 = "#544b3d"
+color2 = "#340068"
+color3 = "#4cb944"
+color4 = "#4f7cac"
+color5 = "#6d2e46"
 
 grb_time = "120711 024453" #(YYMMDD HHMMSS) - from GBM trigger time
 background_time_interval_1_spi = "-500--10"

### 2021-12-02 src/figures/corner_gbm_pyspi_band.py
bug fix

@@ -16,7 +16,7 @@ def loadtxt2d(intext):
             return np.loadtxt(intext)
 
 c = ChainConsumer()
-c.configure(plot_hists=False, kde=1.0)
+
 chain = loadtxt2d('./chains/PYSPI_BAND_post_equal_weights.dat')
 
 c.add_chain(chain[:,:4], parameters=['K', r'$\alpha$', r'$E_{peak}$', r'$\beta$'],

### 2021-12-09 src/figures/corner_osa_pyspi_band.py
new plot

@@ -1,0 +1,33 @@
+from chainconsumer import ChainConsumer
+import numpy as np
+import matplotlib.pyplot as plt
+plt.style.use("matplotlibrc")
+
+color1 = "#544b3d"
+color2 = "#340068"
+color3 = "#4cb944"
+color4 = "#4f7cac"
+color5 = "#6d2e46"
+
+def loadtxt2d(intext):
+        try:
+            return np.loadtxt(intext, ndmin=2)
+        except:
+            return np.loadtxt(intext)
+
+c = ChainConsumer()
+
+chain = loadtxt2d('./chains/OSA_BAND_post_equal_weights.dat')
+
+c.add_chain(chain[:,:4], parameters=['K', r'$\alpha$', r'$E_{peak}$', r'$\beta$'],
+            name='Official Tools', color=color2)
+
+chain = loadtxt2d('./chains/PYSPI_BAND_post_equal_weights.dat')
+
+c.add_chain(chain[:,:4], parameters=['K', r'$\alpha$', r'$E_{peak}$', r'$\beta$'], name='PYSPI',
+            color=color1)
+
+c.configure(plot_hists=False, kde=1.0, shade_alpha=0.5)
+
+c.plotter.plot(filename="pyspi_vs_osa_band.pdf",
+               parameters=['K', r'$\alpha$', r'$E_{peak}$', r'$\beta$']);

### 2021-12-09 src/fit_scripts/band_fits.py

@@ -127,14 +127,29 @@ model1 = Model(ps1)
 
 #### INIT OSA plugin #####
 
+from threeML import OGIPLike
+spi = OGIPLike("spi",
+               observation="/home/bjorn/Downloads/spectra_GRB_peak.fits",
+               response="/home/bjorn/Downloads/spectral_response_peak.rmf.fits")
 
 ########################### FITS ##################################
 
 #### OSA ###########
 from threeML import DataList, BayesianAnalysis
+from astromodels import clone_model
+model_osa = clone_model(model1)
+datalist = DataList(spi)
+ba_osa_band_1 = BayesianAnalysis(model_osa, datalist)
+name_fit = 'OSA_BAND'
+ba_osa_band_1.set_sampler("multinest", share_spectrum=True)
+ba_osa_band_1.sampler.setup(800,
+                    chain_name='chains/{}_'.format(name_fit),
+                    resume=False,
+                    verbose=True,
+                    importance_nested_sampling=False)
+ba_osa_band_1.sample()
 
 #### PYSPI ###########
-from astromodels import clone_model
 model_pyspi = clone_model(model1)
 datalist_spi = DataList(*spilikes_sgl, *spilikes_sgl2, *spilikes_psd)#, *spilikes_sgl2)
 ba_spi_new_band = BayesianAnalysis(model_pyspi, datalist_spi)

### 2021-12-10 src/ms.tex
typo
new plot
test
final plot

@@
 \subsection{Synchrotron Model}
-
+\label{synch}
 We use pynchrotron (cite github) to calculate the spectrum from a physical, time dependent spectral synchrotron model.
@@
 These electrons are cooled via synchrotron cooling in a magnetic field and produce radiation in this process.
-The resulting photon spectrum is defined by five quantities:
+The resulting photon spectrum is the sum of the photon spectra at every time step in the cooling process and is defined by five quantities:
 
@@
 
+There exists a strong degeneracy between $B$ and $\gamma_{inj}$, as their combination sets the peak of the photon spectrum.
+Therefore one usually fixes $\gamma_{inj}=10^{5}$ and only fits for $B$.
+It is important to keep in mind, that the results for $\gamma_{max}$ and $\gamma_{cool}$ are determined relative to the fixed $\gamma_{inj}$.
 For more details about the model check (cite Syn paper).
@@
 
-We analyze the SPI data for the same time interval with PySPI and OSA, to check if the results are in agreement.
+We analyze the SPI data with a band function as spectral model for the same time interval with PySPI and OSA, to check if the results are in agreement.
 The two methods are described in \ref{OSA} and \ref{pyspi}.
-This is done for a fit with an empirical model (Band function) and a fit with the physical synchrotron model.
-The resulting posterior distributions, displayed as corner plots, and the PPC plots (see \ref{PPC}) are shown in Fig.
-?
-- Fig.
-?.
-The posterior distributions show, that the results from the two analysis techniques are in agreement, but PySPI can constrain the parameters much better.
+Fig.
+\ref{fig:corner_osa_pyspi_band} shows the resulting posterior distributions of the fits, displayed as a corner plot.
+The results for the spectral shape from the two analysis techniques agree within their uncertainty region, but PySPI can constrain the parameters more precise.
 
-(include figs for band function and syn. fits!)
+\begin{figure}
+  \begin{centering}
+    \includegraphics[width=1\linewidth]{figures/pyspi_vs_osa_band.pdf}
+    \label{fig:corner_osa_pyspi_band}
+    \caption{Corner plot for the SPI fit with PySPI and the official tools.
+The spectral model in this fit is a band function.
+It shows, that the results are in agreement, but PySPI can constrain the parameters better.}
+  \end{centering}
+\end{figure}
 
@@
 
-Next, we analyze the SPI data with PySPI and the GBM data with the GRB analysis within 3ML (cite a paper for this?).
-Again we do this for an empirical model and the physical synchrotron model.
-The fit results are shown in Fig.
-?
-- Fig.
-?.
+Next, we analyze the SPI data with PySPI and the GBM data with the GRB analysis within 3ML (cite a paper for this?) for a band function model.
+Fig.
+\ref{fig:corner_gbm_pyspi_band} displays the corner plots for these fits, showing that the results for the spectral shape form PySPI and GBM are in agreement.
+It also shows that the calibration for SPI and GBM are well aligned within only $\approx$ 10\% difference.
 
@@
     \includegraphics[width=1\linewidth]{figures/pyspi_vs_gbm_band.pdf}
-    \label{fig:corner_gb_pyspi_band}
+    \label{fig:corner_gbm_pyspi_band}
     \caption{Corner plot for the SPI fit with PySPI and the GBM fit. In this fit we used a Band function as spectral model.}
@@
 
-The final analysis is a joint fit with SPI and GBM. This
+The final analysis is a joint fit for the SPI and the GBM data with the physical synchrotron model (see \ref{synch}).
+
+\begin{figure}
+  \begin{centering}
+    \includegraphics[width=1\linewidth]{figures/pyspi_and_gbm_syn.pdf}
+    \label{fig:corner_gbm_pyspi_joined_syn}
+    \caption{Corner plot for the SPI fit with PySPI and the GBM fit. In this fit we used a Band function as spectral model.}
+  \end{centering}
+\end{figure}
 

### 2021-12-10 src/figures/corner_gbm_pyspi_joined_syn.py

@@ -1,0 +1,38 @@
+from chainconsumer import ChainConsumer
+import numpy as np
+import matplotlib.pyplot as plt
+plt.style.use("matplotlibrc")
+
+color1 = "#544b3d"
+color2 = "#340068"
+color3 = "#4cb944"
+color4 = "#4f7cac"
+color5 = "#6d2e46"
+
+def loadtxt2d(intext):
+        try:
+            return np.loadtxt(intext, ndmin=2)
+        except:
+            return np.loadtxt(intext)
+
+c = ChainConsumer()
+
+chain = loadtxt2d('./chains/GBM_SYN_post_equal_weights.dat')
+
+c.add_chain(chain[:,:4], parameters=['K','B', 'p', r'$\gamma_{cool}$'],
+            name='GBM', color=color2)
+
+chain = loadtxt2d('./chains/PYSPI_SYN_post_equal_weights.dat')
+
+c.add_chain(chain[:,:4], parameters=['K','B', 'p', r'$\gamma_{cool}$'], name='PYSPI',
+            color=color1)
+
+chain = loadtxt2d('./chains/BOTH_SYN_post_equal_weights.dat')
+
+c.add_chain(chain[:,:4], parameters=['K','B', 'p', r'$\gamma_{cool}$'], name='Combined',
+            color=color4)
+
+c.configure(plot_hists=False, kde=1.0, shade_alpha=0.5)
+
+c.plotter.plot(filename="pyspi_and_gbm_syn.pdf",
+               parameters=['B', 'p', r'$\gamma_{cool}$']);

### 2021-12-10 src/ms.tex
add qq and ppc plots

@@
 In this work we analyze GRB 120711A, which was a bright, multi pulse GRB with a precursor and a long emission period of $\approx$100 seconds.
-It was detected by SPI and GBM.
-In this work we only look at one time slice with a duration of 10 seconds around the highest peak in the light curves
+It was detected with SPI and GBM.
+We only look at one time slice with a duration of 10 seconds around the highest peak in the light curves (see Fig.
+\ref{fig:time_selection}).
 
@@
 
-First we analyze the data from the two instruments independently with empirical and physical models, to check if the results for SPI and GBM are in agreement as well as show a comparison between the fit results with PySPI and the official software tools for GRB analysis within OSA.
-After that we fit the data of SPI and GBM simultaneously, to show that it can reduce the allowed parameter space significantly.
+We analyze the data from the two instruments independently first with the empirical Band function, to check if the results for SPI and GBM are in agreement as well as show a comparison between the fit results with PySPI and the official software tools for GRB analysis within OSA.
+Then we fit the SPI and GBM data simultaneously with a physical synchrotron model, and show that it can reduce the allowed parameter space significantly, compared to the individual fits.
 
-All the fits in this section are done with 3ML and the Bayesian sampler algorithm MultiNest (cite) to create full posterior distributions of the parameters.
+All the fits in this section are done with 3ML (cite) and the Bayesian sampler algorithm MultiNest (cite) to create full posterior distributions of the parameters.
+To visualize the posterior distribution we use ChainConsumer (cite) with the output from MultiNest to create corner plots.
 
@@
 Fig.
-\ref{fig:corner_gbm_pyspi_band} displays the corner plots for these fits, showing that the results for the spectral shape form PySPI and GBM are in agreement.
-It also shows that the calibration for SPI and GBM are well aligned within only $\approx$ 10\% difference.
+\ref{fig:corner_gbm_pyspi_band} displays the corner plots for these fits, demonstrating that the results for the spectral shape from SPI and GBM are in agreement.
+It also shows that the calibration for SPI and GBM are well aligned within only $\approx$ 10\% difference in this case.
 
@@
     \label{fig:corner_gbm_pyspi_band}
-    \caption{Corner plot for the SPI fit with PySPI and the GBM fit. In this fit we used a Band function as spectral model.}
+    \caption{Corner plot for the SPI fit with PySPI and the GBM fit.
+In this fit we used a Band function as spectral model.
+The spectral shape for the SPI and GBM fits coincide within their uncertainty regions and the normalization is off by $\approx$10\%, which is within the usual calibration offsets of Gamma-Ray space telescopes.}
   \end{centering}
@@
 
-The final analysis is a joint fit for the SPI and the GBM data with the physical synchrotron model (see \ref{synch}).
+The final analysis is a joint fit for the SPI and the GBM data with a physical synchrotron model (see \ref{synch}).
+Fig.
+\ref{fig:corner_gbm_pyspi_joined_syn} shows the corner plots for the individual and the combined fits.
+The posterior distribution of the parameters from the GBM and the SPI fit agree within their uncertainty regions and the combined fit reduces the allowed parameter space.
+The physical synchrotron model was able to fit the data of GBM and SPI well, which is shown with PPC and QQ plots in \ref{appendix}.
 
@@
     \label{fig:corner_gbm_pyspi_joined_syn}
-    \caption{Corner plot for the SPI fit with PySPI and the GBM fit. In this fit we used a Band function as spectral model.}
+    \caption{Corner plot for the SPI fit with PySPI and the GBM fit.
+In this fit we used a physical synchrotron model (see \ref{synch}) as spectral model.
+The results from SPI and GBM agree within their uncertainty region and the combined fit constrains the parameter better than the individual ones.}
   \end{centering}
@@
 
-- Possible to fit physical models to GRB data of SPI and get same parameters as GBM
-- Combined fits reduce available parameter space
-- PySPI can be used to fit all SPI GRBs in the future with different physical models to help distinguishing between them
+We analyzed the data of GRB120711A with the data from INTGRAL/SPI and Fermi/GBM.
+The results for SPI with PySPI are in agreement with those from the official analysis software, but more constraining.
+Also the resulting spectral shape for the fits with GBM and SPI data are in agreement and the relative calibration difference between SPI and GBM we construct from the fits is $\approx$ 10\% or less.
+We show that the GBM as well as the SPI data for GRB120711A can be fitted well with a physical, time dependent synchrotron model and that combining the data in a simultaneous fit improve the parameter constrains.
 
+Generally PySPI can improves the scientific output from SPI for GRBs significantly.
+Due to a new analysis method, that folds the source model directly into the data space of every SPI detector with the full response of the individual detectors, the results are more constraining than the results with the official analysis software.
+
+\begin{appendix}
+  \section{Model Checking Plots}
+  \label{appendix1}
+  In this section we show a selection of the PPC- and QQ-plots for the simultaneous synchrotron fit to the SPI and GBM data for GRB120711A.
+  \begin{figure}
+    \begin{centering}
+      \includegraphics[width=0.45\linewidth]{figures/n0_ppc.pdf}
+      \includegraphics[width=0.45\linewidth]{figures/n0_qq.pdf}
+      \label{fig:n0_model_check}
+      \caption{PPC (left) and QQ (right) plot for the GBM detector n0.}
+    \end{centering}
+  \end{figure}
+  \begin{figure}
+    \begin{centering}
+      \includegraphics[width=0.45\linewidth]{figures/b0_qq.pdf}
+      \includegraphics[width=0.45\linewidth]{figures/b0_qq.pdf}
+      \label{fig:b0_model_check}
+      \caption{PPC (left) and QQ (right) plot for the GBM detector b0.}
+    \end{centering}
+  \end{figure}
+  \begin{figure}
+    \begin{centering}
+      \includegraphics[width=0.45\linewidth]{figures/low_13_ppc.pdf}
+      \includegraphics[width=0.45\linewidth]{figures/low_13_qq.pdf}
+      \label{fig:low_13_model_check}
+      \caption{PPC (left) and QQ (right) plot for the low energy range of SPI detector 13 (all single events).}
+    \end{centering}
+  \end{figure}
+  \begin{figure}
+    \begin{centering}
+      \includegraphics[width=0.45\linewidth]{figures/psd_13_ppc.pdf}
+      \includegraphics[width=0.45\linewidth]{figures/psd_13_qq.pdf}
+      \label{fig:psd_13_model_check}
+      \caption{PPC (left) and QQ (right) plot for the middle energy range of SPI detector 13 (only PSD events).}
+    \end{centering}
+  \end{figure}
+\end{appendix}
 \end{document}

### 2021-12-10 src/figures/b0_model_check.py

@@ -1,0 +1,30 @@
+from twopc import PPC
+import numpy as np
+import matplotlib.pyplot as plt
+plt.style.use("matplotlibrc")
+
+color1 = "#544b3d"
+color2 = "#340068"
+color3 = "#4cb944"
+color4 = "#4f7cac"
+color5 = "#6d2e46"
+
+p = PPC("ppc_output/both_syn_grb.h5")
+
+f = p.detectors["gbmb0"].plot(
+    bkg_subtract=False,
+    levels=[95,68],
+    colors=[color2, color3],
+    lc=color1
+)
+
+f.savefig("b0_ppc.pdf")
+
+f = p.detectors["gbmb0"].plot_qq(
+    channel_energies=[],
+    levels=[95,68],
+    colors=[color2, color3],
+    center_color=color1
+)
+
+f.savefig("b0_qq.pdf")

### 2021-12-10 src/figures/low_13_model_check.py

@@ -1,0 +1,29 @@
+from twopc import PPC
+import numpy as np
+import matplotlib.pyplot as plt
+plt.style.use("matplotlibrc")
+
+color1 = "#544b3d"
+color2 = "#340068"
+color3 = "#4cb944"
+color4 = "#4f7cac"
+color5 = "#6d2e46"
+
+p = PPC("ppc_output/both_syn_grb.h5")
+
+f = p.detectors["SPIDet13"].plot(
+    bkg_subtract=False,
+    levels=[95,68],
+    colors=[color2, color3],
+    lc=color1)
+
+f.savefig("low_13_ppc.pdf")
+
+f = p.detectors["SPIDet13"].plot_qq(
+    channel_energies=[],
+    levels=[95,68],
+    colors=[color2, color3],
+    center_color=color1
+)
+
+f.savefig("low_13_qq.pdf")

### 2021-12-10 src/figures/n0_model_check.py

@@ -1,0 +1,29 @@
+from twopc import PPC
+import numpy as np
+import matplotlib.pyplot as plt
+plt.style.use("matplotlibrc")
+
+color1 = "#544b3d"
+color2 = "#340068"
+color3 = "#4cb944"
+color4 = "#4f7cac"
+color5 = "#6d2e46"
+
+p = PPC("ppc_output/both_syn_grb.h5")
+
+f = p.detectors["gbmn0"].plot(
+    bkg_subtract=False,
+    levels=[95,68],
+    colors=[color2, color3],
+    lc=color1)
+
+f.savefig("n0_ppc.pdf")
+
+f = p.detectors["gbmn0"].plot_qq(
+    channel_energies=[],
+    levels=[95,68],
+    colors=[color2, color3],
+    center_color=color1
+)
+
+f.savefig("n0_qq.pdf")

### 2021-12-10 src/figures/psd_13_model_check.py

@@ -1,0 +1,29 @@
+from twopc import PPC
+import numpy as np
+import matplotlib.pyplot as plt
+plt.style.use("matplotlibrc")
+
+color1 = "#544b3d"
+color2 = "#340068"
+color3 = "#4cb944"
+color4 = "#4f7cac"
+color5 = "#6d2e46"
+
+p = PPC("ppc_output/both_syn_grb.h5")
+
+f = p.detectors["SPIDet13MID"].plot(
+    bkg_subtract=False,
+    levels=[95,68],
+    colors=[color2, color3],
+    lc=color1)
+
+f.savefig("psd_13_ppc.pdf")
+
+f = p.detectors["SPIDet13MID"].plot_qq(
+    channel_energies=[],
+    levels=[95,68],
+    colors=[color2, color3],
+    center_color=color1
+)
+
+f.savefig("psd_13_qq.pdf")

### 2021-12-10 src/figures/corner_gbm_pyspi_band.py
change color in corner plot

@@ -20,7 +20,7 @@ c = ChainConsumer()
 chain = loadtxt2d('./chains/PYSPI_BAND_post_equal_weights.dat')
 
 c.add_chain(chain[:,:4], parameters=['K', r'$\alpha$', r'$E_{peak}$', r'$\beta$'],
-            name='PYSPI', color=color1)
+            name='PYSPI', color=color3)
 
 chain = loadtxt2d('./chains/GBM_BAND_post_equal_weights.dat')
 

### 2021-12-10 src/figures/corner_gbm_pyspi_joined_syn.py

@@ -25,7 +25,7 @@ c.add_chain(chain[:,:4], parameters=['K','B', 'p', r'$\gamma_{cool}$'],
 chain = loadtxt2d('./chains/PYSPI_SYN_post_equal_weights.dat')
 
 c.add_chain(chain[:,:4], parameters=['K','B', 'p', r'$\gamma_{cool}$'], name='PYSPI',
-            color=color1)
+            color=color3)
 
 chain = loadtxt2d('./chains/BOTH_SYN_post_equal_weights.dat')
 

### 2021-12-10 src/figures/corner_osa_pyspi_band.py

@@ -25,7 +25,7 @@ c.add_chain(chain[:,:4], parameters=['K', r'$\alpha$', r'$E_{peak}$', r'$\beta$'
 chain = loadtxt2d('./chains/PYSPI_BAND_post_equal_weights.dat')
 
 c.add_chain(chain[:,:4], parameters=['K', r'$\alpha$', r'$E_{peak}$', r'$\beta$'], name='PYSPI',
-            color=color1)
+            color=color3)
 
 c.configure(plot_hists=False, kde=1.0, shade_alpha=0.5)
 

### 2021-12-11 src/ms.tex
fix qq->ppc
change caption label order

@@
 This fitting can be done in different spectral fitting software like 3ML or XSPEC.
-In this work we always used 3ML.
+In this work we use 3ML.
 
@@
 Measurements like reduced $\chi^{2}$ use many assumptions, like for example that all the probability distributions in the problem are described as normal distributions, which is definitely not the case here, as the measurement process is a Poisson process.
-Therefore we decided to use Posterior Predictive Checks (PPCs, see Eq.
-\ref{eq:ppc}), which use the full posterior of the fit as well as the measurement process to simulate new data and compare them to the observed data.
+Therefore we decided to use Posterior Predictive Checks (PPC) and quantile-quantile (QQ) plots.
+For the PPCs one simulate new data from the full posterior of the fit as well as the measurement process (see Eq.
+\ref{eq:ppc}) and compare them to the observed data.
+QQ plots use the same simualtion process, but instead of comparing the observed data of every energy channel individually to the simulated data, one compares the cumulative counts of the observation and the simulations over energy channels.
+QQ plots are very sensitive to weak systematic deviations of the model from the data.
 
@@
     \includegraphics[width=1\linewidth]{figures/gbm_lightcurve_ts.pdf}
+    \caption{Light curve for GRB120711A.}
     \label{fig:time_selection}
-    \caption{Light curve for GRB120711A.}
   \end{centering}
@@
     \includegraphics[width=1\linewidth]{figures/pyspi_vs_osa_band.pdf}
-    \label{fig:corner_osa_pyspi_band}
     \caption{Corner plot for the SPI fit with PySPI and the official tools.
@@
 It shows, that the results are in agreement, but PySPI can constrain the parameters better.}
+    \label{fig:corner_osa_pyspi_band}
   \end{centering}
@@
     \includegraphics[width=1\linewidth]{figures/pyspi_vs_gbm_band.pdf}
-    \label{fig:corner_gbm_pyspi_band}
     \caption{Corner plot for the SPI fit with PySPI and the GBM fit.
@@
 The spectral shape for the SPI and GBM fits coincide within their uncertainty regions and the normalization is off by $\approx$10\%, which is within the usual calibration offsets of Gamma-Ray space telescopes.}
+    \label{fig:corner_gbm_pyspi_band}
   \end{centering}
@@
     \includegraphics[width=1\linewidth]{figures/pyspi_and_gbm_syn.pdf}
-    \label{fig:corner_gbm_pyspi_joined_syn}
     \caption{Corner plot for the SPI fit with PySPI and the GBM fit.
@@
 The results from SPI and GBM agree within their uncertainty region and the combined fit constrains the parameter better than the individual ones.}
+    \label{fig:corner_gbm_pyspi_joined_syn}
   \end{centering}
@@
 The results for SPI with PySPI are in agreement with those from the official analysis software, but more constraining.
-Also the resulting spectral shape for the fits with GBM and SPI data are in agreement and the relative calibration difference between SPI and GBM we construct from the fits is $\approx$ 10\% or less.
+Also the resulting spectral shape for the fits with GBM and SPI data are in agreement and the relative calibration difference between SPI and GBM we conclude from the fits is $\approx$ 10\% or less.
 We show that the GBM as well as the SPI data for GRB120711A can be fitted well with a physical, time dependent synchrotron model and that combining the data in a simultaneous fit improve the parameter constrains.
@@
       \includegraphics[width=0.45\linewidth]{figures/n0_qq.pdf}
+      \caption{PPC (left) and QQ (right) plot for the GBM detector n0.}
       \label{fig:n0_model_check}
-      \caption{PPC (left) and QQ (right) plot for the GBM detector n0.}
     \end{centering}
@@
     \begin{centering}
+      \includegraphics[width=0.45\linewidth]{figures/b0_ppc.pdf}
       \includegraphics[width=0.45\linewidth]{figures/b0_qq.pdf}
-      \includegraphics[width=0.45\linewidth]{figures/b0_qq.pdf}
+      \caption{PPC (left) and QQ (right) plot for the GBM detector b0.}
       \label{fig:b0_model_check}
-      \caption{PPC (left) and QQ (right) plot for the GBM detector b0.}
     \end{centering}
@@
       \includegraphics[width=0.45\linewidth]{figures/low_13_qq.pdf}
+      \caption{PPC (left) and QQ (right) plot for the low energy range of SPI detector 13 (all single events).}
       \label{fig:low_13_model_check}
-      \caption{PPC (left) and QQ (right) plot for the low energy range of SPI detector 13 (all single events).}
     \end{centering}
@@
       \includegraphics[width=0.45\linewidth]{figures/psd_13_qq.pdf}
+      \caption{PPC (left) and QQ (right) plot for the middle energy range of SPI detector 13 (only PSD events).}
       \label{fig:psd_13_model_check}
-      \caption{PPC (left) and QQ (right) plot for the middle energy range of SPI detector 13 (only PSD events).}
     \end{centering}

### 2021-12-16 src/ms.tex
test citation

@@
   In the last years it has been shown, that it is needed to fit physical models to Gamma-Ray Burst (GRB) data to get more insights into their emission mechanism.
-For the energy range between ~ 10 keV to ~ 10 MeV Fermi/GBM has been the main instrument....
+For the energy range between ~ 10 keV to ~ 10 MeV Fermi/GBM has been the main instrument to analyze GRBs.
 In this paper we show how we can add INTEGRAL/SPI to this analysis.
@@
 Therefore INTEGRAL/SPI is an ideal instrument to precisely measure the curvature of the spectrum.
-In this work we present PySPI, a new analysis software we developed to analyze GRB data from SPI, and apply it to the GRB 120711A.
-We show that PySPI improves the analysis of SPI data, for GRBs, compared to the official analysis software.
-Also we show that the GBM and the SPI data of this GRB can be fitted well with a physical synchrotron model and that combining both, reduces the allowed parameter space.
+We present PySPI, a new analysis software we developed to analyze GRB data from SPI, and apply it to the GRB 120711A.
+We show that PySPI improves the analysis of SPI data, for GRBs, compared to the official analysis software and that the GBM and the SPI data of this GRB can be fitted well with a physical synchrotron model and that combining both, reduces the allowed parameter space.
+This demonstrates that SPI can play an important role in GRB model fitting.
 }
@@
 Gamma-Ray Bursts (GRBs) are short transient bursts of gamma rays, with a typical active time range between a few ms and few hundred seconds for the prompt phase, which is mostly observed in X- and Gamma-Rays.
-After the prompt emission there is a long lasting afterglow phase when the ejecta interacts with the Inter Stellar Medium (ISM).
-Long GRBs ($\approx$> 2s) have been associated to the collapse of massive stars (cite), whereas short GRBs are believed to be caused by mergers of compact objects, like Neutron Stars (cite grb-gw).
+After the prompt emission, there is a long lasting afterglow phase when the ejecta interacts with the Inter Stellar Medium (ISM).
+Long GRBs ($\approx$> 2s) have been associated to the collapse of massive stars, whereas short GRBs are believed to be caused by mergers of compact objects, like Neutron Stars.
 In both cases it is commonly agreed on, that the progenitor events of GRBs produce jetted relativistic outflows, which consists of several shells with different velocities, resulting in internal shell collisions.
 But it is still highly debated what the exact emission mechanism of the Gamma-Rays is.
+\citep{gamma-ray-burst, gw}
 
@@
 (cite) have shown that this conclusion is not correct and that you can fit GRB spectra well with a physical synchrotron model even though the same spectra violate the line-of-death if fitted with a Band function.
-The Gamma-Ray Burst Monitor (GBM) onboard of the Fermi satellite is often used to fit GRB data in the Gamma-Ray energy range.
-GBM is an all-sky instrument, that observes the whole sky, except the part that is occulted by the Earth at that time.
-It consists of 12 NaI and two BGO scintillator detectors that cover in total an energy range between 8 keV and 10 MeV.
+
+The Gamma-Ray Burst Monitor (GBM) onboard of the Fermi satellite is often used to fit GRB data in the 8 keV to 10 MeV energy range.
+GBM consists of 12 NaI and two BGO scintillator detectors and is an all-sky instrument, that observes the whole sky, except the part that is occulted by the Earth at that time.
 (cite)
@@
 GRBs are transient sources with a typical duration only up to a few tens of seconds.
-%Therefore we can use the time before and after the GRB signal, but within the same science window, as a background measurement.
-%The background treatment we use, depends on two assumptions, namely that within one science window the background is stable and the pointing direction of SPI does not change.
-%Due to the high orbit and pointing scheme of INTEGRAL both these assumptions are valid.
-Therefore we can use the time intervals during a science window when the transient source is not active as an independent temporal off-source observation (see Fig.
+Therefore we can use the time intervals during a science window, when the transient source is not active, as an independent temporal off-source observation (see Fig.
 \ref{fig:lightcurve}).
-Similar to other instruments that use spatially off-source observation as an independent background measurement.
+Similar to other instruments, that use spatially off-source observation as an independent background measurement.
 From the background observations we construct the probability of the background model rates per energy channel from a poisson distribution, like given in equation \ref{eq:poisson_bkg}, where $b_{i}$ are the background rates per energy channel, $B_{i}$ are the detected counts in the off-source observation and $t_{b}$ is the exposure of the off-source observation.
@@
 
-Because there is no easy analytical solution for this integral, one often uses a so-called profiled likelihood as an approximation.
+Because there is no easy analytical solution for this integral, one often uses a so-called profiled likelihood as an approximation (cite).
 For the profiled likelihood we use the fact, that the derivative of the likelihood at its maximum is zero.
-Therefore one can construct from $\frac{\textrm{dL}}{\textrm{db}_i}=0$ the background rates $b_{i, max}$ that maximize the likelihood for a given model $m_{i}(\theta)$ and observed counts.
+Therefore one can construct from $\frac{\textrm{dL}}{\textrm{db}_i}=0$ the background rates $b_{i, max}$ that maximize the likelihood for a given model $m_{i}(\theta)$ and observed quantities.
 Solving $\frac{\textrm{dL}}{\textrm{db}_i}=0$ for b gives equation \ref{eq:bmax}.
@@
 These values can then be substituted in the likelihood \ref{eq:likelihood_m_and_b} to eliminate the $b_{i}$ dependency.
-This approximation gives the exact solution for the maximum of the likelihood, for likelihood values close to the maximum the assumption is that most of the likelihood in the integrand in \ref{eq:likelihood_marg} is in a small area around $b_{i,max}$ and we can basically add a $\delta(b_{i}-b_{{i,max}})$.
-This assumption is used in many works (cite) and works very well as long as one does not have too few counts in the background observation (for a derivation see cite Giacomo derivation).
+This approximation gives the exact solution for the maximum of the likelihood, for likelihood values close to the maximum, the assumption is that most of the likelihood in the integrand in \ref{eq:likelihood_marg} is in a small area around $b_{i,max}$.
+This assumption is used in many spectral analyses and works very well as long as one does not have too few counts in the background observation \footnote{For a derivation see https://giacomov.github.io/Bias-in-profile-poisson-likelihood/}.
 
@@
 
-These effective areas were calculated for 51 photon energies and on a 0.5 degree grid.
-For each of the three interaction type there is one RMF, to define the shape of the redistributed spectra, assuming that this shape does not depend on the detector or the incident angles of the photons.
+These effective areas were simulated for 51 photon energies and on a 0.5 degree grid.
+For each of the three interaction type, there is one RMF, to define the shape of the redistributed spectra, assuming that this shape does not depend on the detector or the incident angles of the photons.
 The procedure to construct the response includes several simplification to keep the computational costs and storage space manageable (cite).
@@
 Since shortly after the start of INTEGRAL, it is known that there are spurious events in the SPI data around 1.5 MeV.
-According to (cite Roques) these spurious events are photons with small energy (<100 keV) that get detected at a higher energy due to saturation of the ???
-electronics by previous high energy deposition.
+According to (cite Roques) these spurious events are photons with small energy (<100 keV) that get detected at a higher energy due to saturation of the Analog Front-End Electronics (AFEE) electronics by previous high energy deposition.
 It is also known, that these spurious events do not show up if one looks only at events with a detection also in the Pulse Shape Discriminator (PSD) electronics.
-The reason for this is that the PSD electronics has an low energy threshold of roughly 450 keV (the exact value has been changed a few times during the mission).
+The reason for this is that the PSD electronics has a low energy threshold of roughly 450 keV (the exact value has been changed a few times during the mission).
 Therefore only events that deposit more than this low energy threshold in the Germanium crystal can trigger this electronic, which eliminates the <100 keV events that are detected at the wrong energies by the AFEE electronics.
@@
   \item Calculate log-likelihood for all detectors
-  \item Sum these log-likelihoods to get the total log-likelihood of SPI
+  \item Sum these log-likelihoods to get the total log-likelihood of the SPI data for the given model parameters
 \end{itemize}
-A sampling algorithm like emcee (cite) or MultiNest (cite) is used to iterate this procedure, in order to determine the posterior distributions.\\
+A sampling algorithm like MultiNest (cite) is used to iterate this procedure, in order to determine the posterior distributions.\\
 This workflow is very similar, like for example for GBM, because fundamentally instruments like SPI and GBM are very similar.
@@
 This allows, without any further work, to fit the SPI data together with the data from other instruments, like Fermi/GBM.
-For more information about 3ML see (cite paper and documentation).
+\footnote{For more information about 3ML see threeml.readthedocs.io/}
 
@@
 
-PySPI is an open source software, which is publicly available on GitHub. There is also a documentation, that shows how to use it. (cite JOSS, link to repo, docs).
+PySPI is an open source software, which is publicly available on GitHub (cite JOSS).
+There is also a documentation, that shows how to use it.
+\footnote{For more information about PySPI see pyspi.readthedocs.io/}
 
@@
 We shortly summarize the official analysis tools for GRB analysis, which are part of the INTEGRAL Offline Scientific Analysis (OSA) software.
-(https://ui.adsabs.harvard.edu/abs/2003A%26A...411L..53C/abstract)
+(cite osa)
 
@@
 The pseudo photon flux data points from the 'Photo Peak Fitting' step, which are no real data points anymore, are fitted with a spectral photon flux model which is convolved with a correction response, which is also available through OSA.
-This correction response depends on the source position and energy bins that are used and should account for energy dispersion as well as resolution.
+This correction response depends on the energy bins that are used and should account for energy dispersion as well as resolution.
 In this step the energy channels are fitted simultaneously, as it is impossible to incorporate energy dispersion in a way that fits every energy channel individually.
@@
 We use pynchrotron (cite github) to calculate the spectrum from a physical, time dependent spectral synchrotron model.
-This model was previously used to successfully fit many single pulse GRBs with GBM in cite syn paper.
-This paper also include a detailed description of the model.
+This model was previously used to successfully fit many single pulse GRBs with GBM in cite syn paper, which also includes a detailed description of the model.
 Here we only want to summarize the main points shortly.
 
-The core of the model is the assumption of some generic acceleration mechanism, that constantly produces an electron spectrum with a power law shape $N(\gamma )\propto gamma^{-p}$ between $\gamma_{inj}$ and $\gamma_{max}$.
+The core of the model is the assumption of some generic acceleration mechanism, that constantly produces an electron spectrum with a power law shape $N(\gamma )\propto \gamma^{-p}$ between $\gamma_{inj}$ and $\gamma_{max}$.
 These electrons are cooled via synchrotron cooling in a magnetic field and produce radiation in this process.
@@
 It is important to keep in mind, that the results for $\gamma_{max}$ and $\gamma_{cool}$ are determined relative to the fixed $\gamma_{inj}$.
-For more details about the model check (cite Syn paper).
 
@@
 To check if the fit of a model is a good description of the measured data is a very complicated topic and highly debated in the statistics community.
-Measurements like reduced $\chi^{2}$ use many assumptions, like for example that all the probability distributions in the problem are described as normal distributions, which is definitely not the case here, as the measurement process is a Poisson process.
-Therefore we decided to use Posterior Predictive Checks (PPC) and quantile-quantile (QQ) plots.
+Measurements like reduced $\chi^{2}$ use many assumptions, like for example that all the probability distributions in the problem are described as normal distributions, which is not the case here, as the measurement process is a Poisson process.
+Therefore we decided to use Posterior Predictive Checks (PPC) and Quantile-Quantile (QQ) plots.
 For the PPCs one simulate new data from the full posterior of the fit as well as the measurement process (see Eq.
@@
 QQ plots use the same simualtion process, but instead of comparing the observed data of every energy channel individually to the simulated data, one compares the cumulative counts of the observation and the simulations over energy channels.
-QQ plots are very sensitive to weak systematic deviations of the model from the data.
+(cite) QQ plots are very sensitive to weak systematic deviations of the model from the data.
 
@@
 Then we fit the SPI and GBM data simultaneously with a physical synchrotron model, and show that it can reduce the allowed parameter space significantly, compared to the individual fits.
+For all GBM and PySPI fits we added effective area correction parameters in the fit, allowing the total effective area of the individual detectors to vary a bit with respect to each other, to account for slightly different calibrations.
+To do this, we always fix the response of one of the detectors to the normal response of that detectors and fit one parameter for every other detector, which gets multiplied with the response in the fit.
+We constrain the effective area correction parameters to be between 0.7 and 1.3.
 
-All the fits in this section are done with 3ML (cite) and the Bayesian sampler algorithm MultiNest (cite) to create full posterior distributions of the parameters.
+All the fits in this section are done with 3ML (cite) and the Bayesian sampling algorithm MultiNest (cite) to create full posterior distributions of the parameters.
 To visualize the posterior distribution we use ChainConsumer (cite) with the output from MultiNest to create corner plots.
@@
     \caption{Corner plot for the SPI fit with PySPI and the official tools.
-The spectral model in this fit is a band function.
+The spectral model in this fit is a Band function.
 It shows, that the results are in agreement, but PySPI can constrain the parameters better.}
@@
 The results for SPI with PySPI are in agreement with those from the official analysis software, but more constraining.
-Also the resulting spectral shape for the fits with GBM and SPI data are in agreement and the relative calibration difference between SPI and GBM we conclude from the fits is $\approx$ 10\% or less.
-We show that the GBM as well as the SPI data for GRB120711A can be fitted well with a physical, time dependent synchrotron model and that combining the data in a simultaneous fit improve the parameter constrains.
+Also the resulting spectral shape for the fits with GBM and SPI data are in agreement and the relative calibration difference between SPI and GBM we conclude from the fits, is $\approx$ 10\% or less.
+We show that the GBM as well as the SPI data for GRB120711A can be fitted well with a physical, time dependent synchrotron model and that combining the data in a simultaneous fit improves the parameter constrains.
 
-Generally PySPI can improves the scientific output from SPI for GRBs significantly.
+Generally PySPI can improve the scientific output from SPI for GRBs significantly.
 Due to a new analysis method, that folds the source model directly into the data space of every SPI detector with the full response of the individual detectors, the results are more constraining than the results with the official analysis software.

### 2021-12-16 src/ms.tex
add citations

@@
 \usepackage{subcaption}
+\usepackage{float}
 % Begin!
@@
 An example for this is the so-called line-of-death for synchrotron emission, which states that synchrotron radiation can not be the emission mechanism, if fits with a Band function give a low energy power law slope larger than -2/3.
-(cite) have shown that this conclusion is not correct and that you can fit GRB spectra well with a physical synchrotron model even though the same spectra violate the line-of-death if fitted with a Band function.
+\citep{line-of-death, line-of-death2}
+\citet{synch} have shown that this conclusion is not correct and that you can fit GRB spectra well with a physical synchrotron model even though the same spectra violate the line-of-death if fitted with a Band function.
 
@@
 sr and covers an energy range between 20 keV and 8 MeV.
-Due to the Germanium detectors it has a very good energy resolution of roughly 2.2 keV at 1.3 MeV, which allows the identification of fine features, like atomic decay lines.
-(cite) In the case of GRBs this excellent energy resolution could allow us to determine the curvature of the spectra with an unmet precision.
+Due to the Germanium detectors it has a very good energy resolution of roughly 2.2 keV at 1.3 MeV, which allows the identification of fine features, like atomic decay lines \cite{spi}.
+In the case of GRBs this excellent energy resolution could allow us to determine the curvature of the spectra with an unmet precision.
 This is the main motivation to use SPI in our analysis.
 
-Several works have used SPI data to fit GRB models (cite), but all of them fitted empirical models like the Band function.
+Several works have used SPI data to fit GRB models \cite{spi_grb1, spi_grb}, but all of them fitted empirical models like the Band function.
 To allow us to fit physical models and to improve the analysis methods we developed PySPI, which will be explained in detail in \ref{pyspi}.
@@
 
-Because there is no easy analytical solution for this integral, one often uses a so-called profiled likelihood as an approximation (cite).
+Because there is no easy analytical solution for this integral, one often uses a so-called profiled likelihood as an approximation.
 For the profiled likelihood we use the fact, that the derivative of the likelihood at its maximum is zero.
@@
 % distribution of how much energy a photon with a certain energy deposit in the crystal and what energy is in the end measured for this deposited energy.
-In PySPI we use the official response files for Image Response Functions (IRFs) and Redistribution Matrix Files (RMFs) derived by Sturner 2003 (cite).
+In PySPI we use the official response files for Image Response Functions (IRFs) and Redistribution Matrix Files (RMFs) derived by \citet{spi_response}.
 The IRF files give the total effective area for three different interaction types:
@@
 For each of the three interaction type, there is one RMF, to define the shape of the redistributed spectra, assuming that this shape does not depend on the detector or the incident angles of the photons.
-The procedure to construct the response includes several simplification to keep the computational costs and storage space manageable (cite).
+The procedure to construct the response includes several simplification to keep the computational costs and storage space manageable \citep{spi_response}.
 This could of course affect every analysis done with SPI.
@@
 Since shortly after the start of INTEGRAL, it is known that there are spurious events in the SPI data around 1.5 MeV.
-According to (cite Roques) these spurious events are photons with small energy (<100 keV) that get detected at a higher energy due to saturation of the Analog Front-End Electronics (AFEE) electronics by previous high energy deposition.
+According to \citet{spi_electronic_noise} these spurious events are photons with small energy (<100 keV) that get detected at a higher energy due to saturation of the Analog Front-End Electronics (AFEE) electronics by previous high energy deposition.
 It is also known, that these spurious events do not show up if one looks only at events with a detection also in the Pulse Shape Discriminator (PSD) electronics.
@@
 In PySPI one can select the energy range in which only the PSD events should be used, to avoid including spurious events.
-To account for the larger dead time of the PSD electronics, an effective area correction can be either fix to 85 \% (cite) or treated as a free parameter in the fit.
+To account for the larger dead time of the PSD electronics, an effective area correction can be either fix to 85 \% \citep{spi_electronic_noise} or treated as a free parameter in the fit.
 
@@
 \end{itemize}
-A sampling algorithm like MultiNest (cite) is used to iterate this procedure, in order to determine the posterior distributions.\\
+A sampling algorithm like MultiNest \citep{multinest} is used to iterate this procedure, in order to determine the posterior distributions.\\
 This workflow is very similar, like for example for GBM, because fundamentally instruments like SPI and GBM are very similar.
@@
 
-PySPI can construct a plugin for the Multi-Mission Maximum Likelihood framework (3ML).
+PySPI can construct a plugin for the Multi-Mission Maximum Likelihood framework (3ML) \citep{3ML}.
 This allows, without any further work, to fit the SPI data together with the data from other instruments, like Fermi/GBM.
@@
 We shortly summarize the official analysis tools for GRB analysis, which are part of the INTEGRAL Offline Scientific Analysis (OSA) software.
-(cite osa)
+\citep{osa}
 
@@
 In this step the energy channels are fitted simultaneously, as it is impossible to incorporate energy dispersion in a way that fits every energy channel individually.
-This fitting can be done in different spectral fitting software like 3ML or XSPEC.
+This fitting can be done in different spectral fitting software.
 In this work we use 3ML.
@@
 \label{synch}
-We use pynchrotron (cite github) to calculate the spectrum from a physical, time dependent spectral synchrotron model.
-This model was previously used to successfully fit many single pulse GRBs with GBM in cite syn paper, which also includes a detailed description of the model.
+We use pynchrotron to calculate the spectrum from a physical, time dependent spectral synchrotron model.
+This model was previously used to successfully fit many single pulse GRBs with GBM in \citet{synch}, which also includes a detailed description of the model.
 Here we only want to summarize the main points shortly.
@@
 QQ plots use the same simualtion process, but instead of comparing the observed data of every energy channel individually to the simulated data, one compares the cumulative counts of the observation and the simulations over energy channels.
-(cite) QQ plots are very sensitive to weak systematic deviations of the model from the data.
+QQ plots are very sensitive to weak systematic deviations of the model from the data.
+\citep{QQ,ppc}
 
@@
 These simulated data are then compared to the observed data and allow for a visual check, whether the posterior distributions of the fit together with the measuring process can reproduce the data.
-(cite paper for this)
 \section{Analysis}
@@
 
-All the fits in this section are done with 3ML (cite) and the Bayesian sampling algorithm MultiNest (cite) to create full posterior distributions of the parameters.
-To visualize the posterior distribution we use ChainConsumer (cite) with the output from MultiNest to create corner plots.
+All the fits in this section are done with 3ML \citep{3ML} and the Bayesian sampling algorithm MultiNest \citep{multinest} to create full posterior distributions of the parameters.
+To visualize the posterior distribution we use ChainConsumer \citep{chainconsumer} with the output from MultiNest to create corner plots.
 
@@
   In this section we show a selection of the PPC- and QQ-plots for the simultaneous synchrotron fit to the SPI and GBM data for GRB120711A.
-  \begin{figure}
+  \begin{figure}[H]
     \begin{centering}
@@
   \end{figure}
-  \begin{figure}
+  \begin{figure}[H]
     \begin{centering}
@@
 \end{appendix}
+
+\bibliographystyle{aa}
+\bibliography{bib}
+
 \end{document}

### 2021-12-16 src/ms.tex
rename
add verbose
fix citation

@@
 Another instrument that operates in a similar energy range is the SPectrometer on INTEGRAL (SPI), which is one of the instruments onboard of the INTErnational Gamma-Ray Astrophysics Laboratory (INTEGRAL) satellite, that was launched in 2002 and is still operating today.
-SPI is a coded mask instrument, which has a FOV of roughly ?
-sr and covers an energy range between 20 keV and 8 MeV.
-Due to the Germanium detectors it has a very good energy resolution of roughly 2.2 keV at 1.3 MeV, which allows the identification of fine features, like atomic decay lines \cite{spi}.
+SPI is a coded mask instrument, which has a fully coded FOV of 16 degrees and covers an energy range between 20 keV and 8 MeV.
+Due to the Germanium detectors it has a very good energy resolution of roughly 2.2 keV at 1.3 MeV, which allows the identification of fine features, like atomic decay lines \citep{spi}.
 In the case of GRBs this excellent energy resolution could allow us to determine the curvature of the spectra with an unmet precision.
@@
 
-Several works have used SPI data to fit GRB models \cite{spi_grb1, spi_grb}, but all of them fitted empirical models like the Band function.
+Several works have used SPI data to fit GRB models \citep{spi_grb1, spi_grb2}, but all of them fitted empirical models like the Band function.
 To allow us to fit physical models and to improve the analysis methods we developed PySPI, which will be explained in detail in \ref{pyspi}.
@@
 \bibliographystyle{aa}
-\bibliography{bib}
+\bibliography{biblio}
 

### 2021-12-17 src/ms.tex
add natbib
other bib style
no bib
test
remove cite

@@
 \usepackage{float}
+%\usepackage{natbib}
 % Begin!
@@
 But it is still highly debated what the exact emission mechanism of the Gamma-Rays is.
-\citep{gamma-ray-burst, gw}
 
@@
 An example for this is the so-called line-of-death for synchrotron emission, which states that synchrotron radiation can not be the emission mechanism, if fits with a Band function give a low energy power law slope larger than -2/3.
-\citep{line-of-death, line-of-death2}
-\citet{synch} have shown that this conclusion is not correct and that you can fit GRB spectra well with a physical synchrotron model even though the same spectra violate the line-of-death if fitted with a Band function.
+have shown that this conclusion is not correct and that you can fit GRB spectra well with a physical synchrotron model even though the same spectra violate the line-of-death if fitted with a Band function.
 
@@
 SPI is a coded mask instrument, which has a fully coded FOV of 16 degrees and covers an energy range between 20 keV and 8 MeV.
-Due to the Germanium detectors it has a very good energy resolution of roughly 2.2 keV at 1.3 MeV, which allows the identification of fine features, like atomic decay lines \citep{spi}.
+Due to the Germanium detectors it has a very good energy resolution of roughly 2.2 keV at 1.3 MeV, which allows the identification of fine features, like atomic decay lines.
 In the case of GRBs this excellent energy resolution could allow us to determine the curvature of the spectra with an unmet precision.
@@
 
-Several works have used SPI data to fit GRB models \citep{spi_grb1, spi_grb2}, but all of them fitted empirical models like the Band function.
+Several works have used SPI data to fit GRB models, but all of them fitted empirical models like the Band function.
 To allow us to fit physical models and to improve the analysis methods we developed PySPI, which will be explained in detail in \ref{pyspi}.
@@
 % distribution of how much energy a photon with a certain energy deposit in the crystal and what energy is in the end measured for this deposited energy.
-In PySPI we use the official response files for Image Response Functions (IRFs) and Redistribution Matrix Files (RMFs) derived by \citet{spi_response}.
+In PySPI we use the official response files for Image Response Functions (IRFs) and Redistribution Matrix Files (RMFs) derived by.
 The IRF files give the total effective area for three different interaction types:
@@
 For each of the three interaction type, there is one RMF, to define the shape of the redistributed spectra, assuming that this shape does not depend on the detector or the incident angles of the photons.
-The procedure to construct the response includes several simplification to keep the computational costs and storage space manageable \citep{spi_response}.
+The procedure to construct the response includes several simplification to keep the computational costs and storage space manageable.
 This could of course affect every analysis done with SPI.
@@
 Since shortly after the start of INTEGRAL, it is known that there are spurious events in the SPI data around 1.5 MeV.
-According to \citet{spi_electronic_noise} these spurious events are photons with small energy (<100 keV) that get detected at a higher energy due to saturation of the Analog Front-End Electronics (AFEE) electronics by previous high energy deposition.
+According to these spurious events are photons with small energy (<100 keV) that get detected at a higher energy due to saturation of the Analog Front-End Electronics (AFEE) electronics by previous high energy deposition.
 It is also known, that these spurious events do not show up if one looks only at events with a detection also in the Pulse Shape Discriminator (PSD) electronics.
@@
 In PySPI one can select the energy range in which only the PSD events should be used, to avoid including spurious events.
-To account for the larger dead time of the PSD electronics, an effective area correction can be either fix to 85 \% \citep{spi_electronic_noise} or treated as a free parameter in the fit.
+To account for the larger dead time of the PSD electronics, an effective area correction can be either fix to 85 \%  or treated as a free parameter in the fit.
 
@@
 \end{itemize}
-A sampling algorithm like MultiNest \citep{multinest} is used to iterate this procedure, in order to determine the posterior distributions.\\
+A sampling algorithm like MultiNest is used to iterate this procedure, in order to determine the posterior distributions.\\
 This workflow is very similar, like for example for GBM, because fundamentally instruments like SPI and GBM are very similar.
@@
 
-PySPI can construct a plugin for the Multi-Mission Maximum Likelihood framework (3ML) \citep{3ML}.
+PySPI can construct a plugin for the Multi-Mission Maximum Likelihood framework (3ML).
 This allows, without any further work, to fit the SPI data together with the data from other instruments, like Fermi/GBM.
@@
 We shortly summarize the official analysis tools for GRB analysis, which are part of the INTEGRAL Offline Scientific Analysis (OSA) software.
-\citep{osa}
 
@@
 We use pynchrotron to calculate the spectrum from a physical, time dependent spectral synchrotron model.
-This model was previously used to successfully fit many single pulse GRBs with GBM in \citet{synch}, which also includes a detailed description of the model.
+This model was previously used to successfully fit many single pulse GRBs with GBM in, which also includes a detailed description of the model.
 Here we only want to summarize the main points shortly.
@@
 QQ plots are very sensitive to weak systematic deviations of the model from the data.
-\citep{QQ,ppc}
-
 \begin{equation}
@@
 
-All the fits in this section are done with 3ML \citep{3ML} and the Bayesian sampling algorithm MultiNest \citep{multinest} to create full posterior distributions of the parameters.
-To visualize the posterior distribution we use ChainConsumer \citep{chainconsumer} with the output from MultiNest to create corner plots.
+All the fits in this section are done with 3ML \3ML and the Bayesian sampling algorithm MultiNest \multinest to create full posterior distributions of the parameters.
+To visualize the posterior distribution we use ChainConsumer \chainconsumer with the output from MultiNest to create corner plots.
 
@@
 
-\bibliographystyle{aa}
+\bibliographystyle{aasjournal}
 \bibliography{biblio}

### 2021-12-17 src/ms.tex
asd

@@
 
-All the fits in this section are done with 3ML \3ML and the Bayesian sampling algorithm MultiNest \multinest to create full posterior distributions of the parameters.
-To visualize the posterior distribution we use ChainConsumer \chainconsumer with the output from MultiNest to create corner plots.
+All the fits in this section are done with 3ML and the Bayesian sampling algorithm MultiNest to create full posterior distributions of the parameters.
+To visualize the posterior distribution we use ChainConsumer with the output from MultiNest to create corner plots.
 

### 2021-12-17 src/ms.tex
asdasdsad
remove all

@@
 
-Gamma-Ray Bursts (GRBs) are short transient bursts of gamma rays, with a typical active time range between a few ms and few hundred seconds for the prompt phase, which is mostly observed in X- and Gamma-Rays.
-After the prompt emission, there is a long lasting afterglow phase when the ejecta interacts with the Inter Stellar Medium (ISM).
-Long GRBs ($\approx$> 2s) have been associated to the collapse of massive stars, whereas short GRBs are believed to be caused by mergers of compact objects, like Neutron Stars.
-In both cases it is commonly agreed on, that the progenitor events of GRBs produce jetted relativistic outflows, which consists of several shells with different velocities, resulting in internal shell collisions.
-But it is still highly debated what the exact emission mechanism of the Gamma-Rays is.
-
-In the past, GRB data was often fitted with empirical function like the Band function (cite band).
-But in recent years it has been shown, that this approach can be misleading and that one should rather fit physical models directly to the data.
-An example for this is the so-called line-of-death for synchrotron emission, which states that synchrotron radiation can not be the emission mechanism, if fits with a Band function give a low energy power law slope larger than -2/3.
-have shown that this conclusion is not correct and that you can fit GRB spectra well with a physical synchrotron model even though the same spectra violate the line-of-death if fitted with a Band function.
-
-The Gamma-Ray Burst Monitor (GBM) onboard of the Fermi satellite is often used to fit GRB data in the 8 keV to 10 MeV energy range.
-GBM consists of 12 NaI and two BGO scintillator detectors and is an all-sky instrument, that observes the whole sky, except the part that is occulted by the Earth at that time.
-(cite)
-%The problem with fitting empirical models to the data and using the individual parameters of these fits to construct constrains on the physics is that the
-Another instrument that operates in a similar energy range is the SPectrometer on INTEGRAL (SPI), which is one of the instruments onboard of the INTErnational Gamma-Ray Astrophysics Laboratory (INTEGRAL) satellite, that was launched in 2002 and is still operating today.
-SPI is a coded mask instrument, which has a fully coded FOV of 16 degrees and covers an energy range between 20 keV and 8 MeV.
-Due to the Germanium detectors it has a very good energy resolution of roughly 2.2 keV at 1.3 MeV, which allows the identification of fine features, like atomic decay lines.
-In the case of GRBs this excellent energy resolution could allow us to determine the curvature of the spectra with an unmet precision.
-This is the main motivation to use SPI in our analysis.
-
-Several works have used SPI data to fit GRB models, but all of them fitted empirical models like the Band function.
-To allow us to fit physical models and to improve the analysis methods we developed PySPI, which will be explained in detail in \ref{pyspi}.
-
-%The other instrument that we use in this work is the Gamma-Ray Burst Monitor (GBM) onboard of the Fermi satellite.
-GBM is an all-sky instrument, that observes the whole sky, except the part that is occulted by the Earth at that time.
-It consists of 12 NaI and two BGO scintillator detectors that cover in total an energy range between 8 keV and 10 MeV.
-(cite)
-
-\section{Methods}
-\subsection{PySPI}
-\label{pyspi}
-To fit the SPI data of GRBs, we developed a new python package PySPI (ref to JOSS?), which is an open source analysis tool. In the following we will summarize the main points of PySPI.
-
-\subsubsection*{Background}
-
-GRBs are transient sources with a typical duration only up to a few tens of seconds.
-Therefore we can use the time intervals during a science window, when the transient source is not active, as an independent temporal off-source observation (see Fig.
-\ref{fig:lightcurve}).
-Similar to other instruments, that use spatially off-source observation as an independent background measurement.
-From the background observations we construct the probability of the background model rates per energy channel from a poisson distribution, like given in equation \ref{eq:poisson_bkg}, where $b_{i}$ are the background rates per energy channel, $B_{i}$ are the detected counts in the off-source observation and $t_{b}$ is the exposure of the off-source observation.
-\begin{equation}
-	L(b_{i}|B_{i}, t_{b})=\frac{(t_{b} b_{i})^{B_{i}}}{B_{i}!}\cdot e^{-t_{b} b_{i}}
-  \label{eq:poisson_bkg}
-\end{equation}
-This expression will be used in the next paragraph to derive the total likelihood.
-
-\begin{figure}
-    \begin{centering}
-        \includegraphics{figures/lightcurve.pdf}
-        \caption{Lightcurve for SPI detector 0 for GRB120711A. The transient source is clearly visible as well as the constant background for the time when the transient is not active.}
-        \label{fig:lightcurve}
-    \end{centering}
-\end{figure}
-
-% add a lightcurve plot?
-
-\subsubsection*{Likelihood}
-
-With the defined background treatment, we can construct a Poisson likelihood with a Poisson measurement of background, like given in \ref{eq:likelihood_m_and_b}.
-Here $\theta$ summarizes all the parameters of the model, $D_{i}$ are the measured counts in the selected active time interval of the transient source, $m_{i}(\theta)$ are the predicted counts from the model evaluated at the parameters $\theta$ and $t_{d}$ is the exposure of the selected active time interval.
-
-\begin{equation}
-	L(\theta, b_{i}|D_{i}, B_{i},t_{d},t_{b}) = \frac{(t_{d}(m_{i}(\theta)+ b_{i}))^{D_{i}}}{D_{i}!}\cdot e^{-t_{d}(m_{i}(\theta)+b_{i})} \frac{(t_{b} b_{i})^{B_{i}}}{B_{i}!}\cdot e^{-t_{b} b_{i}}
-  \label{eq:likelihood_m_and_b}
-\end{equation}
-
-Now we can marginalize over the parameters $b_{i}$, that we are not interested in, which leaves us with equation \ref{eq:likelihood_marg}.
-
-\begin{equation}
-	L(\theta|D_{i}, B_{i},t_{d},t_{b}) = \int_{0}^{\infty}\textrm{db}_{i}\frac{(t_{d}(m_{i}(\theta)+ b_{i}))^{D_{i}}}{D_{i}!}\cdot e^{-t_{d}(m_{i}(\theta)+b_{i})} \frac{(t_{b} b_{i})^{B_{i}}}{B_{i}!}\cdot e^{-t_{b}b_{i}}
-  \label{eq:likelihood_marg}
-\end{equation}
-
-Because there is no easy analytical solution for this integral, one often uses a so-called profiled likelihood as an approximation.
-For the profiled likelihood we use the fact, that the derivative of the likelihood at its maximum is zero.
-Therefore one can construct from $\frac{\textrm{dL}}{\textrm{db}_i}=0$ the background rates $b_{i, max}$ that maximize the likelihood for a given model $m_{i}(\theta)$ and observed quantities.
-Solving $\frac{\textrm{dL}}{\textrm{db}_i}=0$ for b gives equation \ref{eq:bmax}.
-\begin{equation}
-	b_{i,max}(\theta)=\frac{1}{2(t_{b}+t_{d})}(B_{i}+D_{i}-m_{i}(\theta)(t_{b}+t_{d})+\sqrt{(B_{i}+D_{i}+m_{i}(\theta)(t_{b}+t_{d}))^{2}-4m_{i}(\theta)D_{i}(t_{d}-t_{b})}
-  \label{eq:bmax}
-\end{equation}
-
-These values can then be substituted in the likelihood \ref{eq:likelihood_m_and_b} to eliminate the $b_{i}$ dependency.
-This approximation gives the exact solution for the maximum of the likelihood, for likelihood values close to the maximum, the assumption is that most of the likelihood in the integrand in \ref{eq:likelihood_marg} is in a small area around $b_{i,max}$.
-This assumption is used in many spectral analyses and works very well as long as one does not have too few counts in the background observation \footnote{For a derivation see https://giacomov.github.io/Bias-in-profile-poisson-likelihood/}.
-
-\subsubsection*{Response}
-
-To convert a physical spectrum to a detected count spectrum, we need the response for a given source position.
-The response encapsulates all the information about the probability of a photon with a certain energy and origin to be detected in a certain energy channel of the detector.
-This includes for example information about partial energy deposition of the photon in the crystal and the process that transforms the deposited energy into an electronic signal, that is measured in the end.
-% distribution of how much energy a photon with a certain energy deposit in the crystal and what energy is in the end measured for this deposited energy.
-In PySPI we use the official response files for Image Response Functions (IRFs) and Redistribution Matrix Files (RMFs) derived by.
-The IRF files give the total effective area for three different interaction types:
-\begin{itemize}
-  \item Photo peak events
-  \item Non photo peak events that first interact in the crystal
-  \item Non photo peak events that first interact in passive material
-\end{itemize}
-
-These effective areas were simulated for 51 photon energies and on a 0.5 degree grid.
-For each of the three interaction type, there is one RMF, to define the shape of the redistributed spectra, assuming that this shape does not depend on the detector or the incident angles of the photons.
-The procedure to construct the response includes several simplification to keep the computational costs and storage space manageable.
-This could of course affect every analysis done with SPI.
-Re-simulating the response without these simplifications could improve the scientific output of SPI, but would take a hugh amount of computational time, even today.
-
-In PySPI we then interpolate the official response files to the user defined energy bins and source positions.
-
-\subsubsection*{Electronic Noise}
-
-Since shortly after the start of INTEGRAL, it is known that there are spurious events in the SPI data around 1.5 MeV.
-According to these spurious events are photons with small energy (<100 keV) that get detected at a higher energy due to saturation of the Analog Front-End Electronics (AFEE) electronics by previous high energy deposition.
-It is also known, that these spurious events do not show up if one looks only at events with a detection also in the Pulse Shape Discriminator (PSD) electronics.
-The reason for this is that the PSD electronics has a low energy threshold of roughly 450 keV (the exact value has been changed a few times during the mission).
-Therefore only events that deposit more than this low energy threshold in the Germanium crystal can trigger this electronic, which eliminates the <100 keV events that are detected at the wrong energies by the AFEE electronics.
-In Fig.
-\ref{fig:electronic} one can see that the feature at 1.5 MeV is nicely visible in the non-PSD events but is missing in the PSD events.
-Even though this problem is the most significant in the area around 1.5 MeV it is also important at lower energies >400 keV.
-In PySPI one can select the energy range in which only the PSD events should be used, to avoid including spurious events.
-To account for the larger dead time of the PSD electronics, an effective area correction can be either fix to 85 \%  or treated as a free parameter in the fit.
-
-\begin{figure}
-    \begin{centering}
-        \includegraphics{figures/electronic_noise.pdf}
-        \caption{Count spectrum for detector 0 integrated over 1000 seconds. One can clearly see the feature in the Non-PSD events at 1.5 MeV that is not visible in the PSD events.}
-        \label{fig:electronic}
-    \end{centering}
-\end{figure}
-
-\subsubsection*{General Procedure}
-
-In PySPI every Germanium detector is treated as an independent detector. The workflow during a fit step is the following:
-\begin{itemize}
-  \item Sample model parameters
-  \item Calculate model flux and responses individually for all detectors for the source position
-  \item Fold model with responses to get predicted model counts in all detectors
-  \item Calculate log-likelihood for all detectors
-  \item Sum these log-likelihoods to get the total log-likelihood of the SPI data for the given model parameters
-\end{itemize}
-A sampling algorithm like MultiNest is used to iterate this procedure, in order to determine the posterior distributions.\\
-This workflow is very similar, like for example for GBM, because fundamentally instruments like SPI and GBM are very similar.
-They both consist of individual detectors that have different responses for a given source position.
-In GBM this is due to the different pointing directions of the detectors and in SPI due to the different occultation by the mask.
-Therefore there is no reason to treat SPI specially, just because it is a coded mask instrument.
-The information the mask encodes into the data is automatically included by using the different responses for the detectors.
-
-\subsubsection*{3ML plugin}
-
-PySPI can construct a plugin for the Multi-Mission Maximum Likelihood framework (3ML).
-This allows, without any further work, to fit the SPI data together with the data from other instruments, like Fermi/GBM.
-\footnote{For more information about 3ML see threeml.readthedocs.io/}
-
-\subsubsection*{Open Source Software}
-
-PySPI is an open source software, which is publicly available on GitHub (cite JOSS).
-There is also a documentation, that shows how to use it.
-\footnote{For more information about PySPI see pyspi.readthedocs.io/}
-
-\subsection{OSA}
-\label{OSA}
-
-As we are introducing a new analysis software in this work, we want to compare it to the existing analysis software, to check if the results are in agreement.
-We shortly summarize the official analysis tools for GRB analysis, which are part of the INTEGRAL Offline Scientific Analysis (OSA) software.
-
-Analyzing GRB data from SPI with the OSA tools is a multistep process.
-The first steps are basic and cover selecting the science window with the GRB, the time intervals for active time and background time as well as the energy bins for the analysis.
-After that one can either find the location of the GRB with SPIROS, i.e.
-an iterative source removal algorithm for SPI data, or set it manually, if it is already known.
-The next steps concern the spectral fitting, which is done in an other two-step procedure, which will be called 'Photo Peak Fitting' and 'Energy Redistribution Fitting' hereafter.
-
-\subsubsection*{Photo Peak Fitting}
-
-The first step in the spectral fitting with OSA is to use only the photo peak response of the detectors.
-These responses depend on the source position, as this defines for example the absorption by the mask.
-With these responses and the measured data in the individual SPI detectors, taking into account the different background rates, a photon flux is fitted individually per energy channel.
-These pseudo photon fluxes are not the final result, as up to this point energy dispersion and detector energy resolution was ignored.
-
-\subsubsection*{Energy Redistribution Fitting}
-
-The pseudo photon flux data points from the 'Photo Peak Fitting' step, which are no real data points anymore, are fitted with a spectral photon flux model which is convolved with a correction response, which is also available through OSA.
-This correction response depends on the energy bins that are used and should account for energy dispersion as well as resolution.
-In this step the energy channels are fitted simultaneously, as it is impossible to incorporate energy dispersion in a way that fits every energy channel individually.
-This fitting can be done in different spectral fitting software.
-In this work we use 3ML.
-
-\subsection{Synchrotron Model}
-\label{synch}
-We use pynchrotron to calculate the spectrum from a physical, time dependent spectral synchrotron model.
-This model was previously used to successfully fit many single pulse GRBs with GBM in, which also includes a detailed description of the model.
-Here we only want to summarize the main points shortly.
-
-The core of the model is the assumption of some generic acceleration mechanism, that constantly produces an electron spectrum with a power law shape $N(\gamma )\propto \gamma^{-p}$ between $\gamma_{inj}$ and $\gamma_{max}$.
-These electrons are cooled via synchrotron cooling in a magnetic field and produce radiation in this process.
-The resulting photon spectrum is the sum of the photon spectra at every time step in the cooling process and is defined by five quantities:
-
-\begin{enumerate}
-	\item Magnetic field strength $B$
-  \item Lower boundary of the injected electron spectrum $\gamma_{inj}$
-  \item Upper boundary of the injected electron spectrum $\gamma_{max}$
-  \item Slope of the injected electron spectrum $p$
-  \item Characteristic Lorentz factor the electrons cool to $\gamma_{cool}$
-\end{enumerate}
-
-There exists a strong degeneracy between $B$ and $\gamma_{inj}$, as their combination sets the peak of the photon spectrum.
-Therefore one usually fixes $\gamma_{inj}=10^{5}$ and only fits for $B$.
-It is important to keep in mind, that the results for $\gamma_{max}$ and $\gamma_{cool}$ are determined relative to the fixed $\gamma_{inj}$.
-
-\subsection{Model Checking}
-\label{PPC}
-To check if the fit of a model is a good description of the measured data is a very complicated topic and highly debated in the statistics community.
-Measurements like reduced $\chi^{2}$ use many assumptions, like for example that all the probability distributions in the problem are described as normal distributions, which is not the case here, as the measurement process is a Poisson process.
-Therefore we decided to use Posterior Predictive Checks (PPC) and Quantile-Quantile (QQ) plots.
-For the PPCs one simulate new data from the full posterior of the fit as well as the measurement process (see Eq.
-\ref{eq:ppc}) and compare them to the observed data.
-QQ plots use the same simualtion process, but instead of comparing the observed data of every energy channel individually to the simulated data, one compares the cumulative counts of the observation and the simulations over energy channels.
-QQ plots are very sensitive to weak systematic deviations of the model from the data.
-\begin{equation}
-  \textrm{P}(y^{\textrm{sim}}|y^{\textrm{obs}}) = \int \textrm{P}(y^{\textrm{sim}}|\theta) \textrm{P}(\theta|y^{\textrm{obs}}) \mathrm{d}\theta
-  \label{eq:ppc}
-\end{equation}
-\noindent
-Here $y^{\textrm{obs}}$ are the observed data, $\textrm{P}(\theta|y^{\textrm{obs}})$ is the posterior distribution of the model parameters $\theta$ given the observed data, $\textrm{P}(y^{\textrm{sim}}|\theta)$ is the probability of new data given the parameters of the model and $y^{\textrm{sim}}$ are the simulated data.
-These simulated data are then compared to the observed data and allow for a visual check, whether the posterior distributions of the fit together with the measuring process can reproduce the data.
-\section{Analysis}
-
-In this work we analyze GRB 120711A, which was a bright, multi pulse GRB with a precursor and a long emission period of $\approx$100 seconds.
-It was detected with SPI and GBM.
-We only look at one time slice with a duration of 10 seconds around the highest peak in the light curves (see Fig.
-\ref{fig:time_selection}).
-
-\begin{figure}
-  \begin{centering}
-    \includegraphics[width=1\linewidth]{figures/spi_lightcurve_ts.pdf}
-    \includegraphics[width=1\linewidth]{figures/gbm_lightcurve_ts.pdf}
-    \caption{Light curve for GRB120711A.}
-    \label{fig:time_selection}
-  \end{centering}
-\end{figure}
-
-We analyze the data from the two instruments independently first with the empirical Band function, to check if the results for SPI and GBM are in agreement as well as show a comparison between the fit results with PySPI and the official software tools for GRB analysis within OSA.
-Then we fit the SPI and GBM data simultaneously with a physical synchrotron model, and show that it can reduce the allowed parameter space significantly, compared to the individual fits.
-For all GBM and PySPI fits we added effective area correction parameters in the fit, allowing the total effective area of the individual detectors to vary a bit with respect to each other, to account for slightly different calibrations.
-To do this, we always fix the response of one of the detectors to the normal response of that detectors and fit one parameter for every other detector, which gets multiplied with the response in the fit.
-We constrain the effective area correction parameters to be between 0.7 and 1.3.
-
-All the fits in this section are done with 3ML and the Bayesian sampling algorithm MultiNest to create full posterior distributions of the parameters.
-To visualize the posterior distribution we use ChainConsumer with the output from MultiNest to create corner plots.
-
-\subsection{Compare PySPI and OSA}
-
-We analyze the SPI data with a band function as spectral model for the same time interval with PySPI and OSA, to check if the results are in agreement.
-The two methods are described in \ref{OSA} and \ref{pyspi}.
-Fig.
-\ref{fig:corner_osa_pyspi_band} shows the resulting posterior distributions of the fits, displayed as a corner plot.
-The results for the spectral shape from the two analysis techniques agree within their uncertainty region, but PySPI can constrain the parameters more precise.
-
-\begin{figure}
-  \begin{centering}
-    \includegraphics[width=1\linewidth]{figures/pyspi_vs_osa_band.pdf}
-    \caption{Corner plot for the SPI fit with PySPI and the official tools.
-The spectral model in this fit is a Band function.
-It shows, that the results are in agreement, but PySPI can constrain the parameters better.}
-    \label{fig:corner_osa_pyspi_band}
-  \end{centering}
-\end{figure}
-
-\subsection{Compare SPI and GBM}
-
-Next, we analyze the SPI data with PySPI and the GBM data with the GRB analysis within 3ML (cite a paper for this?) for a band function model.
-Fig.
-\ref{fig:corner_gbm_pyspi_band} displays the corner plots for these fits, demonstrating that the results for the spectral shape from SPI and GBM are in agreement.
-It also shows that the calibration for SPI and GBM are well aligned within only $\approx$ 10\% difference in this case.
-
-\begin{figure}
-  \begin{centering}
-    \includegraphics[width=1\linewidth]{figures/pyspi_vs_gbm_band.pdf}
-    \caption{Corner plot for the SPI fit with PySPI and the GBM fit.
-In this fit we used a Band function as spectral model.
-The spectral shape for the SPI and GBM fits coincide within their uncertainty regions and the normalization is off by $\approx$10\%, which is within the usual calibration offsets of Gamma-Ray space telescopes.}
-    \label{fig:corner_gbm_pyspi_band}
-  \end{centering}
-\end{figure}
-
-\subsection{Joint Fit of SPI and GBM}
-
-The final analysis is a joint fit for the SPI and the GBM data with a physical synchrotron model (see \ref{synch}).
-Fig.
-\ref{fig:corner_gbm_pyspi_joined_syn} shows the corner plots for the individual and the combined fits.
-The posterior distribution of the parameters from the GBM and the SPI fit agree within their uncertainty regions and the combined fit reduces the allowed parameter space.
-The physical synchrotron model was able to fit the data of GBM and SPI well, which is shown with PPC and QQ plots in \ref{appendix}.
-
-\begin{figure}
-  \begin{centering}
-    \includegraphics[width=1\linewidth]{figures/pyspi_and_gbm_syn.pdf}
-    \caption{Corner plot for the SPI fit with PySPI and the GBM fit.
-In this fit we used a physical synchrotron model (see \ref{synch}) as spectral model.
-The results from SPI and GBM agree within their uncertainty region and the combined fit constrains the parameter better than the individual ones.}
-    \label{fig:corner_gbm_pyspi_joined_syn}
-  \end{centering}
-\end{figure}
-
-\section{Conclusion}
-
-We analyzed the data of GRB120711A with the data from INTGRAL/SPI and Fermi/GBM.
-The results for SPI with PySPI are in agreement with those from the official analysis software, but more constraining.
-Also the resulting spectral shape for the fits with GBM and SPI data are in agreement and the relative calibration difference between SPI and GBM we conclude from the fits, is $\approx$ 10\% or less.
-We show that the GBM as well as the SPI data for GRB120711A can be fitted well with a physical, time dependent synchrotron model and that combining the data in a simultaneous fit improves the parameter constrains.
-
-Generally PySPI can improve the scientific output from SPI for GRBs significantly.
-Due to a new analysis method, that folds the source model directly into the data space of every SPI detector with the full response of the individual detectors, the results are more constraining than the results with the official analysis software.
-
-\begin{appendix}
-  \section{Model Checking Plots}
-  \label{appendix1}
-  In this section we show a selection of the PPC- and QQ-plots for the simultaneous synchrotron fit to the SPI and GBM data for GRB120711A.
-  \begin{figure}[H]
-    \begin{centering}
-      \includegraphics[width=0.45\linewidth]{figures/n0_ppc.pdf}
-      \includegraphics[width=0.45\linewidth]{figures/n0_qq.pdf}
-      \caption{PPC (left) and QQ (right) plot for the GBM detector n0.}
-      \label{fig:n0_model_check}
-    \end{centering}
-  \end{figure}
-  \begin{figure}[H]
-    \begin{centering}
-      \includegraphics[width=0.45\linewidth]{figures/b0_ppc.pdf}
-      \includegraphics[width=0.45\linewidth]{figures/b0_qq.pdf}
-      \caption{PPC (left) and QQ (right) plot for the GBM detector b0.}
-      \label{fig:b0_model_check}
-    \end{centering}
-  \end{figure}
-  \begin{figure}[H]
-    \begin{centering}
-      \includegraphics[width=0.45\linewidth]{figures/low_13_ppc.pdf}
-      \includegraphics[width=0.45\linewidth]{figures/low_13_qq.pdf}
-      \caption{PPC (left) and QQ (right) plot for the low energy range of SPI detector 13 (all single events).}
-      \label{fig:low_13_model_check}
-    \end{centering}
-  \end{figure}
-  \begin{figure}[H]
-    \begin{centering}
-      \includegraphics[width=0.45\linewidth]{figures/psd_13_ppc.pdf}
-      \includegraphics[width=0.45\linewidth]{figures/psd_13_qq.pdf}
-      \caption{PPC (left) and QQ (right) plot for the middle energy range of SPI detector 13 (only PSD events).}
-      \label{fig:psd_13_model_check}
-    \end{centering}
-  \end{figure}
-\end{appendix}
-
-\bibliographystyle{aasjournal}
-\bibliography{biblio}
+%\bibliographystyle{aasjournal}
+%\bibliography{biblio}
 

### 2021-12-17 src/ms.tex
add1

@@
 \section{Introduction}
+Gamma-Ray Bursts (GRBs) are short transient bursts of gamma rays, with a typical active time range between a few ms and few hundred seconds for the prompt phase, which is mostly observed in X- and Gamma-Rays.
+After the prompt emission, there is a long lasting afterglow phase when the ejecta interacts with the Inter Stellar Medium (ISM).
+Long GRBs ($\approx$> 2s) have been associated to the collapse of massive stars, whereas short GRBs are believed to be caused by mergers of compact objects, like Neutron Stars.
+In both cases it is commonly agreed on, that the progenitor events of GRBs produce jetted relativistic outflows, which consists of several shells with different velocities, resulting in internal shell collisions.
+But it is still highly debated what the exact emission mechanism of the Gamma-Rays is.
+\citep{gamma-ray-burst, gw}
+
+In the past, GRB data was often fitted with empirical function like the Band function (cite band).
+But in recent years it has been shown, that this approach can be misleading and that one should rather fit physical models directly to the data.
+An example for this is the so-called line-of-death for synchrotron emission, which states that synchrotron radiation can not be the emission mechanism, if fits with a Band function give a low energy power law slope larger than -2/3.
+\citep{line-of-death, line-of-death2}
+\citet{synch} have shown that this conclusion is not correct and that you can fit GRB spectra well with a physical synchrotron model even though the same spectra violate the line-of-death if fitted with a Band function.
+
+The Gamma-Ray Burst Monitor (GBM) onboard of the Fermi satellite is often used to fit GRB data in the 8 keV to 10 MeV energy range.
+GBM consists of 12 NaI and two BGO scintillator detectors and is an all-sky instrument, that observes the whole sky, except the part that is occulted by the Earth at that time.
+(cite)
+%The problem with fitting empirical models to the data and using the individual parameters of these fits to construct constrains on the physics is that the
+Another instrument that operates in a similar energy range is the SPectrometer on INTEGRAL (SPI), which is one of the instruments onboard of the INTErnational Gamma-Ray Astrophysics Laboratory (INTEGRAL) satellite, that was launched in 2002 and is still operating today.
+SPI is a coded mask instrument, which has a fully coded FOV of 16 degrees and covers an energy range between 20 keV and 8 MeV.
+Due to the Germanium detectors it has a very good energy resolution of roughly 2.2 keV at 1.3 MeV, which allows the identification of fine features, like atomic decay lines \citep{spi}.
+In the case of GRBs this excellent energy resolution could allow us to determine the curvature of the spectra with an unmet precision.
+This is the main motivation to use SPI in our analysis.
+
+Several works have used SPI data to fit GRB models \citep{spi_grb1, spi_grb2}, but all of them fitted empirical models like the Band function.
+To allow us to fit physical models and to improve the analysis methods we developed PySPI, which will be explained in detail in \ref{pyspi}.
+
+%The other instrument that we use in this work is the Gamma-Ray Burst Monitor (GBM) onboard of the Fermi satellite.
+GBM is an all-sky instrument, that observes the whole sky, except the part that is occulted by the Earth at that time.
+It consists of 12 NaI and two BGO scintillator detectors that cover in total an energy range between 8 keV and 10 MeV.
+(cite)
+
+\section{Methods}
+\subsection{PySPI}
+\label{pyspi}
+To fit the SPI data of GRBs, we developed a new python package PySPI (ref to JOSS?), which is an open source analysis tool. In the following we will summarize the main points of PySPI.
+
+\subsubsection*{Background}
+
+GRBs are transient sources with a typical duration only up to a few tens of seconds.
+Therefore we can use the time intervals during a science window, when the transient source is not active, as an independent temporal off-source observation (see Fig.
+\ref{fig:lightcurve}).
+Similar to other instruments, that use spatially off-source observation as an independent background measurement.
+From the background observations we construct the probability of the background model rates per energy channel from a poisson distribution, like given in equation \ref{eq:poisson_bkg}, where $b_{i}$ are the background rates per energy channel, $B_{i}$ are the detected counts in the off-source observation and $t_{b}$ is the exposure of the off-source observation.
+\begin{equation}
+	L(b_{i}|B_{i}, t_{b})=\frac{(t_{b} b_{i})^{B_{i}}}{B_{i}!}\cdot e^{-t_{b} b_{i}}
+  \label{eq:poisson_bkg}
+\end{equation}
+This expression will be used in the next paragraph to derive the total likelihood.
+
+\begin{figure}
+    \begin{centering}
+        \includegraphics{figures/lightcurve.pdf}
+        \caption{Lightcurve for SPI detector 0 for GRB120711A. The transient source is clearly visible as well as the constant background for the time when the transient is not active.}
+        \label{fig:lightcurve}
+    \end{centering}
+\end{figure}
+
+% add a lightcurve plot?
+
+\subsubsection*{Likelihood}
+
+With the defined background treatment, we can construct a Poisson likelihood with a Poisson measurement of background, like given in \ref{eq:likelihood_m_and_b}.
+Here $\theta$ summarizes all the parameters of the model, $D_{i}$ are the measured counts in the selected active time interval of the transient source, $m_{i}(\theta)$ are the predicted counts from the model evaluated at the parameters $\theta$ and $t_{d}$ is the exposure of the selected active time interval.
+
+\begin{equation}
+	L(\theta, b_{i}|D_{i}, B_{i},t_{d},t_{b}) = \frac{(t_{d}(m_{i}(\theta)+ b_{i}))^{D_{i}}}{D_{i}!}\cdot e^{-t_{d}(m_{i}(\theta)+b_{i})} \frac{(t_{b} b_{i})^{B_{i}}}{B_{i}!}\cdot e^{-t_{b} b_{i}}
+  \label{eq:likelihood_m_and_b}
+\end{equation}
+
+Now we can marginalize over the parameters $b_{i}$, that we are not interested in, which leaves us with equation \ref{eq:likelihood_marg}.
+
+\begin{equation}
+	L(\theta|D_{i}, B_{i},t_{d},t_{b}) = \int_{0}^{\infty}\textrm{db}_{i}\frac{(t_{d}(m_{i}(\theta)+ b_{i}))^{D_{i}}}{D_{i}!}\cdot e^{-t_{d}(m_{i}(\theta)+b_{i})} \frac{(t_{b} b_{i})^{B_{i}}}{B_{i}!}\cdot e^{-t_{b}b_{i}}
+  \label{eq:likelihood_marg}
+\end{equation}
+
+Because there is no easy analytical solution for this integral, one often uses a so-called profiled likelihood as an approximation.
+For the profiled likelihood we use the fact, that the derivative of the likelihood at its maximum is zero.
+Therefore one can construct from $\frac{\textrm{dL}}{\textrm{db}_i}=0$ the background rates $b_{i, max}$ that maximize the likelihood for a given model $m_{i}(\theta)$ and observed quantities.
+Solving $\frac{\textrm{dL}}{\textrm{db}_i}=0$ for b gives equation \ref{eq:bmax}.
+\begin{equation}
+	b_{i,max}(\theta)=\frac{1}{2(t_{b}+t_{d})}(B_{i}+D_{i}-m_{i}(\theta)(t_{b}+t_{d})+\sqrt{(B_{i}+D_{i}+m_{i}(\theta)(t_{b}+t_{d}))^{2}-4m_{i}(\theta)D_{i}(t_{d}-t_{b})}
+  \label{eq:bmax}
+\end{equation}
+
+These values can then be substituted in the likelihood \ref{eq:likelihood_m_and_b} to eliminate the $b_{i}$ dependency.
+This approximation gives the exact solution for the maximum of the likelihood, for likelihood values close to the maximum, the assumption is that most of the likelihood in the integrand in \ref{eq:likelihood_marg} is in a small area around $b_{i,max}$.
+This assumption is used in many spectral analyses and works very well as long as one does not have too few counts in the background observation \footnote{For a derivation see https://giacomov.github.io/Bias-in-profile-poisson-likelihood/}.
+
+\subsubsection*{Response}
+
+To convert a physical spectrum to a detected count spectrum, we need the response for a given source position.
+The response encapsulates all the information about the probability of a photon with a certain energy and origin to be detected in a certain energy channel of the detector.
+This includes for example information about partial energy deposition of the photon in the crystal and the process that transforms the deposited energy into an electronic signal, that is measured in the end.
+% distribution of how much energy a photon with a certain energy deposit in the crystal and what energy is in the end measured for this deposited energy.
+In PySPI we use the official response files for Image Response Functions (IRFs) and Redistribution Matrix Files (RMFs) derived by \citet{spi_response}.
+The IRF files give the total effective area for three different interaction types:
+\begin{itemize}
+  \item Photo peak events
+  \item Non photo peak events that first interact in the crystal
+  \item Non photo peak events that first interact in passive material
+\end{itemize}
+
+These effective areas were simulated for 51 photon energies and on a 0.5 degree grid.
+For each of the three interaction type, there is one RMF, to define the shape of the redistributed spectra, assuming that this shape does not depend on the detector or the incident angles of the photons.
+The procedure to construct the response includes several simplification to keep the computational costs and storage space manageable \citep{spi_response}.
+This could of course affect every analysis done with SPI.
+Re-simulating the response without these simplifications could improve the scientific output of SPI, but would take a hugh amount of computational time, even today.
+
+In PySPI we then interpolate the official response files to the user defined energy bins and source positions.
+
+\subsubsection*{Electronic Noise}
+
+Since shortly after the start of INTEGRAL, it is known that there are spurious events in the SPI data around 1.5 MeV.
+According to \citet{spi_electronic_noise} these spurious events are photons with small energy (<100 keV) that get detected at a higher energy due to saturation of the Analog Front-End Electronics (AFEE) electronics by previous high energy deposition.
+It is also known, that these spurious events do not show up if one looks only at events with a detection also in the Pulse Shape Discriminator (PSD) electronics.
+The reason for this is that the PSD electronics has a low energy threshold of roughly 450 keV (the exact value has been changed a few times during the mission).
+Therefore only events that deposit more than this low energy threshold in the Germanium crystal can trigger this electronic, which eliminates the <100 keV events that are detected at the wrong energies by the AFEE electronics.
+In Fig.
+\ref{fig:electronic} one can see that the feature at 1.5 MeV is nicely visible in the non-PSD events but is missing in the PSD events.
+Even though this problem is the most significant in the area around 1.5 MeV it is also important at lower energies >400 keV.
+In PySPI one can select the energy range in which only the PSD events should be used, to avoid including spurious events.
+To account for the larger dead time of the PSD electronics, an effective area correction can be either fix to 85 \% \citep{spi_electronic_noise} or treated as a free parameter in the fit.
+
+\begin{figure}
+    \begin{centering}
+        \includegraphics{figures/electronic_noise.pdf}
+        \caption{Count spectrum for detector 0 integrated over 1000 seconds. One can clearly see the feature in the Non-PSD events at 1.5 MeV that is not visible in the PSD events.}
+        \label{fig:electronic}
+    \end{centering}
+\end{figure}
+
+\subsubsection*{General Procedure}
+
+In PySPI every Germanium detector is treated as an independent detector. The workflow during a fit step is the following:
+\begin{itemize}
+  \item Sample model parameters
+  \item Calculate model flux and responses individually for all detectors for the source position
+  \item Fold model with responses to get predicted model counts in all detectors
+  \item Calculate log-likelihood for all detectors
+  \item Sum these log-likelihoods to get the total log-likelihood of the SPI data for the given model parameters
+\end{itemize}
+A sampling algorithm like MultiNest \citep{multinest} is used to iterate this procedure, in order to determine the posterior distributions.\\
+This workflow is very similar, like for example for GBM, because fundamentally instruments like SPI and GBM are very similar.
+They both consist of individual detectors that have different responses for a given source position.
+In GBM this is due to the different pointing directions of the detectors and in SPI due to the different occultation by the mask.
+Therefore there is no reason to treat SPI specially, just because it is a coded mask instrument.
+The information the mask encodes into the data is automatically included by using the different responses for the detectors.
+
+\subsubsection*{3ML plugin}
+
+PySPI can construct a plugin for the Multi-Mission Maximum Likelihood framework (3ML) \citep{3ML}.
+This allows, without any further work, to fit the SPI data together with the data from other instruments, like Fermi/GBM.
+\footnote{For more information about 3ML see threeml.readthedocs.io/}
+
+\subsubsection*{Open Source Software}
+
+PySPI is an open source software, which is publicly available on GitHub (cite JOSS).
+There is also a documentation, that shows how to use it.
+\footnote{For more information about PySPI see pyspi.readthedocs.io/}
 

### 2021-12-17 src/ms.tex
add2

@@
 
+\subsection{OSA}
+\label{OSA}
+
+As we are introducing a new analysis software in this work, we want to compare it to the existing analysis software, to check if the results are in agreement.
+We shortly summarize the official analysis tools for GRB analysis, which are part of the INTEGRAL Offline Scientific Analysis (OSA) software.
+\citep{osa}
+
+Analyzing GRB data from SPI with the OSA tools is a multistep process.
+The first steps are basic and cover selecting the science window with the GRB, the time intervals for active time and background time as well as the energy bins for the analysis.
+After that one can either find the location of the GRB with SPIROS, i.e.
+an iterative source removal algorithm for SPI data, or set it manually, if it is already known.
+The next steps concern the spectral fitting, which is done in an other two-step procedure, which will be called 'Photo Peak Fitting' and 'Energy Redistribution Fitting' hereafter.
+
+\subsubsection*{Photo Peak Fitting}
+
+The first step in the spectral fitting with OSA is to use only the photo peak response of the detectors.
+These responses depend on the source position, as this defines for example the absorption by the mask.
+With these responses and the measured data in the individual SPI detectors, taking into account the different background rates, a photon flux is fitted individually per energy channel.
+These pseudo photon fluxes are not the final result, as up to this point energy dispersion and detector energy resolution was ignored.
+
+\subsubsection*{Energy Redistribution Fitting}
+
+The pseudo photon flux data points from the 'Photo Peak Fitting' step, which are no real data points anymore, are fitted with a spectral photon flux model which is convolved with a correction response, which is also available through OSA.
+This correction response depends on the energy bins that are used and should account for energy dispersion as well as resolution.
+In this step the energy channels are fitted simultaneously, as it is impossible to incorporate energy dispersion in a way that fits every energy channel individually.
+This fitting can be done in different spectral fitting software.
+In this work we use 3ML.
+
+\subsection{Synchrotron Model}
+\label{synch}
+We use pynchrotron to calculate the spectrum from a physical, time dependent spectral synchrotron model.
+This model was previously used to successfully fit many single pulse GRBs with GBM in \citet{synch}, which also includes a detailed description of the model.
+Here we only want to summarize the main points shortly.
+
+The core of the model is the assumption of some generic acceleration mechanism, that constantly produces an electron spectrum with a power law shape $N(\gamma )\propto \gamma^{-p}$ between $\gamma_{inj}$ and $\gamma_{max}$.
+These electrons are cooled via synchrotron cooling in a magnetic field and produce radiation in this process.
+The resulting photon spectrum is the sum of the photon spectra at every time step in the cooling process and is defined by five quantities:
+
+\begin{enumerate}
+	\item Magnetic field strength $B$
+  \item Lower boundary of the injected electron spectrum $\gamma_{inj}$
+  \item Upper boundary of the injected electron spectrum $\gamma_{max}$
+  \item Slope of the injected electron spectrum $p$
+  \item Characteristic Lorentz factor the electrons cool to $\gamma_{cool}$
+\end{enumerate}
+
+There exists a strong degeneracy between $B$ and $\gamma_{inj}$, as their combination sets the peak of the photon spectrum.
+Therefore one usually fixes $\gamma_{inj}=10^{5}$ and only fits for $B$.
+It is important to keep in mind, that the results for $\gamma_{max}$ and $\gamma_{cool}$ are determined relative to the fixed $\gamma_{inj}$.
+
+\subsection{Model Checking}
+\label{PPC}
+To check if the fit of a model is a good description of the measured data is a very complicated topic and highly debated in the statistics community.
+Measurements like reduced $\chi^{2}$ use many assumptions, like for example that all the probability distributions in the problem are described as normal distributions, which is not the case here, as the measurement process is a Poisson process.
+Therefore we decided to use Posterior Predictive Checks (PPC) and Quantile-Quantile (QQ) plots.
+For the PPCs one simulate new data from the full posterior of the fit as well as the measurement process (see Eq.
+\ref{eq:ppc}) and compare them to the observed data.
+QQ plots use the same simualtion process, but instead of comparing the observed data of every energy channel individually to the simulated data, one compares the cumulative counts of the observation and the simulations over energy channels.
+QQ plots are very sensitive to weak systematic deviations of the model from the data.
+\citep{QQ,ppc}
+
+\begin{equation}
+  \textrm{P}(y^{\textrm{sim}}|y^{\textrm{obs}}) = \int \textrm{P}(y^{\textrm{sim}}|\theta) \textrm{P}(\theta|y^{\textrm{obs}}) \mathrm{d}\theta
+  \label{eq:ppc}
+\end{equation}
+\noindent
+Here $y^{\textrm{obs}}$ are the observed data, $\textrm{P}(\theta|y^{\textrm{obs}})$ is the posterior distribution of the model parameters $\theta$ given the observed data, $\textrm{P}(y^{\textrm{sim}}|\theta)$ is the probability of new data given the parameters of the model and $y^{\textrm{sim}}$ are the simulated data.
+These simulated data are then compared to the observed data and allow for a visual check, whether the posterior distributions of the fit together with the measuring process can reproduce the data.
+\section{Analysis}
+
+In this work we analyze GRB 120711A, which was a bright, multi pulse GRB with a precursor and a long emission period of $\approx$100 seconds.
+It was detected with SPI and GBM.
+We only look at one time slice with a duration of 10 seconds around the highest peak in the light curves (see Fig.
+\ref{fig:time_selection}).
+
+\begin{figure}
+  \begin{centering}
+    \includegraphics[width=1\linewidth]{figures/spi_lightcurve_ts.pdf}
+    \includegraphics[width=1\linewidth]{figures/gbm_lightcurve_ts.pdf}
+    \caption{Light curve for GRB120711A.}
+    \label{fig:time_selection}
+  \end{centering}
+\end{figure}
+
+We analyze the data from the two instruments independently first with the empirical Band function, to check if the results for SPI and GBM are in agreement as well as show a comparison between the fit results with PySPI and the official software tools for GRB analysis within OSA.
+Then we fit the SPI and GBM data simultaneously with a physical synchrotron model, and show that it can reduce the allowed parameter space significantly, compared to the individual fits.
+For all GBM and PySPI fits we added effective area correction parameters in the fit, allowing the total effective area of the individual detectors to vary a bit with respect to each other, to account for slightly different calibrations.
+To do this, we always fix the response of one of the detectors to the normal response of that detectors and fit one parameter for every other detector, which gets multiplied with the response in the fit.
+We constrain the effective area correction parameters to be between 0.7 and 1.3.
+
+All the fits in this section are done with 3ML \citep{3ML} and the Bayesian sampling algorithm MultiNest \citep{multinest} to create full posterior distributions of the parameters.
+To visualize the posterior distribution we use ChainConsumer \citep{chainconsumer} with the output from MultiNest to create corner plots.
+
 %\bibliographystyle{aasjournal}

### 2021-12-17 src/ms.tex
add3

@@
 
+\subsection{Compare PySPI and OSA}
+
+We analyze the SPI data with a band function as spectral model for the same time interval with PySPI and OSA, to check if the results are in agreement.
+The two methods are described in \ref{OSA} and \ref{pyspi}.
+Fig.
+\ref{fig:corner_osa_pyspi_band} shows the resulting posterior distributions of the fits, displayed as a corner plot.
+The results for the spectral shape from the two analysis techniques agree within their uncertainty region, but PySPI can constrain the parameters more precise.
+
+\begin{figure}
+  \begin{centering}
+    \includegraphics[width=1\linewidth]{figures/pyspi_vs_osa_band.pdf}
+    \caption{Corner plot for the SPI fit with PySPI and the official tools.
+The spectral model in this fit is a Band function.
+It shows, that the results are in agreement, but PySPI can constrain the parameters better.}
+    \label{fig:corner_osa_pyspi_band}
+  \end{centering}
+\end{figure}
+
+\subsection{Compare SPI and GBM}
+
+Next, we analyze the SPI data with PySPI and the GBM data with the GRB analysis within 3ML (cite a paper for this?) for a band function model.
+Fig.
+\ref{fig:corner_gbm_pyspi_band} displays the corner plots for these fits, demonstrating that the results for the spectral shape from SPI and GBM are in agreement.
+It also shows that the calibration for SPI and GBM are well aligned within only $\approx$ 10\% difference in this case.
+
+\begin{figure}
+  \begin{centering}
+    \includegraphics[width=1\linewidth]{figures/pyspi_vs_gbm_band.pdf}
+    \caption{Corner plot for the SPI fit with PySPI and the GBM fit.
+In this fit we used a Band function as spectral model.
+The spectral shape for the SPI and GBM fits coincide within their uncertainty regions and the normalization is off by $\approx$10\%, which is within the usual calibration offsets of Gamma-Ray space telescopes.}
+    \label{fig:corner_gbm_pyspi_band}
+  \end{centering}
+\end{figure}
+
+\subsection{Joint Fit of SPI and GBM}
+
+The final analysis is a joint fit for the SPI and the GBM data with a physical synchrotron model (see \ref{synch}).
+Fig.
+\ref{fig:corner_gbm_pyspi_joined_syn} shows the corner plots for the individual and the combined fits.
+The posterior distribution of the parameters from the GBM and the SPI fit agree within their uncertainty regions and the combined fit reduces the allowed parameter space.
+The physical synchrotron model was able to fit the data of GBM and SPI well, which is shown with PPC and QQ plots in \ref{appendix}.
+
+\begin{figure}
+  \begin{centering}
+    \includegraphics[width=1\linewidth]{figures/pyspi_and_gbm_syn.pdf}
+    \caption{Corner plot for the SPI fit with PySPI and the GBM fit.
+In this fit we used a physical synchrotron model (see \ref{synch}) as spectral model.
+The results from SPI and GBM agree within their uncertainty region and the combined fit constrains the parameter better than the individual ones.}
+    \label{fig:corner_gbm_pyspi_joined_syn}
+  \end{centering}
+\end{figure}
+
+\section{Conclusion}
+
+We analyzed the data of GRB120711A with the data from INTGRAL/SPI and Fermi/GBM.
+The results for SPI with PySPI are in agreement with those from the official analysis software, but more constraining.
+Also the resulting spectral shape for the fits with GBM and SPI data are in agreement and the relative calibration difference between SPI and GBM we conclude from the fits, is $\approx$ 10\% or less.
+We show that the GBM as well as the SPI data for GRB120711A can be fitted well with a physical, time dependent synchrotron model and that combining the data in a simultaneous fit improves the parameter constrains.
+
+Generally PySPI can improve the scientific output from SPI for GRBs significantly.
+Due to a new analysis method, that folds the source model directly into the data space of every SPI detector with the full response of the individual detectors, the results are more constraining than the results with the official analysis software.
+
 %\bibliographystyle{aasjournal}

### 2021-12-17 src/ms.tex
add4

@@
 Due to a new analysis method, that folds the source model directly into the data space of every SPI detector with the full response of the individual detectors, the results are more constraining than the results with the official analysis software.
+\begin{appendix}
+  \section{Model Checking Plots}
+  \label{appendix1}
+  In this section we show a selection of the PPC- and QQ-plots for the simultaneous synchrotron fit to the SPI and GBM data for GRB120711A.
+  \begin{figure}[h]
+    \begin{centering}
+      \includegraphics[width=0.45\linewidth]{figures/n0_ppc.pdf}
+      \includegraphics[width=0.45\linewidth]{figures/n0_qq.pdf}
+      \caption{PPC (left) and QQ (right) plot for the GBM detector n0.}
+      \label{fig:n0_model_check}
+    \end{centering}
+  \end{figure}
+  \begin{figure}[h]
+    \begin{centering}
+      \includegraphics[width=0.45\linewidth]{figures/b0_ppc.pdf}
+      \includegraphics[width=0.45\linewidth]{figures/b0_qq.pdf}
+      \caption{PPC (left) and QQ (right) plot for the GBM detector b0.}
+      \label{fig:b0_model_check}
+    \end{centering}
+  \end{figure}
+  \begin{figure}[h]
+    \begin{centering}
+      \includegraphics[width=0.45\linewidth]{figures/low_13_ppc.pdf}
+      \includegraphics[width=0.45\linewidth]{figures/low_13_qq.pdf}
+      \caption{PPC (left) and QQ (right) plot for the low energy range of SPI detector 13 (all single events).}
+      \label{fig:low_13_model_check}
+    \end{centering}
+  \end{figure}
+  \begin{figure}[h]
+    \begin{centering}
+      \includegraphics[width=0.45\linewidth]{figures/psd_13_ppc.pdf}
+      \includegraphics[width=0.45\linewidth]{figures/psd_13_qq.pdf}
+      \caption{PPC (left) and QQ (right) plot for the middle energy range of SPI detector 13 (only PSD events).}
+      \label{fig:psd_13_model_check}
+    \end{centering}
+  \end{figure}
+\end{appendix}
 
-%\bibliographystyle{aasjournal}
-%\bibliography{biblio}
+\bibliographystyle{aasjournal}
+\bibliography{biblio}
 

### 2021-12-17 src/ms.tex
H->h

@@
 Due to a new analysis method, that folds the source model directly into the data space of every SPI detector with the full response of the individual detectors, the results are more constraining than the results with the official analysis software.
+
 \begin{appendix}
@@
 
-\bibliographystyle{aasjournal}
+\bibliographystyle{aa}
 \bibliography{biblio}

### 2021-12-17 src/ms.tex
rename bib file
change legend

@@
         \includegraphics{figures/lightcurve.pdf}
-        \caption{Lightcurve for SPI detector 0 for GRB120711A. The transient source is clearly visible as well as the constant background for the time when the transient is not active.}
+        \caption{Lightcurve for SPI detector 0 for GRB120711A.
+The transient source is clearly visible as well as the constant background for the time when the transient is not active.
+The time intervals we use for the independent background observation is marked with the green shaded area.}
         \label{fig:lightcurve}
@@
 
-\begin{equation}
-	L(\theta, b_{i}|D_{i}, B_{i},t_{d},t_{b}) = \frac{(t_{d}(m_{i}(\theta)+ b_{i}))^{D_{i}}}{D_{i}!}\cdot e^{-t_{d}(m_{i}(\theta)+b_{i})} \frac{(t_{b} b_{i})^{B_{i}}}{B_{i}!}\cdot e^{-t_{b} b_{i}}
+\begin{multline}
+	L(\theta, b_{i}|D_{i}, B_{i},t_{d},t_{b}) = \frac{(t_{d}(m_{i}(\theta)+ b_{i}))^{D_{i}}}{D_{i}!}\cdot \\
+  e^{-t_{d}(m_{i}(\theta)+b_{i})}\frac{(t_{b} b_{i})^{B_{i}}}{B_{i}!} e^{-t_{b} b_{i}}
   \label{eq:likelihood_m_and_b}
-\end{equation}
+\end{multline}
 
-Now we can marginalize over the parameters $b_{i}$, that we are not interested in, which leaves us with equation \ref{eq:likelihood_marg}.
+Now we can marginalize over the parameters $b_{i}$, that we are not interested in and that we have no further information about a priori, despite the fact that they can not be negative, which leaves us with equation \ref{eq:likelihood_marg}.
 
-\begin{equation}
-	L(\theta|D_{i}, B_{i},t_{d},t_{b}) = \int_{0}^{\infty}\textrm{db}_{i}\frac{(t_{d}(m_{i}(\theta)+ b_{i}))^{D_{i}}}{D_{i}!}\cdot e^{-t_{d}(m_{i}(\theta)+b_{i})} \frac{(t_{b} b_{i})^{B_{i}}}{B_{i}!}\cdot e^{-t_{b}b_{i}}
+\begin{multline}
+	L(\theta|D_{i}, B_{i},t_{d},t_{b}) = \int_{0}^{\infty}\textrm{db}_{i}\frac{(t_{d}(m_{i}(\theta)+ b_{i}))^{D_{i}}}{D_{i}!}\cdot\\
+  e^{-t_{d}(m_{i}(\theta)+b_{i})} \frac{(t_{b} b_{i})^{B_{i}}}{B_{i}!} e^{-t_{b}b_{i}}
   \label{eq:likelihood_marg}
-\end{equation}
+\end{multline}
 
@@
 Solving $\frac{\textrm{dL}}{\textrm{db}_i}=0$ for b gives equation \ref{eq:bmax}.
-\begin{equation}
-	b_{i,max}(\theta)=\frac{1}{2(t_{b}+t_{d})}(B_{i}+D_{i}-m_{i}(\theta)(t_{b}+t_{d})+\sqrt{(B_{i}+D_{i}+m_{i}(\theta)(t_{b}+t_{d}))^{2}-4m_{i}(\theta)D_{i}(t_{d}-t_{b})}
+\begin{multline}
+	b_{i,max}(\theta)=\frac{1}{2(t_{b}+t_{d})}(B_{i}+D_{i}-m_{i}(\theta)(t_{b}+t_{d})+\\
+  \sqrt{(B_{i}+D_{i}+m_{i}(\theta)(t_{b}+t_{d}))^{2}-4m_{i}(\theta)D_{i}(t_{d}-t_{b})}
   \label{eq:bmax}
-\end{equation}
+\end{multline}
 
@@
         \includegraphics{figures/electronic_noise.pdf}
-        \caption{Count spectrum for detector 0 integrated over 1000 seconds. One can clearly see the feature in the Non-PSD events at 1.5 MeV that is not visible in the PSD events.}
+        \caption{Count spectrum for detector 0 integrated over 1000 seconds.
+The Non-PSD event count spectrum is drawn in purple and the PSD events in grey.
+One can clearly see the feature in the Non-PSD events at 1.5 MeV (green shaded area) that is not visible in the PSD events.}
         \label{fig:electronic}
@@
     \includegraphics[width=1\linewidth]{figures/gbm_lightcurve_ts.pdf}
-    \caption{Light curve for GRB120711A.}
+    \caption{Light curve for GRB120711A in one GBM and one SPI detector.
+The green shaded area marks the time intervals used for the independent background observation and the blue shaded area is the active time interval used in the fit.}
     \label{fig:time_selection}
@@
       \includegraphics[width=0.45\linewidth]{figures/n0_qq.pdf}
-      \caption{PPC (left) and QQ (right) plot for the GBM detector n0.}
+      \caption{PPC (left) and QQ (right) plot for the GBM detector n0.
+The green and purple shaded area are the one and two sigma contours.
+In the PPC plots the grey curve is the detected count spectrum and in the QQ plots the expected 1:1 relation between the cumulative model and observed counts.}
       \label{fig:n0_model_check}
@@
       \includegraphics[width=0.45\linewidth]{figures/b0_qq.pdf}
-      \caption{PPC (left) and QQ (right) plot for the GBM detector b0.}
+      \caption{PPC (left) and QQ (right) plot for the GBM detector b0.
+The green and purple shaded area are the one and two sigma contours.
+In the PPC plots the grey curve is the detected count spectrum and in the QQ plots the expected 1:1 relation between the cumulative model and observed counts.}
       \label{fig:b0_model_check}
@@
       \includegraphics[width=0.45\linewidth]{figures/low_13_qq.pdf}
-      \caption{PPC (left) and QQ (right) plot for the low energy range of SPI detector 13 (all single events).}
+      \caption{PPC (left) and QQ (right) plot for the low energy range of SPI detector 13 (all single events).
+The green and purple shaded area are the one and two sigma contours.
+In the PPC plots the grey curve is the detected count spectrum and in the QQ plots the expected 1:1 relation between the cumulative model and observed counts.}
       \label{fig:low_13_model_check}
@@
   \end{figure}
-  \begin{figure}[h]
+  \begin{figure}[h]9
     \begin{centering}
@@
       \includegraphics[width=0.45\linewidth]{figures/psd_13_qq.pdf}
-      \caption{PPC (left) and QQ (right) plot for the middle energy range of SPI detector 13 (only PSD events).}
+      \caption{PPC (left) and QQ (right) plot for the middle energy range of SPI detector 13 (only PSD events).
+The green and purple shaded area are the one and two sigma contours.
+In the PPC plots the grey curve is the detected count spectrum and in the QQ plots the expected 1:1 relation between the cumulative model and observed counts.}
       \label{fig:psd_13_model_check}
@@
 \bibliographystyle{aa}
-\bibliography{biblio}
+\bibliography{bib}
 

### 2021-12-17 src/figures/electronic.py

@@ -31,13 +31,12 @@ counts_psd = tsb_psd.time_series.count_per_channel_over_interval(-1000,0)
 counts_non_psd = tsb_non_psd.time_series.count_per_channel_over_interval(-1000,0)
 
 fig, ax = plt.subplots(1,1)
-ax.step(ebounds[1:], counts_psd, label="PSD events", color=color1)
-ax.step(ebounds[1:], counts_non_psd, label="Non-PSD events", color=color2)
-ax.fill_betweenx(np.linspace(0,np.max(counts_non_psd),10),1400, 1900, alpha=0.5, color=color3, label="Main Electronic Noise Region")
+ax.step(ebounds[1:], counts_psd, color=color1)
+ax.step(ebounds[1:], counts_non_psd, color=color2)
+ax.fill_betweenx(np.linspace(0,np.max(counts_non_psd),10),1400, 1900, alpha=0.5, color=color3)
 ax.set_yscale("log")
 ax.set_xscale("log")
 ax.set_xlabel("Detected Energy [keV]")
 ax.set_ylabel("Counts")
-ax.legend()
 
 fig.savefig("electronic_noise.pdf")

### 2021-12-17 src/figures/lightcurve.py

@@ -32,6 +32,9 @@ axis = f.axes[0]
 axis.get_lines()[0].set_color(color1)
 axis.collections[0].set_color(color3)
 axis.collections[1].set_color(color3)
+axis.get_lines()[0].set_label(None)
+axis.collections[0].set_label(None)
+axis.collections[1].set_label(None)
 
 axis.legend()
 

### 2021-12-17 src/figures/time_selection.py

@@ -72,10 +72,10 @@ x, y = lines[0].get_xydata().T
 ax.plot(x,y, color=color1, label="Light Curve")
 active_mask = np.logical_and(x>=ts.time_series.time_intervals.absolute_start,
                              x<=ts.time_series.time_intervals.absolute_stop)
-ax.fill_between(x[active_mask], y[active_mask], 0, color=color4, alpha=0.4, label="Selection")
+ax.fill_between(x[active_mask], y[active_mask], 0, color=color4, alpha=0.4)#, label="Selection")
 bkg_mask = np.logical_and(x>=ts.time_series.bkg_intervals[0].start,
                           x<=ts.time_series.bkg_intervals[0].stop)
-ax.fill_between(x[bkg_mask], y[bkg_mask], 0, color=color3, alpha=0.4, label="Bkg. Selection")
+ax.fill_between(x[bkg_mask], y[bkg_mask], 0, color=color3, alpha=0.4)#, label="Bkg. Selection")
 bkg_mask = np.logical_and(x>=ts.time_series.bkg_intervals[1].start,
                           x<=ts.time_series.bkg_intervals[1].stop)
 ax.fill_between(x[bkg_mask], y[bkg_mask], 0, color=color3, alpha=0.4)
@@ -94,13 +94,13 @@ x, y = lines[0].get_xydata().T
 ax2.plot(x,y, color=color1, label="Light Curve")
 active_mask = np.logical_and(x>=tsb.time_series.time_intervals.absolute_start,
                              x<=tsb.time_series.time_intervals.absolute_stop)
-ax2.fill_between(x[active_mask], y[active_mask], 0, color=color4, alpha=0.4, label="Selection")
+ax2.fill_between(x[active_mask], y[active_mask], 0, color=color4, alpha=0.4)#, label="Selection")
 bkg_mask = np.logical_and(x>=tsb.time_series.bkg_intervals[0].start,
                           x<=tsb.time_series.bkg_intervals[0].stop)
 ax2.fill_between(x[bkg_mask], y[bkg_mask], 0, color=color3, alpha=0.4)
 bkg_mask = np.logical_and(x>=tsb.time_series.bkg_intervals[1].start,
                           x<=tsb.time_series.bkg_intervals[1].stop)
-ax2.fill_between(x[bkg_mask], y[bkg_mask], 0, color=color3, alpha=0.4, label="Bkg. Selection")
[…]

### 2021-12-17 src/ms.tex
fix plot label

@@
   In this section we show a selection of the PPC- and QQ-plots for the simultaneous synchrotron fit to the SPI and GBM data for GRB120711A.
+The green and purple shaded area are the one and two sigma contours.
+In the PPC plots the grey curve is the detected count spectrum and in the QQ plots the expected 1:1 relation between the cumulative model and observed counts.
   \begin{figure}[h]
@@
       \includegraphics[width=0.45\linewidth]{figures/n0_qq.pdf}
-      \caption{PPC (left) and QQ (right) plot for the GBM detector n0.
-The green and purple shaded area are the one and two sigma contours.
-In the PPC plots the grey curve is the detected count spectrum and in the QQ plots the expected 1:1 relation between the cumulative model and observed counts.}
+      \caption{PPC (left) and QQ (right) plot for the GBM detector n0. The green and purple shaded area are the one and two sigma contours.}
       \label{fig:n0_model_check}
@@
       \includegraphics[width=0.45\linewidth]{figures/b0_qq.pdf}
-      \caption{PPC (left) and QQ (right) plot for the GBM detector b0.
-The green and purple shaded area are the one and two sigma contours.
-In the PPC plots the grey curve is the detected count spectrum and in the QQ plots the expected 1:1 relation between the cumulative model and observed counts.}
+      \caption{PPC (left) and QQ (right) plot for the GBM detector b0. The green and purple shaded area are the one and two sigma contours.}
       \label{fig:b0_model_check}
@@
       \includegraphics[width=0.45\linewidth]{figures/low_13_qq.pdf}
-      \caption{PPC (left) and QQ (right) plot for the low energy range of SPI detector 13 (all single events).
-The green and purple shaded area are the one and two sigma contours.
-In the PPC plots the grey curve is the detected count spectrum and in the QQ plots the expected 1:1 relation between the cumulative model and observed counts.}
+      \caption{PPC (left) and QQ (right) plot for the low energy range of SPI detector 13 (all single events).}
       \label{fig:low_13_model_check}
@@
       \includegraphics[width=0.45\linewidth]{figures/psd_13_qq.pdf}
-      \caption{PPC (left) and QQ (right) plot for the middle energy range of SPI detector 13 (only PSD events).
-The green and purple shaded area are the one and two sigma contours.
-In the PPC plots the grey curve is the detected count spectrum and in the QQ plots the expected 1:1 relation between the cumulative model and observed counts.}
+      \caption{PPC (left) and QQ (right) plot for the middle energy range of SPI detector 13 (only PSD events).}
       \label{fig:psd_13_model_check}

### 2021-12-17 src/figures/time_selection.py

@@ -69,7 +69,7 @@ fig, ax = plt.subplots(1,1,sharex=True)
 
 lines = f_gbm.axes[0].get_lines()
 x, y = lines[0].get_xydata().T
-ax.plot(x,y, color=color1, label="Light Curve")
+ax.plot(x,y, color=color1)
 active_mask = np.logical_and(x>=ts.time_series.time_intervals.absolute_start,
                              x<=ts.time_series.time_intervals.absolute_stop)
 ax.fill_between(x[active_mask], y[active_mask], 0, color=color4, alpha=0.4)#, label="Selection")
@@ -91,7 +91,7 @@ fig, ax2 = plt.subplots(1,1,sharex=True)
 
 lines = f_spi.axes[0].get_lines()
 x, y = lines[0].get_xydata().T
-ax2.plot(x,y, color=color1, label="Light Curve")
+ax2.plot(x,y, color=color1)
 active_mask = np.logical_and(x>=tsb.time_series.time_intervals.absolute_start,
                              x<=tsb.time_series.time_intervals.absolute_stop)
 ax2.fill_between(x[active_mask], y[active_mask], 0, color=color4, alpha=0.4)#, label="Selection")

### 2021-12-20 src/ms.tex
final first draft

@@
   In the last years it has been shown, that it is needed to fit physical models to Gamma-Ray Burst (GRB) data to get more insights into their emission mechanism.
-For the energy range between ~ 10 keV to ~ 10 MeV Fermi/GBM has been the main instrument to analyze GRBs.
+For the energy range between $\approx$ 10 keV to $\approx$ 10 MeV Fermi/GBM has been the main instrument to analyze GRBs.
 In this paper we show how we can add INTEGRAL/SPI to this analysis.
@@
 We present PySPI, a new analysis software we developed to analyze GRB data from SPI, and apply it to the GRB 120711A.
-We show that PySPI improves the analysis of SPI data, for GRBs, compared to the official analysis software and that the GBM and the SPI data of this GRB can be fitted well with a physical synchrotron model and that combining both, reduces the allowed parameter space.
-This demonstrates that SPI can play an important role in GRB model fitting.
+We show that PySPI improves the analysis of SPI GRB data compared to the official analysis software.
+Also we demonstrate that the GBM and the SPI data of this GRB can be fitted well with a physical synchrotron model and that combining both, reduces the allowed parameter space.
+This evinces that SPI can play an important role in GRB model fitting.
 }
@@
 
-Gamma-Ray Bursts (GRBs) are short transient bursts of gamma rays, with a typical active time range between a few ms and few hundred seconds for the prompt phase, which is mostly observed in X- and Gamma-Rays.
+Gamma-Ray Bursts (GRBs) are short transient bursts of Gamma-Rays, with a typical active time range between a few ms and few hundred seconds for the prompt phase, which is mostly observed in X- and Gamma-Rays.
 After the prompt emission, there is a long lasting afterglow phase when the ejecta interacts with the Inter Stellar Medium (ISM).
-Long GRBs ($\approx$> 2s) have been associated to the collapse of massive stars, whereas short GRBs are believed to be caused by mergers of compact objects, like Neutron Stars.
+Long GRBs (prompt phase $\approx$> 2s) have been associated to the collapse of massive stars, whereas short GRBs are believed to be caused by mergers of compact objects, like Neutron Stars.
 In both cases it is commonly agreed on, that the progenitor events of GRBs produce jetted relativistic outflows, which consists of several shells with different velocities, resulting in internal shell collisions.
@@
 
-In the past, GRB data was often fitted with empirical function like the Band function (cite band).
+In the past, GRB data was often fitted with empirical function like the Band function \citep{band}.
 But in recent years it has been shown, that this approach can be misleading and that one should rather fit physical models directly to the data.
-An example for this is the so-called line-of-death for synchrotron emission, which states that synchrotron radiation can not be the emission mechanism, if fits with a Band function give a low energy power law slope larger than -2/3.
-\citep{line-of-death, line-of-death2}
+An example for this is the so-called line-of-death for synchrotron emission \citep{line-of-death, line-of-death2}, which states that synchrotron radiation can not be the emission mechanism, if fits with a Band function give a low energy power law slope larger than -2/3.
 \citet{synch} have shown that this conclusion is not correct and that you can fit GRB spectra well with a physical synchrotron model even though the same spectra violate the line-of-death if fitted with a Band function.
@@
 GBM consists of 12 NaI and two BGO scintillator detectors and is an all-sky instrument, that observes the whole sky, except the part that is occulted by the Earth at that time.
-(cite)
-%The problem with fitting empirical models to the data and using the individual parameters of these fits to construct constrains on the physics is that the
+\citep{gbm}
+
 Another instrument that operates in a similar energy range is the SPectrometer on INTEGRAL (SPI), which is one of the instruments onboard of the INTErnational Gamma-Ray Astrophysics Laboratory (INTEGRAL) satellite, that was launched in 2002 and is still operating today.
@@
 \label{pyspi}
-To fit the SPI data of GRBs, we developed a new python package PySPI (ref to JOSS?), which is an open source analysis tool. In the following we will summarize the main points of PySPI.
+To fit the SPI data of GRBs, we developed a new python package PySPI \citep{joss}, which is an open source analysis tool.
+In the following we will summarize the main points of GRB analysis within PySPI.
 
@@
 Similar to other instruments, that use spatially off-source observation as an independent background measurement.
-From the background observations we construct the probability of the background model rates per energy channel from a poisson distribution, like given in equation \ref{eq:poisson_bkg}, where $b_{i}$ are the background rates per energy channel, $B_{i}$ are the detected counts in the off-source observation and $t_{b}$ is the exposure of the off-source observation.
+From the background observations we construct the probability of the background model rates per energy channel from a poisson distribution, like given in Eq.
+\ref{eq:poisson_bkg}, where $b_{i}$ are the background rates per energy channel, $B_{i}$ are the detected counts in the off-source observation and $t_{b}$ is the exposure of the off-source observation.
 \begin{equation}
@@
 
-With the defined background treatment, we can construct a Poisson likelihood with a Poisson measurement of background, like given in \ref{eq:likelihood_m_and_b}.
+With the defined background treatment, we can construct a Poisson likelihood with a Poisson measurement of background, like given in Eq.
+\ref{eq:likelihood_m_and_b}.
 Here $\theta$ summarizes all the parameters of the model, $D_{i}$ are the measured counts in the selected active time interval of the transient source, $m_{i}(\theta)$ are the predicted counts from the model evaluated at the parameters $\theta$ and $t_{d}$ is the exposure of the selected active time interval.
@@
 
-Now we can marginalize over the parameters $b_{i}$, that we are not interested in and that we have no further information about a priori, despite the fact that they can not be negative, which leaves us with equation \ref{eq:likelihood_marg}.
+Now we can marginalize over the parameters $b_{i}$, that we are not interested in and that we have no further information about a priori, despite the fact that they can not be negative, which leaves us with Eq.
+\ref{eq:likelihood_marg}.
 
@@
 Therefore one can construct from $\frac{\textrm{dL}}{\textrm{db}_i}=0$ the background rates $b_{i, max}$ that maximize the likelihood for a given model $m_{i}(\theta)$ and observed quantities.
-Solving $\frac{\textrm{dL}}{\textrm{db}_i}=0$ for b gives equation \ref{eq:bmax}.
+Solving $\frac{\textrm{dL}}{\textrm{db}_i}=0$ for b gives Eq.
+\ref{eq:bmax}.
 \begin{multline}
@@
 
-These values can then be substituted in the likelihood \ref{eq:likelihood_m_and_b} to eliminate the $b_{i}$ dependency.
-This approximation gives the exact solution for the maximum of the likelihood, for likelihood values close to the maximum, the assumption is that most of the likelihood in the integrand in \ref{eq:likelihood_marg} is in a small area around $b_{i,max}$.
+These values can then be substituted in the likelihood Eq.
+\ref{eq:likelihood_m_and_b} to eliminate the $b_{i}$ dependency.
+This approximation gives the exact solution for the maximum of the likelihood, for likelihood values close to the maximum, the assumption is that most of the likelihood in the integrand in Eq.
+\ref{eq:likelihood_marg} is in a small area around $b_{i,max}$.
 This assumption is used in many spectral analyses and works very well as long as one does not have too few counts in the background observation \footnote{For a derivation see https://giacomov.github.io/Bias-in-profile-poisson-likelihood/}.
@@
 \end{itemize}
-
+\noindent
 These effective areas were simulated for 51 photon energies and on a 0.5 degree grid.
@@
 \ref{fig:electronic} one can see that the feature at 1.5 MeV is nicely visible in the non-PSD events but is missing in the PSD events.
-Even though this problem is the most significant in the area around 1.5 MeV it is also important at lower energies >400 keV.
+Even though this problem is most significant in the area around 1.5 MeV it is also important at lower energies >400 keV.
 In PySPI one can select the energy range in which only the PSD events should be used, to avoid including spurious events.
@@
 
-PySPI is an open source software, which is publicly available on GitHub (cite JOSS).
+PySPI is an open source software, which is publicly available on GitHub \citep{joss}.
 There is also a documentation, that shows how to use it.
@@
 an iterative source removal algorithm for SPI data, or set it manually, if it is already known.
-The next steps concern the spectral fitting, which is done in an other two-step procedure, which will be called 'Photo Peak Fitting' and 'Energy Redistribution Fitting' hereafter.
+The next steps concern the spectral fitting, which is done in another two-step procedure, which will be called 'Photo Peak Fitting' and 'Energy Redistribution Fitting' hereafter.
 
@@
 The pseudo photon flux data points from the 'Photo Peak Fitting' step, which are no real data points anymore, are fitted with a spectral photon flux model which is convolved with a correction response, which is also available through OSA.
-This correction response depends on the energy bins that are used and should account for energy dispersion as well as resolution.
+This correction response depends on the energy bins that are used and should account for energy dispersion.
 In this step the energy channels are fitted simultaneously, as it is impossible to incorporate energy dispersion in a way that fits every energy channel individually.
 This fitting can be done in different spectral fitting software.
-In this work we use 3ML.
 
@@
 	\item Magnetic field strength $B$
+  \item Slope of the injected electron spectrum $p$
   \item Lower boundary of the injected electron spectrum $\gamma_{inj}$
   \item Upper boundary of the injected electron spectrum $\gamma_{max}$
-  \item Slope of the injected electron spectrum $p$
   \item Characteristic Lorentz factor the electrons cool to $\gamma_{cool}$
@@
 Here $y^{\textrm{obs}}$ are the observed data, $\textrm{P}(\theta|y^{\textrm{obs}})$ is the posterior distribution of the model parameters $\theta$ given the observed data, $\textrm{P}(y^{\textrm{sim}}|\theta)$ is the probability of new data given the parameters of the model and $y^{\textrm{sim}}$ are the simulated data.
-These simulated data are then compared to the observed data and allow for a visual check, whether the posterior distributions of the fit together with the measuring process can reproduce the data.
+%These simulated data are then compared to the observed data and allow for a visual check, whether the posterior distributions of the fit together with the measuring process can reproduce the data.
 \section{Analysis}
@@
 For all GBM and PySPI fits we added effective area correction parameters in the fit, allowing the total effective area of the individual detectors to vary a bit with respect to each other, to account for slightly different calibrations.
-To do this, we always fix the response of one of the detectors to the normal response of that detectors and fit one parameter for every other detector, which gets multiplied with the response in the fit.
+To do this, we always fix the response of one of the detectors to the official response of that detectors and fit one parameter for every other detector, which gets multiplied with the response in the fit.
 We constrain the effective area correction parameters to be between 0.7 and 1.3.
@@
 
-Next, we analyze the SPI data with PySPI and the GBM data with the GRB analysis within 3ML (cite a paper for this?) for a band function model.
+Next, we analyze the SPI data with PySPI and the GBM data with the GRB analysis within 3ML for a band function model.
 Fig.
@@
   \section{Model Checking Plots}
-  \label{appendix1}
+  \label{appendix}
   In this section we show a selection of the PPC- and QQ-plots for the simultaneous synchrotron fit to the SPI and GBM data for GRB120711A.

### 2021-12-20 src/figures/lightcurve.py
remove empty legend

@@ -37,5 +37,6 @@ axis.collections[0].set_label(None)
 axis.collections[1].set_label(None)
 
 axis.legend()
+axis.get_legend().remove()
 
 f.savefig("lightcurve.pdf")

### 2021-12-20 src/figures/time_selection.py

@@ -80,6 +80,7 @@ bkg_mask = np.logical_and(x>=ts.time_series.bkg_intervals[1].start,
                           x<=ts.time_series.bkg_intervals[1].stop)
 ax.fill_between(x[bkg_mask], y[bkg_mask], 0, color=color3, alpha=0.4)
 ax.legend()
+ax.get_legend().remove()
 ax.set_title("GBM detector n2")
 ax.set_xlabel("Time (s)")
 ax.set_ylabel("Rate (cnts/s)")
@@ -102,6 +103,7 @@ bkg_mask = np.logical_and(x>=tsb.time_series.bkg_intervals[1].start,
                           x<=tsb.time_series.bkg_intervals[1].stop)
 ax2.fill_between(x[bkg_mask], y[bkg_mask], 0, color=color3, alpha=0.4)#, label="Bkg. Selection")
 ax2.legend()
+ax2.get_legend().remove()
 ax2.set_title("SPI detector 0")
 ax2.set_xlabel("Time (s)")
 ax2.set_ylabel("Rate (cnts/s)")

### 2021-12-20 src/ms.tex
Update ms.tex

@@
   \and
-  Siegert
+  Thomas Siegert
 }
@@
 % Abstract with filler text
-\abstract {
+\abstract{
   In the last years it has been shown, that it is needed to fit physical models to Gamma-Ray Burst (GRB) data to get more insights into their emission mechanism.

### 2022-01-13 src/figures/electronic.py
add shade to psd plot

@@ -33,7 +33,8 @@ counts_non_psd = tsb_non_psd.time_series.count_per_channel_over_interval(-1000,0
 fig, ax = plt.subplots(1,1)
 ax.step(ebounds[1:], counts_psd, color=color1)
 ax.step(ebounds[1:], counts_non_psd, color=color2)
-ax.fill_betweenx(np.linspace(0,np.max(counts_non_psd),10),1400, 1900, alpha=0.5, color=color3)
+ax.fill_betweenx(np.linspace(0,np.max(counts_non_psd),10), 400, 2700, alpha=0.3, color=color3)
+ax.fill_betweenx(np.linspace(0,np.max(counts_non_psd),10), 1400, 1900, alpha=0.5, color=color3)
 ax.set_yscale("log")
 ax.set_xscale("log")
 ax.set_xlabel("Detected Energy [keV]")

### 2022-01-13 src/ms.tex
add comments

--- 2021-12-20 src/ms.tex
@@
 \author{
-  Björn Biltzinger
+  Björn Biltzinger \inst{1}
   \and
-  Jochen Greiner
+  Jochen Greiner \inst{1}
   \and
-  Michael Burgess
+  J. Michael Burgess \inst{1}
   \and
-  Siegert
+  Thomas Siegert \inst{1,2}
 }
 
-\institute{Max-Planck-Institut fur extraterrestrische Physik, Giessenbachstrasse 1, D-85748 Garching, Germany \label{mpe}}
-\date{Received 18 December, 2019; accepted 22 May, 2020}
+\institute{Max-Planck-Institut f\"ur extraterrestrische Physik, Giessenbachstra{\ss}e 1, D-85748 Garching, Germany \and Institut f\"ur Theoretische Physik und Astrophysik, Universit\"at W\"urzburg, Campus Hubland Nord, Emil-Fischer-Str.
+31, 97074 W\"urzburg, Germany }
+\date{Received --; accepted --}
 
@@
 % Abstract with filler text
-\abstract {
-  In the last years it has been shown, that it is needed to fit physical models to Gamma-Ray Burst (GRB) data to get more insights into their emission mechanism.
-For the energy range between $\approx$ 10 keV to $\approx$ 10 MeV Fermi/GBM has been the main instrument to analyze GRBs.
+\abstract{
+  In recent years it has been shown, that one has to fit physical models to Gamma-Ray Burst (GRB) data to obtain more insights into their emission mechanism.
+For the energy range between $\approx$ 10 keV to $\approx$ 10 MeV Fermi/GBM has been the main instrument to analyze GRBs in the last 15 years.
 In this paper we show how we can add INTEGRAL/SPI to this analysis.
-INTEGRAL/SPI covers a similar energy range like Fermi/GBM and has a very good energy resolution of 2.2 keV at 1.3 MeV.
-Therefore INTEGRAL/SPI is an ideal instrument to precisely measure the curvature of the spectrum.
-We present PySPI, a new analysis software we developed to analyze GRB data from SPI, and apply it to the GRB 120711A.
-We show that PySPI improves the analysis of SPI GRB data compared to the official analysis software.
-Also we demonstrate that the GBM and the SPI data of this GRB can be fitted well with a physical synchrotron model and that combining both, reduces the allowed parameter space.
-This evinces that SPI can play an important role in GRB model fitting.
+SPI covers a similar energy range and has a very good energy resolution of $\approx$ 0.2\% at 1.3 MeV compared to $\approx$ 10\% for GBM.
+Therefore it is an ideal instrument to measure precisely the curvature of the spectrum.
+We present {\tt PySPI}, a new analysis software that we developed to analyze GRB data from SPI.
+To demonstrate its usage and capabilities, we apply it to the GRB 120711A.
+We show that {\tt PySPI} improves the analysis of SPI GRB data compared to the official analysis software.
+In addition we demonstrate that the GBM and the SPI data of this GRB can be fitted well with a physical synchrotron model and that combining both, reduces the allowed parameter space.
+This evinces that SPI plays an important role in GRB model fitting.
 }
@@
 
-Gamma-Ray Bursts (GRBs) are short transient bursts of Gamma-Rays, with a typical active time range between a few ms and few hundred seconds for the prompt phase, which is mostly observed in X- and Gamma-Rays.
-After the prompt emission, there is a long lasting afterglow phase when the ejecta interacts with the Inter Stellar Medium (ISM).
-Long GRBs (prompt phase $\approx$> 2s) have been associated to the collapse of massive stars, whereas short GRBs are believed to be caused by mergers of compact objects, like Neutron Stars.
-In both cases it is commonly agreed on, that the progenitor events of GRBs produce jetted relativistic outflows, which consists of several shells with different velocities, resulting in internal shell collisions.
-But it is still highly debated what the exact emission mechanism of the Gamma-Rays is.
-\citep{gamma-ray-burst, gw}
+Gamma-Ray Bursts (GRBs) are short transient bursts of $\gamma$-rays, with a typical active time range between a few ms and few hundred seconds for the prompt phase, which is mostly observed in $x$- and $\gamma$-rays.
+After the prompt emission, there is a long lasting afterglow phase when the ejecta interacts with the Inter Stellar Medium (ISM) \citep{afterglow}.
+GRBs are classified in two groups depending on the the duration of the prompt emission \citep{shortlong}.
+Long GRBs (prompt phase $\gtrapprox$ 2s) have been associated with the collapse of massive stars \citep{SN1, SN2}, whereas short GRBs are believed to be caused by mergers of compact objects, like neutron stars \citep{gw}.
+In both cases it is consensus, that the progenitor events of GRBs produce jetted relativistic outflows, which consists of several shells with different velocities, resulting in internal shell collisions \citep{gamma-ray-burst}.
 
-In the past, GRB data was often fitted with empirical function like the Band function \citep{band}.
-But in recent years it has been shown, that this approach can be misleading and that one should rather fit physical models directly to the data.
-An example for this is the so-called line-of-death for synchrotron emission \citep{line-of-death, line-of-death2}, which states that synchrotron radiation can not be the emission mechanism, if fits with a Band function give a low energy power law slope larger than -2/3.
-\citet{synch} have shown that this conclusion is not correct and that you can fit GRB spectra well with a physical synchrotron model even though the same spectra violate the line-of-death if fitted with a Band function.
+It is still highly debated what the emission mechanism of the prompt emission is \citep[for a review see][]{gamma-ray-burst}.
+Two of the possible emission mechanism are synchrotron \citep[e.g.][]{syn_shell, bosnjak_syn, synch} and photospheric emission \citep[e.g.][]{photo_1, photo_2, photo_3}.
+In the past, GRB data were often fitted with empirical function like the Band function \citep{band}, to conclude from the fit parameters which physical model is preferred.
+In recent years it has been shown, that this approach can be misleading and that one should rather fit physical models directly to the data \citep{physical_models, synch}.
+An example for this is the so-called `line-of-death' for synchrotron emission \citep{line-of-death, line-of-death2}, which states that synchrotron radiation can not be the universal emission mechanism, if fits with a Band function give a low energy power law slope larger than $-2/3$.
+\citet{synch} have shown that this conclusion is flawed and that one can fit GRB spectra well with a physical synchrotron model even though the same spectra violate the line-of-death if fitted with a Band function.
+Especially the curvature of GRB spectra has been debated heavily towards extracting the physical emission process dominating GRBs (citation for this?).
+Here, we make use of INTEGTRAL/SPI which provides a factor 100 better spectral resolution in the 0.5-1 MeV band compared to Fermi/GBM.
 
-The Gamma-Ray Burst Monitor (GBM) onboard of the Fermi satellite is often used to fit GRB data in the 8 keV to 10 MeV energy range.
+The spectrometer SPI, is one of the instruments onboard of the INTErnational Gamma-Ray Astrophysics Laboratory \citep[INTEGRAL][]{integral} satellite, that was launched in 2002.
+It is a coded mask instrument, with a fully coded FOV of 16 degrees, that covers an energy range between 20 keV and 8 MeV.
+The energy resolution allows the identification of fine features, like atomic decay lines \citep{spi_main}.
+In the case of GRBs this energy resolution gives us the possibility to determine the curvature of the spectra with an unmet precision.
+
+The standard analysis of SPI GRB data is done within the INTEGRAL Offline Scientific Analysis ({\tt OSA}) software \citep{osa}.
+That uses a two step method of first using only the photo peak response to incorporate the mask pattern on the detectors and in a second step applying an energy redistribution correction response.
+This method is used in several works which fitted empirical GRB models to the SPI data \citep[e.g.][]{spi_grb1, spi_grb2}.
+%Several works have used SPI data for GRBs \citep{spi_grb1, spi_grb2}, but all of them fitted empirical models like the Band function.
+We developed the pure python-based analysis tool {\tt PySPI} in order to progress to fitting physical models and getting the maximal amount of information out of the data.
+This improves the analysis method in general because we use the full response and forward model the expected spectra to the native SPI data space and offers an easy to install and use interface.
+%In this paper we introduce the new analysis method and show that we can fit complicated physical GRB models to the SPI data
+
+This paper is structured as follows: In Sec.
+\ref{methods} we summarize the different methods and concepts for SPI GRB data analysis, which also includes a detailed description of the new analysis method within {\tt PySPI} in Sec.
+\ref{pyspi}.
+Sec.
+\ref{synch} introduces the physical synchrotron model we used in the fits and Sec.
+\ref{PPC} explains how we check if a fit is a good description of the data.
+We analyse the SPI and GBM data for GRB 120711A in Sec.
+\ref{analysis} and conclude our results in Sec.
+\ref{conclusion}.
+
+%But even if we fit physical models directly to the data, it can be difficult to reject certain physical models, because multiple models can give acceptable fits to the data.
+This is due to energy dispersion and finite energy resolution of the detectors, which makes this an inversion problem, that can cause photon spectra that are different, to produce similar detected count spectra.
+This can be improved by a detector with better energy resolution, which INTEGRAL/SPI can provide.
+Due to the Germanium detectors it has an energy resolution of $\approx$ 2.2 keV at 1.3 MeV \citep{spi} compared to $\approx$ 10\% for Fermi/GBM \citep{gbm}.
+%Generally, it can be difficult to reject models, because often several models can give acceptable fits to the data.
+This is due to energy dispersion and finite energy resolution of the detectors, that can cause photon spectra that are different, to produce the same detected count spectra.
+%Therefore the parameters the fit with an empirical model returns, is only the best fit within the build-in constraints of the model shape and can be a good fit to the data.
+But if we loose the constrains on the shape of the model, we can maybe find other solutions that are also good fits to the data.
+This results in many GRBs
+%The underlying problem is that empirical functions like the Band function only allow a certain range of spectral shapes and can not fully reproduce for example a synchrotron photon spectrum
+%The Gamma-Ray Burst Monitor (GBM) onboard of the Fermi satellite is often used to fit GRB data in the 8 keV to 10 MeV energy range.
 GBM consists of 12 NaI and two BGO scintillator detectors and is an all-sky instrument, that observes the whole sky, except the part that is occulted by the Earth at that time.
@@
 
-Another instrument that operates in a similar energy range is the SPectrometer on INTEGRAL (SPI), which is one of the instruments onboard of the INTErnational Gamma-Ray Astrophysics Laboratory (INTEGRAL) satellite, that was launched in 2002 and is still operating today.
-SPI is a coded mask instrument, which has a fully coded FOV of 16 degrees and covers an energy range between 20 keV and 8 MeV.
-Due to the Germanium detectors it has a very good energy resolution of roughly 2.2 keV at 1.3 MeV, which allows the identification of fine features, like atomic decay lines \citep{spi}.
-In the case of GRBs this excellent energy resolution could allow us to determine the curvature of the spectra with an unmet precision.
-This is the main motivation to use SPI in our analysis.
-
-Several works have used SPI data to fit GRB models \citep{spi_grb1, spi_grb2}, but all of them fitted empirical models like the Band function.
-To allow us to fit physical models and to improve the analysis methods we developed PySPI, which will be explained in detail in \ref{pyspi}.
+%To allow us to fit physical models and to improve the analysis methods we developed {\tt PySPI}, which will be explained in detail in \ref{pyspi}.
 
@@
 
-\section{Methods}
-\subsection{PySPI}
+\section{SPI GRB Analysis Methods}
+\label{methods}
+All gamma-ray instruments suffer from energy dispersion and finite energy resolution.
+The information about this is encoded in the response matrix, that gives the probability of a photon with a certain energy and starting position on the sky to be detected in one of electronic channels of the detector.
+These response matrices are usually not invertible, and therefore we have to forward fold the photon spectrum trough the response matrix into the data space of the detected counts and compare them, using the correct likelihood.
+This is a general statement that also applies to SPI.
+In the following subsection we will first cover some general concepts for SPI and then the official analysis software method as well as the method within our new analysis tool {\tt PySPI}.
+The main difference is that the method in {\tt PySPI} is a full forward folding method, fulfilling the statement above, which results in maximising the information we can get from the data in the analysis.
+
+\subsection{Response}
+\label{response}
+
+The response connects the photon spectrum to an expected detected count spectrum, for a given source position.
+The response encapsulates all the information about the probability of a photon with a certain energy and origin to be detected in a certain electronic channel of the detector.
+This includes, for example, information about partial energy deposition of the photon in the crystal and the process that transforms the deposited energy into an electronic signal, that is actually measured.
+% distribution of how much energy a photon with a certain energy deposit in the crystal and what energy is in the end measured for this deposited energy.
+The response is split into two components: The Image Response Functions (IRFs) and Redistribution Matrix Files (RMFs).
+The IRFs contain the information of the total effective area for a photon to interact at all and the RMFs contain the information about the probability in which electronic channel an interacting photon will be measured.
+For SPI both these components were derived by \citet{spi_response}.
+The SPI IRF files give the total effective area for three different interaction types:
+\begin{itemize}
+  \item Photo peak events
+  \item Non photo peak events that first interact in the Ge crystal
+  \item Non photo peak events that first interact in passive material
+\end{itemize}
+\noindent
+These effective areas were calculated for 51 photon energies and on a 0.5 degree grid out to 23.5 degree from on-axis.
+For each of the three interaction types, there is one RMF, to define the shape of the redistributed spectra, assuming that this shape does not depend on the detector or the incident angles of the photons.
+The procedure to construct the response includes several simplification to keep the computational costs and storage space manageable \citep{spi_response}.
+Re-simulating the response without these simplifications could improve the scientific output of SPI, but would be computationally very expensive, even today.
+
+\subsection{Electronic Noise}
+\label{electronic}
+%Since shortly after the start of INTEGRAL, it is known that there are spurious events in the SPI data around 1.5 MeV.
+According to \citet{spi_electronic_noise} there are spurious events in the SPI data, which are photons with small energy (<100 keV) that get detected at a higher energy due to saturation of the Analog Front-End Electronics (AFEE) electronics by previous high energy deposition.
+It is also known, that these spurious events do not show up in events with a detection also in the Pulse Shape Discriminator (PSD) electronics.
+The reason for this is that the PSD electronics have a low energy threshold of $\approx$ 450 keV (the exact value has been changed a few times during the mission) \citep{spi_electronic_noise}.
+Therefore only events that deposit more than this low energy threshold in the Germanium crystal can trigger this electronic chain, which eliminates the <100 keV events that are detected at the wrong energies by the AFEE electronics.
+In Fig.
+\ref{fig:electronic} one can see that the feature at 1.5 MeV is nicely visible in the Non-PSD events but is missing in the PSD events.
+Even though this problem is most significant in the area around 1.5 MeV it is also important at lower energies >400 keV.
+
+\begin{figure}
+    \begin{centering}
+        \includegraphics{figures/electronic_noise.pdf}
+        \caption{Count spectrum for detector 0 integrated over 1000 seconds in revolution 1189.
+The Non-PSD event count spectrum is drawn in purple and the PSD events in grey.
+The light green shaded area marks the energy range within the PSD energy thresholds \citep{spi_electronic_noise}.
+One can clearly see the feature in the Non-PSD events at 1.5 MeV (stronger green shaded area) that is not visible in the PSD events.}
+        \label{fig:electronic}
+    \end{centering}
+\end{figure}
+
+\subsection{{\tt OSA}}
+\label{{\tt OSA}}
+
+As we are introducing a new analysis software in this work, we want to compare it to the existing analysis software, to check if the results are in agreement.
+We shortly summarize the official analysis tools for GRB analysis, which are part of the INTEGRAL Offline Scientific Analysis ({\tt OSA}) software \citep{osa}.
+
+Analyzing GRB data from SPI with the {\tt OSA} tools is a multistep process.
+The first steps cover selecting the science window containing the GRB, the time intervals for active time and background time as well as the energy bins for the analysis.
+After that one can either find the location of the GRB with SPIROS, i.e.
+an iterative source removal algorithm for SPI data, or set it manually if it is already known.
+The next steps concern the spectral fitting, which is done in another two-step procedure.
+
+The first step in the spectral fitting with {\tt OSA} is to use only the photo peak response of the detectors.
+These responses depend on the source position, as this defines for example the absorption by the mask.
+With these responses and the measured data in the individual SPI detectors, taking into account the different background rates, a photon flux is fitted individually per energy channel.
+These pseudo photon fluxes are not the final result, as up to this point energy dispersion and detector energy resolution was not accounted for.
+The pseudo photon flux data points are fitted with a spectral photon flux model and a correction response, that is also available through {\tt OSA}.
+This correction response depends on the energy bins that are used and should account for energy dispersion.
+In this step the energy channels are fitted simultaneously, as it is impossible to incorporate energy dispersion in a way that fits every energy channel individually.
+This fitting can be done in different spectral fitting software, like {\tt XSPEC} or {\tt 3ML}.
+
+\subsection{{\tt PySPI}}
 \label{pyspi}
-To fit the SPI data of GRBs, we developed a new python package PySPI \citep{joss}, which is an open source analysis tool.
-In the following we will summarize the main points of GRB analysis within PySPI.
+To fit SPI GRB data, we developed a new python package {\tt PySPI} \citep{joss}, which is an open source analysis tool.
+In the following we will summarize the main points of GRB analysis within {\tt PySPI}.
 
-\subsubsection*{Background}
+\subsubsection{Background}
 
-GRBs are transient sources with a typical duration only up to a few tens of seconds.
-Therefore we can use the time intervals during a science window, when the transient source is not active, as an independent temporal off-source observation (see Fig.
+GRBs are transient sources with a typical duration of up to a few tens of seconds.
+Therefore we can use the time intervals during a pointed observation, when the transient source is not active, as an independent temporal off-source observation (see Fig.
 \ref{fig:lightcurve}).
-Similar to other instruments, that use spatially off-source observation as an independent background measurement.
-From the background observations we construct the probability of the background model rates per energy channel from a poisson distribution, like given in Eq.
-\ref{eq:poisson_bkg}, where $b_{i}$ are the background rates per energy channel, $B_{i}$ are the detected counts in the off-source observation and $t_{b}$ is the exposure of the off-source observation.
+This approach is similar to what is done with other instruments, that use spatially off-source observations as an independent background measurements.
+The probability distribution for the background model rates per energy channel are given by the background observation being a Poisson process
+%From the background observations we construct the probability of the background model rates per energy channel from a Poisson distribution, like given in Eq.
+\ref{eq:poisson_bkg}, where $b_{\mathrm{i}}$ are the background rates per energy channel, $B_{\mathrm{i}}$ are the detected counts in the off-source observation and $t_{\mathrm{b}}$ is the exposure of the off-source observation.
 \begin{equation}
-	L(b_{i}|B_{i}, t_{b})=\frac{(t_{b} b_{i})^{B_{i}}}{B_{i}!}\cdot e^{-t_{b} b_{i}}
+	\mathcal{L}(b_{\mathrm{i}}|B_{\mathrm{i}}, t_{\mathrm{b}})=\frac{(t_{\mathrm{b}} b_{\mathrm{i}})^{B_{\mathrm{i}}}}{B_{\mathrm{i}}!}\cdot e^{-t_{\mathrm{b}} b_{\mathrm{i}}},
   \label{eq:poisson_bkg}
 \end{equation}
-This expression will be used in the next paragraph to derive the total likelihood.
-
+where $b_{\mathrm{i}}$ are the background rates per energy channel, $B_{\mathrm{i}}$ are the detected counts in the off-source observation and $t_{\mathrm{b}}$ is the exposure of the off-source observation.
 \begin{figure}
@@
 
-\subsubsection*{Likelihood}
+\subsubsection{Likelihood}
 
-With the defined background treatment, we can construct a Poisson likelihood with a Poisson measurement of background, like given in Eq.
-\ref{eq:likelihood_m_and_b}.
-Here $\theta$ summarizes all the parameters of the model, $D_{i}$ are the measured counts in the selected active time interval of the transient source, $m_{i}(\theta)$ are the predicted counts from the model evaluated at the parameters $\theta$ and $t_{d}$ is the exposure of the selected active time interval.
+With the defined background distributions, we can construct a likelihood, given by Eq.
+\ref{eq:likelihood_m_and_b}, that connects the source and background model with the Poisson process data of the background and active time interval, via the response.
+Here $\vec{\theta}$ summarizes all the parameters of the source model, $D_{\mathrm{i}}$ are the measured counts in the selected active time interval of the transient source, $m_{\mathrm{i}}(\vec{\theta})$ are the predicted counts from the model evaluated at the parameters $\vec{\theta}$ and $t_{\mathrm{d}}$ is the exposure of the selected active time interval.
 
 \begin{multline}
-	L(\theta, b_{i}|D_{i}, B_{i},t_{d},t_{b}) = \frac{(t_{d}(m_{i}(\theta)+ b_{i}))^{D_{i}}}{D_{i}!}\cdot \\
-  e^{-t_{d}(m_{i}(\theta)+b_{i})}\frac{(t_{b} b_{i})^{B_{i}}}{B_{i}!} e^{-t_{b} b_{i}}
+	\mathcal{L}(\vec{\theta}, b_{\mathrm{i}}|D_{\mathrm{i}}, B_{\mathrm{i}},t_{\mathrm{d}},t_{\mathrm{b}}) = \frac{(t_{\mathrm{d}}(m_{\mathrm{i}}(\vec{\theta})+ b_{\mathrm{i}}))^{D_{\mathrm{i}}}}{D_{\mathrm{i}}!}\cdot \\
+  e^{-t_{\mathrm{d}}(m_{\mathrm{i}}(\vec{\theta})+b_{\mathrm{i}})}\frac{(t_{\mathrm{b}} b_{\mathrm{i}})^{B_{\mathrm{i}}}}{B_{\mathrm{i}}!} e^{-t_{\mathrm{b}} b_{\mathrm{i}}}
   \label{eq:likelihood_m_and_b}
@@
 
-Now we can marginalize over the parameters $b_{i}$, that we are not interested in and that we have no further information about a priori, despite the fact that they can not be negative, which leaves us with Eq.
+If we would have a spectral model for the background, we would fit the background and the source model at the same time with the likelihood given in Eq.
+\ref{eq:likelihood_m_and_b}, but we do not have such a model for the SPI background.
+The background in SPI is dominated by the interaction of cosmic rays in the satellite material, which produces e.g.
+nuclear de-excitation line emission \citep{spi_bkg}.
+Therefore the background consists of several hundred different atomic lines \citep{spi_bkg}, which makes an accurate spectral model for the background impossible at the moment.
+But we can marginalize over the parameters $b_{\mathrm{i}}$ using only the fact that they can not be negative, which leaves us with Eq.
 \ref{eq:likelihood_marg}.
@@
 \begin{multline}
-	L(\theta|D_{i}, B_{i},t_{d},t_{b}) = \int_{0}^{\infty}\textrm{db}_{i}\frac{(t_{d}(m_{i}(\theta)+ b_{i}))^{D_{i}}}{D_{i}!}\cdot\\
-  e^{-t_{d}(m_{i}(\theta)+b_{i})} \frac{(t_{b} b_{i})^{B_{i}}}{B_{i}!} e^{-t_{b}b_{i}}
+	L(\vec{\theta}|D_{\mathrm{i}}, B_{\mathrm{i}},t_{\mathrm{d}},t_{\mathrm{b}}) = \int_{0}^{\infty}\textrm{db}_{\mathrm{i}}\frac{(t_{\mathrm{d}}(m_{\mathrm{i}}(\vec{\theta})+ b_{\mathrm{i}}))^{D_{\mathrm{i}}}}{D_{\mathrm{i}}!}\cdot\\
+  e^{-t_{\mathrm{d}}(m_{\mathrm{i}}(\vec{\theta})+b_{\mathrm{i}})} \frac{(t_{\mathrm{b}} b_{\mathrm{i}})^{B_{\mathrm{i}}}}{B_{\mathrm{i}}!} e^{-t_{\mathrm{b}}b_{\mathrm{i}}}
   \label{eq:likelihood_marg}
@@
 
-Because there is no easy analytical solution for this integral, one often uses a so-called profiled likelihood as an approximation.
-For the profiled likelihood we use the fact, that the derivative of the likelihood at its maximum is zero.
-Therefore one can construct from $\frac{\textrm{dL}}{\textrm{db}_i}=0$ the background rates $b_{i, max}$ that maximize the likelihood for a given model $m_{i}(\theta)$ and observed quantities.
-Solving $\frac{\textrm{dL}}{\textrm{db}_i}=0$ for b gives Eq.
-\ref{eq:bmax}.
+The marginalisation is equivalent to integrating out the background rate parameter assuming a uniform prior from 0 to $\infty$.
+Because solving this integral is computationally expensive, we use a profile likelihood as an auxiliary but still statistically sound figure of merit.
+For the profile likelihood we use the fact, that the derivative of the likelihood at its maximum is zero ($\frac{\textrm{dL}}{\textrm{db}_i}=0$).
+This defines the background rates $b_\mathrm{{i, max}}$ (see Eq.
+\ref{eq:bmax}) that maximize the likelihood for a given model $m_{\mathrm{i}}(\vec{\theta})$ and observed quantities.
 \begin{multline}
-	b_{i,max}(\theta)=\frac{1}{2(t_{b}+t_{d})}(B_{i}+D_{i}-m_{i}(\theta)(t_{b}+t_{d})+\\
-  \sqrt{(B_{i}+D_{i}+m_{i}(\theta)(t_{b}+t_{d}))^{2}-4m_{i}(\theta)D_{i}(t_{d}-t_{b})}
+	b_{\mathrm{i,max}}(\vec{\theta})=\frac{1}{2(t_{\mathrm{b}}+t_{\mathrm{d}})}(B_{\mathrm{i}}+D_{\mathrm{i}}-m_{\mathrm{i}}(\vec{\theta})(t_{\mathrm{b}}+t_{\mathrm{d}})+\\
+  \sqrt{(B_{\mathrm{i}}+D_{\mathrm{i}}+m_{\mathrm{i}}(\vec{\theta})(t_{\mathrm{b}}+t_{\mathrm{d}}))^{2}-4m_{\mathrm{i}}(\vec{\theta})D_{\mathrm{i}}(t_{\mathrm{d}}-t_{\mathrm{b}})}.
   \label{eq:bmax}
@@
 
-These values can then be substituted in the likelihood Eq.
-\ref{eq:likelihood_m_and_b} to eliminate the $b_{i}$ dependency.
-This approximation gives the exact solution for the maximum of the likelihood, for likelihood values close to the maximum, the assumption is that most of the likelihood in the integrand in Eq.
-\ref{eq:likelihood_marg} is in a small area around $b_{i,max}$.
-This assumption is used in many spectral analyses and works very well as long as one does not have too few counts in the background observation \footnote{For a derivation see https://giacomov.github.io/Bias-in-profile-poisson-likelihood/}.
+These values are then substituted into the likelihood Eq.
+\ref{eq:likelihood_m_and_b} to eliminate the $b_{\mathrm{i}}$ dependency.
+This gives the exact solution for the maximum of the likelihood, for likelihood values close to the maximum, the assumption is that most of the likelihood in the integrand in Eq.
+\ref{eq:likelihood_marg} is in a small area around $b_{\mathrm{i,max}}$.
+This profile likelihood method is used in many spectral analysis works \citep[e.g.][]{profile2, profile1} and is also available in {\tt XSPEC} \citep{xspec} as cstat and pgstat.
+%\footnote{https://heasarc.gsfc.nasa.gov/xanadu/xspec/manual/XSappendixStatistics.html}.
+%and works very well as long as one does not have too few counts in the background observation \footnote{For a derivation see https://giacomov.github.io/Bias-in-profile-poisson-likelihood/}.
 
-\subsubsection*{Response}
+\subsubsection{Response}
 
-To convert a physical spectrum to a detected count spectrum, we need the response for a given source position.
-The response encapsulates all the information about the probability of a photon with a certain energy and origin to be detected in a certain energy channel of the detector.
-This includes for example information about partial energy deposition of the photon in the crystal and the process that transforms the deposited energy into an electronic signal, that is measured in the end.
-% distribution of how much energy a photon with a certain energy deposit in the crystal and what energy is in the end measured for this deposited energy.
-In PySPI we use the official response files for Image Response Functions (IRFs) and Redistribution Matrix Files (RMFs) derived by \citet{spi_response}.
-The IRF files give the total effective area for three different interaction types:
+In {\tt PySPI}, we use the official response files, like described in Sec.
+\ref{response}, interpolate them to the wanted energy bins and source positions and construct one response matrix incorporating all the information about the effective areas and energy redistribution.
+
+\subsubsection{Electronic Noise}
+
+In {\tt PySPI}, one can select the energy range in which only the PSD events should be used to avoid including spurious events (See Sec.
+\ref{electronic}).
+To account for the larger dead time of the PSD electronics, an effective area correction can be either fixed to 85 \% \citep{spi_electronic_noise} or treated as a free parameter of the model.
+
+\subsubsection{General Procedure}
+
+Every Ge detector is treated as an independent detector unit. The workflow during a fit step is a forward folding method:
 \begin{itemize}
-  \item Photo peak events
-  \item Non photo peak events that first interact in the crystal
-  \item Non photo peak events that first interact in passive material
+  \item sample model parameters
+  \item calculate model flux and responses individually for all detectors for the given source position
+  \item fold model with responses to get predicted model counts in all detectors
+  \item calculate log-likelihood for all detectors
+  \item sum these log-likelihoods to get the total log-likelihood of the SPI data for the given model parameters
 \end{itemize}
-\noindent
-These effective areas were simulated for 51 photon energies and on a 0.5 degree grid.
-For each of the three interaction type, there is one RMF, to define the shape of the redistributed spectra, assuming that this shape does not depend on the detector or the incident angles of the photons.
-The procedure to construct the response includes several simplification to keep the computational costs and storage space manageable \citep{spi_response}.
-This could of course affect every analysis done with SPI.
-Re-simulating the response without these simplifications could improve the scientific output of SPI, but would take a hugh amount of computational time, even today.
+%A sampling algorithm like MultiNest \citep{multinest} is used to iterate this procedure, in order to determine the posterior distributions.\\
 
-In PySPI we then interpolate the official response files to the user defined energy bins and source positions.
+The BALROG (BAyesian Lo-cation Reconstruction Of GRBs) algorithm to localize GRBs with Fermi/GBM uses the same method \citep{balrog}, which shows that forward folding allows to localize with a non imaging instrument, like GBM.
+It is important to note, that for example the instruments SPI and GBM are fundamentally very similar.
+They both consist of individual detectors that have different responses for a given source position.
+In GBM this is due to the different pointing directions of the detectors and in SPI due to the different occultations by the mask.
+Even though SPI is defined as a coded mask instrument, we don't have to treat it specially.
+The information the mask encodes into the data is automatically included by using the different responses for the detectors and a forward folding method.
 
-\subsubsection*{Electronic Noise}
+\subsubsection{Software Interface}
 
-Since shortly after the start of INTEGRAL, it is known that there are spurious events in the SPI data around 1.5 MeV.
-According to \citet{spi_electronic_noise} these spurious events are photons with small energy (<100 keV) that get detected at a higher energy due to saturation of the Analog Front-End Electronics (AFEE) electronics by previous high energy deposition.
-It is also known, that these spurious events do not show up if one looks only at events with a detection also in the Pulse Shape Discriminator (PSD) electronics.
-The reason for this is that the PSD electronics has a low energy threshold of roughly 450 keV (the exact value has been changed a few times during the mission).
-Therefore only events that deposit more than this low energy threshold in the Germanium crystal can trigger this electronic, which eliminates the <100 keV events that are detected at the wrong energies by the AFEE electronics.
-In Fig.
-\ref{fig:electronic} one can see that the feature at 1.5 MeV is nicely visible in the non-PSD events but is missing in the PSD events.
-Even though this problem is most significant in the area around 1.5 MeV it is also important at lower energies >400 keV.
-In PySPI one can select the energy range in which only the PSD events should be used, to avoid including spurious events.
-To account for the larger dead time of the PSD electronics, an effective area correction can be either fix to 85 \% \citep{spi_electronic_noise} or treated as a free parameter in the fit.
+{\tt PySPI} constructs a plugin for the Multi-Mission Maximum Likelihood framework \citep[3ML][]{3ML}.
+This allows to fit the SPI data together with the data from other instruments, such as Fermi/GBM\footnote{See threeml.readthedocs.io}.
+Also {\tt PySPI} is an open source software, which is publicly available on GitHub \citep{joss} and there is a documentation, with a few examples\footnote{See pyspi.readthedocs.io}.
 
-\begin{figure}
-    \begin{centering}
-        \includegraphics{figures/electronic_noise.pdf}
-        \caption{Count spectrum for detector 0 integrated over 1000 seconds.
-The Non-PSD event count spectrum is drawn in purple and the PSD events in grey.
-One can clearly see the feature in the Non-PSD events at 1.5 MeV (green shaded area) that is not visible in the PSD events.}
-        \label{fig:electronic}
-    \end{centering}
-\end{figure}
+\section{Physical Synchrotron Model}
+\label{synch}
+We use {\tt pynchrotron}\footnote{https://github.com/grburgess/pynchrotron} to calculate the spectrum from a physical spectral synchrotron model.
+This model was previously used to successfully fit many single pulse GRBs observed with GBM in \citet{synch}, which also includes a detailed description of the model.
+Here we summarize the main points briefly.
 
-\subsubsection*{General Procedure}
-
-In PySPI every Germanium detector is treated as an independent detector. The workflow during a fit step is the following:
-\begin{itemize}
-  \item Sample model parameters
-  \item Calculate model flux and responses individually for all detectors for the source position
-  \item Fold model with responses to get predicted model counts in all detectors
-  \item Calculate log-likelihood for all detectors
-  \item Sum these log-likelihoods to get the total log-likelihood of the SPI data for the given model parameters
-\end{itemize}
-A sampling algorithm like MultiNest \citep{multinest} is used to iterate this procedure, in order to determine the posterior distributions.\\
-This workflow is very similar, like for example for GBM, because fundamentally instruments like SPI and GBM are very similar.
-They both consist of individual detectors that have different responses for a given source position.
-In GBM this is due to the different pointing directions of the detectors and in SPI due to the different occultation by the mask.
-Therefore there is no reason to treat SPI specially, just because it is a coded mask instrument.
-The information the mask encodes into the data is automatically included by using the different responses for the detectors.
-
-\subsubsection*{3ML plugin}
-
-PySPI can construct a plugin for the Multi-Mission Maximum Likelihood framework (3ML) \citep{3ML}.
-This allows, without any further work, to fit the SPI data together with the data from other instruments, like Fermi/GBM.
-\footnote{For more information about 3ML see threeml.readthedocs.io/}
-
-\subsubsection*{Open Source Software}
-
-PySPI is an open source software, which is publicly available on GitHub \citep{joss}.
-There is also a documentation, that shows how to use it.
-\footnote{For more information about PySPI see pyspi.readthedocs.io/}
-
-\subsection{OSA}
-\label{OSA}
-
-As we are introducing a new analysis software in this work, we want to compare it to the existing analysis software, to check if the results are in agreement.
-We shortly summarize the official analysis tools for GRB analysis, which are part of the INTEGRAL Offline Scientific Analysis (OSA) software.
-\citep{osa}
-
-Analyzing GRB data from SPI with the OSA tools is a multistep process.
-The first steps are basic and cover selecting the science window with the GRB, the time intervals for active time and background time as well as the energy bins for the analysis.
-After that one can either find the location of the GRB with SPIROS, i.e.
-an iterative source removal algorithm for SPI data, or set it manually, if it is already known.
-The next steps concern the spectral fitting, which is done in another two-step procedure, which will be called 'Photo Peak Fitting' and 'Energy Redistribution Fitting' hereafter.
-
-\subsubsection*{Photo Peak Fitting}
-
-The first step in the spectral fitting with OSA is to use only the photo peak response of the detectors.
-These responses depend on the source position, as this defines for example the absorption by the mask.
-With these responses and the measured data in the individual SPI detectors, taking into account the different background rates, a photon flux is fitted individually per energy channel.
-These pseudo photon fluxes are not the final result, as up to this point energy dispersion and detector energy resolution was ignored.
-
-\subsubsection*{Energy Redistribution Fitting}
-
-The pseudo photon flux data points from the 'Photo Peak Fitting' step, which are no real data points anymore, are fitted with a spectral photon flux model which is convolved with a correction response, which is also available through OSA.
-This correction response depends on the energy bins that are used and should account for energy dispersion.
-In this step the energy channels are fitted simultaneously, as it is impossible to incorporate energy dispersion in a way that fits every energy channel individually.
-This fitting can be done in different spectral fitting software.
-
-\subsection{Synchrotron Model}
-\label{synch}
-We use pynchrotron to calculate the spectrum from a physical, time dependent spectral synchrotron model.
-This model was previously used to successfully fit many single pulse GRBs with GBM in \citet{synch}, which also includes a detailed description of the model.
-Here we only want to summarize the main points shortly.
-
-The core of the model is the assumption of some generic acceleration mechanism, that constantly produces an electron spectrum with a power law shape $N(\gamma )\propto \gamma^{-p}$ between $\gamma_{inj}$ and $\gamma_{max}$.
-These electrons are cooled via synchrotron cooling in a magnetic field and produce radiation in this process.
+The core of the model is the assumption of some generic acceleration mechanism, that constantly accelerates an electron spectrum into a power law $N(\gamma )\propto \gamma^{-p}$ between $\gamma_{\textrm{inj}}$ and $\gamma_{\textrm{max}}$.
+These electrons are cooled via the emission of synchrotron photons in a magnetic field.
 The resulting photon spectrum is the sum of the photon spectra at every time step in the cooling process and is defined by five quantities:
@@
   \item Slope of the injected electron spectrum $p$
-  \item Lower boundary of the injected electron spectrum $\gamma_{inj}$
-  \item Upper boundary of the injected electron spectrum $\gamma_{max}$
-  \item Characteristic Lorentz factor the electrons cool to $\gamma_{cool}$
+  \item Lower boundary of the injected electron spectrum $\gamma_{\mathrm{inj}}$
+  \item Upper boundary of the injected electron spectrum $\gamma_{\mathrm{max}}$
+  \item Characteristic Lorentz factor the electrons cool to $\gamma_{\mathrm{cool}}$
 \end{enumerate}
 
-There exists a strong degeneracy between $B$ and $\gamma_{inj}$, as their combination sets the peak of the photon spectrum.
-Therefore one usually fixes $\gamma_{inj}=10^{5}$ and only fits for $B$.
-It is important to keep in mind, that the results for $\gamma_{max}$ and $\gamma_{cool}$ are determined relative to the fixed $\gamma_{inj}$.
+There exists a strong degeneracy between $B$ and $\gamma_{\mathrm{inj}}$, as their combination sets the peak of the photon spectrum.
+Therefore we fix $\gamma_{\mathrm{inj}}=10^{5}$ and only fits for $B$.
+Thus the results for $\gamma_{\mathrm{max}}$ and $\gamma_{\mathrm{cool}}$ are determined relative to the fixed $\gamma_{\mathrm{inj}}$.
 
-\subsection{Model Checking}
+\section{Model Checking}
 \label{PPC}
 To check if the fit of a model is a good description of the measured data is a very complicated topic and highly debated in the statistics community.
-Measurements like reduced $\chi^{2}$ use many assumptions, like for example that all the probability distributions in the problem are described as normal distributions, which is not the case here, as the measurement process is a Poisson process.
+Measurements like reduced $\chi^{2}$ use many assumptions, like for example that all the probability distributions in the problem are described as normal distributions \citep{dosanddonts}.
+This is not the case here, as the measurement process is a Poisson process.
 Therefore we decided to use Posterior Predictive Checks (PPC) and Quantile-Quantile (QQ) plots.
-For the PPCs one simulate new data from the full posterior of the fit as well as the measurement process (see Eq.
-\ref{eq:ppc}) and compare them to the observed data.
-QQ plots use the same simualtion process, but instead of comparing the observed data of every energy channel individually to the simulated data, one compares the cumulative counts of the observation and the simulations over energy channels.
+
+For the PPCs one simulates new data from the full posterior of the fit as well as the measurement process (see Eq.
+\ref{eq:ppc}) and compares them to the observed data \citep{ppc}.
+QQ plots use the same simulation process, but instead of comparing the observed data of every energy channel individually to the simulated data, one compares the cumulative counts of the observation and the simulations over energy channels  \citep{QQ}.
 QQ plots are very sensitive to weak systematic deviations of the model from the data.
-\citep{QQ,ppc}
 
 \begin{equation}
-  \textrm{P}(y^{\textrm{sim}}|y^{\textrm{obs}}) = \int \textrm{P}(y^{\textrm{sim}}|\theta) \textrm{P}(\theta|y^{\textrm{obs}}) \mathrm{d}\theta
+  \textrm{P}(y^{\textrm{sim}}|y^{\textrm{obs}}) = \int \textrm{P}(y^{\textrm{sim}}|\vec{\theta}) \textrm{P}(\vec{\theta}|y^{\textrm{obs}}) \mathrm{d}\vec{\theta}
   \label{eq:ppc}
@@
 \noindent
-Here $y^{\textrm{obs}}$ are the observed data, $\textrm{P}(\theta|y^{\textrm{obs}})$ is the posterior distribution of the model parameters $\theta$ given the observed data, $\textrm{P}(y^{\textrm{sim}}|\theta)$ is the probability of new data given the parameters of the model and $y^{\textrm{sim}}$ are the simulated data.
+Here $y^{\textrm{obs}}$ are the observed data, $\textrm{P}(\vec{\theta}|y^{\textrm{obs}})$ is the posterior distribution of the model parameters $\vec{\theta}$ given the observed data, $\textrm{P}(y^{\textrm{sim}}|\vec{\theta})$ is the probability of new data given the parameters of the model and $y^{\textrm{sim}}$ are the simulated data.
 %These simulated data are then compared to the observed data and allow for a visual check, whether the posterior distributions of the fit together with the measuring process can reproduce the data.
+
 \section{Analysis}
-
-In this work we analyze GRB 120711A, which was a bright, multi pulse GRB with a precursor and a long emission period of $\approx$100 seconds.
-It was detected with SPI and GBM.
-We only look at one time slice with a duration of 10 seconds around the highest peak in the light curves (see Fig.
+\label{analysis}
+In this work, we analyze GRB 120711A, which was a bright, multi-pulse GRB with a precursor and a long emission period of $\approx$100 s.
+It was detected by SPI, GBM and Swift-XRT \citep{GCN_integral, GCN_gbm, GCN_swift}.
+We look at one time interval with a duration of 10 seconds around the first peak in the light curve (see Fig.
 \ref{fig:time_selection}).
+From the XRT detection we know the position of the GRB (RA: 94.68 °, DEC: -71.00 ° in J2000).
 
@@
 
-We analyze the data from the two instruments independently first with the empirical Band function, to check if the results for SPI and GBM are in agreement as well as show a comparison between the fit results with PySPI and the official software tools for GRB analysis within OSA.
-Then we fit the SPI and GBM data simultaneously with a physical synchrotron model, and show that it can reduce the allowed parameter space significantly, compared to the individual fits.
-For all GBM and PySPI fits we added effective area correction parameters in the fit, allowing the total effective area of the individual detectors to vary a bit with respect to each other, to account for slightly different calibrations.
-To do this, we always fix the response of one of the detectors to the official response of that detectors and fit one parameter for every other detector, which gets multiplied with the response in the fit.
+First, we fit the data with the empirical Band function.
+With this we show a comparison between the fit results with {\tt PySPI} and the official software tools for GRB analysis using {\tt OSA} (Sec.
+\ref{pyspi_osa}) and check if the results for SPI and GBM are in agreement (Sec.
+\ref{pyspi_gbm}).
+Then, we fit the SPI and GBM data simultaneously with a physical synchrotron model, to check wether including SPI in the analysis can reduce the allowed parameter space (Sec.
+\ref{pyspi_gbm_joined}).
+
+%We analyze the data from the two instruments independently first with the empirical Band function, to check if the results for SPI and GBM are in agreement as well as show a comparison between the fit results with {\tt PySPI} and the official software tools for GRB analysis within {\tt OSA}.
+Then, we fit the SPI and GBM data simultaneously with a physical synchrotron model, and show that it can reduce the allowed parameter space significantly, compared to the individual fits.
+For all GBM and {\tt PySPI} fits we added effective area correction parameters in the fit, allowing the total effective area of the individual detectors to vary with respect to each other, to account for slightly different calibrations.
+To do this, we fix the response of one of the detectors to the response of that detector and fit one parameter for every other detector.
 We constrain the effective area correction parameters to be between 0.7 and 1.3.
 
-All the fits in this section are done with 3ML \citep{3ML} and the Bayesian sampling algorithm MultiNest \citep{multinest} to create full posterior distributions of the parameters.
-To visualize the posterior distribution we use ChainConsumer \citep{chainconsumer} with the output from MultiNest to create corner plots.
+All the fits utilize 3ML \citep{3ML} and the Bayesian sampling algorithm MultiNest \citep{multinest} to create posterior distributions of the parameters.
+%To visualize the posterior distribution we use ChainConsumer \citep{chainconsumer} with the output from MultiNest to create corner plots.
 
-\subsection{Compare PySPI and OSA}
-
-We analyze the SPI data with a band function as spectral model for the same time interval with PySPI and OSA, to check if the results are in agreement.
-The two methods are described in \ref{OSA} and \ref{pyspi}.
+\subsection{Compare {\tt PySPI} and {\tt OSA}}
+\label{pyspi_osa}
+We analyze the SPI data with a band function as a spectral model for the same time interval with {\tt PySPI} and {\tt OSA}, to check if the results are in agreement.
 Fig.
-\ref{fig:corner_osa_pyspi_band} shows the resulting posterior distributions of the fits, displayed as a corner plot.
-The results for the spectral shape from the two analysis techniques agree within their uncertainty region, but PySPI can constrain the parameters more precise.
+\ref{fig:corner_osa_pyspi_band} shows the resulting posterior distributions of the fits.
+The results for the spectral shape from the two analysis techniques agree within their uncertainty regions, but {\tt PySPI} can constrain the parameters more precise.
 
@@
     \includegraphics[width=1\linewidth]{figures/pyspi_vs_osa_band.pdf}
-    \caption{Corner plot for the SPI fit with PySPI and the official tools.
+    \caption{Corner plot for the SPI fit with {\tt PySPI} and the official tools.
 The spectral model in this fit is a Band function.
-It shows, that the results are in agreement, but PySPI can constrain the parameters better.}
+The results are in agreement, however {\tt PySPI} constrains the parameters better.}
     \label{fig:corner_osa_pyspi_band}
+  \end{centering}
+\end{figure}
+\begin{figure}
+  \begin{centering}
+    \includegraphics[width=1\linewidth]{figures/pyspi_vs_gbm_band.pdf}
+    \caption{Corner plot for the SPI fit with {\tt PySPI} and the GBM fit.
+In this fit we used a Band function as spectral model.
+The spectral shape for the SPI and GBM fits coincide within their uncertainty regions and the normalization is off by $\approx$10\%.}
+    \label{fig:corner_gbm_pyspi_band}
   \end{centering}
@@
 \subsection{Compare SPI and GBM}
-
-Next, we analyze the SPI data with PySPI and the GBM data with the GRB analysis within 3ML for a band function model.
+\label{pyspi_gbm}
+Next, we analyze SPI data with {\tt PySPI} and the GBM data with the GRB analysis within 3ML with a Band function model.
 Fig.
-\ref{fig:corner_gbm_pyspi_band} displays the corner plots for these fits, demonstrating that the results for the spectral shape from SPI and GBM are in agreement.
-It also shows that the calibration for SPI and GBM are well aligned within only $\approx$ 10\% difference in this case.
-
-\begin{figure}
-  \begin{centering}
-    \includegraphics[width=1\linewidth]{figures/pyspi_vs_gbm_band.pdf}
-    \caption{Corner plot for the SPI fit with PySPI and the GBM fit.
-In this fit we used a Band function as spectral model.
-The spectral shape for the SPI and GBM fits coincide within their uncertainty regions and the normalization is off by $\approx$10\%, which is within the usual calibration offsets of Gamma-Ray space telescopes.}
-    \label{fig:corner_gbm_pyspi_band}
-  \end{centering}
-\end{figure}
+\ref{fig:corner_gbm_pyspi_band} shows the results for these fits, demonstrating that the results for the spectral shape from SPI and GBM are in agreement.
+It also shows that the calibration for SPI and GBM are well aligned within only $\approx$ 10\% difference in this case, which is within the usual calibration offsets of gamma-ray space telescopes..
 
 \subsection{Joint Fit of SPI and GBM}
-
-The final analysis is a joint fit for the SPI and the GBM data with a physical synchrotron model (see \ref{synch}).
+\label{pyspi_gbm_joined}
+We perform a a joint fit of SPI and GBM data with a physical synchrotron model (see \ref{synch}).
 Fig.
@@
 The posterior distribution of the parameters from the GBM and the SPI fit agree within their uncertainty regions and the combined fit reduces the allowed parameter space.
-The physical synchrotron model was able to fit the data of GBM and SPI well, which is shown with PPC and QQ plots in \ref{appendix}.
+The physical synchrotron model was able to fit the data of GBM and SPI well, which is shown with PPC and QQ plots in Appendix \ref{appendix}.
 
@@
     \includegraphics[width=1\linewidth]{figures/pyspi_and_gbm_syn.pdf}
-    \caption{Corner plot for the SPI fit with PySPI and the GBM fit.
+    \caption{Corner plot for the SPI fit with {\tt PySPI} and the GBM fit.
 In this fit we used a physical synchrotron model (see \ref{synch}) as spectral model.
@@
 \section{Conclusion}
+\label{conclusion}
+In this paper we have presented a new analysis method for GRBs detected by INTEGRAL/SPI and the software package utilizing this method ({\tt PySPI}).
+To show that it improves the analysis of GRBs detected by SPI, we have analyzed the data of GRB120711A with the data from INTGRAL/SPI and Fermi/GBM.
+The results for SPI with {\tt PySPI} are in agreement with those from the official analysis software, but more constraining.
+Also the resulting spectral shape for the fits with GBM and SPI data are in agreement and the relative calibration difference between SPI and GBM we conclude from the fits, is $\approx$ 10\% or less.
+We show that the GBM as well as the SPI data for GRB120711A can be fitted well with a physical synchrotron model and that combining the data in a simultaneous fit improves the parameter constrains.
+Consequently, SPI can play an important role in physical GRB model checking, if we apply a forward modelling method which is used in {\tt PySPI}, as described in Sec.
+\ref{pyspi}.
 
-We analyzed the data of GRB120711A with the data from INTGRAL/SPI and Fermi/GBM.
-The results for SPI with PySPI are in agreement with those from the official analysis software, but more constraining.
-Also the resulting spectral shape for the fits with GBM and SPI data are in agreement and the relative calibration difference between SPI and GBM we conclude from the fits, is $\approx$ 10\% or less.
-We show that the GBM as well as the SPI data for GRB120711A can be fitted well with a physical, time dependent synchrotron model and that combining the data in a simultaneous fit improves the parameter constrains.
+The next steps will be the analysis of all GRBs detected by SPI with different physical models and {\tt PySPI}, to check if some of these models can be rejected with the SPI data.
+This will be covered in a future work.
+%Generally {\tt PySPI} can improve the scientific output from SPI for GRBs significantly.
+Due to a new analysis method, that folds the source model directly into the data space of every SPI detector with the full response of the individual detectors, the results are more constraining than the results with the official analysis software.
 
-Generally PySPI can improve the scientific output from SPI for GRBs significantly.
-Due to a new analysis method, that folds the source model directly into the data space of every SPI detector with the full response of the individual detectors, the results are more constraining than the results with the official analysis software.
+\section*{Software}
+
+{\tt 3ML} \citep{3ML}, {\tt Astromodels} \citep{astromodels}, {\tt Matplotlib} \citep{matplotlib}, {\tt ChainConsumer} \citep{chainconsumer}, {\tt OSA} \citep{osa}, {\tt Numpy} \citep{numpy}, {\tt MultiNest} \citep{multinest1, multinest2, multinest3}
 
@@
 In the PPC plots the grey curve is the detected count spectrum and in the QQ plots the expected 1:1 relation between the cumulative model and observed counts.
-  \begin{figure}[h]
+  \begin{figure*}[h]
     \begin{centering}
@@
     \end{centering}
-  \end{figure}
-  \begin{figure}[h]
+  \end{figure*}
+  \begin{figure*}[h]
     \begin{centering}
@@
     \end{centering}
-  \end{figure}
-  \begin{figure}[h]9
+  \end{figure*}
+  \begin{figure*}[h]9
     \begin{centering}
@@
     \end{centering}
-  \end{figure}
+  \end{figure*}
 \end{appendix}

### 2022-01-20 src/ms.tex
fix
fix try
final version

@@
 % Define document class
-\documentclass[twocolumn]{aa}
+\documentclass[twocolumn,traditabstract]{aa}
 
 % Filler text
-\usepackage{caption}
-\usepackage{subcaption}
+%\usepackage{caption}
+%\usepackage{subcaption}
 \usepackage{float}
+\usepackage[pdftex]{xcolor}
+\definecolor{citecolor}{HTML}{195D95}
+\definecolor{BrickRed}{HTML}{C41010}
+
+\def\mike#1{\textcolor{BrickRed}{jmb: \textbf{ #1}}}
+
 %\usepackage{natbib}
 % Begin!
+
 \begin{document}
@@
 % Title
-\title{Fitting Synchrotron Models to Gamma-Ray Burst Data from INTEGRAL/SPI}
+\title{Improving INTEGRAL/SPI data analysis of GRBs}
+
+\titlerunning{Improving INTEGRAL/SPI analysis for GRBs}
 
@@
 \author{
-  Björn Biltzinger \inst{1}
+  Björn Biltzinger\inst{1}
   \and
-  Jochen Greiner \inst{1}
+  Jochen Greiner\inst{1}
   \and
-  J. Michael Burgess \inst{1}
+  J. Michael Burgess\inst{1}
   \and
-  Thomas Siegert \inst{1,2}
+  Thomas Siegert\inst{1,2}
 }
 
-\institute{Max-Planck-Institut f\"ur extraterrestrische Physik, Giessenbachstra{\ss}e 1, D-85748 Garching, Germany \and Institut f\"ur Theoretische Physik und Astrophysik, Universit\"at W\"urzburg, Campus Hubland Nord, Emil-Fischer-Str.
-31, 97074 W\"urzburg, Germany }
+\institute{Max-Planck-Institut f\"ur extraterrestrische Physik, Giessenbachstra{\ss}e 1, D-85748 Garching, Germany
+\and Institut f\"ur Theoretische Physik und Astrophysik, Universit\"at W\"urzburg,  Emil-Fischer-Str. 31, 97074 W\"urzburg, Germany }
+
 \date{Received --; accepted --}
 
-\label{firstpage}
+%\label{firstpage}
 % Abstract with filler text
 \abstract{
-  In recent years it has been shown, that one has to fit physical models to Gamma-Ray Burst (GRB) data to obtain more insights into their emission mechanism.
-For the energy range between $\approx$ 10 keV to $\approx$ 10 MeV Fermi/GBM has been the main instrument to analyze GRBs in the last 15 years.
-In this paper we show how we can add INTEGRAL/SPI to this analysis.
-SPI covers a similar energy range and has a very good energy resolution of $\approx$ 0.2\% at 1.3 MeV compared to $\approx$ 10\% for GBM.
-Therefore it is an ideal instrument to measure precisely the curvature of the spectrum.
-We present {\tt PySPI}, a new analysis software that we developed to analyze GRB data from SPI.
-To demonstrate its usage and capabilities, we apply it to the GRB 120711A.
+INTEGRAL/SPI is a coded mask instrument observing in the keV to MeV energy range, which covers the peak of the $\nu F\nu$ spectrum of most Gamma-Ray Bursts (GRBs).
+For the energy range between $\approx$ 10 keV to $\approx$ 10 MeV, Fermi/GBM has been the primary instrument for analyzing GRBs over the last 15 years.
+Herein, we show that SPI, covering a similar energy range, can give equivalently constraining results if we use an advanced analysis method.
+Also, combining the data of both instruments reduces the allowed parameter space.
+The main advantage of SPI as compared to GBM is the energy resolution of $\approx$ 0.2\% at 1.3 MeV compared to $\approx$ 10\% for GBM.
+Therefore, it is an ideal instrument to precisely measure the curvature of the spectrum.
+This is important, as it has been shown in recent years that one has to fit physical models to GRB data to obtain more insights into their still unknown emission mechanism and the curvature of the peak is unique to the different physical models.
+To fit physical models to SPI GRB data and get the maximal amount of information from the data, we developed a new analysis software {\tt PySPI}.
+We apply these new techniques to GRB 120711A in order to validate and showcase {\tt PySPI}'s capabilities.
 We show that {\tt PySPI} improves the analysis of SPI GRB data compared to the official analysis software.
-In addition we demonstrate that the GBM and the SPI data of this GRB can be fitted well with a physical synchrotron model and that combining both, reduces the allowed parameter space.
-This evinces that SPI plays an important role in GRB model fitting.
+In addition, we demonstrate that the GBM and the SPI data of this GRB can be fitted well with a physical synchrotron model.
+This evinces that SPI can play an important role in GRB model fitting.
 }
 
-\keywords{ (stars:) gamma ray bursts -- methods: data analysis --
-  methods: statistical}
+%\abstract{In recent years it has been shown that one has to fit physical models to Gamma-Ray Burst (GRB) data to obtain more insights into their emission mechanism.
+For the energy range between $\approx$ 10 keV to $\approx$ 10 MeV, Fermi/GBM has been the main instrument to analyze GRBs in the last 15 years.
+Here, we show how to add INTEGRAL/SPI to this analysis.
+SPI covers a similar energy range and has a very good energy resolution of $\approx$ 0.2\% at 1.3 MeV compared to $\approx$ 10\% for GBM.
+Therefore, it is an ideal instrument to measure precisely the curvature of the spectrum.
+We present {\tt PySPI}, a new analysis software that we developed to analyze GRB data from SPI.
+To demonstrate its usage and capabilities, we apply it to GRB 120711A.
+We show that {\tt PySPI} improves the analysis of SPI GRB data compared to the official analysis software.
+In addition, we demonstrate that the GBM and the SPI data of this GRB can be fitted well with a  synchrotron model, and that combining both instruments reduces the allowed parameter space.
+This evinces that SPI can play an important role in GRB model fitting.}
+
+\keywords{ (stars:) gamma-ray bursts -- methods: data analysis -- methods: statistical}
 
@@
 
-Gamma-Ray Bursts (GRBs) are short transient bursts of $\gamma$-rays, with a typical active time range between a few ms and few hundred seconds for the prompt phase, which is mostly observed in $x$- and $\gamma$-rays.
-After the prompt emission, there is a long lasting afterglow phase when the ejecta interacts with the Inter Stellar Medium (ISM) \citep{afterglow}.
-GRBs are classified in two groups depending on the the duration of the prompt emission \citep{shortlong}.
-Long GRBs (prompt phase $\gtrapprox$ 2s) have been associated with the collapse of massive stars \citep{SN1, SN2}, whereas short GRBs are believed to be caused by mergers of compact objects, like neutron stars \citep{gw}.
-In both cases it is consensus, that the progenitor events of GRBs produce jetted relativistic outflows, which consists of several shells with different velocities, resulting in internal shell collisions \citep{gamma-ray-burst}.
+Gamma-Ray Bursts (GRBs) are short transient bursts of $X-$ and $\gamma$-rays \citep{Klebesadel+1973}, with a typical active time range between a few ms and few hundred seconds for the prompt phase.
+%which is mostly observed in $X$- and $\gamma$-rays.
+After the prompt emission, there is a long-lasting afterglow phase when the ejecta interact with the interstellar medium \citep{MeszarosRees1997, afterglow}.
+GRBs are classified into two groups depending on the duration of the prompt emission \citep{shortlong}.
+Long GRBs (prompt phase $\gtrapprox$ 2s) have been associated with the collapse of massive stars \citep{SN1, Hjorth+2003, SN2}, whereas short GRBs are  caused by mergers of compact objects, like neutron stars \citep{Eichler+1989, gw}.
+In both cases it is consensus, that the progenitor events of GRBs produce jetted relativistic outflows, which consists of several shells with different velocities, resulting in internal shell collisions \citep{ReesMeszaros1994, Mochkovitch+1995}.
+%\citep{gamma-ray-burst}. Edo Berger is an observer, and has never worked on shocks, so I (jcg) wouldn't cite this review
 
-It is still highly debated what the emission mechanism of the prompt emission is \citep[for a review see][]{gamma-ray-burst}.
-Two of the possible emission mechanism are synchrotron \citep[e.g.][]{syn_shell, bosnjak_syn, synch} and photospheric emission \citep[e.g.][]{photo_1, photo_2, photo_3}.
+The true physical mechanism(s) responsible for the prompt emission of GRBs is a heavily debated topic \citep[for a review see][]{KumarZhang2015}.
+%\citep[for a review see][]{gamma-ray-burst}.
+see above
+Two of the possible emission mechanisms are synchrotron \citep[e.g.][]{syn_shell, bosnjak_syn, synch} and photospheric emission \citep[e.g.][]{Goodman1986, photo_1, photo_2, photo_3}.
 In the past, GRB data were often fitted with empirical function like the Band function \citep{band}, to conclude from the fit parameters which physical model is preferred.
-In recent years it has been shown, that this approach can be misleading and that one should rather fit physical models directly to the data \citep{physical_models, synch}.
+In recent years it has been shown, that this approach can be misleading and that one should rather fit physical models directly to the data \citep{Burgess-2014, physical_models, synch}.
 An example for this is the so-called `line-of-death' for synchrotron emission \citep{line-of-death, line-of-death2}, which states that synchrotron radiation can not be the universal emission mechanism, if fits with a Band function give a low energy power law slope larger than $-2/3$.
 \citet{synch} have shown that this conclusion is flawed and that one can fit GRB spectra well with a physical synchrotron model even though the same spectra violate the line-of-death if fitted with a Band function.
-Especially the curvature of GRB spectra has been debated heavily towards extracting the physical emission process dominating GRBs (citation for this?).
-Here, we make use of INTEGTRAL/SPI which provides a factor 100 better spectral resolution in the 0.5-1 MeV band compared to Fermi/GBM.
+Another proposed proxy for physical emission processes in GRB  is the spectral curvature of empirical model fits to GRB data \citep{Yu-2015, Axelsson-2015}.
+This too has been shown to be an inaccurate indicator of the emission process \citep{Burgess2019}.
+Thus, the use of physical models remains the best tool for deciphering the emission processes occurring in these relativistic outflows.
 
-The spectrometer SPI, is one of the instruments onboard of the INTErnational Gamma-Ray Astrophysics Laboratory \citep[INTEGRAL][]{integral} satellite, that was launched in 2002.
-It is a coded mask instrument, with a fully coded FOV of 16 degrees, that covers an energy range between 20 keV and 8 MeV.
-The energy resolution allows the identification of fine features, like atomic decay lines \citep{spi_main}.
-In the case of GRBs this energy resolution gives us the possibility to determine the curvature of the spectra with an unmet precision.
+Apart from the model used, also the data play an important role.
+Earlier analysis has shown, that the shape of the spectrum around the peak is a decisive feature.
+Therefore, we make use of INTEGTRAL/SPI which provides a factor 100 better spectral resolution in the 0.1--1 MeV band compared to the frequently used Fermi/GBM instrument.
+
+The spectrometer SPI, is one of the instruments onboard of the INTErnational Gamma-Ray Astrophysics Laboratory \citep[INTEGRAL;][]{integral} satellite, that was launched in 2002.
+It is a coded mask instrument, with a fully coded field-of-view of 16 degrees, that covers an energy range between 20 keV and 8 MeV.
+The energy resolution allows the identification of fine features, like nuclear decay lines \citep{spi_main}.
+In the case of GRBs this energy resolution gives us the possibility to determine the curvature of the spectra with unprecedented precision.
 
 The standard analysis of SPI GRB data is done within the INTEGRAL Offline Scientific Analysis ({\tt OSA}) software \citep{osa}.
-That uses a two step method of first using only the photo peak response to incorporate the mask pattern on the detectors and in a second step applying an energy redistribution correction response.
-This method is used in several works which fitted empirical GRB models to the SPI data \citep[e.g.][]{spi_grb1, spi_grb2}.
+This uses a two step method of first using only the photo peak response to incorporate the mask pattern on the detectors and in a second step applying an energy redistribution correction response.
+This method is used in several works which fitted empirical GRB models to the SPI data \citep[e.g.][]{spi_grb1,Grebenev-2007}.
+\citet{spi_grb2} used a different approach to create a spectral catalogue of INTEGRAL GRBs, with a joined analysis of SPI and the Imager on Board the INTEGRAL Satellite (IBIS).
+They construct a response for every SPI detector and forward model the photon model directly into the data space of every detector, which is similar to our approach in this work.
+But they build the response simply according to the exposed fraction of the detector for the GRB direction and treat the background differently than we do in this work.
 %Several works have used SPI data for GRBs \citep{spi_grb1, spi_grb2}, but all of them fitted empirical models like the Band function.
-We developed the pure python-based analysis tool {\tt PySPI} in order to progress to fitting physical models and getting the maximal amount of information out of the data.
-This improves the analysis method in general because we use the full response and forward model the expected spectra to the native SPI data space and offers an easy to install and use interface.
+We developed a pure python-based analysis tool {\tt PySPI} in order to provide an easy to use data reduction and fitting tool while getting the maximal amount of information out of the data to progress to fitting physical models.
+This improves the analysis methods in general, because we use the full response to forward model the expected spectra to the native SPI data space in the correct way and offers an easy to install and use interface.
 %In this paper we introduce the new analysis method and show that we can fit complicated physical GRB models to the SPI data
 
-This paper is structured as follows: In Sec.
+This work is structured as follows: In Sec.
 \ref{methods} we summarize the different methods and concepts for SPI GRB data analysis, which also includes a detailed description of the new analysis method within {\tt PySPI} in Sec.
@@
 
-The response connects the photon spectrum to an expected detected count spectrum, for a given source position.
+The response connects the photon spectrum to an expected detected count spectrum for a given source position.
 The response encapsulates all the information about the probability of a photon with a certain energy and origin to be detected in a certain electronic channel of the detector.
-This includes, for example, information about partial energy deposition of the photon in the crystal and the process that transforms the deposited energy into an electronic signal, that is actually measured.
+This includes, for example, information about partial energy deposition of the photon in a crystal and the process that transforms the deposited energy into the electronic signal that is measured.
 % distribution of how much energy a photon with a certain energy deposit in the crystal and what energy is in the end measured for this deposited energy.
@@
 
-\begin{figure}
+\begin{figure}[ht]
     \begin{centering}
@@
 
-\subsection{{\tt OSA}}
-\label{{\tt OSA}}
+\subsection{INTEGRAL OSA software}
+\label{OSA}
 
@@
 GRBs are transient sources with a typical duration of up to a few tens of seconds.
-Therefore we can use the time intervals during a pointed observation, when the transient source is not active, as an independent temporal off-source observation (see Fig.
+Therefore, we can use the time intervals during a pointed observation, when the transient source is not active, as an independent temporal off-source observation (see Fig.
 \ref{fig:lightcurve}).
 This approach is similar to what is done with other instruments, that use spatially off-source observations as an independent background measurements.
-The probability distribution for the background model rates per energy channel are given by the background observation being a Poisson process
+The probability distribution for the background model rates per energy channel is the Poisson distribution
 %From the background observations we construct the probability of the background model rates per energy channel from a Poisson distribution, like given in Eq.
@@
 \begin{equation}
-	\mathcal{L}(b_{\mathrm{i}}|B_{\mathrm{i}}, t_{\mathrm{b}})=\frac{(t_{\mathrm{b}} b_{\mathrm{i}})^{B_{\mathrm{i}}}}{B_{\mathrm{i}}!}\cdot e^{-t_{\mathrm{b}} b_{\mathrm{i}}},
+	\mathcal{L}(B_{\mathrm{i}}, t_{\mathrm{b}}|b_{\mathrm{i}})=\frac{(t_{\mathrm{b}} b_{\mathrm{i}})^{B_{\mathrm{i}}}}{B_{\mathrm{i}}!}\cdot e^{-t_{\mathrm{b}} b_{\mathrm{i}}},
   \label{eq:poisson_bkg}
@@
 \begin{multline}
-	\mathcal{L}(\vec{\theta}, b_{\mathrm{i}}|D_{\mathrm{i}}, B_{\mathrm{i}},t_{\mathrm{d}},t_{\mathrm{b}}) = \frac{(t_{\mathrm{d}}(m_{\mathrm{i}}(\vec{\theta})+ b_{\mathrm{i}}))^{D_{\mathrm{i}}}}{D_{\mathrm{i}}!}\cdot \\
+	\mathcal{L}(D_{\mathrm{i}}, B_{\mathrm{i}},t_{\mathrm{d}},t_{\mathrm{b}}|\vec{\theta}, b_{\mathrm{i}}) = \frac{(t_{\mathrm{d}}(m_{\mathrm{i}}(\vec{\theta})+ b_{\mathrm{i}}))^{D_{\mathrm{i}}}}{D_{\mathrm{i}}!}\cdot \\
   e^{-t_{\mathrm{d}}(m_{\mathrm{i}}(\vec{\theta})+b_{\mathrm{i}})}\frac{(t_{\mathrm{b}} b_{\mathrm{i}})^{B_{\mathrm{i}}}}{B_{\mathrm{i}}!} e^{-t_{\mathrm{b}} b_{\mathrm{i}}}
@@
 \begin{multline}
-	L(\vec{\theta}|D_{\mathrm{i}}, B_{\mathrm{i}},t_{\mathrm{d}},t_{\mathrm{b}}) = \int_{0}^{\infty}\textrm{db}_{\mathrm{i}}\frac{(t_{\mathrm{d}}(m_{\mathrm{i}}(\vec{\theta})+ b_{\mathrm{i}}))^{D_{\mathrm{i}}}}{D_{\mathrm{i}}!}\cdot\\
+	\mathcal{L}(D_{\mathrm{i}}, B_{\mathrm{i}},t_{\mathrm{d}},t_{\mathrm{b}}|\vec{\theta}) = \int_{0}^{\infty}\textrm{db}_{\mathrm{i}}\frac{(t_{\mathrm{d}}(m_{\mathrm{i}}(\vec{\theta})+ b_{\mathrm{i}}))^{D_{\mathrm{i}}}}{D_{\mathrm{i}}!}\cdot\\
   e^{-t_{\mathrm{d}}(m_{\mathrm{i}}(\vec{\theta})+b_{\mathrm{i}})} \frac{(t_{\mathrm{b}} b_{\mathrm{i}})^{B_{\mathrm{i}}}}{B_{\mathrm{i}}!} e^{-t_{\mathrm{b}}b_{\mathrm{i}}}
@@
 
-The BALROG (BAyesian Lo-cation Reconstruction Of GRBs) algorithm to localize GRBs with Fermi/GBM uses the same method \citep{balrog}, which shows that forward folding allows to localize with a non imaging instrument, like GBM.
-It is important to note, that for example the instruments SPI and GBM are fundamentally very similar.
+Similarly, the BALROG (BAyesian Lo-cation Reconstruction Of GRBs) algorithm for localizing GRBs with Fermi/GBM employs the same method \citep{balrog}, which shows that forward folding allows one to localize photons with a non-imaging instrument.
+It is important to note that the instruments SPI and GBM are fundamentally very similar.
 They both consist of individual detectors that have different responses for a given source position.
-In GBM this is due to the different pointing directions of the detectors and in SPI due to the different occultations by the mask.
+In GBM, this is due to the different pointing directions of the detectors and in SPI due to the varying obscuration by the mask.
 Even though SPI is defined as a coded mask instrument, we don't have to treat it specially.
@@
 {\tt PySPI} constructs a plugin for the Multi-Mission Maximum Likelihood framework \citep[3ML][]{3ML}.
-This allows to fit the SPI data together with the data from other instruments, such as Fermi/GBM\footnote{See threeml.readthedocs.io}.
+This allows one to fit SPI data together with data from other instruments, such as Fermi/GBM\footnote{See threeml.readthedocs.io}.
 Also {\tt PySPI} is an open source software, which is publicly available on GitHub \citep{joss} and there is a documentation, with a few examples\footnote{See pyspi.readthedocs.io}.
@@
     \caption{Light curve for GRB120711A in one GBM and one SPI detector.
-The green shaded area marks the time intervals used for the independent background observation and the blue shaded area is the active time interval used in the fit.}
+The green shaded area marks part of the time intervals used for the independent background observation and the blue shaded area is the active time interval used in the fit.}
     \label{fig:time_selection}
@@
 \ref{fig:corner_osa_pyspi_band} shows the resulting posterior distributions of the fits.
-The results for the spectral shape from the two analysis techniques agree within their uncertainty regions, but {\tt PySPI} can constrain the parameters more precise.
+The results for the spectral shape from the two analysis techniques agree within their uncertainty regions, but {\tt PySPI} can constrain the model more precise (see Fig.
+\ref{fig:model_plot_band}).
 
@@
 \end{figure}
-
-\subsection{Compare SPI and GBM}
-\label{pyspi_gbm}
-Next, we analyze SPI data with {\tt PySPI} and the GBM data with the GRB analysis within 3ML with a Band function model.
-Fig.
-\ref{fig:corner_gbm_pyspi_band} shows the results for these fits, demonstrating that the results for the spectral shape from SPI and GBM are in agreement.
-It also shows that the calibration for SPI and GBM are well aligned within only $\approx$ 10\% difference in this case, which is within the usual calibration offsets of gamma-ray space telescopes..
-
-\subsection{Joint Fit of SPI and GBM}
-\label{pyspi_gbm_joined}
-We perform a a joint fit of SPI and GBM data with a physical synchrotron model (see \ref{synch}).
-Fig.
-\ref{fig:corner_gbm_pyspi_joined_syn} shows the corner plots for the individual and the combined fits.
-The posterior distribution of the parameters from the GBM and the SPI fit agree within their uncertainty regions and the combined fit reduces the allowed parameter space.
-The physical synchrotron model was able to fit the data of GBM and SPI well, which is shown with PPC and QQ plots in Appendix \ref{appendix}.
-
 \begin{figure}
@@
 
+\begin{figure*}
+  \begin{centering}
+    \includegraphics[width=0.45\linewidth]{figures/band_pyspi_osa.pdf}
+    \includegraphics[width=0.45\linewidth]{figures/band_pyspi_gbm.pdf}   \caption{Model posterior plots (95\% confidence region) for the results with the Band function model.
+Left panel shows the results for the PySPI compared to the fit using the official method and the right panel the PySPI fit compared to the GBM fit.}
+    \label{fig:model_plot_band}
+  \end{centering}
+\end{figure*}
+
+\subsection{Compare SPI and GBM}
+\label{pyspi_gbm}
+Next, we analyze SPI data with {\tt PySPI} and the GBM data with the GRB analysis within 3ML with a Band function model.
+Fig.
+\ref{fig:corner_gbm_pyspi_band} shows the results for these fits, demonstrating that the results for the spectral shape from SPI and GBM are in agreement.
+It also shows that the calibration for SPI and GBM are well aligned within only $\approx$ 10\% difference in this case, which is within the usual calibration offsets of gamma-ray space telescopes.
+
+\subsection{Joint Fit of SPI and GBM}
+\label{pyspi_gbm_joined}
+We perform a a joint fit of SPI and GBM data with a physical synchrotron model (see Sec.
+\ref{synch}).
+Fig.
+\ref{fig:corner_gbm_pyspi_joined_syn} shows the corner plots for the individual and the combined fits.
+The posterior distribution of the parameters from the GBM and the SPI fit agree within their uncertainty regions and the combined fit reduces the allowed parameter space.
+The physical synchrotron model was able to fit the data of GBM and SPI well, which is shown with PPC and QQ plots in Appendix \ref{appendix}.
+
+\begin{figure*}
+  \begin{centering}
+    \includegraphics[width=0.45\linewidth]{figures/spi_combined.pdf}
+    \includegraphics[width=0.45\linewidth]{figures/gbm_combined.pdf}   \caption{Model posterior plots (95\% confidence region) for the results with the physical synchrotron model.
+Left panel shows the results for the SPI alone fit compared to the combined fit and the right panel the GBM alone fit compared to the combined fit.}
+    \label{fig:model_plot_syn}
+  \end{centering}
+\end{figure*}
+\begin{figure*}
+  \begin{centering}
+    \includegraphics[width=1\linewidth]{figures/fit_plot.pdf}
+    \caption{Data and best fit model for four of the SPI detectors. The spectral model for this fit was a physical synchrotron model.}
+    \label{fig:Data }
+  \end{centering}
+\end{figure*}
+\clearpage
 \section{Conclusion}
 \label{conclusion}
-In this paper we have presented a new analysis method for GRBs detected by INTEGRAL/SPI and the software package utilizing this method ({\tt PySPI}).
-To show that it improves the analysis of GRBs detected by SPI, we have analyzed the data of GRB120711A with the data from INTGRAL/SPI and Fermi/GBM.
-The results for SPI with {\tt PySPI} are in agreement with those from the official analysis software, but more constraining.
-Also the resulting spectral shape for the fits with GBM and SPI data are in agreement and the relative calibration difference between SPI and GBM we conclude from the fits, is $\approx$ 10\% or less.
-We show that the GBM as well as the SPI data for GRB120711A can be fitted well with a physical synchrotron model and that combining the data in a simultaneous fit improves the parameter constrains.
-Consequently, SPI can play an important role in physical GRB model checking, if we apply a forward modelling method which is used in {\tt PySPI}, as described in Sec.
-\ref{pyspi}.
+We have presented a new analysis method for GRBs detected by INTEGRAL/SPI and the corresponding software package utilizing this method ({\tt PySPI}), which uses a proper forward-folding technique for each detector (see sec.
+\ref{pyspi}).
+To show that this improves the analysis of GRBs detected by SPI, we have analyzed GRB 120711A using the data from INTGRAL/SPI and Fermi/GBM.
+The results for SPI with {\tt PySPI} are in agreement with those from the official INTEGRAL OSA software, but more constraining.
+Also, the resulting spectral shape for the fits with GBM and SPI data are in agreement and the relative calibration difference between SPI and GBM we conclude from the fits, is $\approx$ 10\% or less.
+We show that the GBM as well as the SPI data for GRB 120711A can be fitted well with a physical synchrotron model and that combining the data in a simultaneous fit improves the parameter constraints.
+Consequently, SPI can play an important role in physical GRB model checking.
+%if we apply a forward modelling method which is used in {\tt PySPI}, as described in Sec. \ref{pyspi}.
 
@@
 This will be covered in a future work.
-%Generally {\tt PySPI} can improve the scientific output from SPI for GRBs significantly.
+% thomas Generally {\tt PySPI} can improve the scientific output from SPI for GRBs significantly.
 Due to a new analysis method, that folds the source model directly into the data space of every SPI detector with the full response of the individual detectors, the results are more constraining than the results with the official analysis software.
 
-\section*{Software}
+\begin{acknowledgement}
+BB acknowledges support from the German Aerospace Center (Deutsches Zentrum f\"ur Luft- und Raumfahrt, DLR) under FKZ 50 0R 1913.
+TS acknowledges support by the Bundesministerium f\"ur Wirtschaft und Energie via the Deutsches Zentrum f\"ur Luft- und Raumfahrt (DLR) under contract number 50 OX 2201.
+This work made use of the following software packages:
+%\section*{Software}
+{\tt 3ML} \citep{3ML}, {\tt Astromodels} \citep{astromodels}, {\tt Matplotlib} \citep{matplotlib}, {\tt ChainConsumer} \citep{chainconsumer, chainconsumer2}, {\tt OSA} \citep{osa}, {\tt Numpy} \citep{numpy}, {\tt MultiNest} \citep{multinest, multinest1, multinest3}
+\end{acknowledgement}
 
-{\tt 3ML} \citep{3ML}, {\tt Astromodels} \citep{astromodels}, {\tt Matplotlib} \citep{matplotlib}, {\tt ChainConsumer} \citep{chainconsumer}, {\tt OSA} \citep{osa}, {\tt Numpy} \citep{numpy}, {\tt MultiNest} \citep{multinest1, multinest2, multinest3}
+\bibliographystyle{aa}
+\bibliography{bib}
 
 \begin{appendix}
+\onecolumn
   \section{Model Checking Plots}
@@
 In the PPC plots the grey curve is the detected count spectrum and in the QQ plots the expected 1:1 relation between the cumulative model and observed counts.
-  \begin{figure*}[h]
+
+  \begin{figure*}[ht]
     \begin{centering}
@@
   \end{figure*}
-  \begin{figure*}[h]
+  \begin{figure*}[ht]
     \begin{centering}
@@
   \end{figure*}
-  \begin{figure*}[h]
+
+  \begin{figure*}[ht]
     \begin{centering}
@@
   \end{figure*}
-  \begin{figure*}[h]9
+
+  \begin{figure*}[ht]
     \begin{centering}
@@
 
-\bibliographystyle{aa}
-\bibliography{bib}
-
 \end{document}

### 2022-01-20 src/figures/dataplot.py

@@ -1,0 +1,151 @@
+from pyspi.utils.data_builder.time_series_builder import TimeSeriesBuilderSPI
+from pyspi.utils.response.spi_response_data import ResponseDataRMF
+from pyspi.utils.response.spi_response import ResponseRMFGenerator
+from pyspi.utils.response.spi_drm import SPIDRM
+from pyspi.utils.livedets import get_live_dets
+from pyspi.SPILike import SPILikeGRB
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+color1 = "#544b3dff"
+color2 = "#340068ff"
+color3 = "#4cb944ff"
+color4 = "#4f7cacff"
+color5 = "#6d2e46ff"
+
+grb_time = "120711 024453" #(YYMMDD HHMMSS) - from GBM trigger time
+background_time_interval_1_spi = "-500--10"
+background_time_interval_2_spi = "150-1000"
+active_time = '65-73'
+det_spi = 0
+det_gbm = "n2"
+ebounds = np.geomspace(25, 8000, 200)
+ebounds_sgl = ebounds[ebounds<400]
+ebounds_psd = ebounds[np.logical_and(ebounds>400, ebounds<2700)]
+ebounds_sgl2 = ebounds[ebounds>2700]
+ein = np.geomspace(20,8000,100)
+
+rsp_base = ResponseDataRMF.from_version(4)
+spilikes_sgl = []
+spilikes_sgl2 = []
+spilikes_psd = []
+
+for d in get_live_dets(time=grb_time, event_types=["single"]):
+    drm_gen_sgl = ResponseRMFGenerator.from_time(grb_time,  d,
+                                            ebounds_sgl, ein,
+                                            rsp_base)
+
+    sd_sgl = SPIDRM(drm_gen_sgl, 94.67830, -70.99905)
+
+    tsb_sgl = TimeSeriesBuilderSPI.from_spi_grb(f"SPIDet{d}",
+                                                d,
+                                                grb_time,
+                                                response=sd_sgl,
+                                                sgl_type="both",
+                                                )
+    #tsb_sgl.set_active_time_interval(active_time)
+    tsb_sgl.set_background_interval(background_time_interval_1_spi,
+                                    background_time_interval_2_spi,
+                                    fit_poly=False
+                                   )
+    tsb_sgl.set_active_time_interval(active_time)
[…]

### 2022-01-20 src/figures/model_plot_band.py

@@ -1,0 +1,114 @@
+from threeML import load_analysis_results
+import numpy as np
+
+res_spi2 = load_analysis_results("results/paper_band_pyspi.fits")
+res_gbm2 = load_analysis_results("results/paper_band_gbm.fits")
+res_osa2 = load_analysis_results("results/paper_band_osa.fits")
+
+num_samples = 300
+samples_spi = res_spi2.samples.T
+np.random.shuffle(samples_spi)
+samples_sel_spi = samples_spi[:num_samples]
+
+samples_gbm = res_gbm2.samples.T
+np.random.shuffle(samples_gbm)
+samples_sel_gbm = samples_gbm[:num_samples]
+
+samples_osa = res_osa2.samples.T
+np.random.shuffle(samples_osa)
+samples_sel_osa = samples_osa[:num_samples]
+
+from astromodels import Band, Log_uniform_prior, Uniform_prior,PointSource, Model
+band1 = Band()
+band1.K.prior = Log_uniform_prior(lower_bound=1e-6, upper_bound=1e4)
+band1.alpha.set_uninformative_prior(Uniform_prior)
+band1.beta.set_uninformative_prior(Uniform_prior)
+band1.xp.prior = Uniform_prior(lower_bound=10,upper_bound=8000)
+ps1 = PointSource('PySPI',ra=94.67830, dec=-70.99905, spectral_shape=band1)
+
+model1 = Model(ps1)
+
+
+e = np.geomspace(10,5000, 1000)
+fig, ax = plt.subplots()
+vals_spi = np.zeros((num_samples, len(e)))
+for i, s in enumerate(samples_sel_spi):
+    band1.K = s[0]
+    band1.alpha = s[1]
+    band1.xp = s[2]
+    band1.beta = s[3]
+    #ax.loglog(e, e*e*synch(e), color="red")
+    vals_spi[i] = band1(e)
+
+vals_gbm = np.zeros((num_samples, len(e)))
+for i, s in enumerate(samples_sel_gbm):
+    band1.K = s[0]
+    band1.alpha = s[1]
+    band1.xp = s[2]
+    band1.beta = s[3]
+    #ax.loglog(e, e*e*synch(e), color="blue")
+    vals_gbm[i] = band1(e)
[…]

### 2022-01-20 src/figures/model_plot_syn.py

@@ -1,0 +1,105 @@
+from threeML import load_analysis_results
+import numpy as np
+
+import pynchrotron
+res_spi = load_analysis_results("results/result_pyspi4_syn_grb.fits")
+res_gbm = load_analysis_results("results/result_gbm3_syn_grb.fits")
+res_both = load_analysis_results("results/result_both3_syn_grb.fits")
+
+num_samples = 300
+samples_spi = res_spi.samples.T
+np.random.shuffle(samples_spi)
+samples_sel_spi = samples_spi[:num_samples]
+
+samples_gbm = res_gbm.samples.T
+np.random.shuffle(samples_gbm)
+samples_sel_gbm = samples_gbm[:num_samples]
+
+samples_both = res_both.samples.T
+np.random.shuffle(samples_both)
+samples_sel_both = samples_both[:num_samples]
+
+synch = pynchrotron.SynchrotronNumericalNormPeak()
+synch.K = 100
+synch.B = 1000
+synch.index=4
+synch.gamma_min= 1E5
+cool_frac = 1E-2
+max_frac = 1E2
+synch.gamma_max.free = False
+synch.index.bounds = (0, None)
+
+
+e = np.geomspace(10,5000, 1000)
+vals_spi = np.zeros((num_samples, len(e)))
+for i, s in enumerate(samples_sel_spi):
+    synch.K = s[0]
+    synch.B = s[1]
+    synch.index = s[2]
+    synch.gamma_cool = s[3]
+    vals_spi[i] = synch(e)
+
+vals_gbm = np.zeros((num_samples, len(e)))
+for i, s in enumerate(samples_sel_gbm):
+    synch.K = s[0]
+    synch.B = s[1]
+    synch.index = s[2]
+    synch.gamma_cool = s[3]
+
+    vals_gbm[i] = synch(e)
+
+vals_both = np.zeros((num_samples, len(e)))
+for i, s in enumerate(samples_sel_both):
+    synch.K = s[0]
+    synch.B = s[1]
+    synch.index = s[2]
+    synch.gamma_cool = s[3]
+    vals_both[i] = synch(e)
+
+import matplotlib.pyplot as plt
+plt.style.use("mplstyle.sty")
+q = 95
[…]

### 2022-01-20 src/figures/dataplot.py
fix path

@@ -109,8 +109,8 @@ dets = ["n0","n1","n2","n4","b0"]
 sls1 = []
 tss1 = []
 for det in dets:
-    tte_file = "/home/bjorn/Downloads/glg_tte_{}_bn120711115_v00.fit".format(det)
-    rsp2_file="/home/bjorn/Downloads/glg_cspec_{}_bn120711115_v00.rsp2".format(det)
+    tte_file = "gbmfiles/glg_tte_{}_bn120711115_v00.fit".format(det)
+    rsp2_file="gbmfiles/glg_cspec_{}_bn120711115_v00.rsp2".format(det)
     ts = TimeSeriesBuilder.from_gbm_tte('gbm{}'.format(det), tte_file, rsp2_file,poly_order=0)
     ts.set_active_time_interval(active_time_gbm)
     ts.set_background_interval(background_time_interval_1_gbm, background_time_interval_2_gbm)

### 2022-01-20 src/figures/dataplot.py
fix typo

@@ -109,8 +109,8 @@ dets = ["n0","n1","n2","n4","b0"]
 sls1 = []
 tss1 = []
 for det in dets:
-    tte_file = "gbmfiles/glg_tte_{}_bn120711115_v00.fit".format(det)
-    rsp2_file="gbmfiles/glg_cspec_{}_bn120711115_v00.rsp2".format(det)
+    tte_file = "gbm_files/glg_tte_{}_bn120711115_v00.fit".format(det)
+    rsp2_file="gbm_files/glg_cspec_{}_bn120711115_v00.rsp2".format(det)
     ts = TimeSeriesBuilder.from_gbm_tte('gbm{}'.format(det), tte_file, rsp2_file,poly_order=0)
     ts.set_active_time_interval(active_time_gbm)
     ts.set_background_interval(background_time_interval_1_gbm, background_time_interval_2_gbm)

### 2022-01-20 src/figures/dataplot.py
path fix

@@ -124,7 +124,7 @@ for det in dets:
     tss1.append(ts)
 
 from threeML import load_analysis_results
-res_both = load_analysis_results("/home/bjorn/Downloads/result_both3_syn_grb.fits")
+res_both = load_analysis_results("results/result_both3_syn_grb.fits")
 datalist = DataList(*spilikes_sgl, *spilikes_sgl2, *spilikes_psd, *sls1)
 ba_gbm_band_1 = BayesianAnalysis(res_both.optimized_model, datalist)
 for i, s in enumerate(sls1):

### 2022-01-20 src/figures/dataplot.py
add pynchrotron

@@ -4,7 +4,7 @@ from pyspi.utils.response.spi_response import ResponseRMFGenerator
 from pyspi.utils.response.spi_drm import SPIDRM
 from pyspi.utils.livedets import get_live_dets
 from pyspi.SPILike import SPILikeGRB
-
+import pynchrotron
 import numpy as np
 import matplotlib.pyplot as plt
 

### 2022-01-20 src/figures/model_plot_band.py
remove plt

@@ -30,7 +30,6 @@ model1 = Model(ps1)
 
 
 e = np.geomspace(10,5000, 1000)
-fig, ax = plt.subplots()
 vals_spi = np.zeros((num_samples, len(e)))
 for i, s in enumerate(samples_sel_spi):
     band1.K = s[0]

### 2022-01-21 src/figures/dataplot.py
fix style sheet name

@@ -138,7 +138,7 @@ for i, s in enumerate(spilikes_psd):
 
 from threeML import display_spectrum_model_counts
 
-plt.style.use("mplplotlibrc")
+plt.style.use("matplotlibrc")
 colors=[color1,color4,color2,color3,color5]
 f = display_spectrum_model_counts(ba_gbm_band_1,
                                      data=['SPIDet13', 'SPIDet14', 'SPIDet15', 'SPIDet16'],

### 2022-01-21 src/figures/model_plot_band.py

@@ -58,7 +58,7 @@ for i, s in enumerate(samples_sel_osa):
     #ax.loglog(e, e*e*synch(e), color="green")
 
 import matplotlib.pyplot as plt
-plt.style.use("mplplotlibrc")
+plt.style.use("matplotlibrc")
 q = 95
 fig, ax = plt.subplots()
 color1 = "#544b3dff"

### 2022-01-21 src/figures/model_plot_syn.py

@@ -57,7 +57,7 @@ for i, s in enumerate(samples_sel_both):
     vals_both[i] = synch(e)
 
 import matplotlib.pyplot as plt
-plt.style.use("mplstyle.sty")
+plt.style.use("matplotlibrc")
 q = 95
 fig, ax = plt.subplots()
 color1 = "#544b3dff"

### 2022-01-21 src/figures/b0_model_check.py
change color in qq and ppc plot

@@ -15,7 +15,7 @@ f = p.detectors["gbmb0"].plot(
     bkg_subtract=False,
     levels=[95,68],
     colors=[color2, color3],
-    lc=color1
+    lc=color4
 )
 
 f.savefig("b0_ppc.pdf")
@@ -24,7 +24,7 @@ f = p.detectors["gbmb0"].plot_qq(
     channel_energies=[],
     levels=[95,68],
     colors=[color2, color3],
-    center_color=color1
+    center_color=color4
 )
 
 f.savefig("b0_qq.pdf")

### 2022-01-21 src/figures/low_13_model_check.py

@@ -15,7 +15,7 @@ f = p.detectors["SPIDet13"].plot(
     bkg_subtract=False,
     levels=[95,68],
     colors=[color2, color3],
-    lc=color1)
+    lc=color4)
 
 f.savefig("low_13_ppc.pdf")
 
@@ -23,7 +23,7 @@ f = p.detectors["SPIDet13"].plot_qq(
     channel_energies=[],
     levels=[95,68],
     colors=[color2, color3],
-    center_color=color1
+    center_color=color4
 )
 
 f.savefig("low_13_qq.pdf")

### 2022-01-21 src/figures/n0_model_check.py

@@ -15,7 +15,7 @@ f = p.detectors["gbmn0"].plot(
     bkg_subtract=False,
     levels=[95,68],
     colors=[color2, color3],
-    lc=color1)
+    lc=color4)
 
 f.savefig("n0_ppc.pdf")
 
@@ -23,7 +23,7 @@ f = p.detectors["gbmn0"].plot_qq(
     channel_energies=[],
     levels=[95,68],
     colors=[color2, color3],
-    center_color=color1
+    center_color=color4
 )
 
 f.savefig("n0_qq.pdf")

### 2022-01-21 src/figures/psd_13_model_check.py

@@ -15,7 +15,7 @@ f = p.detectors["SPIDet13MID"].plot(
     bkg_subtract=False,
     levels=[95,68],
     colors=[color2, color3],
-    lc=color1)
+    lc=color4)
 
 f.savefig("psd_13_ppc.pdf")
 
@@ -23,7 +23,7 @@ f = p.detectors["SPIDet13MID"].plot_qq(
     channel_energies=[],
     levels=[95,68],
     colors=[color2, color3],
-    center_color=color1
+    center_color=color4
 )
 
 f.savefig("psd_13_qq.pdf")

### 2022-01-21 src/figures/b0_model_check.py
try differen color

@@ -15,7 +15,7 @@ f = p.detectors["gbmb0"].plot(
     bkg_subtract=False,
     levels=[95,68],
     colors=[color2, color3],
-    lc=color4
+    lc="#818704"
 )
 
 f.savefig("b0_ppc.pdf")
@@ -24,7 +24,7 @@ f = p.detectors["gbmb0"].plot_qq(
     channel_energies=[],
     levels=[95,68],
     colors=[color2, color3],
-    center_color=color4
+    center_color="#818704"
 )
 
 f.savefig("b0_qq.pdf")

### 2022-01-21 src/figures/low_13_model_check.py

@@ -15,7 +15,7 @@ f = p.detectors["SPIDet13"].plot(
     bkg_subtract=False,
     levels=[95,68],
     colors=[color2, color3],
-    lc=color4)
+    lc="#818704")
 
 f.savefig("low_13_ppc.pdf")
 
@@ -23,7 +23,7 @@ f = p.detectors["SPIDet13"].plot_qq(
     channel_energies=[],
     levels=[95,68],
     colors=[color2, color3],
-    center_color=color4
+    center_color="#818704"
 )
 
 f.savefig("low_13_qq.pdf")

### 2022-01-21 src/figures/n0_model_check.py

@@ -15,7 +15,7 @@ f = p.detectors["gbmn0"].plot(
     bkg_subtract=False,
     levels=[95,68],
     colors=[color2, color3],
-    lc=color4)
+    lc="#818704")
 
 f.savefig("n0_ppc.pdf")
 
@@ -23,7 +23,7 @@ f = p.detectors["gbmn0"].plot_qq(
     channel_energies=[],
     levels=[95,68],
     colors=[color2, color3],
-    center_color=color4
+    center_color="#818704"
 )
 
 f.savefig("n0_qq.pdf")

### 2022-01-21 src/figures/psd_13_model_check.py

@@ -15,7 +15,7 @@ f = p.detectors["SPIDet13MID"].plot(
     bkg_subtract=False,
     levels=[95,68],
     colors=[color2, color3],
-    lc=color4)
+    lc="#818704")
 
 f.savefig("psd_13_ppc.pdf")
 
@@ -23,7 +23,7 @@ f = p.detectors["SPIDet13MID"].plot_qq(
     channel_energies=[],
     levels=[95,68],
     colors=[color2, color3],
-    center_color=color4
+    center_color="#818704"
 )
 
 f.savefig("psd_13_qq.pdf")

### 2022-01-21 src/ms.tex
remove edit color
remove cite color
remove xcolor
fix script name in tex
chagnes in tex and bib

@@
 \usepackage{float}
-\usepackage[pdftex]{xcolor}
-\definecolor{citecolor}{HTML}{195D95}
-\definecolor{BrickRed}{HTML}{C41010}
-
-\def\mike#1{\textcolor{BrickRed}{jmb: \textbf{ #1}}}
 
@@
 % Begin!
-
+\def\fdg{\hbox{$.\!\!^\circ$}}          % Fractions of degrees
 \begin{document}
@@
 INTEGRAL/SPI is a coded mask instrument observing in the keV to MeV energy range, which covers the peak of the $\nu F\nu$ spectrum of most Gamma-Ray Bursts (GRBs).
-For the energy range between $\approx$ 10 keV to $\approx$ 10 MeV, Fermi/GBM has been the primary instrument for analyzing GRBs over the last 15 years.
+Since its launch, Fermi/GBM has been the primary instrument for analyzing GRBs in the energy range between $\approx$ 10 keV to $\approx$ 10 MeV.
 Herein, we show that SPI, covering a similar energy range, can give equivalently constraining results if we use an advanced analysis method.
@@
 We apply these new techniques to GRB 120711A in order to validate and showcase {\tt PySPI}'s capabilities.
-We show that {\tt PySPI} improves the analysis of SPI GRB data compared to the official analysis software.
+We show that {\tt PySPI} improves the analysis of SPI GRB data compared to the {\tt OSA} analysis.
 In addition, we demonstrate that the GBM and the SPI data of this GRB can be fitted well with a physical synchrotron model.
@@
 Long GRBs (prompt phase $\gtrapprox$ 2s) have been associated with the collapse of massive stars \citep{SN1, Hjorth+2003, SN2}, whereas short GRBs are  caused by mergers of compact objects, like neutron stars \citep{Eichler+1989, gw}.
-In both cases it is consensus, that the progenitor events of GRBs produce jetted relativistic outflows, which consists of several shells with different velocities, resulting in internal shell collisions \citep{ReesMeszaros1994, Mochkovitch+1995}.
+In both cases it is consensus, that the progenitor events of GRBs produce jetted relativistic outflows, which consist of several shells with different velocities, resulting in internal shell collisions \citep{ReesMeszaros1994, Mochkovitch+1995}.
 %\citep{gamma-ray-burst}. Edo Berger is an observer, and has never worked on shocks, so I (jcg) wouldn't cite this review
@@
 
-The spectrometer SPI, is one of the instruments onboard of the INTErnational Gamma-Ray Astrophysics Laboratory \citep[INTEGRAL;][]{integral} satellite, that was launched in 2002.
+The spectrometer SPI is one of the instruments onboard of the INTErnational Gamma-Ray Astrophysics Laboratory \citep[INTEGRAL;][]{integral} satellite, that was launched in 2002.
 It is a coded mask instrument, with a fully coded field-of-view of 16 degrees, that covers an energy range between 20 keV and 8 MeV.
@@
 This uses a two step method of first using only the photo peak response to incorporate the mask pattern on the detectors and in a second step applying an energy redistribution correction response.
-This method is used in several works which fitted empirical GRB models to the SPI data \citep[e.g.][]{spi_grb1,Grebenev-2007}.
-\citet{spi_grb2} used a different approach to create a spectral catalogue of INTEGRAL GRBs, with a joined analysis of SPI and the Imager on Board the INTEGRAL Satellite (IBIS).
+This method is used in several works which fitted empirical GRB models to the SPI data \citep{Malaguti-2003, Mereghetti-2003, Mereghetti-2003.2, Kienlin-2003, Kienlin-2003.2,Beckmann-2004, Moran-2005, Filliatre-2005.1, Filliatre-2005.2, McBreen-2006, Grebenev-2007, McGlynn-2008, Foley-2008, McGlynn-2009, Martin-Carrillo-2014}.
+\citet{Bosnjak-2014} used a different approach to create a spectral catalogue of INTEGRAL GRBs, with a joined analysis of SPI and the Imager on Board the INTEGRAL Satellite (IBIS).
 They construct a response for every SPI detector and forward model the photon model directly into the data space of every detector, which is similar to our approach in this work.
-But they build the response simply according to the exposed fraction of the detector for the GRB direction and treat the background differently than we do in this work.
+But they build the response simply according to the exposed fraction of the detector for the GRB direction and use background subtracted data for their fits.
 %Several works have used SPI data for GRBs \citep{spi_grb1, spi_grb2}, but all of them fitted empirical models like the Band function.
@@
 This is a general statement that also applies to SPI.
-In the following subsection we will first cover some general concepts for SPI and then the official analysis software method as well as the method within our new analysis tool {\tt PySPI}.
+In the following subsection we will first cover some general concepts for SPI and then the standard analysis method within {\tt OSA} as well as the method within our new analysis tool {\tt PySPI}.
 The main difference is that the method in {\tt PySPI} is a full forward folding method, fulfilling the statement above, which results in maximising the information we can get from the data in the analysis.
@@
 %Since shortly after the start of INTEGRAL, it is known that there are spurious events in the SPI data around 1.5 MeV.
-According to \citet{spi_electronic_noise} there are spurious events in the SPI data, which are photons with small energy (<100 keV) that get detected at a higher energy due to saturation of the Analog Front-End Electronics (AFEE) electronics by previous high energy deposition.
+According to \citet{spi_electronic_noise} there are spurious events in the SPI data, which are photons with small energy (<100 keV) that get detected at a higher energy due to saturation of the Analog Front-End Electronics (AFEE) by previous high energy deposition.
 It is also known, that these spurious events do not show up in events with a detection also in the Pulse Shape Discriminator (PSD) electronics.
 The reason for this is that the PSD electronics have a low energy threshold of $\approx$ 450 keV (the exact value has been changed a few times during the mission) \citep{spi_electronic_noise}.
-Therefore only events that deposit more than this low energy threshold in the Germanium crystal can trigger this electronic chain, which eliminates the <100 keV events that are detected at the wrong energies by the AFEE electronics.
+Therefore only events that deposit more than this low energy threshold in the Germanium crystal can trigger this electronic chain, which eliminates the <100 keV events that are detected at the wrong energies by the AFEE.
 In Fig.
@@
 As we are introducing a new analysis software in this work, we want to compare it to the existing analysis software, to check if the results are in agreement.
-We shortly summarize the official analysis tools for GRB analysis, which are part of the INTEGRAL Offline Scientific Analysis ({\tt OSA}) software \citep{osa}.
+We shortly summarize the standard analysis tools for GRB analysis, which are part of the INTEGRAL Offline Scientific Analysis ({\tt OSA}) software \citep{osa}.
 
@@
 After that one can either find the location of the GRB with SPIROS, i.e.
-an iterative source removal algorithm for SPI data, or set it manually if it is already known.
+an iterative source removal algorithm for SPI data \citep{Skinner-2003}, or set it manually if it is already known.
 The next steps concern the spectral fitting, which is done in another two-step procedure.
@@
 In this step the energy channels are fitted simultaneously, as it is impossible to incorporate energy dispersion in a way that fits every energy channel individually.
-This fitting can be done in different spectral fitting software, like {\tt XSPEC} or {\tt 3ML}.
+This fitting can be done in different spectral fitting software, like {\tt XSPEC} \citep{xspec} or {\tt 3ML} \citep{3ML}.
 
@@
 \ref{eq:likelihood_m_and_b}, that connects the source and background model with the Poisson process data of the background and active time interval, via the response.
-Here $\vec{\theta}$ summarizes all the parameters of the source model, $D_{\mathrm{i}}$ are the measured counts in the selected active time interval of the transient source, $m_{\mathrm{i}}(\vec{\theta})$ are the predicted counts from the model evaluated at the parameters $\vec{\theta}$ and $t_{\mathrm{d}}$ is the exposure of the selected active time interval.
+Here $\vec{\theta}$ summarizes all the parameters of the source model, $D_{\mathrm{i}}$ are the measured counts in the selected active time interval of the transient source, $m_{\mathrm{i}}(\vec{\theta})$ are the predicted count rates from the model evaluated at the parameters $\vec{\theta}$ and $t_{\mathrm{d}}$ is the exposure of the selected active time interval.
 
@@
 
-If we would have a spectral model for the background, we would fit the background and the source model at the same time with the likelihood given in Eq.
+If there was a spectral model for the background, we would fit the background and the source model at the same time with the likelihood given in Eq.
 \ref{eq:likelihood_m_and_b}, but we do not have such a model for the SPI background.
@@
 nuclear de-excitation line emission \citep{spi_bkg}.
-Therefore the background consists of several hundred different atomic lines \citep{spi_bkg}, which makes an accurate spectral model for the background impossible at the moment.
+Therefore the background consists of several hundred different nuclear lines \citep{spi_bkg}, which makes an accurate spectral model for the background impossible at the moment.
 But we can marginalize over the parameters $b_{\mathrm{i}}$ using only the fact that they can not be negative, which leaves us with Eq.
@@
 
-In {\tt PySPI}, one can select the energy range in which only the PSD events should be used to avoid including spurious events (See Sec.
+In {\tt PySPI}, one can select the energy range in which only the PSD events should be used to avoid including spurious events (see Sec.
 \ref{electronic}).
@@
 There exists a strong degeneracy between $B$ and $\gamma_{\mathrm{inj}}$, as their combination sets the peak of the photon spectrum.
-Therefore we fix $\gamma_{\mathrm{inj}}=10^{5}$ and only fits for $B$.
+Therefore we fix $\gamma_{\mathrm{inj}}=10^{5}$ and only fit for $B$.
 Thus the results for $\gamma_{\mathrm{max}}$ and $\gamma_{\mathrm{cool}}$ are determined relative to the fixed $\gamma_{\mathrm{inj}}$.
@@
 In this work, we analyze GRB 120711A, which was a bright, multi-pulse GRB with a precursor and a long emission period of $\approx$100 s.
-It was detected by SPI, GBM and Swift-XRT \citep{GCN_integral, GCN_gbm, GCN_swift}.
-We look at one time interval with a duration of 10 seconds around the first peak in the light curve (see Fig.
+It was detected by SPI and GBM \citep{GCN_integral, GCN_gbm}.
+Additionally Swift-XRT \citep{GCN_swift} observed the afterglow.
+We look at one time interval with a duration of 10 seconds around the first bright peak in the light curve (see Fig.
 \ref{fig:time_selection}).
-From the XRT detection we know the position of the GRB (RA: 94.68 °, DEC: -71.00 ° in J2000).
+From the XRT detection we know the position of the GRB (RA: 94\fdg68, DEC: -71\fdg00 in J2000).
+GRB 120711A was previously analyzed with SPI data by \citet{Martin-Carrillo-2014}, but their work was mainly focused on the post-GRB emission properties.
+For the prompt emission they only fitted the time averaged spectrum over the $T_{90}$ emission (between 0 and 115 seconds after the trigger), with an empirical exponential cutoff power-law model.
 
@@
 First, we fit the data with the empirical Band function.
-With this we show a comparison between the fit results with {\tt PySPI} and the official software tools for GRB analysis using {\tt OSA} (Sec.
+With this we show a comparison between the fit results with {\tt PySPI} and {\tt OSA} (Sec.
 \ref{pyspi_osa}) and check if the results for SPI and GBM are in agreement (Sec.
@@
 \label{pyspi_osa}
-We analyze the SPI data with a band function as a spectral model for the same time interval with {\tt PySPI} and {\tt OSA}, to check if the results are in agreement.
+We analyze the SPI data with a Band function as a spectral model for the same time interval with {\tt PySPI} and {\tt OSA}, to check if the results are in agreement.
 Fig.
 \ref{fig:corner_osa_pyspi_band} shows the resulting posterior distributions of the fits.
-The results for the spectral shape from the two analysis techniques agree within their uncertainty regions, but {\tt PySPI} can constrain the model more precise (see Fig.
+The results for the spectral shape from the two analysis techniques agree within their uncertainty regions, but {\tt PySPI} can constrain the model more precisely (see Fig.
 \ref{fig:model_plot_band}).
@@
     \includegraphics[width=1\linewidth]{figures/pyspi_vs_osa_band.pdf}
-    \caption{Corner plot for the SPI fit with {\tt PySPI} and the official tools.
+    \caption{Corner plot for the SPI fit with {\tt PySPI} and {\tt OSA}.
 The spectral model in this fit is a Band function.
-The results are in agreement, however {\tt PySPI} constrains the parameters better.}
+The results are in agreement, however {\tt PySPI} constrains the parameters more precisely.}
     \label{fig:corner_osa_pyspi_band}
@@
     \caption{Corner plot for the SPI fit with {\tt PySPI} and the GBM fit.
-In this fit we used a physical synchrotron model (see \ref{synch}) as spectral model.
+In this fit we used a physical synchrotron model (see Sec.
+\ref{synch}) as spectral model.
 The results from SPI and GBM agree within their uncertainty region and the combined fit constrains the parameter better than the individual ones.}
@@
     \includegraphics[width=0.45\linewidth]{figures/band_pyspi_osa.pdf}
-    \includegraphics[width=0.45\linewidth]{figures/band_pyspi_gbm.pdf}   \caption{Model posterior plots (95\% confidence region) for the results with the Band function model.
-Left panel shows the results for the PySPI compared to the fit using the official method and the right panel the PySPI fit compared to the GBM fit.}
+    \includegraphics[width=0.45\linewidth]{figures/band_pyspi_gbm.pdf}
+    \caption{Model posterior plots (95\% confidence region) for the results with the Band function model.
+Left panel shows the results for the {\tt PySPI} fit compared to the fit using {\tt OSA} and the right panel the {\tt PySPI} fit compared to the GBM fit.}
     \label{fig:model_plot_band}
@@
     \includegraphics[width=0.45\linewidth]{figures/spi_combined.pdf}
-    \includegraphics[width=0.45\linewidth]{figures/gbm_combined.pdf}   \caption{Model posterior plots (95\% confidence region) for the results with the physical synchrotron model.
-Left panel shows the results for the SPI alone fit compared to the combined fit and the right panel the GBM alone fit compared to the combined fit.}
+    \includegraphics[width=0.45\linewidth]{figures/gbm_combined.pdf}
+    \caption{Model posterior plots (95\% confidence region) for the results with the physical synchrotron model.
+Left panel shows the results for the SPI alone fit compared to the combined fit and the right panel the GBM alone fit compared to the combined fit.
+The combined fit reduces the allowed model space.}
     \label{fig:model_plot_syn}
@@
     \includegraphics[width=1\linewidth]{figures/fit_plot.pdf}
-    \caption{Data and best fit model for four of the SPI detectors. The spectral model for this fit was a physical synchrotron model.}
-    \label{fig:Data }
+    \caption{Data and best fit model for four of the SPI detectors in count space. The spectral model for this fit was a physical synchrotron model.}
+    \label{fig:dataplot}
   \end{centering}
@@
 \label{conclusion}
-We have presented a new analysis method for GRBs detected by INTEGRAL/SPI and the corresponding software package utilizing this method ({\tt PySPI}), which uses a proper forward-folding technique for each detector (see sec.
+We have presented a new analysis method for GRBs detected by INTEGRAL/SPI and the corresponding software package utilizing this method ({\tt PySPI}), which uses a proper forward-folding technique for each detector (see Sec.
 \ref{pyspi}).
 To show that this improves the analysis of GRBs detected by SPI, we have analyzed GRB 120711A using the data from INTGRAL/SPI and Fermi/GBM.
-The results for SPI with {\tt PySPI} are in agreement with those from the official INTEGRAL OSA software, but more constraining.
+The results for SPI with {\tt PySPI} are in agreement with those from the INTEGRAL OSA software, but more constraining.
 Also, the resulting spectral shape for the fits with GBM and SPI data are in agreement and the relative calibration difference between SPI and GBM we conclude from the fits, is $\approx$ 10\% or less.
@@
 The green and purple shaded area are the one and two sigma contours.
-In the PPC plots the grey curve is the detected count spectrum and in the QQ plots the expected 1:1 relation between the cumulative model and observed counts.
+In the PPC plots the dark yellow curve is the detected count spectrum and in the QQ plots the expected 1:1 relation between the cumulative model and observed counts.
 
@@
       \includegraphics[width=0.45\linewidth]{figures/n0_qq.pdf}
-      \caption{PPC (left) and QQ (right) plot for the GBM detector n0. The green and purple shaded area are the one and two sigma contours.}
+      \caption{PPC (left) and QQ (right) plot for the GBM detector n0.
+The green and purple shaded area are the one and two sigma contours.
+In the PPC plots the dark yellow curve is the detected count spectrum and in the QQ plots the expected 1:1 relation between the cumulative model and observed counts.}
       \label{fig:n0_model_check}
@@
       \includegraphics[width=0.45\linewidth]{figures/b0_qq.pdf}
-      \caption{PPC (left) and QQ (right) plot for the GBM detector b0. The green and purple shaded area are the one and two sigma contours.}
+      \caption{PPC (left) and QQ (right) plot for the GBM detector b0.
+The green and purple shaded area are the one and two sigma contours.
+In the PPC plots the dark yellow curve is the detected count spectrum and in the QQ plots the expected 1:1 relation between the cumulative model and observed counts.}
       \label{fig:b0_model_check}
@@
       \includegraphics[width=0.45\linewidth]{figures/low_13_qq.pdf}
-      \caption{PPC (left) and QQ (right) plot for the low energy range of SPI detector 13 (all single events).}
+      \caption{PPC (left) and QQ (right) plot for the low energy range of SPI detector 13 (all single events).
+In the PPC plots the dark yellow curve is the detected count spectrum and in the QQ plots the expected 1:1 relation between the cumulative model and observed counts.}
       \label{fig:low_13_model_check}
@@
       \includegraphics[width=0.45\linewidth]{figures/psd_13_qq.pdf}
-      \caption{PPC (left) and QQ (right) plot for the middle energy range of SPI detector 13 (only PSD events).}
+      \caption{PPC (left) and QQ (right) plot for the middle energy range of SPI detector 13 (only PSD events).
+In the PPC plots the dark yellow curve is the detected count spectrum and in the QQ plots the expected 1:1 relation between the cumulative model and observed counts.}
       \label{fig:psd_13_model_check}

### 2022-01-24 src/figures/dataplot.py
add plot for high energy

@@ -140,12 +140,22 @@ from threeML import display_spectrum_model_counts
 
 plt.style.use("matplotlibrc")
 colors=[color1,color4,color2,color3,color5]
-f = display_spectrum_model_counts(ba_gbm_band_1,
-                                     data=['SPIDet13', 'SPIDet14', 'SPIDet15', 'SPIDet16'],
-                                     data_per_plot=5, min_rate=0.3,
-                                     model_colors=colors, data_colors=colors,
-                                     show_residuals=False);
-
+f = display_spectrum_model_counts(ba_gbm_band_1, data=['SPIDet13', 'SPIDet14', 'SPIDet16', "gbmn4"], data_per_plot=5, min_rate=0.3, model_colors=colors, data_colors=colors, show_residuals=False, source_only=True);
 f.axes[0].get_legend().remove()
-lgd = f.legend(loc='center left', bbox_to_anchor=(1, 0.6))
+f.axes[0].set_xlim(30,400)
+lgd = f.legend(loc='center left', bbox_to_anchor=(1, 0.6), labels=["SPI Det13 PSD Model", "SPI Det14 PSD Model", "SPI Det16 PSD Model",
+                                                                    "GBM NaI-4 Model","SPI Det13 PSD Data", "SPI Det14 PSD Data",
+                                                                    "SPI Det16 PSD Data", "GBM NaI-4 Data"])
 f.savefig("fit_plot.pdf")
+
+f = display_spectrum_model_counts(ba_gbm_band_1,
+                                  data=['SPIDet13MID', 'SPIDet14MID', 'SPIDet16MID', "gbmb0"],
+                                  data_per_plot=5, min_rate=0.3, model_colors=colors,
+                                  data_colors=colors, show_residuals=False, source_only=True);
+f.axes[0].get_legend().remove()
+
+f.axes[0].set_xlim(400,2000)
+lgd = f.legend(labels=["SPI Det13 PSD Model", "SPI Det14 PSD Model", "SPI Det16 PSD Model",
+                       "GBM BGO-0 Model","SPI Det13 PSD Data", "SPI Det14 PSD Data", "SPI Det16 PSD Data", "GBM BGO-0 Data"],
+               loc='center left', bbox_to_anchor=(1, 0.6))
+f.savefig("fit_plot_high.pdf")

### 2022-01-24 src/figures/dataplot.py
label fix

@@ -143,9 +143,9 @@ colors=[color1,color4,color2,color3,color5]
 f = display_spectrum_model_counts(ba_gbm_band_1, data=['SPIDet13', 'SPIDet14', 'SPIDet16', "gbmn4"], data_per_plot=5, min_rate=0.3, model_colors=colors, data_colors=colors, show_residuals=False, source_only=True);
 f.axes[0].get_legend().remove()
 f.axes[0].set_xlim(30,400)
-lgd = f.legend(loc='center left', bbox_to_anchor=(1, 0.6), labels=["SPI Det13 PSD Model", "SPI Det14 PSD Model", "SPI Det16 PSD Model",
-                                                                    "GBM NaI-4 Model","SPI Det13 PSD Data", "SPI Det14 PSD Data",
-                                                                    "SPI Det16 PSD Data", "GBM NaI-4 Data"])
+lgd = f.legend(loc='center left', bbox_to_anchor=(1, 0.6), labels=["SPI Det13 Model", "SPI Det14 Model", "SPI Det16 Model",
+                                                                    "GBM NaI-4 Model","SPI Det13 Data", "SPI Det14 Data",
+                                                                    "SPI Det16 Data", "GBM NaI-4 Data"])
 f.savefig("fit_plot.pdf")
 
 f = display_spectrum_model_counts(ba_gbm_band_1,

### 2022-01-25 src/ms.tex
add plot for high energy
next version

@@
 
+%\usepackage[style=authoryear-comp, maxnames=2, uniquelist=false]{natbib}
 %\usepackage{natbib}
@@
 \def\fdg{\hbox{$.\!\!^\circ$}}          % Fractions of degrees
+
 \begin{document}
@@
 \abstract{
-INTEGRAL/SPI is a coded mask instrument observing in the keV to MeV energy range, which covers the peak of the $\nu F\nu$ spectrum of most Gamma-Ray Bursts (GRBs).
-Since its launch, Fermi/GBM has been the primary instrument for analyzing GRBs in the energy range between $\approx$ 10 keV to $\approx$ 10 MeV.
-Herein, we show that SPI, covering a similar energy range, can give equivalently constraining results if we use an advanced analysis method.
-Also, combining the data of both instruments reduces the allowed parameter space.
+INTEGRAL/SPI is a coded mask instrument observing since 2002 in the keV to MeV energy range, which covers the peak of the $\nu F\nu$ spectrum of most Gamma-Ray Bursts (GRBs).
+Since its launch in 2008, Fermi/GBM has been the primary instrument for analyzing GRBs in the energy range between $\approx$ 10 keV to $\approx$ 10 MeV.
+Herein, we show that SPI, covering a similar energy range, can give equivalently constraining results for some parameters if we use an advanced analysis method.
+Also, combining the data of both instruments reduces the allowed parameter space in spectral fits.
 The main advantage of SPI as compared to GBM is the energy resolution of $\approx$ 0.2\% at 1.3 MeV compared to $\approx$ 10\% for GBM.
-Therefore, it is an ideal instrument to precisely measure the curvature of the spectrum.
-This is important, as it has been shown in recent years that one has to fit physical models to GRB data to obtain more insights into their still unknown emission mechanism and the curvature of the peak is unique to the different physical models.
-To fit physical models to SPI GRB data and get the maximal amount of information from the data, we developed a new analysis software {\tt PySPI}.
+Therefore, SPI is an ideal instrument to precisely measure the curvature of the spectrum.
+This is important, as it has been shown in recent years that physical models rather than heuristic functions have should be fit to GRB data to obtain better insights into their still unknown emission mechanism, and the curvature of the peak is unique to the different physical models.
+To fit physical models to SPI GRB data and get the maximal amount of information from the data, we developed a new open source analysis software {\tt PySPI}.
 We apply these new techniques to GRB 120711A in order to validate and showcase {\tt PySPI}'s capabilities.
@@
 In addition, we demonstrate that the GBM and the SPI data of this GRB can be fitted well with a physical synchrotron model.
-This evinces that SPI can play an important role in GRB model fitting.
+This evinces that SPI can play an important role in GRB spectral model fitting.
 }
@@
 
-Gamma-Ray Bursts (GRBs) are short transient bursts of $X-$ and $\gamma$-rays \citep{Klebesadel+1973}, with a typical active time range between a few ms and few hundred seconds for the prompt phase.
+Gamma-Ray Bursts (GRBs) are short transient bursts of $X-$ and $\gamma$-rays \citep{Klebesadel+1973}, with a typical active time between a few ms and few hundred seconds for the prompt phase.
 %which is mostly observed in $X$- and $\gamma$-rays.
@@
 Two of the possible emission mechanisms are synchrotron \citep[e.g.][]{syn_shell, bosnjak_syn, synch} and photospheric emission \citep[e.g.][]{Goodman1986, photo_1, photo_2, photo_3}.
-In the past, GRB data were often fitted with empirical function like the Band function \citep{band}, to conclude from the fit parameters which physical model is preferred.
+In the past, GRB data were often fitted with empirical functions like the Band function \citep{band}, to conclude from the fit parameters which physical model is preferred.
 In recent years it has been shown, that this approach can be misleading and that one should rather fit physical models directly to the data \citep{Burgess-2014, physical_models, synch}.
-An example for this is the so-called `line-of-death' for synchrotron emission \citep{line-of-death, line-of-death2}, which states that synchrotron radiation can not be the universal emission mechanism, if fits with a Band function give a low energy power law slope larger than $-2/3$.
+A prominent example for this is the so-called `line-of-death' for synchrotron emission \citep{line-of-death, line-of-death2}, which states that synchrotron radiation can not be the universal emission mechanism, if fits with a Band function give a low energy power law slope larger than $-2/3$.
 \citet{synch} have shown that this conclusion is flawed and that one can fit GRB spectra well with a physical synchrotron model even though the same spectra violate the line-of-death if fitted with a Band function.
-Another proposed proxy for physical emission processes in GRB  is the spectral curvature of empirical model fits to GRB data \citep{Yu-2015, Axelsson-2015}.
+Another proposed proxy for physical emission processes in GRBs is the spectral curvature of empirical model fits to GRB data \citep{Yu-2015, Axelsson-2015}.
 This too has been shown to be an inaccurate indicator of the emission process \citep{Burgess2019}.
-Thus, the use of physical models remains the best tool for deciphering the emission processes occurring in these relativistic outflows.
+Thus, the use of physical models remains the best tool for deciphering the emission processes occurring in the relativistic outflows of GRBs.
 
@@
 
-The spectrometer SPI is one of the instruments onboard of the INTErnational Gamma-Ray Astrophysics Laboratory \citep[INTEGRAL;][]{integral} satellite, that was launched in 2002.
-It is a coded mask instrument, with a fully coded field-of-view of 16 degrees, that covers an energy range between 20 keV and 8 MeV.
-The energy resolution allows the identification of fine features, like nuclear decay lines \citep{spi_main}.
-In the case of GRBs this energy resolution gives us the possibility to determine the curvature of the spectra with unprecedented precision.
+The spectrometer SPI \citep{spi_main} is one of the instruments onboard of the INTErnational Gamma-Ray Astrophysics Laboratory \citep[INTEGRAL;][]{integral} satellite, that was launched in 2002.
+It is a coded mask instrument, with a fully coded field-of-view of 16 degrees, covering an energy range between 20 keV and 8 MeV.
+The unprecedented energy resolution allows the identification of fine spectral features, like nuclear decay lines \citep{Roques+2003, Diehl+2006} and curvature in continuous spectra \citep{Jourdain-2020}.
+%In the case of GRBs this energy resolution gives us the possibility to determine the curvature of the spectra with unprecedented precision.
 
-The standard analysis of SPI GRB data is done within the INTEGRAL Offline Scientific Analysis ({\tt OSA}) software \citep{osa}.
-This uses a two step method of first using only the photo peak response to incorporate the mask pattern on the detectors and in a second step applying an energy redistribution correction response.
+The standard analysis of SPI GRB data is done within the INTEGRAL Offline Scientific Analysis ({\tt OSA}) software \citep{osa}, including SPI-specific routines \citep{Diehl+2003}.
+A two step method is applied, by first using only the photo peak response to incorporate the mask pattern on the detectors and in a second step applying an energy redistribution correction response.
 This method is used in several works which fitted empirical GRB models to the SPI data \citep{Malaguti-2003, Mereghetti-2003, Mereghetti-2003.2, Kienlin-2003, Kienlin-2003.2,Beckmann-2004, Moran-2005, Filliatre-2005.1, Filliatre-2005.2, McBreen-2006, Grebenev-2007, McGlynn-2008, Foley-2008, McGlynn-2009, Martin-Carrillo-2014}.
+
 \citet{Bosnjak-2014} used a different approach to create a spectral catalogue of INTEGRAL GRBs, with a joined analysis of SPI and the Imager on Board the INTEGRAL Satellite (IBIS).
 They construct a response for every SPI detector and forward model the photon model directly into the data space of every detector, which is similar to our approach in this work.
-But they build the response simply according to the exposed fraction of the detector for the GRB direction and use background subtracted data for their fits.
+But they build the responses and treated the background differently then we do in this work.
+We will point out the differences in the corresponding chapters in Sec.
+\ref{pyspi}.
+%But they build the response simply according to the exposed fraction of the detector for the GRB direction and use background subtracted data for their fits.
 %Several works have used SPI data for GRBs \citep{spi_grb1, spi_grb2}, but all of them fitted empirical models like the Band function.
-We developed a pure python-based analysis tool {\tt PySPI} in order to provide an easy to use data reduction and fitting tool while getting the maximal amount of information out of the data to progress to fitting physical models.
-This improves the analysis methods in general, because we use the full response to forward model the expected spectra to the native SPI data space in the correct way and offers an easy to install and use interface.
+
+Here, we developed a pure python-based analysis tool {\tt PySPI} in order to provide an easy to use data reduction and fitting tool while getting the maximal amount of information out of the data to progress to fitting physical models.
+This improves the analysis method in general, because we use the full response to forward model the expected spectra to the native SPI data space and use the correct likelihood to take the Poisson nature of the measurements into account.
+It also offers an easy to install and use interface.
 %In this paper we introduce the new analysis method and show that we can fit complicated physical GRB models to the SPI data
-
 This work is structured as follows: In Sec.
-\ref{methods} we summarize the different methods and concepts for SPI GRB data analysis, which also includes a detailed description of the new analysis method within {\tt PySPI} in Sec.
+\ref{methods} we summarize the different methods and concepts for SPI GRB data analysis, and provide a detailed description of the new analysis method within {\tt PySPI} in Sec.
 \ref{pyspi}.
@@
 All gamma-ray instruments suffer from energy dispersion and finite energy resolution.
-The information about this is encoded in the response matrix, that gives the probability of a photon with a certain energy and starting position on the sky to be detected in one of electronic channels of the detector.
+The information about this is encoded in the response matrix, that gives the probability of a photon with a certain energy and starting position on the sky to be detected in one of the electronic channels of the detector.
 These response matrices are usually not invertible, and therefore we have to forward fold the photon spectrum trough the response matrix into the data space of the detected counts and compare them, using the correct likelihood.
@@
 % distribution of how much energy a photon with a certain energy deposit in the crystal and what energy is in the end measured for this deposited energy.
-The response is split into two components: The Image Response Functions (IRFs) and Redistribution Matrix Files (RMFs).
+The response is split into two components, namely the Image Response Functions (IRFs) and Redistribution Matrix Files (RMFs).
 The IRFs contain the information of the total effective area for a photon to interact at all and the RMFs contain the information about the probability in which electronic channel an interacting photon will be measured.
-For SPI both these components were derived by \citet{spi_response}.
+
+For SPI both these components were derived with extensive GEANT simulations \citep{spi_response}.
 The SPI IRF files give the total effective area for three different interaction types:
-\begin{itemize}
-  \item Photo peak events
-  \item Non photo peak events that first interact in the Ge crystal
-  \item Non photo peak events that first interact in passive material
-\end{itemize}
-\noindent
-These effective areas were calculated for 51 photon energies and on a 0.5 degree grid out to 23.5 degree from on-axis.
-For each of the three interaction types, there is one RMF, to define the shape of the redistributed spectra, assuming that this shape does not depend on the detector or the incident angles of the photons.
+%\begin{itemize}
+ (1) Photo peak events;
+ (2) Non photo-peak events that first interact in the Ge crystal, and
+ (3) Non photo-peak events that first interact in passive material.
+%\end{itemize}
+%\noindent
+These effective areas were calculated for 51 photon energies and on a 0\fdg5  grid out to 23\fdg5 from the on-axis direction.
+For each of the three interaction types, there is one RMF to define the shape of the redistributed spectra, assuming that this shape does not depend on the detector or the incident angles of the photons.
 The procedure to construct the response includes several simplification to keep the computational costs and storage space manageable \citep{spi_response}.
@@
 It is also known, that these spurious events do not show up in events with a detection also in the Pulse Shape Discriminator (PSD) electronics.
-The reason for this is that the PSD electronics have a low energy threshold of $\approx$ 450 keV (the exact value has been changed a few times during the mission) \citep{spi_electronic_noise}.
-Therefore only events that deposit more than this low energy threshold in the Germanium crystal can trigger this electronic chain, which eliminates the <100 keV events that are detected at the wrong energies by the AFEE.
+The reason for this is that the PSD electronics have a low energy threshold of $\approx$450 keV and a high energy threshold of $\approx$2700 keV (the exact value has been changed a few times during the mission) \citep{spi_electronic_noise}.
+Therefore, only events that deposit more than this low energy threshold in the Germanium crystal can trigger this electronic chain, which eliminates the $<$100 keV events that are detected at the wrong energies by the AFEE.
 In Fig.
 \ref{fig:electronic} one can see that the feature at 1.5 MeV is nicely visible in the Non-PSD events but is missing in the PSD events.
-Even though this problem is most significant in the area around 1.5 MeV it is also important at lower energies >400 keV.
+Even though this problem is most significant in the area around 1.5 MeV it is also important at lower energies $>$400 keV.
+The electronic noise is not stable and depends on the signal strength \citep{spi_electronic_noise}, therefore it can not be included in the response and has to be treated differently.
 
@@
 
-Analyzing GRB data from SPI with the {\tt OSA} tools is a multistep process.
+Analyzing GRB data from SPI with the {\tt OSA} tools is a multi-step process.
 The first steps cover selecting the science window containing the GRB, the time intervals for active time and background time as well as the energy bins for the analysis.
-After that one can either find the location of the GRB with SPIROS, i.e.
+Then, one can either find the location of the GRB with SPIROS, i.e.
 an iterative source removal algorithm for SPI data \citep{Skinner-2003}, or set it manually if it is already known.
@@
 
-The first step in the spectral fitting with {\tt OSA} is to use only the photo peak response of the detectors.
+The first step in the spectral fitting with {\tt OSA} is to use only the photo-peak response of the detectors.
 These responses depend on the source position, as this defines for example the absorption by the mask.
@@
 \label{pyspi}
-To fit SPI GRB data, we developed a new python package {\tt PySPI} \citep{joss}, which is an open source analysis tool.
-In the following we will summarize the main points of GRB analysis within {\tt PySPI}.
+To fit SPI GRB data, we developed a new python package {\tt PySPI} \citep{joss}.
+%which is an open source analysis tool. In the following
+Below, e summarize the main points of GRB analysis within {\tt PySPI}.
 
@@
 GRBs are transient sources with a typical duration of up to a few tens of seconds.
-Therefore, we can use the time intervals during a pointed observation, when the transient source is not active, as an independent temporal off-source observation (see Fig.
+Therefore, we can use the time intervals during a single pointed observation (science window), when the transient source is not active, as an independent temporal off-source observation (see Fig.
 \ref{fig:lightcurve}).
@@
 where $b_{\mathrm{i}}$ are the background rates per energy channel, $B_{\mathrm{i}}$ are the detected counts in the off-source observation and $t_{\mathrm{b}}$ is the exposure of the off-source observation.
+
 \begin{figure}
@@
         \includegraphics{figures/lightcurve.pdf}
-        \caption{Lightcurve for SPI detector 0 for GRB120711A.
+        \caption{Lightcurve for SPI detector 0 for GRB 120711A.
 The transient source is clearly visible as well as the constant background for the time when the transient is not active.
@@
 
-% add a lightcurve plot?
+This background treatment is different from what is done in \citet{Bosnjak-2014}, where they used background subtracted data in their analysis.
+It has been shown that using background subtraction can give misleading results \citep[e.g.][]{Greiner-2016}.
 
@@
 
-With the defined background distributions, we can construct a likelihood, given by Eq.
+With the defined background distribution, we can construct a likelihood, given by Eq.
 \ref{eq:likelihood_m_and_b}, that connects the source and background model with the Poisson process data of the background and active time interval, via the response.
@@
 
+\noindent
 If there was a spectral model for the background, we would fit the background and the source model at the same time with the likelihood given in Eq.
@@
 nuclear de-excitation line emission \citep{spi_bkg}.
-Therefore the background consists of several hundred different nuclear lines \citep{spi_bkg}, which makes an accurate spectral model for the background impossible at the moment.
+Therefore, the background consists of several hundred different nuclear lines \citep{spi_bkg}, which makes an accurate spectral model for the background impossible at the moment.
 But we can marginalize over the parameters $b_{\mathrm{i}}$ using only the fact that they can not be negative, which leaves us with Eq.
@@
 
+\noindent
 The marginalisation is equivalent to integrating out the background rate parameter assuming a uniform prior from 0 to $\infty$.
@@
 
+\noindent
 These values are then substituted into the likelihood Eq.
 \ref{eq:likelihood_m_and_b} to eliminate the $b_{\mathrm{i}}$ dependency.
-This gives the exact solution for the maximum of the likelihood, for likelihood values close to the maximum, the assumption is that most of the likelihood in the integrand in Eq.
+This gives the exact solution for the maximum of the likelihood; for likelihood values close to the maximum, the assumption is that most of the likelihood in the integrand in Eq.
 \ref{eq:likelihood_marg} is in a small area around $b_{\mathrm{i,max}}$.
@@
 
-In {\tt PySPI}, we use the official response files, like described in Sec.
-\ref{response}, interpolate them to the wanted energy bins and source positions and construct one response matrix incorporating all the information about the effective areas and energy redistribution.
-
+In {\tt PySPI}, we use the official response files, as described in Sec.
+\ref{response}, interpolate them to the wanted energy bins and source positions and construct one response matrix incorporating all the information about the effective area and energy redistribution.
+This also includes that we take into account that the mask is not absorbing 100\% of the photons flying through it.
+This is different to the work presented in \citet{Bosnjak-2014}, that used a `response function' simply taking into account the exposed fraction of each detector and therefore assuming a mask that absorbs 100\% of the photons for every photon energy.
 \subsubsection{Electronic Noise}
@@
 \ref{electronic}).
-To account for the larger dead time of the PSD electronics, an effective area correction can be either fixed to 85 \% \citep{spi_electronic_noise} or treated as a free parameter of the model.
+To account for the larger dead time of the PSD electronics, an effective area correction can be either fixed to 85\% \citep{spi_electronic_noise}, or treated as a free parameter of the model.
 
@@
 \begin{itemize}
+  \vspace{-0.2cm}
   \item sample model parameters
@@
 
-Similarly, the BALROG (BAyesian Lo-cation Reconstruction Of GRBs) algorithm for localizing GRBs with Fermi/GBM employs the same method \citep{balrog}, which shows that forward folding allows one to localize photons with a non-imaging instrument.
-It is important to note that the instruments SPI and GBM are fundamentally very similar.
+\noindent
+The BALROG (BAyesian Lo-cation Reconstruction Of GRBs) algorithm for localizing GRBs with Fermi/GBM employs the same method \citep{balrog}, which shows that forward folding allows one to localize photons with a non-imaging instrument.
+It is important to realize that the instruments SPI and GBM are fundamentally very similar.
 They both consist of individual detectors that have different responses for a given source position.
-In GBM, this is due to the different pointing directions of the detectors and in SPI due to the varying obscuration by the mask.
-Even though SPI is defined as a coded mask instrument, we don't have to treat it specially.
-The information the mask encodes into the data is automatically included by using the different responses for the detectors and a forward folding method.
+In GBM, this is due to the different pointing directions of the detectors, and in SPI due to the varying obscuration by the mask.
+Even though SPI is defined as a coded-mask instrument, we don't have to treat it specially.
+The information which the mask encodes into the data is automatically included by using the different responses for the detectors and a forward folding method.
 
@@
 This allows one to fit SPI data together with data from other instruments, such as Fermi/GBM\footnote{See threeml.readthedocs.io}.
-Also {\tt PySPI} is an open source software, which is publicly available on GitHub \citep{joss} and there is a documentation, with a few examples\footnote{See pyspi.readthedocs.io}.
+{\tt PySPI} is an open source software, which is publicly available on GitHub \citep{joss}, including documentation with examples\footnote{See pyspi.readthedocs.io}.
 
@@
 We use {\tt pynchrotron}\footnote{https://github.com/grburgess/pynchrotron} to calculate the spectrum from a physical spectral synchrotron model.
-This model was previously used to successfully fit many single pulse GRBs observed with GBM in \citet{synch}, which also includes a detailed description of the model.
-Here we summarize the main points briefly.
+This model was previously used to successfully fit many single-pulse GRBs observed with Fermi/GBM in \citet{synch}, which also includes a detailed description of the model.
+Here we summarize the main points.
 
-The core of the model is the assumption of some generic acceleration mechanism, that constantly accelerates an electron spectrum into a power law $N(\gamma )\propto \gamma^{-p}$ between $\gamma_{\textrm{inj}}$ and $\gamma_{\textrm{max}}$.
+The core of the model is the assumption of some generic acceleration mechanism, that constantly accelerates electrons into a power law spectrum $N(\gamma )\propto \gamma^{-p}$ between $\gamma_{\textrm{inj}}$ and $\gamma_{\textrm{max}}$.
 These electrons are cooled via the emission of synchrotron photons in a magnetic field.
@@
 \begin{enumerate}
+  \vspace{-0.2cm}
 	\item Magnetic field strength $B$
@@
 
+\noindent
 There exists a strong degeneracy between $B$ and $\gamma_{\mathrm{inj}}$, as their combination sets the peak of the photon spectrum.
 Therefore we fix $\gamma_{\mathrm{inj}}=10^{5}$ and only fit for $B$.
-Thus the results for $\gamma_{\mathrm{max}}$ and $\gamma_{\mathrm{cool}}$ are determined relative to the fixed $\gamma_{\mathrm{inj}}$.
+% the following is just duplication
+%Thus, the results for $\gamma_{\mathrm{max}}$ and $\gamma_{\mathrm{cool}}$ are determined relative to the fixed $\gamma_{\mathrm{inj}}$.
 
@@
 \end{equation}
+
 \noindent
@@
 \label{analysis}
-In this work, we analyze GRB 120711A, which was a bright, multi-pulse GRB with a precursor and a long emission period of $\approx$100 s.
-It was detected by SPI and GBM \citep{GCN_integral, GCN_gbm}.
-Additionally Swift-XRT \citep{GCN_swift} observed the afterglow.
+As an example, we analyze GRB 120711A, a bright, multi-pulse GRB with a precursor and a long emission period of $\approx$100 s. It was detected by SPI and GBM \citep{GCN_integral, GCN_gbm}.
+%Additionally, Swift-XRT \citep{GCN_swift} observed the afterglow.
 We look at one time interval with a duration of 10 seconds around the first bright peak in the light curve (see Fig.
 \ref{fig:time_selection}).
-From the XRT detection we know the position of the GRB (RA: 94\fdg68, DEC: -71\fdg00 in J2000).
-GRB 120711A was previously analyzed with SPI data by \citet{Martin-Carrillo-2014}, but their work was mainly focused on the post-GRB emission properties.
-For the prompt emission they only fitted the time averaged spectrum over the $T_{90}$ emission (between 0 and 115 seconds after the trigger), with an empirical exponential cutoff power-law model.
+From the Swift/XRT detection of the afterglow we know an accurate position of the GRB (RA = 94\fdg68, Decl.
+= -71\fdg00 in J2000) \citep{GCN_swift}.
+The SPI data of GRB 120711A were previously analyzed by \citet{Martin-Carrillo-2014}, but only fitted the time averaged spectrum over the $T_{90}$ emission (between 0 and 115 seconds after the trigger) with an empirical exponential cutoff power-law model, while focussing on the post-GRB emission properties.
 
@@
     \includegraphics[width=1\linewidth]{figures/gbm_lightcurve_ts.pdf}
-    \caption{Light curve for GRB120711A in one GBM and one SPI detector.
+    \caption{Light curve for GRB 120711A in one GBM and one SPI detector.
 The green shaded area marks part of the time intervals used for the independent background observation and the blue shaded area is the active time interval used in the fit.}
@@
 
-First, we fit the data with the empirical Band function.
-With this we show a comparison between the fit results with {\tt PySPI} and {\tt OSA} (Sec.
-\ref{pyspi_osa}) and check if the results for SPI and GBM are in agreement (Sec.
+First, we fit the data with the empirical Band function, show a comparison between the fit results using {\tt PySPI} versus {\tt OSA} (Sec.
+\ref{pyspi_osa}), and check if the results for SPI and GBM are in agreement (Sec.
 \ref{pyspi_gbm}).
-Then, we fit the SPI and GBM data simultaneously with a physical synchrotron model, to check wether including SPI in the analysis can reduce the allowed parameter space (Sec.
+Then, we fit the SPI and GBM data simultaneously with a physical synchrotron model, to check whether including SPI in the analysis can reduce the allowed parameter space (Sec.
 \ref{pyspi_gbm_joined}).
@@
 For all GBM and {\tt PySPI} fits we added effective area correction parameters in the fit, allowing the total effective area of the individual detectors to vary with respect to each other, to account for slightly different calibrations.
-To do this, we fix the response of one of the detectors to the response of that detector and fit one parameter for every other detector.
-We constrain the effective area correction parameters to be between 0.7 and 1.3.
+To do this, we fix the response of one of the detectors
+%to the response of that detector
+and fit one parameter for every other detector. We constrain the effective area correction parameters to be between 0.7 and 1.3.
 
@@
 
-\subsection{Compare {\tt PySPI} and {\tt OSA}}
+\subsection{Comparing {\tt PySPI} and {\tt OSA}}
 \label{pyspi_osa}
-We analyze the SPI data with a Band function as a spectral model for the same time interval with {\tt PySPI} and {\tt OSA}, to check if the results are in agreement.
+We fit the SPI data of an identical time interval with a Band function
+%as a spectral model
+within {\tt PySPI} and {\tt OSA}.
+%to check if the results are in agreement.
 Fig.
@@
     \includegraphics[width=1\linewidth]{figures/pyspi_vs_osa_band.pdf}
-    \caption{Corner plot for the SPI fit with {\tt PySPI} and {\tt OSA}.
-The spectral model in this fit is a Band function.
-The results are in agreement, however {\tt PySPI} constrains the parameters more precisely.}
+    \caption{Corner plot for the Band function fit to the SPI data with {\tt PySPI} and {\tt OSA}.  The results are in agreement, but {\tt PySPI} constrains the parameters more precisely.}
     \label{fig:corner_osa_pyspi_band}
@@
 
-\subsection{Compare SPI and GBM}
+\subsection{Comparing SPI and GBM}
 \label{pyspi_gbm}
-Next, we analyze SPI data with {\tt PySPI} and the GBM data with the GRB analysis within 3ML with a Band function model.
+Next, we analyze SPI data with {\tt PySPI} and the GBM data with the GRB analysis within 3ML, again with a Band function.
 Fig.
 \ref{fig:corner_gbm_pyspi_band} shows the results for these fits, demonstrating that the results for the spectral shape from SPI and GBM are in agreement.
-It also shows that the calibration for SPI and GBM are well aligned within only $\approx$ 10\% difference in this case, which is within the usual calibration offsets of gamma-ray space telescopes.
+It also shows that the effective area calibration for SPI and GBM are well aligned within only $\approx$10\% difference ($K$ parameter), which is well within the
+%usual calibration offsets of gamma-ray space telescopes.
+uncertainties as specified in the corresponding instrument publications.
 
@@
 \label{pyspi_gbm_joined}
-We perform a a joint fit of SPI and GBM data with a physical synchrotron model (see Sec.
+We perform a joint fit of SPI and GBM data with a physical synchrotron model (see Sec.
 \ref{synch}).
@@
     \includegraphics[width=1\linewidth]{figures/fit_plot.pdf}
-    \caption{Data and best fit model for four of the SPI detectors in count space. The spectral model for this fit was a physical synchrotron model.}
+    \includegraphics[width=1\linewidth]{figures/fit_plot_high.pdf}
+    \caption{Data and best fit model in count space for three of the SPI detectors and one of the NaI (BGO) detectors of GBM in the upper (lower) plot.
+The spectral model for this fit was a physical synchrotron model.}
     \label{fig:dataplot}
@@
 \end{figure*}
-\clearpage
+
 \section{Conclusion}
@@
 We show that the GBM as well as the SPI data for GRB 120711A can be fitted well with a physical synchrotron model and that combining the data in a simultaneous fit improves the parameter constraints.
-Consequently, SPI can play an important role in physical GRB model checking.
-%if we apply a forward modelling method which is used in {\tt PySPI}, as described in Sec. \ref{pyspi}.
+Consequently, SPI can play an important role in physical GRB model checking, if we apply a forward modelling method which is used in {\tt PySPI}, as described in Sec.
+\ref{pyspi}.
 
@@
 TS acknowledges support by the Bundesministerium f\"ur Wirtschaft und Energie via the Deutsches Zentrum f\"ur Luft- und Raumfahrt (DLR) under contract number 50 OX 2201.
-This work made use of the following software packages:
-%\section*{Software}
+This work made use of the following software packages:\\
 {\tt 3ML} \citep{3ML}, {\tt Astromodels} \citep{astromodels}, {\tt Matplotlib} \citep{matplotlib}, {\tt ChainConsumer} \citep{chainconsumer, chainconsumer2}, {\tt OSA} \citep{osa}, {\tt Numpy} \citep{numpy}, {\tt MultiNest} \citep{multinest, multinest1, multinest3}

### 2022-01-25 src/figures/corner_osa_pyspi_band.py

@@ -20,7 +20,7 @@ c = ChainConsumer()
 chain = loadtxt2d('./chains/OSA_BAND_post_equal_weights.dat')
 
 c.add_chain(chain[:,:4], parameters=['K', r'$\alpha$', r'$E_{peak}$', r'$\beta$'],
-            name='Official Tools', color=color2)
+            name='Standard Tools', color=color2)
 
 chain = loadtxt2d('./chains/PYSPI_BAND_post_equal_weights.dat')
 

### 2022-01-25 src/figures/model_plot_band.py

@@ -76,7 +76,7 @@ ax.fill_between(e, e**2*mi, e**2*ma, color=color3, alpha=1, label="PySPI")
 
 mi = np.percentile(vals_osa, 50-q/2, axis=0)
 ma = np.percentile(vals_osa, 50+q/2, axis=0)
-ax.fill_between(e, e**2*mi, e**2*ma, color=color2, alpha=0.5, label="Official Tools")
+ax.fill_between(e, e**2*mi, e**2*ma, color=color2, alpha=0.5, label="Standard Tools")
 
 ax.set_xscale("log")
 ax.set_yscale("log")

### 2022-01-25 src/ms.tex
tex fix
READY FOR SUBMISSION

@@
 \usepackage{float}
+
+\usepackage[pdftex]{xcolor}
+\definecolor{citecolor}{HTML}{195D95}
+\definecolor{BrickRed}{HTML}{C41010}
+\definecolor{Navy}{HTML}{C41010}
+
+\def\me#1{\textcolor{BrickRed}{jcg: \textbf{ #1}}}
+\newcommand{\BB}[1]{\textcolor{purple}{\textsf{(BB: #1)}}}
 
@@
 But they build the responses and treated the background differently then we do in this work.
-We will point out the differences in the corresponding chapters in Sec.
+We will point out the differences in Sec.
 \ref{pyspi}.
@@
 It is also known, that these spurious events do not show up in events with a detection also in the Pulse Shape Discriminator (PSD) electronics.
-The reason for this is that the PSD electronics have a low energy threshold of $\approx$450 keV and a high energy threshold of $\approx$2700 keV (the exact value has been changed a few times during the mission) \citep{spi_electronic_noise}.
+The reason for this is that the PSD electronics have a low energy threshold of $\approx$450 keV and a high energy threshold of $\approx$2700 keV (the exact values have been changed a few times during the mission) \citep{spi_electronic_noise}.
 Therefore, only events that deposit more than this low energy threshold in the Germanium crystal can trigger this electronic chain, which eliminates the $<$100 keV events that are detected at the wrong energies by the AFEE.
@@
 This also includes that we take into account that the mask is not absorbing 100\% of the photons flying through it.
-This is different to the work presented in \citet{Bosnjak-2014}, that used a `response function' simply taking into account the exposed fraction of each detector and therefore assuming a mask that absorbs 100\% of the photons for every photon energy.
+This is different to the work presented in \citet{Bosnjak-2014}, which used a `response function' simply taking into account the exposed fraction of each detector and therefore assuming a mask that absorbs 100\% of the photons for every photon energy.
+
 \subsubsection{Electronic Noise}
@@
     \includegraphics[width=1\linewidth]{figures/pyspi_vs_osa_band.pdf}
-    \caption{Corner plot for the Band function fit to the SPI data with {\tt PySPI} and {\tt OSA}.  The results are in agreement, but {\tt PySPI} constrains the parameters more precisely.}
+    \caption{Corner plot for the Band function fit to the SPI data with {\tt PySPI} and {\tt OSA} to the data of GRB120711A}.
+The results are in agreement, but {\tt PySPI} constrains the parameters more precisely.
     \label{fig:corner_osa_pyspi_band}
@@
     \includegraphics[width=1\linewidth]{figures/pyspi_vs_gbm_band.pdf}
-    \caption{Corner plot for the SPI fit with {\tt PySPI} and the GBM fit.
+    \caption{Corner plot for the SPI fit with {\tt PySPI} and the GBM fit to the data of GRB120711A.
 In this fit we used a Band function as spectral model.
@@
     \includegraphics[width=1\linewidth]{figures/pyspi_and_gbm_syn.pdf}
-    \caption{Corner plot for the SPI fit with {\tt PySPI} and the GBM fit.
+    \caption{Corner plot for the SPI fit with {\tt PySPI} and the GBM fit to the data of GRB120711A.
 In this fit we used a physical synchrotron model (see Sec.
@@
     \includegraphics[width=0.45\linewidth]{figures/band_pyspi_gbm.pdf}
-    \caption{Model posterior plots (95\% confidence region) for the results with the Band function model.
+    \caption{Model posterior plots (95\% confidence region) for the results with the Band function model and the data for GRB120711A.
 Left panel shows the results for the {\tt PySPI} fit compared to the fit using {\tt OSA} and the right panel the {\tt PySPI} fit compared to the GBM fit.}
@@
     \includegraphics[width=0.45\linewidth]{figures/gbm_combined.pdf}
-    \caption{Model posterior plots (95\% confidence region) for the results with the physical synchrotron model.
+    \caption{Model posterior plots (95\% confidence region) for the results with the physical synchrotron model and the data for GRB120711A.
 Left panel shows the results for the SPI alone fit compared to the combined fit and the right panel the GBM alone fit compared to the combined fit.
@@
     \includegraphics[width=1\linewidth]{figures/fit_plot_high.pdf}
-    \caption{Data and best fit model in count space for three of the SPI detectors and one of the NaI (BGO) detectors of GBM in the upper (lower) plot.
+    \caption{Data (for GRB120711A) and best fit model in count space for three of the SPI detectors and one of the NaI (BGO) detectors of GBM in the upper (lower) plot.
 The spectral model for this fit was a physical synchrotron model.}
@@
 We show that the GBM as well as the SPI data for GRB 120711A can be fitted well with a physical synchrotron model and that combining the data in a simultaneous fit improves the parameter constraints.
-Consequently, SPI can play an important role in physical GRB model checking, if we apply a forward modelling method which is used in {\tt PySPI}, as described in Sec.
-\ref{pyspi}.
+Consequently, SPI can play an important role in physical GRB model checking.
+%, if we apply a forward modelling method which is used in {\tt PySPI}, as described in Sec. \ref{pyspi}.
 

### 2022-01-25 src/ms.tex
fix
few typos

@@
 \usepackage{float}
-
-\usepackage[pdftex]{xcolor}
-\definecolor{citecolor}{HTML}{195D95}
-\definecolor{BrickRed}{HTML}{C41010}
-\definecolor{Navy}{HTML}{C41010}
-
-\def\me#1{\textcolor{BrickRed}{jcg: \textbf{ #1}}}
-\newcommand{\BB}[1]{\textcolor{purple}{\textsf{(BB: #1)}}}
 
@@
 Therefore, SPI is an ideal instrument to precisely measure the curvature of the spectrum.
-This is important, as it has been shown in recent years that physical models rather than heuristic functions have should be fit to GRB data to obtain better insights into their still unknown emission mechanism, and the curvature of the peak is unique to the different physical models.
+This is important, as it has been shown in recent years that physical models rather than heuristic functions should be fit to GRB data to obtain better insights into their still unknown emission mechanism, and the curvature of the peak is unique to the different physical models.
 To fit physical models to SPI GRB data and get the maximal amount of information from the data, we developed a new open source analysis software {\tt PySPI}.
@@
 It is also known, that these spurious events do not show up in events with a detection also in the Pulse Shape Discriminator (PSD) electronics.
-The reason for this is that the PSD electronics have a low energy threshold of $\approx$450 keV and a high energy threshold of $\approx$2700 keV (the exact values have been changed a few times during the mission) \citep{spi_electronic_noise}.
+The reason for this is that the PSD electronics have a low energy threshold of $\approx$450 keV and a high energy threshold of $\approx$2700 keV \citep[the exact values have been changed a few times during the mission; ][]{spi_electronic_noise}.
 Therefore, only events that deposit more than this low energy threshold in the Germanium crystal can trigger this electronic chain, which eliminates the $<$100 keV events that are detected at the wrong energies by the AFEE.
@@
 %which is an open source analysis tool. In the following
-Below, e summarize the main points of GRB analysis within {\tt PySPI}.
+Below, we summarize the main points of GRB analysis within {\tt PySPI}.
 
@@
 \noindent
-The BALROG (BAyesian Lo-cation Reconstruction Of GRBs) algorithm for localizing GRBs with Fermi/GBM employs the same method \citep{balrog}, which shows that forward folding allows one to localize photons with a non-imaging instrument.
+The BALROG (BAyesian Lo-cation Reconstruction Of GRBs) algorithm for localizing GRBs with Fermi/GBM employs the same method \citep{balrog}, which shows that forward folding allows one to localize photon sources with a non-imaging instrument.
 It is important to realize that the instruments SPI and GBM are fundamentally very similar.
@@
     \includegraphics[width=1\linewidth]{figures/pyspi_vs_osa_band.pdf}
-    \caption{Corner plot for the Band function fit to the SPI data with {\tt PySPI} and {\tt OSA} to the data of GRB120711A}.
-The results are in agreement, but {\tt PySPI} constrains the parameters more precisely.
+    \caption{Corner plot for the Band function fit to the SPI data with {\tt PySPI} and {\tt OSA} to the data of GRB120711A.
+The results are in agreement, but {\tt PySPI} constrains the parameters more precisely.}
     \label{fig:corner_osa_pyspi_band}

### 2022-02-03 src/ms.tex
add cite
fix

@@
 It is a coded mask instrument, with a fully coded field-of-view of 16 degrees, covering an energy range between 20 keV and 8 MeV.
-The unprecedented energy resolution allows the identification of fine spectral features, like nuclear decay lines \citep{Roques+2003, Diehl+2006} and curvature in continuous spectra \citep{Jourdain-2020}.
+The unprecedented energy resolution allows the identification of fine spectral features, like nuclear decay lines \citep{Roques-2003, Diehl-2006} and curvature in continuous spectra \citep{Jourdain-2020}.
 %In the case of GRBs this energy resolution gives us the possibility to determine the curvature of the spectra with unprecedented precision.
 
-The standard analysis of SPI GRB data is done within the INTEGRAL Offline Scientific Analysis ({\tt OSA}) software \citep{osa}, including SPI-specific routines \citep{Diehl+2003}.
+The standard analysis of SPI GRB data is done within the INTEGRAL Offline Scientific Analysis ({\tt OSA}) software \citep{osa}, including SPI-specific routines \citep{Diehl-2003}.
 A two step method is applied, by first using only the photo peak response to incorporate the mask pattern on the detectors and in a second step applying an energy redistribution correction response.
@@
 The information which the mask encodes into the data is automatically included by using the different responses for the detectors and a forward folding method.
+A similar approach is used in \citet{Tohuvavohu-2021}, that introduces a new forward folding method to detect and localize faint GRBs with the coded mask instrument Swift/BAT.
 

### 2022-03-01 src/ms.tex
add loc

@@
 \bibliography{bib}
+\begin{appendix}
 
-\begin{appendix}
+  \section{Localizing GRB 120711A}
+
+  It is also possible to localize GRBs with PySPI.
+To localize we vary the spectrum parameters and the location of the source at the same time in one fit.
+For this, PySPi has a fast response generator, that uses the base response simulation grid to generate the response for any given source position quickly.
+Fig ?
+shows the localization we get if we fit the location and use a Band function as spectral model.
+We also marked the position of the GRB measured by Swift/XRT, which shows that the result with the SPI data is in agreement with the Swift/XRT observation.
+For this fit we only used the energies up to 600 keV, to avoid the PSD energy region.
+
+  \begin{figure}
+  \begin{centering}
+    \includegraphics[width=1\linewidth]{figures/loc.pdf}
+    \caption{Localization of GRB120711A with PySPI with contours giving the statistical only 1 and 2 sigma areas.
+We estimate an additional systematic error of $\approx$ 0.5 degree because that is the resolution of the grid points in the response simulation.
+The dashed lines mark the position observed by Swift/XRT.}
+    \label{fig:dataplot}
+  \end{centering}
+\end{figure}
+
 \onecolumn

### 2022-03-01 src/figures/localization.py

@@ -1,0 +1,29 @@
+from chainconsumer import ChainConsumer
+import numpy as np
+import matplotlib.pyplot as plt
+plt.style.use("matplotlibrc")
+
+color1 = "#544b3d"
+color2 = "#340068"
+color3 = "#4cb944"
+color4 = "#4f7cac"
+color5 = "#6d2e46"
+
+def loadtxt2d(intext):
+        try:
+            return np.loadtxt(intext, ndmin=2)
+        except:
+            return np.loadtxt(intext)
+
+c = ChainConsumer()
+
+chain = loadtxt2d('./chains/PYSPI_BAND_loc2_post_equal_weights.dat')
+
+c.add_chain(chain[:,:6], parameters=['ra', 'dec', 'K', r'$\alpha$', r'$E_{peak}$', r'$\beta$'],
+            name='PYSPI', color=color3)
+
+c.configure(plot_hists=False, kde=1.0, shade_alpha=0.5)
+
+c.plotter.plot(filename="loc.pdf",
+               parameters=['ra', 'dec'],
+               truth=[94.67830, -70.99905]);

### 2022-03-01 src/ms.tex
right label
add Bosnjak section

@@
 \usepackage{float}
-
+\newcommand{\BB}[1]{\textcolor{red}{\textsf{#1}}}
 %\usepackage[style=authoryear-comp, maxnames=2, uniquelist=false]{natbib}
@@
 
-\citet{Bosnjak-2014} used a different approach to create a spectral catalogue of INTEGRAL GRBs, with a joined analysis of SPI and the Imager on Board the INTEGRAL Satellite (IBIS).
+%\citet{Bosnjak-2014} used a different approach to create a spectral catalogue of INTEGRAL GRBs, with a joined analysis of SPI and the Imager on Board the INTEGRAL Satellite (IBIS).
 They construct a response for every SPI detector and forward model the photon model directly into the data space of every detector, which is similar to our approach in this work.
@@
 \label{methods}
-All gamma-ray instruments suffer from energy dispersion and finite energy resolution.
+\BB{All instruments, especially gamma-ray instrument, suffer from energy dispersion and finite energy resolution}.
 The information about this is encoded in the response matrix, that gives the probability of a photon with a certain energy and starting position on the sky to be detected in one of the electronic channels of the detector.
@@
 
-This background treatment is different from what is done in \citet{Bosnjak-2014}, where they used background subtracted data in their analysis.
+%This background treatment is different from what is done in \citet{Bosnjak-2014}, where they used background subtracted data in their analysis.
 It has been shown that using background subtraction can give misleading results \citep[e.g.][]{Greiner-2016}.
@@
 This also includes that we take into account that the mask is not absorbing 100\% of the photons flying through it.
-This is different to the work presented in \citet{Bosnjak-2014}, which used a `response function' simply taking into account the exposed fraction of each detector and therefore assuming a mask that absorbs 100\% of the photons for every photon energy.
+%This is different to the work presented in \citet{Bosnjak-2014}, which used a `response function' simply taking into account the exposed fraction of each detector and therefore assuming a mask that absorbs 100\% of the photons for every photon energy.
 
@@
 %Thus, the results for $\gamma_{\mathrm{max}}$ and $\gamma_{\mathrm{cool}}$ are determined relative to the fixed $\gamma_{\mathrm{inj}}$.
+
+\subsection{Comparison to Bo{\v{s}}njak et al. 2014}
+
+BB{\citet{Bosnjak-2014} did a joined analysis of SPI and the Imager on Board the INTEGRAL Satellite (IBIS) data of GRBs to create a spectral catalque of INTEGRAL GRBs \citep{Ubertini-2003}.
+They construct a response for every SPI detector and forward model the photon model directly into the data space of every detector, which is similar to our approach in this work.
+But following their paper we see three main differences compared to our methods: Background treatment, response generation and PSD events.\\
+In the paper the authors argue that background subtracting is better than using a model template for the background within OSA, as well as cite Cash 1979 \citep{Cash-1979} for their likelihood.
+Therefore we conclude that they used a Poisson likelihood on the background subtracted data.
+This is different to our approach and it has been shown that using background subtraction can give misleading results \citep[e.g.][]{Greiner-2016}.
+For the response generation the authors in \citet{Bosnjak-2014} state that they calculate a response function taking into account the exposed fraction of each detector for the GRB position and that for a detector completely shadowed the net spectrum is zero.
+Therefore we conclude that they used an idealistic mask with zero transparency at all energies.
+We on the other hand used the official response simulations that also include some transparency, especially at high energies.
+The last point are the PSD events, which are ignored completely in \citet{Bosnjak-2014}.
+\citet{spi_electronic_noise} have shown that the effect of the PSD events gets stronger for bright sources, therefore it is important to account for this effect in the case of GRBs.\\
+Unfortunately the software used in \citet{Bosnjak-2014} is not public, so we can not compare our method with theirs directly.}
 
@@
 
-  It is also possible to localize GRBs with PySPI.
+  \BB{It is also possible to localize GRBs with PySPI.
 To localize we vary the spectrum parameters and the location of the source at the same time in one fit.
 For this, PySPi has a fast response generator, that uses the base response simulation grid to generate the response for any given source position quickly.
-Fig ?
-shows the localization we get if we fit the location and use a Band function as spectral model.
-We also marked the position of the GRB measured by Swift/XRT, which shows that the result with the SPI data is in agreement with the Swift/XRT observation.
-For this fit we only used the energies up to 600 keV, to avoid the PSD energy region.
+Fig.
+\ref{fig:localization} shows the localization we get if we fit the location and use a Band function as spectral model.
+We also marked the position of the GRB measured by Swift/XRT, which shows that the result with the SPI data is in agreement with the Swift/XRT observation \citep{GCN_swift}.
+For this fit we only used the energies up to 600 keV, to avoid the PSD energy region.}
 
@@
 We estimate an additional systematic error of $\approx$ 0.5 degree because that is the resolution of the grid points in the response simulation.
-The dashed lines mark the position observed by Swift/XRT.}
-    \label{fig:dataplot}
+The dashed lines mark the position observed by Swift/XRT \citep{GCN_swift}.}
+    \label{fig:localization}
   \end{centering}

### 2022-03-01 src/ms.tex
add \

@@
 
-BB{\citet{Bosnjak-2014} did a joined analysis of SPI and the Imager on Board the INTEGRAL Satellite (IBIS) data of GRBs to create a spectral catalque of INTEGRAL GRBs \citep{Ubertini-2003}.
+\BB{\citet{Bosnjak-2014} did a joined analysis of SPI and the Imager on Board the INTEGRAL Satellite (IBIS) data of GRBs to create a spectral catalque of INTEGRAL GRBs \citep{Ubertini-2003}.
 They construct a response for every SPI detector and forward model the photon model directly into the data space of every detector, which is similar to our approach in this work.

### 2022-03-01 src/ms.tex
add italic for Satellites

--- 2022-03-01 src/ms.tex
@@
 % Title
-\title{Improving INTEGRAL/SPI data analysis of GRBs}
+\title{Improving \textit{INTEGRAL}/SPI data analysis of GRBs}
 
-\titlerunning{Improving INTEGRAL/SPI analysis for GRBs}
+\titlerunning{Improving \textit{INTEGRAL}/SPI analysis for GRBs}
 
@@
 \abstract{
-INTEGRAL/SPI is a coded mask instrument observing since 2002 in the keV to MeV energy range, which covers the peak of the $\nu F\nu$ spectrum of most Gamma-Ray Bursts (GRBs).
-Since its launch in 2008, Fermi/GBM has been the primary instrument for analyzing GRBs in the energy range between $\approx$ 10 keV to $\approx$ 10 MeV.
+\textit{INTEGRAL}/SPI is a coded mask instrument observing since 2002 in the keV to MeV energy range, which covers the peak of the $\nu F\nu$ spectrum of most Gamma-Ray Bursts (GRBs).
+Since its launch in 2008, \textit{Fermi}/GBM has been the primary instrument for analyzing GRBs in the energy range between $\approx$ 10 keV to $\approx$ 10 MeV.
 Herein, we show that SPI, covering a similar energy range, can give equivalently constraining results for some parameters if we use an advanced analysis method.
@@
 %\abstract{In recent years it has been shown that one has to fit physical models to Gamma-Ray Burst (GRB) data to obtain more insights into their emission mechanism.
-For the energy range between $\approx$ 10 keV to $\approx$ 10 MeV, Fermi/GBM has been the main instrument to analyze GRBs in the last 15 years.
-Here, we show how to add INTEGRAL/SPI to this analysis.
+For the energy range between $\approx$ 10 keV to $\approx$ 10 MeV, \textit{Fermi}/GBM has been the main instrument to analyze GRBs in the last 15 years.
+Here, we show how to add \textit{\textit{INTEGRAL}}/SPI to this analysis.
 SPI covers a similar energy range and has a very good energy resolution of $\approx$ 0.2\% at 1.3 MeV compared to $\approx$ 10\% for GBM.
@@
 Earlier analysis has shown, that the shape of the spectrum around the peak is a decisive feature.
-Therefore, we make use of INTEGTRAL/SPI which provides a factor 100 better spectral resolution in the 0.1--1 MeV band compared to the frequently used Fermi/GBM instrument.
+Therefore, we make use of \textit{INTEGTRAL}/SPI which provides a factor 100 better spectral resolution in the 0.1--1 MeV band compared to the frequently used \textit{Fermi}/GBM instrument.
 
-The spectrometer SPI \citep{spi_main} is one of the instruments onboard of the INTErnational Gamma-Ray Astrophysics Laboratory \citep[INTEGRAL;][]{integral} satellite, that was launched in 2002.
+The spectrometer SPI \citep{spi_main} is one of the instruments onboard of the INTErnational Gamma-Ray Astrophysics Laboratory \citep[\textit{INTEGRAL};][]{integral} satellite, that was launched in 2002.
 It is a coded mask instrument, with a fully coded field-of-view of 16 degrees, covering an energy range between 20 keV and 8 MeV.
@@
 
-The standard analysis of SPI GRB data is done within the INTEGRAL Offline Scientific Analysis ({\tt OSA}) software \citep{osa}, including SPI-specific routines \citep{Diehl-2003}.
+The standard analysis of SPI GRB data is done within the \textit{INTEGRAL} Offline Scientific Analysis ({\tt OSA}) software \citep{osa}, including SPI-specific routines \citep{Diehl-2003}.
 A two step method is applied, by first using only the photo peak response to incorporate the mask pattern on the detectors and in a second step applying an energy redistribution correction response.
@@
 
-%\citet{Bosnjak-2014} used a different approach to create a spectral catalogue of INTEGRAL GRBs, with a joined analysis of SPI and the Imager on Board the INTEGRAL Satellite (IBIS).
+%\citet{Bosnjak-2014} used a different approach to create a spectral catalogue of \textit{\textit{INTEGRAL}} GRBs, with a joined analysis of SPI and the Imager on Board the \textit{\textit{INTEGRAL}} Satellite (IBIS).
 They construct a response for every SPI detector and forward model the photon model directly into the data space of every detector, which is similar to our approach in this work.
@@
 This is due to energy dispersion and finite energy resolution of the detectors, which makes this an inversion problem, that can cause photon spectra that are different, to produce similar detected count spectra.
-This can be improved by a detector with better energy resolution, which INTEGRAL/SPI can provide.
-Due to the Germanium detectors it has an energy resolution of $\approx$ 2.2 keV at 1.3 MeV \citep{spi} compared to $\approx$ 10\% for Fermi/GBM \citep{gbm}.
+This can be improved by a detector with better energy resolution, which \textit{\textit{INTEGRAL}}/SPI can provide.
+Due to the Germanium detectors it has an energy resolution of $\approx$ 2.2 keV at 1.3 MeV \citep{spi} compared to $\approx$ 10\% for \textit{Fermi}/GBM \citep{gbm}.
 %Generally, it can be difficult to reject models, because often several models can give acceptable fits to the data.
@@
 %The underlying problem is that empirical functions like the Band function only allow a certain range of spectral shapes and can not fully reproduce for example a synchrotron photon spectrum
-%The Gamma-Ray Burst Monitor (GBM) onboard of the Fermi satellite is often used to fit GRB data in the 8 keV to 10 MeV energy range.
+%The Gamma-Ray Burst Monitor (GBM) onboard of the \textit{Fermi} satellite is often used to fit GRB data in the 8 keV to 10 MeV energy range.
 GBM consists of 12 NaI and two BGO scintillator detectors and is an all-sky instrument, that observes the whole sky, except the part that is occulted by the Earth at that time.
@@
 
-%The other instrument that we use in this work is the Gamma-Ray Burst Monitor (GBM) onboard of the Fermi satellite.
+%The other instrument that we use in this work is the Gamma-Ray Burst Monitor (GBM) onboard of the \textit{Fermi} satellite.
 GBM is an all-sky instrument, that observes the whole sky, except the part that is occulted by the Earth at that time.
@@
 \label{electronic}
-%Since shortly after the start of INTEGRAL, it is known that there are spurious events in the SPI data around 1.5 MeV.
+%Since shortly after the start of \textit{\textit{INTEGRAL}}, it is known that there are spurious events in the SPI data around 1.5 MeV.
 According to \citet{spi_electronic_noise} there are spurious events in the SPI data, which are photons with small energy (<100 keV) that get detected at a higher energy due to saturation of the Analog Front-End Electronics (AFEE) by previous high energy deposition.
@@
 
-\subsection{INTEGRAL OSA software}
+\subsection{\textit{INTEGRAL} OSA software}
 \label{OSA}
@@
 As we are introducing a new analysis software in this work, we want to compare it to the existing analysis software, to check if the results are in agreement.
-We shortly summarize the standard analysis tools for GRB analysis, which are part of the INTEGRAL Offline Scientific Analysis ({\tt OSA}) software \citep{osa}.
+We shortly summarize the standard analysis tools for GRB analysis, which are part of the \textit{INTEGRAL} Offline Scientific Analysis ({\tt OSA}) software \citep{osa}.
 
@@
 \noindent
-The BALROG (BAyesian Lo-cation Reconstruction Of GRBs) algorithm for localizing GRBs with Fermi/GBM employs the same method \citep{balrog}, which shows that forward folding allows one to localize photon sources with a non-imaging instrument.
+The BALROG (BAyesian Lo-cation Reconstruction Of GRBs) algorithm for localizing GRBs with \textit{Fermi}/GBM employs the same method \citep{balrog}, which shows that forward folding allows one to localize photon sources with a non-imaging instrument.
 It is important to realize that the instruments SPI and GBM are fundamentally very similar.
@@
 {\tt PySPI} constructs a plugin for the Multi-Mission Maximum Likelihood framework \citep[3ML][]{3ML}.
-This allows one to fit SPI data together with data from other instruments, such as Fermi/GBM\footnote{See threeml.readthedocs.io}.
+This allows one to fit SPI data together with data from other instruments, such as \textit{Fermi}/GBM\footnote{See threeml.readthedocs.io}.
 {\tt PySPI} is an open source software, which is publicly available on GitHub \citep{joss}, including documentation with examples\footnote{See pyspi.readthedocs.io}.
@@
 We use {\tt pynchrotron}\footnote{https://github.com/grburgess/pynchrotron} to calculate the spectrum from a physical spectral synchrotron model.
-This model was previously used to successfully fit many single-pulse GRBs observed with Fermi/GBM in \citet{synch}, which also includes a detailed description of the model.
+This model was previously used to successfully fit many single-pulse GRBs observed with \textit{Fermi}/GBM in \citet{synch}, which also includes a detailed description of the model.
 Here we summarize the main points.
@@
 
-BB{\citet{Bosnjak-2014} did a joined analysis of SPI and the Imager on Board the INTEGRAL Satellite (IBIS) data of GRBs to create a spectral catalque of INTEGRAL GRBs \citep{Ubertini-2003}.
+\BB{\citet{Bosnjak-2014} did a joined analysis of SPI and the Imager on Board the \textit{INTEGRAL} Satellite (IBIS) data of GRBs to create a spectral catalque of \textit{INTEGRAL} GRBs \citep{Ubertini-2003}.
 They construct a response for every SPI detector and forward model the photon model directly into the data space of every detector, which is similar to our approach in this work.
@@
 \label{conclusion}
-We have presented a new analysis method for GRBs detected by INTEGRAL/SPI and the corresponding software package utilizing this method ({\tt PySPI}), which uses a proper forward-folding technique for each detector (see Sec.
+We have presented a new analysis method for GRBs detected by \textit{INTEGRAL}/SPI and the corresponding software package utilizing this method ({\tt PySPI}), which uses a proper forward-folding technique for each detector (see Sec.
 \ref{pyspi}).
-To show that this improves the analysis of GRBs detected by SPI, we have analyzed GRB 120711A using the data from INTGRAL/SPI and Fermi/GBM.
-The results for SPI with {\tt PySPI} are in agreement with those from the INTEGRAL OSA software, but more constraining.
+To show that this improves the analysis of GRBs detected by SPI, we have analyzed GRB 120711A using the data from INTGRAL/SPI and \textit{Fermi}/GBM.
+The results for SPI with {\tt PySPI} are in agreement with those from the \textit{INTEGRAL} OSA software, but more constraining.
 Also, the resulting spectral shape for the fits with GBM and SPI data are in agreement and the relative calibration difference between SPI and GBM we conclude from the fits, is $\approx$ 10\% or less.

### 2022-04-21 src/ms.tex
final accepted version

@@
 % Define document class
-\documentclass[twocolumn,traditabstract]{aa}
+\documentclass{aa}
 
 % Filler text
-%\usepackage{caption}
+\usepackage{txfonts}
 %\usepackage{subcaption}
-\usepackage{float}
-\newcommand{\BB}[1]{\textcolor{red}{\textsf{#1}}}
+\usepackage{graphicx}
+%\usepackage{xcolor}
 %\usepackage[style=authoryear-comp, maxnames=2, uniquelist=false]{natbib}
@@
 % Begin!
+\newcommand{\CH}[1]{\textcolor{red}{\textsf{#1}}}
 \def\fdg{\hbox{$.\!\!^\circ$}}          % Fractions of degrees
+%\usepackage{color}
 
@@
 \abstract{
-\textit{INTEGRAL}/SPI is a coded mask instrument observing since 2002 in the keV to MeV energy range, which covers the peak of the $\nu F\nu$ spectrum of most Gamma-Ray Bursts (GRBs).
-Since its launch in 2008, \textit{Fermi}/GBM has been the primary instrument for analyzing GRBs in the energy range between $\approx$ 10 keV to $\approx$ 10 MeV.
-Herein, we show that SPI, covering a similar energy range, can give equivalently constraining results for some parameters if we use an advanced analysis method.
+The spectrometer on the international gamma-ray astrophysics laboratory (\textit{INTEGRAL}/SPI) is a coded mask instrument observing since 2002 in the keV to MeV energy range, which covers the peak of the $\nu F\nu$ spectrum of most gamma-ray bursts (GRBs).
+Since its launch in 2008, the gamma-ray burst monitor (GBM) on board the \textit{Fermi} satellite has been the primary instrument for analysing GRBs in the energy range between $\approx$ 10 keV and $\approx$ 10 MeV.
+Here, we show that the spectrometer on board \textit{INTEGRAL}, named `SPI', which  covers a similar energy range, can give equivalently constraining results for some parameters if we use an advanced analysis method.
 Also, combining the data of both instruments reduces the allowed parameter space in spectral fits.
-The main advantage of SPI as compared to GBM is the energy resolution of $\approx$ 0.2\% at 1.3 MeV compared to $\approx$ 10\% for GBM.
-Therefore, SPI is an ideal instrument to precisely measure the curvature of the spectrum.
+The main advantage of SPI over GBM is the energy resolution of $\approx$ 0.2\% at 1.3 MeV compared to $\approx$ 10\% for GBM.
+Therefore, SPI is an ideal instrument for precisely measuring the curvature of the spectrum.
 This is important, as it has been shown in recent years that physical models rather than heuristic functions should be fit to GRB data to obtain better insights into their still unknown emission mechanism, and the curvature of the peak is unique to the different physical models.
-To fit physical models to SPI GRB data and get the maximal amount of information from the data, we developed a new open source analysis software {\tt PySPI}.
-We apply these new techniques to GRB 120711A in order to validate and showcase {\tt PySPI}'s capabilities.
-We show that {\tt PySPI} improves the analysis of SPI GRB data compared to the {\tt OSA} analysis.
-In addition, we demonstrate that the GBM and the SPI data of this GRB can be fitted well with a physical synchrotron model.
-This evinces that SPI can play an important role in GRB spectral model fitting.
+To fit physical models to SPI GRB data and get the maximal amount of information from the data, we developed new open-source analysis software, {\tt PySPI}.
+We apply these new techniques to GRB 120711A in order to validate and showcase the capabilities of this software.
+We show that {\tt PySPI} improves the analysis of SPI GRB data compared to the \textit{INTEGRAL} off-line scientific analysis software ({\tt OSA}).
+In addition, we demonstrate that the GBM and the SPI data for this particular GRB can be fitted well with a physical synchrotron model.
+This demonstrates that SPI can play an important role in GRB spectral model fitting.
 }
-
-%\abstract{In recent years it has been shown that one has to fit physical models to Gamma-Ray Burst (GRB) data to obtain more insights into their emission mechanism.
-For the energy range between $\approx$ 10 keV to $\approx$ 10 MeV, \textit{Fermi}/GBM has been the main instrument to analyze GRBs in the last 15 years.
-Here, we show how to add \textit{\textit{INTEGRAL}}/SPI to this analysis.
-SPI covers a similar energy range and has a very good energy resolution of $\approx$ 0.2\% at 1.3 MeV compared to $\approx$ 10\% for GBM.
-Therefore, it is an ideal instrument to measure precisely the curvature of the spectrum.
-We present {\tt PySPI}, a new analysis software that we developed to analyze GRB data from SPI.
-To demonstrate its usage and capabilities, we apply it to GRB 120711A.
-We show that {\tt PySPI} improves the analysis of SPI GRB data compared to the official analysis software.
-In addition, we demonstrate that the GBM and the SPI data of this GRB can be fitted well with a  synchrotron model, and that combining both instruments reduces the allowed parameter space.
-This evinces that SPI can play an important role in GRB model fitting.}
 
@@
 
-Gamma-Ray Bursts (GRBs) are short transient bursts of $X-$ and $\gamma$-rays \citep{Klebesadel+1973}, with a typical active time between a few ms and few hundred seconds for the prompt phase.
-%which is mostly observed in $X$- and $\gamma$-rays.
+Gamma-ray bursts (GRBs) are short transient bursts of $X-$ and $\gamma$-rays \citep{Klebesadel+1973} with a typical active time of between a few milliseconds and a few hundred seconds for the prompt phase.
 After the prompt emission, there is a long-lasting afterglow phase when the ejecta interact with the interstellar medium \citep{MeszarosRees1997, afterglow}.
 GRBs are classified into two groups depending on the duration of the prompt emission \citep{shortlong}.
-Long GRBs (prompt phase $\gtrapprox$ 2s) have been associated with the collapse of massive stars \citep{SN1, Hjorth+2003, SN2}, whereas short GRBs are  caused by mergers of compact objects, like neutron stars \citep{Eichler+1989, gw}.
-In both cases it is consensus, that the progenitor events of GRBs produce jetted relativistic outflows, which consist of several shells with different velocities, resulting in internal shell collisions \citep{ReesMeszaros1994, Mochkovitch+1995}.
-%\citep{gamma-ray-burst}. Edo Berger is an observer, and has never worked on shocks, so I (jcg) wouldn't cite this review
+Long GRBs (prompt phase $\gtrapprox$ 2s) have been associated with the collapse of massive stars \citep{SN1, Hjorth+2003, SN2}, whereas short GRBs are  caused by mergers of compact objects, such as neutron stars \citep{Eichler+1989, gw}.
+In both cases there is consensus that the progenitor events of GRBs produce jetted relativistic outflows, which consist of several shells with different velocities, resulting in internal shell collisions \citep{ReesMeszaros1994, Mochkovitch+1995}.
 
-The true physical mechanism(s) responsible for the prompt emission of GRBs is a heavily debated topic \citep[for a review see][]{KumarZhang2015}.
-%\citep[for a review see][]{gamma-ray-burst}.
-see above
+The true physical mechanism(s) responsible for the prompt emission of GRBs is a heavily debated topic \citep[for a review, see][]{KumarZhang2015}.
 Two of the possible emission mechanisms are synchrotron \citep[e.g.][]{syn_shell, bosnjak_syn, synch} and photospheric emission \citep[e.g.][]{Goodman1986, photo_1, photo_2, photo_3}.
-In the past, GRB data were often fitted with empirical functions like the Band function \citep{band}, to conclude from the fit parameters which physical model is preferred.
-In recent years it has been shown, that this approach can be misleading and that one should rather fit physical models directly to the data \citep{Burgess-2014, physical_models, synch}.
-A prominent example for this is the so-called `line-of-death' for synchrotron emission \citep{line-of-death, line-of-death2}, which states that synchrotron radiation can not be the universal emission mechanism, if fits with a Band function give a low energy power law slope larger than $-2/3$.
-\citet{synch} have shown that this conclusion is flawed and that one can fit GRB spectra well with a physical synchrotron model even though the same spectra violate the line-of-death if fitted with a Band function.
+In the past, GRB data were often fitted with empirical functions like the Band function \citep{band} in order to decipher the preferred physical model from the fit parameters.
+In recent years, it has been shown that this approach can be misleading and that it is preferable to fit physical models directly to the data \citep{Burgess-2014, physical_models, synch}.
+A prominent example of this is the so-called `line of death' for synchrotron emission \citep{line-of-death, line-of-death2}, which states that synchrotron radiation cannot be the universal emission mechanism if fits with a Band function give a low-energy power law slope larger than $-2/3$.
+\citet{synch} showed that this conclusion is flawed and that one can fit GRB spectra well with a physical synchrotron model even though the same spectra violate the line of death if fitted with a Band function.
 Another proposed proxy for physical emission processes in GRBs is the spectral curvature of empirical model fits to GRB data \citep{Yu-2015, Axelsson-2015}.
 This too has been shown to be an inaccurate indicator of the emission process \citep{Burgess2019}.
-Thus, the use of physical models remains the best tool for deciphering the emission processes occurring in the relativistic outflows of GRBs.
+Therefore, the use of physical models remains the best tool for deciphering the emission processes occurring in the relativistic outflows of GRBs.
 
-Apart from the model used, also the data play an important role.
-Earlier analysis has shown, that the shape of the spectrum around the peak is a decisive feature.
-Therefore, we make use of \textit{INTEGTRAL}/SPI which provides a factor 100 better spectral resolution in the 0.1--1 MeV band compared to the frequently used \textit{Fermi}/GBM instrument.
+In addition to the model used, the data also play an important role.
+Earlier analyses showed that the shape of the spectrum around the peak is a decisive feature.
+Therefore, we make use of the spectrometer (SPI) on the international gamma-ray astrophysics laboratory \citep[\textit{INTEGRAL};][]{integral} which provides 100 times higher spectral resolution in the 0.1--1 MeV band compared to the frequently used gamma-ray burst monitor (GBM) on board the \textit{Fermi} satellite.
 
-The spectrometer SPI \citep{spi_main} is one of the instruments onboard of the INTErnational Gamma-Ray Astrophysics Laboratory \citep[\textit{INTEGRAL};][]{integral} satellite, that was launched in 2002.
+The spectrometer SPI \citep{spi_main} is one of the instruments on board the \textit{INTEGRAL} satellite, which was launched in 2002.
 It is a coded mask instrument, with a fully coded field-of-view of 16 degrees, covering an energy range between 20 keV and 8 MeV.
-The unprecedented energy resolution allows the identification of fine spectral features, like nuclear decay lines \citep{Roques-2003, Diehl-2006} and curvature in continuous spectra \citep{Jourdain-2020}.
-%In the case of GRBs this energy resolution gives us the possibility to determine the curvature of the spectra with unprecedented precision.
+The unprecedented energy resolution allows the identification of fine spectral features, such as nuclear decay lines \citep{Roques-2003, Diehl-2006} and curvature in continuous spectra \citep{Jourdain-2020}.
 
 The standard analysis of SPI GRB data is done within the \textit{INTEGRAL} Offline Scientific Analysis ({\tt OSA}) software \citep{osa}, including SPI-specific routines \citep{Diehl-2003}.
-A two step method is applied, by first using only the photo peak response to incorporate the mask pattern on the detectors and in a second step applying an energy redistribution correction response.
-This method is used in several works which fitted empirical GRB models to the SPI data \citep{Malaguti-2003, Mereghetti-2003, Mereghetti-2003.2, Kienlin-2003, Kienlin-2003.2,Beckmann-2004, Moran-2005, Filliatre-2005.1, Filliatre-2005.2, McBreen-2006, Grebenev-2007, McGlynn-2008, Foley-2008, McGlynn-2009, Martin-Carrillo-2014}.
+A two-step method is applied, whereby first only the photo peak response is used to incorporate the mask pattern on the detectors, and then an energy redistribution correction response is applied.
+This method was used in several works that fitted empirical GRB models to the SPI data \citep{Malaguti-2003, Mereghetti-2003, Mereghetti-2003.2, Kienlin-2003, Kienlin-2003.2,Beckmann-2004, Moran-2005, Filliatre-2005.1, Filliatre-2005.2, McBreen-2006, Grebenev-2007, McGlynn-2008, Foley-2008, McGlynn-2009, Martin-Carrillo-2014}.
+The noteworthy exception of \citet{Bosnjak-2014} is discussed separately below in Sect.
+2.5.
+Apart from data handling, all previous analysis of GRB data from INTEGRAL/SPI used heuristic functions like the Band function, but not a physical model.
 
-%\citet{Bosnjak-2014} used a different approach to create a spectral catalogue of \textit{\textit{INTEGRAL}} GRBs, with a joined analysis of SPI and the Imager on Board the \textit{\textit{INTEGRAL}} Satellite (IBIS).
-They construct a response for every SPI detector and forward model the photon model directly into the data space of every detector, which is similar to our approach in this work.
-But they build the responses and treated the background differently then we do in this work.
-We will point out the differences in Sec.
+Here, we developed the pure Python-based analysis tool {\tt PySPI} in order to provide an easy-to-use data-reduction and fitting tool while getting the maximal amount of information out of the data to progress to fitting physical models.
+This improves the analysis method in general, because we use the full response to forward model the expected spectra to the native SPI data space and use the correct likelihood to take the Poisson nature of the measurements into account.
+It also offers an  interface that is easy to install and use.
+This work is structured as follows: In Sect.
+\ref{methods}, we summarise the different methods and concepts for SPI GRB data analysis, and provide a detailed description of the new analysis method within {\tt PySPI} in Sect.
 \ref{pyspi}.
-%But they build the response simply according to the exposed fraction of the detector for the GRB direction and use background subtracted data for their fits.
-%Several works have used SPI data for GRBs \citep{spi_grb1, spi_grb2}, but all of them fitted empirical models like the Band function.
-
-Here, we developed a pure python-based analysis tool {\tt PySPI} in order to provide an easy to use data reduction and fitting tool while getting the maximal amount of information out of the data to progress to fitting physical models.
-This improves the analysis method in general, because we use the full response to forward model the expected spectra to the native SPI data space and use the correct likelihood to take the Poisson nature of the measurements into account.
-It also offers an easy to install and use interface.
-%In this paper we introduce the new analysis method and show that we can fit complicated physical GRB models to the SPI data
-This work is structured as follows: In Sec.
-\ref{methods} we summarize the different methods and concepts for SPI GRB data analysis, and provide a detailed description of the new analysis method within {\tt PySPI} in Sec.
-\ref{pyspi}.
-Sec.
-\ref{synch} introduces the physical synchrotron model we used in the fits and Sec.
-\ref{PPC} explains how we check if a fit is a good description of the data.
-We analyse the SPI and GBM data for GRB 120711A in Sec.
-\ref{analysis} and conclude our results in Sec.
+Section \ref{synch} introduces the physical synchrotron model we used in the fits and Sect.
+\ref{PPC} explains how we check whethre or not a fit is a good description of the data.
+We analyse the SPI and GBM data for GRB 120711A in Sect.
+\ref{analysis} and conclude our results in Sect.
 \ref{conclusion}.
 
-%But even if we fit physical models directly to the data, it can be difficult to reject certain physical models, because multiple models can give acceptable fits to the data.
-This is due to energy dispersion and finite energy resolution of the detectors, which makes this an inversion problem, that can cause photon spectra that are different, to produce similar detected count spectra.
-This can be improved by a detector with better energy resolution, which \textit{\textit{INTEGRAL}}/SPI can provide.
-Due to the Germanium detectors it has an energy resolution of $\approx$ 2.2 keV at 1.3 MeV \citep{spi} compared to $\approx$ 10\% for \textit{Fermi}/GBM \citep{gbm}.
-%Generally, it can be difficult to reject models, because often several models can give acceptable fits to the data.
-This is due to energy dispersion and finite energy resolution of the detectors, that can cause photon spectra that are different, to produce the same detected count spectra.
-%Therefore the parameters the fit with an empirical model returns, is only the best fit within the build-in constraints of the model shape and can be a good fit to the data.
-But if we loose the constrains on the shape of the model, we can maybe find other solutions that are also good fits to the data.
-This results in many GRBs
-%The underlying problem is that empirical functions like the Band function only allow a certain range of spectral shapes and can not fully reproduce for example a synchrotron photon spectrum
-%The Gamma-Ray Burst Monitor (GBM) onboard of the \textit{Fermi} satellite is often used to fit GRB data in the 8 keV to 10 MeV energy range.
-GBM consists of 12 NaI and two BGO scintillator detectors and is an all-sky instrument, that observes the whole sky, except the part that is occulted by the Earth at that time.
-\citep{gbm}
-
-%To allow us to fit physical models and to improve the analysis methods we developed {\tt PySPI}, which will be explained in detail in \ref{pyspi}.
-
-%The other instrument that we use in this work is the Gamma-Ray Burst Monitor (GBM) onboard of the \textit{Fermi} satellite.
-GBM is an all-sky instrument, that observes the whole sky, except the part that is occulted by the Earth at that time.
-It consists of 12 NaI and two BGO scintillator detectors that cover in total an energy range between 8 keV and 10 MeV.
-(cite)
-
-\section{SPI GRB Analysis Methods}
+\section{SPI GRB analysis methods}
 \label{methods}
-\BB{All instruments, especially gamma-ray instrument, suffer from energy dispersion and finite energy resolution}.
-The information about this is encoded in the response matrix, that gives the probability of a photon with a certain energy and starting position on the sky to be detected in one of the electronic channels of the detector.
-These response matrices are usually not invertible, and therefore we have to forward fold the photon spectrum trough the response matrix into the data space of the detected counts and compare them, using the correct likelihood.
+All instruments, especially gamma-ray instruments, suffer from energy dispersion and finite energy resolution.
+The information about this is encoded in the response matrix, which gives the probability that a photon with a certain energy and starting position on the sky will be detected in one of the electronic channels of the detector.
+These response matrices are usually not invertible, and therefore we have to forward fold the photon spectrum through the response matrix into the data space of the detected counts and compare them using the correct likelihood.
 This is a general statement that also applies to SPI.
-In the following subsection we will first cover some general concepts for SPI and then the standard analysis method within {\tt OSA} as well as the method within our new analysis tool {\tt PySPI}.
-The main difference is that the method in {\tt PySPI} is a full forward folding method, fulfilling the statement above, which results in maximising the information we can get from the data in the analysis.
+In the following subsection, we first cover some general concepts for SPI and then the standard analysis method within {\tt OSA,} as well as the method within our new analysis tool {\tt PySPI}.
+The main difference is that the method in {\tt PySPI} is a full forward-folding method, fulfilling the statement above, which results in maximising the information we can get from the data in the analysis.
 
@@
 This includes, for example, information about partial energy deposition of the photon in a crystal and the process that transforms the deposited energy into the electronic signal that is measured.
-% distribution of how much energy a photon with a certain energy deposit in the crystal and what energy is in the end measured for this deposited energy.
-The response is split into two components, namely the Image Response Functions (IRFs) and Redistribution Matrix Files (RMFs).
-The IRFs contain the information of the total effective area for a photon to interact at all and the RMFs contain the information about the probability in which electronic channel an interacting photon will be measured.
-
-For SPI both these components were derived with extensive GEANT simulations \citep{spi_response}.
+The response is split into two components, namely the image response functions (IRFs) and redistribution matrix files (RMFs).
+The IRFs contain information about the total effective area over which a photon can interact with the detector and the RMFs contain information about the probability in which electronic channel the photon will be measured.
+For SPI, both these components were derived with extensive geometry and tracking (Geant) simulations \citep{spi_response}.
 The SPI IRF files give the total effective area for three different interaction types:
 %\begin{itemize}
- (1) Photo peak events;
- (2) Non photo-peak events that first interact in the Ge crystal, and
- (3) Non photo-peak events that first interact in passive material.
+ (1) photo peak events;
+ (2) non-photo-peak events that first interact in the Ge crystal, and
+ (3) non-photo-peak events that first interact in passive material.
 %\end{itemize}
@@
 For each of the three interaction types, there is one RMF to define the shape of the redistributed spectra, assuming that this shape does not depend on the detector or the incident angles of the photons.
-The procedure to construct the response includes several simplification to keep the computational costs and storage space manageable \citep{spi_response}.
+The procedure used to construct the response includes several simplifications to keep the computational costs and storage space at manageable levels \citep{spi_response}.
 Re-simulating the response without these simplifications could improve the scientific output of SPI, but would be computationally very expensive, even today.
 
-\subsection{Electronic Noise}
+\subsection{Electronic noise}
 \label{electronic}
-%Since shortly after the start of \textit{\textit{INTEGRAL}}, it is known that there are spurious events in the SPI data around 1.5 MeV.
-According to \citet{spi_electronic_noise} there are spurious events in the SPI data, which are photons with small energy (<100 keV) that get detected at a higher energy due to saturation of the Analog Front-End Electronics (AFEE) by previous high energy deposition.
-It is also known, that these spurious events do not show up in events with a detection also in the Pulse Shape Discriminator (PSD) electronics.
-The reason for this is that the PSD electronics have a low energy threshold of $\approx$450 keV and a high energy threshold of $\approx$2700 keV \citep[the exact values have been changed a few times during the mission; ][]{spi_electronic_noise}.
-Therefore, only events that deposit more than this low energy threshold in the Germanium crystal can trigger this electronic chain, which eliminates the $<$100 keV events that are detected at the wrong energies by the AFEE.
+According to \citet{spi_electronic_noise}, there are spurious events in the SPI data, which are photons with small energy (<100 keV) that get detected at a higher energy due to saturation of the analog front-end electronics (AFEE) by previous high-energy deposition.
+It is also known that these spurious events do not show up in events that also have a detection in the pulse shape discriminator (PSD) electronics.
+The reason for this is that the PSD electronics have a low-energy threshold of $\approx$450 keV and a high-energy threshold of $\approx$2700 keV \citep[the exact values have been changed a few times during the mission; ][]{spi_electronic_noise}.
+Therefore, only events that deposit more than this low-energy threshold in the germanium crystal can trigger this electronic chain, which eliminates the $<$100 keV events that are detected at the wrong energies by the AFEE.
 In Fig.
-\ref{fig:electronic} one can see that the feature at 1.5 MeV is nicely visible in the Non-PSD events but is missing in the PSD events.
-Even though this problem is most significant in the area around 1.5 MeV it is also important at lower energies $>$400 keV.
-The electronic noise is not stable and depends on the signal strength \citep{spi_electronic_noise}, therefore it can not be included in the response and has to be treated differently.
+\ref{fig:electronic}, the feature at 1.5 MeV is nicely visible in the non-PSD events but is missing in the PSD events.
+Even though this problem is most significant in the area around 1.5 MeV, it is also important at lower energies $>$400 keV.
+The electronic noise is not stable and depends on the signal strength \citep{spi_electronic_noise}, and therefore it cannot be included in the response and has to be treated differently.
 
@@
         \caption{Count spectrum for detector 0 integrated over 1000 seconds in revolution 1189.
-The Non-PSD event count spectrum is drawn in purple and the PSD events in grey.
+The non-PSD event count spectrum is drawn in purple and the PSD events in grey.
 The light green shaded area marks the energy range within the PSD energy thresholds \citep{spi_electronic_noise}.
-One can clearly see the feature in the Non-PSD events at 1.5 MeV (stronger green shaded area) that is not visible in the PSD events.}
+The feature is clearly seen in the non-PSD events at 1.5 MeV (stronger green shaded area) and is not visible in the PSD events.}
         \label{fig:electronic}
@@
 
-As we are introducing a new analysis software in this work, we want to compare it to the existing analysis software, to check if the results are in agreement.
-We shortly summarize the standard analysis tools for GRB analysis, which are part of the \textit{INTEGRAL} Offline Scientific Analysis ({\tt OSA}) software \citep{osa}.
+As we are introducing new analysis software in this work, we want to compare it to the existing analysis software to check whether or not the results are in agreement.
+We briefly summarise the standard analysis tools for GRB analysis, which are part of the {\tt OSA} software \citep{osa}.
 
-Analyzing GRB data from SPI with the {\tt OSA} tools is a multi-step process.
-The first steps cover selecting the science window containing the GRB, the time intervals for active time and background time as well as the energy bins for the analysis.
-Then, one can either find the location of the GRB with SPIROS, i.e.
-an iterative source removal algorithm for SPI data \citep{Skinner-2003}, or set it manually if it is already known.
-The next steps concern the spectral fitting, which is done in another two-step procedure.
+Analysing GRB data from SPI with the {\tt OSA} tools is a multi-step process.
+The first steps involve selecting the science window containing the GRB, the time intervals for active time and background time, and the energy bins for the analysis.
+One can either find the location of the GRB with SPIROS, which is an iterative source-removal algorithm for SPI data \citep{Skinner-2003}, or set it manually if it is already known.
+The next steps encompass the spectral fitting, which is done in another two-step procedure.
 
@@
 With these responses and the measured data in the individual SPI detectors, taking into account the different background rates, a photon flux is fitted individually per energy channel.
-These pseudo photon fluxes are not the final result, as up to this point energy dispersion and detector energy resolution was not accounted for.
-The pseudo photon flux data points are fitted with a spectral photon flux model and a correction response, that is also available through {\tt OSA}.
-This correction response depends on the energy bins that are used and should account for energy dispersion.
-In this step the energy channels are fitted simultaneously, as it is impossible to incorporate energy dispersion in a way that fits every energy channel individually.
-This fitting can be done in different spectral fitting software, like {\tt XSPEC} \citep{xspec} or {\tt 3ML} \citep{3ML}.
+These pseudo photon fluxes are not the final result, as at this point, energy dispersion and detector energy resolution have not yet been accounted for.
+The pseudo photon flux data points are fitted with a spectral photon flux model and a correction response.
+The correction response, that is available through {\tt OSA}, depends on the energy bins that are used and should account for energy dispersion.
+In this step, the energy channels are fitted simultaneously, as it is impossible to incorporate energy dispersion in a way that fits every energy channel individually.
+This fitting can be done in different spectral fitting software, such as {\tt XSPEC} \citep{xspec} or the Multi-Mission Maximum Likelihood framework \citep[3ML;][]{3ML}.
 
@@
 \label{pyspi}
-To fit SPI GRB data, we developed a new python package {\tt PySPI} \citep{joss}.
-%which is an open source analysis tool. In the following
-Below, we summarize the main points of GRB analysis within {\tt PySPI}.
+To fit SPI GRB data, we developed a new Python package {\tt PySPI} \citep{joss}.
+Below, we summarise the main points of GRB analysis within {\tt PySPI}.
 
@@
 GRBs are transient sources with a typical duration of up to a few tens of seconds.
-Therefore, we can use the time intervals during a single pointed observation (science window), when the transient source is not active, as an independent temporal off-source observation (see Fig.
+Therefore, we can use the time intervals during a single pointed observation (science window) ---when the transient source is not active--- as an independent temporal off-source observation (see Fig.
 \ref{fig:lightcurve}).
-This approach is similar to what is done with other instruments, that use spatially off-source observations as an independent background measurements.
-The probability distribution for the background model rates per energy channel is the Poisson distribution
-%From the background observations we construct the probability of the background model rates per energy channel from a Poisson distribution, like given in Eq.
-\ref{eq:poisson_bkg}, where $b_{\mathrm{i}}$ are the background rates per energy channel, $B_{\mathrm{i}}$ are the detected counts in the off-source observation and $t_{\mathrm{b}}$ is the exposure of the off-source observation.
+This approach is similar to what is done with other instruments that use off-source observations to make independent background measurements.
+The probability distribution for the background model rates per energy channel is the Poisson distribution:
+
 \begin{equation}
@@
 \end{equation}
-where $b_{\mathrm{i}}$ are the background rates per energy channel, $B_{\mathrm{i}}$ are the detected counts in the off-source observation and $t_{\mathrm{b}}$ is the exposure of the off-source observation.
+where $b_{\mathrm{i}}$ are the background rates per energy channel, $B_{\mathrm{i}}$ are the detected counts in the off-source observation, and $t_{\mathrm{b}}$ is the exposure of the off-source observation.
 
@@
         \includegraphics{figures/lightcurve.pdf}
-        \caption{Lightcurve for SPI detector 0 for GRB 120711A.
+        \caption{Light curve for SPI detector 0 for GRB 120711A.
 The transient source is clearly visible as well as the constant background for the time when the transient is not active.
-The time intervals we use for the independent background observation is marked with the green shaded area.}
+The time interval we use for the independent background observation is marked with the green shaded area.}
         \label{fig:lightcurve}
@@
 
-%This background treatment is different from what is done in \citet{Bosnjak-2014}, where they used background subtracted data in their analysis.
-It has been shown that using background subtraction can give misleading results \citep[e.g.][]{Greiner-2016}.
-
 \subsubsection{Likelihood}
@@
 With the defined background distribution, we can construct a likelihood, given by Eq.
-\ref{eq:likelihood_m_and_b}, that connects the source and background model with the Poisson process data of the background and active time interval, via the response.
-Here $\vec{\theta}$ summarizes all the parameters of the source model, $D_{\mathrm{i}}$ are the measured counts in the selected active time interval of the transient source, $m_{\mathrm{i}}(\vec{\theta})$ are the predicted count rates from the model evaluated at the parameters $\vec{\theta}$ and $t_{\mathrm{d}}$ is the exposure of the selected active time interval.
+\ref{eq:likelihood_m_and_b}, that connects the source and background model with the Poisson process data of the background and active time interval via the response.
+Here, $\vec{\theta}$ summarises all the parameters of the source model, $D_{\mathrm{i}}$ are the measured counts in the selected active time interval of the transient source, $m_{\mathrm{i}}(\vec{\theta})$ are the predicted count rates from the model evaluated at the parameters $\vec{\theta,}$ and $t_{\mathrm{d}}$ is the exposure of the selected active time interval.
 
@@
         \mathcal{L}(D_{\mathrm{i}}, B_{\mathrm{i}},t_{\mathrm{d}},t_{\mathrm{b}}|\vec{\theta}, b_{\mathrm{i}}) = \frac{(t_{\mathrm{d}}(m_{\mathrm{i}}(\vec{\theta})+ b_{\mathrm{i}}))^{D_{\mathrm{i}}}}{D_{\mathrm{i}}!}\cdot \\
-  e^{-t_{\mathrm{d}}(m_{\mathrm{i}}(\vec{\theta})+b_{\mathrm{i}})}\frac{(t_{\mathrm{b}} b_{\mathrm{i}})^{B_{\mathrm{i}}}}{B_{\mathrm{i}}!} e^{-t_{\mathrm{b}} b_{\mathrm{i}}}
+  e^{-t_{\mathrm{d}}(m_{\mathrm{i}}(\vec{\theta})+b_{\mathrm{i}})}\frac{(t_{\mathrm{b}} b_{\mathrm{i}})^{B_{\mathrm{i}}}}{B_{\mathrm{i}}!} e^{-t_{\mathrm{b}} b_{\mathrm{i}}}.
   \label{eq:likelihood_m_and_b}
@@
 \ref{eq:likelihood_m_and_b}, but we do not have such a model for the SPI background.
-The background in SPI is dominated by the interaction of cosmic rays in the satellite material, which produces e.g.
-nuclear de-excitation line emission \citep{spi_bkg}.
-Therefore, the background consists of several hundred different nuclear lines \citep{spi_bkg}, which makes an accurate spectral model for the background impossible at the moment.
-But we can marginalize over the parameters $b_{\mathrm{i}}$ using only the fact that they can not be negative, which leaves us with Eq.
+The background in SPI is dominated by the interaction of cosmic rays in the satellite material, which produces nuclear de-excitation line emission for example \citep{spi_bkg}.
+For this reason, the background consists of several hundred different nuclear lines \citep{spi_bkg}, which makes an accurate spectral model for the background impossible at present.
+However, we can marginalise over the parameters $b_{\mathrm{i}}$ using only the simple fact that they cannot be negative, which leaves us with Eq.
 \ref{eq:likelihood_marg}.
@@
         \mathcal{L}(D_{\mathrm{i}}, B_{\mathrm{i}},t_{\mathrm{d}},t_{\mathrm{b}}|\vec{\theta}) = \int_{0}^{\infty}\textrm{db}_{\mathrm{i}}\frac{(t_{\mathrm{d}}(m_{\mathrm{i}}(\vec{\theta})+ b_{\mathrm{i}}))^{D_{\mathrm{i}}}}{D_{\mathrm{i}}!}\cdot\\
-  e^{-t_{\mathrm{d}}(m_{\mathrm{i}}(\vec{\theta})+b_{\mathrm{i}})} \frac{(t_{\mathrm{b}} b_{\mathrm{i}})^{B_{\mathrm{i}}}}{B_{\mathrm{i}}!} e^{-t_{\mathrm{b}}b_{\mathrm{i}}}
+  e^{-t_{\mathrm{d}}(m_{\mathrm{i}}(\vec{\theta})+b_{\mathrm{i}})} \frac{(t_{\mathrm{b}} b_{\mathrm{i}})^{B_{\mathrm{i}}}}{B_{\mathrm{i}}!} e^{-t_{\mathrm{b}}b_{\mathrm{i}}}.
   \label{eq:likelihood_marg}
@@
 \noindent
-The marginalisation is equivalent to integrating out the background rate parameter assuming a uniform prior from 0 to $\infty$.
+The marginalisation is equivalent to integrating out the background rate parameter assuming a uniform prior from zero to $\infty$.
 Because solving this integral is computationally expensive, we use a profile likelihood as an auxiliary but still statistically sound figure of merit.
-For the profile likelihood we use the fact, that the derivative of the likelihood at its maximum is zero ($\frac{\textrm{dL}}{\textrm{db}_i}=0$).
+For the profile likelihood, we use the fact that the derivative of the likelihood at its maximum is zero ($\frac{\textrm{dL}}{\textrm{db}_i}=0$).
 This defines the background rates $b_\mathrm{{i, max}}$ (see Eq.
-\ref{eq:bmax}) that maximize the likelihood for a given model $m_{\mathrm{i}}(\vec{\theta})$ and observed quantities.
+\ref{eq:bmax}) that maximise the likelihood for a given model $m_{\mathrm{i}}(\vec{\theta})$ and observed quantities:
 \begin{multline}
@@
 \ref{eq:likelihood_marg} is in a small area around $b_{\mathrm{i,max}}$.
-This profile likelihood method is used in many spectral analysis works \citep[e.g.][]{profile2, profile1} and is also available in {\tt XSPEC} \citep{xspec} as cstat and pgstat.
-%\footnote{https://heasarc.gsfc.nasa.gov/xanadu/xspec/manual/XSappendixStatistics.html}.
-%and works very well as long as one does not have too few counts in the background observation \footnote{For a derivation see https://giacomov.github.io/Bias-in-profile-poisson-likelihood/}.
+This profile likelihood method has been used in many spectral analysis works \citep[e.g.][]{profile2, profile1} and is also available in {\tt XSPEC} \citep{xspec} as cstat and pgstat.
 
@@
 
-In {\tt PySPI}, we use the official response files, as described in Sec.
-\ref{response}, interpolate them to the wanted energy bins and source positions and construct one response matrix incorporating all the information about the effective area and energy redistribution.
-This also includes that we take into account that the mask is not absorbing 100\% of the photons flying through it.
-%This is different to the work presented in \citet{Bosnjak-2014}, which used a `response function' simply taking into account the exposed fraction of each detector and therefore assuming a mask that absorbs 100\% of the photons for every photon energy.
+In {\tt PySPI}, we use the official response files, as described in Sect.
+\ref{response}, interpolate them to the wanted energy bins and source positions, and construct one response matrix incorporating all the information about the effective area and energy redistribution.
+During this process, we take into account that the mask is not absorbing 100\% of the photons flying through it.
 
-\subsubsection{Electronic Noise}
+\subsubsection{Electronic noise}
 
@@
 
-\subsubsection{General Procedure}
+\subsubsection{General procedure}
 
 Every Ge detector is treated as an independent detector unit. The workflow during a fit step is a forward folding method:
-\begin{itemize}
-  \vspace{-0.2cm}
-  \item sample model parameters
-  \item calculate model flux and responses individually for all detectors for the given source position
-  \item fold model with responses to get predicted model counts in all detectors
-  \item calculate log-likelihood for all detectors
-  \item sum these log-likelihoods to get the total log-likelihood of the SPI data for the given model parameters
-\end{itemize}
-%A sampling algorithm like MultiNest \citep{multinest} is used to iterate this procedure, in order to determine the posterior distributions.\\
+(1) sample model parameters, (2) calculate the model flux and responses individually for all detectors for the given source position, (3) fold the model with responses to get the predicted model counts in all detectors, (4) calculate the log-likelihood for all detectors, and (5) sum these log-likelihoods to get the total log-likelihood of the SPI data for the given model parameters.
+The BALROG (BAyesian Lo-cation Reconstruction Of GRBs) algorithm for localising GRBs with \textit{Fermi}/GBM employs the same method \citep{balrog}, which shows that forward folding allows one to localise photon sources with a non-imaging instrument.
+It is important to realise that the instruments SPI and GBM are fundamentally very similar; they both consist of individual detectors that have different responses for a given source position.
+In GBM, this is due to the different pointing directions of the detectors, and in SPI it is due to the varying obscuration by the mask.
+Even though SPI is defined as a coded-mask instrument, it does not require special treatment.
+The information that the mask encodes into the data is automatically included by using the different responses for the detectors and a forward folding method.
+A similar approach was used by \citet{Tohuvavohu-2021} that introduces a new forward folding method to detect and localise faint GRBs with the coded mask instrument Swift/BAT.
 
-\noindent
-The BALROG (BAyesian Lo-cation Reconstruction Of GRBs) algorithm for localizing GRBs with \textit{Fermi}/GBM employs the same method \citep{balrog}, which shows that forward folding allows one to localize photon sources with a non-imaging instrument.
-It is important to realize that the instruments SPI and GBM are fundamentally very similar.
-They both consist of individual detectors that have different responses for a given source position.
-In GBM, this is due to the different pointing directions of the detectors, and in SPI due to the varying obscuration by the mask.
-Even though SPI is defined as a coded-mask instrument, we don't have to treat it specially.
-The information which the mask encodes into the data is automatically included by using the different responses for the detectors and a forward folding method.
-A similar approach is used in \citet{Tohuvavohu-2021}, that introduces a new forward folding method to detect and localize faint GRBs with the coded mask instrument Swift/BAT.
+\subsubsection{Software interface}
 
-\subsubsection{Software Interface}
+{\tt PySPI} constructs a plug-in for 3ML \citep{3ML}.
+This allows one to fit SPI data together with data from other instruments, such as \textit{Fermi}/GBM\footnote{See threeml.readthedocs.io}.
+{\tt PySPI} is open source software, and is publicly available on GitHub \citep{joss}, including documentation with examples\footnote{See pyspi.readthedocs.io}.
 
-{\tt PySPI} constructs a plugin for the Multi-Mission Maximum Likelihood framework \citep[3ML][]{3ML}.
-This allows one to fit SPI data together with data from other instruments, such as \textit{Fermi}/GBM\footnote{See threeml.readthedocs.io}.
-{\tt PySPI} is an open source software, which is publicly available on GitHub \citep{joss}, including documentation with examples\footnote{See pyspi.readthedocs.io}.
+\subsection{Comparison of our method to Bo{\v{s}}njak et al. 2014}
 
-\section{Physical Synchrotron Model}
+\citet{Bosnjak-2014} performed a joint analysis of SPI and IBIS (Imager on Board the \textit{INTEGRAL} Satellite) data of GRBs and created a spectral catalogue of \textit{INTEGRAL} GRBs \citep{Ubertini-2003}.
+\citet{Bosnjak-2014} construct a response for every SPI detector and forward fold the photon model directly into the data space of every detector, which is similar to our approach in this work.
+Following their paper, we see two main differences compared to our method, namely response generation and treatment of the electronic noise, and one ill-defined issue (background treatment).
+
+For the response generation, \citet{Bosnjak-2014} state that they calculate a response function taking into account the exposed fraction of each detector for the GRB position and that  the net
+spectrum is zero for a completely shadowed detector.
+Therefore, we conclude that they used an idealistic mask with zero transparency at all energies.
+We on the other hand used the official response simulations that also include some transparency, especially at high energies.
+The second point is that the electronic noise is ignored completely in \citet{Bosnjak-2014}.
+\citet{spi_electronic_noise}  showed that the effect of the PSD events gets stronger for bright sources, and therefore it is important to account for this effect in the case of GRBs.
+
+Concerning the background treatment, \citet{Bosnjak-2014} argue that background subtraction is better than using a model template for the background within {\tt OSA}, and cite  \citet{Cash-1979} for their likelihood.
+Therefore, one would conclude that they used a Poisson likelihood on the background-subtracted data, but they also state that they provide on-burst and background spectra separately to XSPEC, which implies that no background subtraction was done before the fit.
+This was clarified with {\v{Z}}.
+Bo{\v{s}}njak in a private communication during the refereeing process: in XSPEC, background and burst(-source) spectra were used separately, and no background subtraction was done for the fits.
+
+Unfortunately, the software used to generate the data files and response files in \citet{Bosnjak-2014} is not public and only the results for combined fits of SPI and IBIS data are shown.
+Therefore, we cannot directly compare our method and results with theirs.
+Also, \citet{Bosnjak-2014} only used data up to 1 MeV for SPI, whereas with PySPI we can use the data up to higher energies (up to 8 MeV), which is needed to constrain the peak energy for GRB 1200711A, which is at $\approx$ 1.4 MeV (see Sec.
+\ref{pyspi_gbm}).
+
+\section{Physical synchrotron model}
 \label{synch}
@@
 This model was previously used to successfully fit many single-pulse GRBs observed with \textit{Fermi}/GBM in \citet{synch}, which also includes a detailed description of the model.
-Here we summarize the main points.
+Here, we summarise the main points.
 
-The core of the model is the assumption of some generic acceleration mechanism, that constantly accelerates electrons into a power law spectrum $N(\gamma )\propto \gamma^{-p}$ between $\gamma_{\textrm{inj}}$ and $\gamma_{\textrm{max}}$.
+The core of the model is the assumption of some generic acceleration mechanism that constantly accelerates electrons into a power-law spectrum $N(\gamma )\propto \gamma^{-p}$ between $\gamma_{\textrm{inj}}$ and $\gamma_{\textrm{max}}$.
 These electrons are cooled via the emission of synchrotron photons in a magnetic field.
-The resulting photon spectrum is the sum of the photon spectra at every time step in the cooling process and is defined by five quantities:
+The resulting photon spectrum is the sum of the photon spectra at every time-step in the cooling process and is defined by five quantities: (1) the magnetic field strength ($B$), (2) the slope of the injected electron spectrum ($p$), (3) the lower boundary of the injected electron spectrum ($\gamma_{\mathrm{inj}}$), (4) the upper boundary of the injected electron spectrum ($\gamma_{\mathrm{max}}$), and (5) the characteristic Lorentz factor the electrons cool to ($\gamma_{\mathrm{cool}}$).
+There exists a strong degeneracy between $B$ and $\gamma_{\mathrm{inj}}$, as their combination sets the peak of the photon spectrum.
+Therefore, we fix $\gamma_{\mathrm{inj}}=10^{5}$ and only fit for $B$.
 
-\begin{enumerate}
-  \vspace{-0.2cm}
-	\item Magnetic field strength $B$
-  \item Slope of the injected electron spectrum $p$
-  \item Lower boundary of the injected electron spectrum $\gamma_{\mathrm{inj}}$
-  \item Upper boundary of the injected electron spectrum $\gamma_{\mathrm{max}}$
-  \item Characteristic Lorentz factor the electrons cool to $\gamma_{\mathrm{cool}}$
-\end{enumerate}
+\section{Model checking}
+\label{PPC}
+How to decipher whether or not the fit of a model is a good description of the measured data is a very complicated and highly debated  topic in the statistics community.
+Measurements like reduced $\chi^{2}$ rely on many assumptions; for example, that all the probability distributions in the problem are described as normal distributions \citep{dosanddonts}.
+This is not the case here, as the measurement process is a Poisson process.
+We therefore decided to use posterior predictive checks (PPCs) and quantile-quantile (QQ) plots.
 
-\noindent
-There exists a strong degeneracy between $B$ and $\gamma_{\mathrm{inj}}$, as their combination sets the peak of the photon spectrum.
-Therefore we fix $\gamma_{\mathrm{inj}}=10^{5}$ and only fit for $B$.
-% the following is just duplication
-%Thus, the results for $\gamma_{\mathrm{max}}$ and $\gamma_{\mathrm{cool}}$ are determined relative to the fixed $\gamma_{\mathrm{inj}}$.
-
-\subsection{Comparison to Bo{\v{s}}njak et al. 2014}
-
-\BB{\citet{Bosnjak-2014} did a joined analysis of SPI and the Imager on Board the \textit{INTEGRAL} Satellite (IBIS) data of GRBs to create a spectral catalque of \textit{INTEGRAL} GRBs \citep{Ubertini-2003}.
-They construct a response for every SPI detector and forward model the photon model directly into the data space of every detector, which is similar to our approach in this work.
-But following their paper we see three main differences compared to our methods: Background treatment, response generation and PSD events.\\
-In the paper the authors argue that background subtracting is better than using a model template for the background within OSA, as well as cite Cash 1979 \citep{Cash-1979} for their likelihood.
-Therefore we conclude that they used a Poisson likelihood on the background subtracted data.
-This is different to our approach and it has been shown that using background subtraction can give misleading results \citep[e.g.][]{Greiner-2016}.
-For the response generation the authors in \citet{Bosnjak-2014} state that they calculate a response function taking into account the exposed fraction of each detector for the GRB position and that for a detector completely shadowed the net spectrum is zero.
-Therefore we conclude that they used an idealistic mask with zero transparency at all energies.
-We on the other hand used the official response simulations that also include some transparency, especially at high energies.
-The last point are the PSD events, which are ignored completely in \citet{Bosnjak-2014}.
-\citet{spi_electronic_noise} have shown that the effect of the PSD events gets stronger for bright sources, therefore it is important to account for this effect in the case of GRBs.\\
-Unfortunately the software used in \citet{Bosnjak-2014} is not public, so we can not compare our method with theirs directly.}
-
-\section{Model Checking}
-\label{PPC}
-To check if the fit of a model is a good description of the measured data is a very complicated topic and highly debated in the statistics community.
-Measurements like reduced $\chi^{2}$ use many assumptions, like for example that all the probability distributions in the problem are described as normal distributions \citep{dosanddonts}.
-This is not the case here, as the measurement process is a Poisson process.
-Therefore we decided to use Posterior Predictive Checks (PPC) and Quantile-Quantile (QQ) plots.
-
-For the PPCs one simulates new data from the full posterior of the fit as well as the measurement process (see Eq.
+For the PPCs, one simulates new data from the full posterior of the fit and the measurement process (see Eq.
 \ref{eq:ppc}) and compares them to the observed data \citep{ppc}.
@@
   \label{eq:ppc}
-\end{equation}
+.\end{equation}
 
 \noindent
-Here $y^{\textrm{obs}}$ are the observed data, $\textrm{P}(\vec{\theta}|y^{\textrm{obs}})$ is the posterior distribution of the model parameters $\vec{\theta}$ given the observed data, $\textrm{P}(y^{\textrm{sim}}|\vec{\theta})$ is the probability of new data given the parameters of the model and $y^{\textrm{sim}}$ are the simulated data.
-%These simulated data are then compared to the observed data and allow for a visual check, whether the posterior distributions of the fit together with the measuring process can reproduce the data.
+Here $y^{\textrm{obs}}$ are the observed data, $\textrm{P}(\vec{\theta}|y^{\textrm{obs}})$ is the posterior distribution of the model parameters $\vec{\theta}$ given the observed data, $\textrm{P}(y^{\textrm{sim}}|\vec{\theta})$ is the probability of new data given the parameters of the model, and $y^{\textrm{sim}}$ are the simulated data.
 
@@
 \label{analysis}
-As an example, we analyze GRB 120711A, a bright, multi-pulse GRB with a precursor and a long emission period of $\approx$100 s. It was detected by SPI and GBM \citep{GCN_integral, GCN_gbm}.
-%Additionally, Swift-XRT \citep{GCN_swift} observed the afterglow.
+As an example, we analyse GRB 120711A, a bright, multi-pulse GRB with a precursor and a long emission period of $\approx$100 s. GRB 120711A was detected by SPI and GBM \citep{GCN_integral, GCN_gbm}.
 We look at one time interval with a duration of 10 seconds around the first bright peak in the light curve (see Fig.
 \ref{fig:time_selection}).
-From the Swift/XRT detection of the afterglow we know an accurate position of the GRB (RA = 94\fdg68, Decl.
+From the detection of the afterglow with the x-ray telescope (XRT) onboard the Swift satellite, we have an accurate position of the GRB (RA = 94\fdg68, Decl.
 = -71\fdg00 in J2000) \citep{GCN_swift}.
-The SPI data of GRB 120711A were previously analyzed by \citet{Martin-Carrillo-2014}, but only fitted the time averaged spectrum over the $T_{90}$ emission (between 0 and 115 seconds after the trigger) with an empirical exponential cutoff power-law model, while focussing on the post-GRB emission properties.
+The SPI data for GRB 120711A were previously analysed by \citet{Martin-Carrillo-2014}, but these authors only fitted the time-averaged spectrum over the $T_{90}$ emission (between 0 and 115 seconds after the trigger) with an empirical exponential cutoff power-law model, while focusing on the post-GRB emission properties.
 
@@
 
-First, we fit the data with the empirical Band function, show a comparison between the fit results using {\tt PySPI} versus {\tt OSA} (Sec.
-\ref{pyspi_osa}), and check if the results for SPI and GBM are in agreement (Sec.
+First, we present our fit of the data with the empirical Band function, and show a comparison between the fit results using {\tt PySPI} versus {\tt OSA} (Sec.
+\ref{pyspi_osa}).
+We then check whether or not the results for SPI and GBM are in agreement (Sec.
 \ref{pyspi_gbm}).
-Then, we fit the SPI and GBM data simultaneously with a physical synchrotron model, to check whether including SPI in the analysis can reduce the allowed parameter space (Sec.
+Subsequently, we present our fit of the SPI and GBM data simultaneously with a physical synchrotron model, which was done to check whether or not including SPI in the analysis can reduce the allowed parameter space (Sec.
 \ref{pyspi_gbm_joined}).
 
-%We analyze the data from the two instruments independently first with the empirical Band function, to check if the results for SPI and GBM are in agreement as well as show a comparison between the fit results with {\tt PySPI} and the official software tools for GRB analysis within {\tt OSA}.
-Then, we fit the SPI and GBM data simultaneously with a physical synchrotron model, and show that it can reduce the allowed parameter space significantly, compared to the individual fits.
-For all GBM and {\tt PySPI} fits we added effective area correction parameters in the fit, allowing the total effective area of the individual detectors to vary with respect to each other, to account for slightly different calibrations.
-To do this, we fix the response of one of the detectors
-%to the response of that detector
-and fit one parameter for every other detector. We constrain the effective area correction parameters to be between 0.7 and 1.3.
-
-All the fits utilize 3ML \citep{3ML} and the Bayesian sampling algorithm MultiNest \citep{multinest} to create posterior distributions of the parameters.
-%To visualize the posterior distribution we use ChainConsumer \citep{chainconsumer} with the output from MultiNest to create corner plots.
+For all GBM and {\tt PySPI} fits, we added effective area correction parameters, allowing the total effective area of the individual detectors to vary with respect to each other in order to account for slightly different calibrations.
+To do this, we fixed the response of one of the detectors and fitted one parameter for every other detector.
+We constrain the effective area correction parameters to be between 0.7 and 1.3.
+All the fits use {\tt 3ML} \citep{3ML} and the Bayesian sampling algorithm {\tt MultiNest} \citep{multinest} to create posterior distributions of the parameters.
 
@@
 \label{pyspi_osa}
-We fit the SPI data of an identical time interval with a Band function
-%as a spectral model
-within {\tt PySPI} and {\tt OSA}.
-%to check if the results are in agreement.
-Fig.
-\ref{fig:corner_osa_pyspi_band} shows the resulting posterior distributions of the fits.
+We fit the SPI data of an identical time interval with a Band function within {\tt PySPI} and {\tt OSA}.
+Figure \ref{fig:corner_osa_pyspi_band} shows the resulting posterior distributions of the fits.
 The results for the spectral shape from the two analysis techniques agree within their uncertainty regions, but {\tt PySPI} can constrain the model more precisely (see Fig.
@@
     \includegraphics[width=1\linewidth]{figures/pyspi_vs_osa_band.pdf}
-    \caption{Corner plot for the Band function fit to the SPI data with {\tt PySPI} and {\tt OSA} to the data of GRB120711A.
+    \caption{Corner plot showing the Band function fit to the SPI data with {\tt PySPI} and {\tt OSA} with the data for GRB120711A.
 The results are in agreement, but {\tt PySPI} constrains the parameters more precisely.}
@@
     \caption{Corner plot for the SPI fit with {\tt PySPI} and the GBM fit to the data of GRB120711A.
-In this fit we used a Band function as spectral model.
-The spectral shape for the SPI and GBM fits coincide within their uncertainty regions and the normalization is off by $\approx$10\%.}
+In this fit, we used a Band function as a spectral model.
+The spectral shapes for the SPI and GBM fits coincide within their uncertainty regions and the normalisation is off by $\approx$10\%.}
     \label{fig:corner_gbm_pyspi_band}
@@
 In this fit we used a physical synchrotron model (see Sec.
-\ref{synch}) as spectral model.
-The results from SPI and GBM agree within their uncertainty region and the combined fit constrains the parameter better than the individual ones.}
+\ref{synch}) as a spectral model.
+The results from SPI and GBM agree within their uncertainty region and the combined fit provides better constraints on the parameter than the individual ones.}
     \label{fig:corner_gbm_pyspi_joined_syn}
@@
     \caption{Model posterior plots (95\% confidence region) for the results with the Band function model and the data for GRB120711A.
-Left panel shows the results for the {\tt PySPI} fit compared to the fit using {\tt OSA} and the right panel the {\tt PySPI} fit compared to the GBM fit.}
+The left panel shows the results for the {\tt PySPI} fit compared to the fit using {\tt OSA} and the right panel shows the {\tt PySPI} fit compared to the GBM fit.}
     \label{fig:model_plot_band}
@@
 \label{pyspi_gbm}
-Next, we analyze SPI data with {\tt PySPI} and the GBM data with the GRB analysis within 3ML, again with a Band function.
-Fig.
-\ref{fig:corner_gbm_pyspi_band} shows the results for these fits, demonstrating that the results for the spectral shape from SPI and GBM are in agreement.
-It also shows that the effective area calibration for SPI and GBM are well aligned within only $\approx$10\% difference ($K$ parameter), which is well within the
+We then analysed SPI data with {\tt PySPI} and the GBM data with the GRB analysis within {\tt 3ML}, again with a Band function.
+Figure \ref{fig:corner_gbm_pyspi_band} shows the results for these fits; we can see that the results for the spectral shape from SPI and GBM are in agreement.
+It also shows that the effective area calibrations for SPI and GBM are well aligned, with a difference of  only $\approx$10\%
+ ($K$ parameter), which is well within the
 %usual calibration offsets of gamma-ray space telescopes.
@@
 
-\subsection{Joint Fit of SPI and GBM}
+\subsection{Joint fit of SPI and GBM}
 \label{pyspi_gbm_joined}
-We perform a joint fit of SPI and GBM data with a physical synchrotron model (see Sec.
+We performed a joint fit of SPI and GBM data with a physical synchrotron model (see Sec.
 \ref{synch}).
-Fig.
-\ref{fig:corner_gbm_pyspi_joined_syn} shows the corner plots for the individual and the combined fits.
+Figure \ref{fig:corner_gbm_pyspi_joined_syn} shows the corner plots for the individual and combined fits.
 The posterior distribution of the parameters from the GBM and the SPI fit agree within their uncertainty regions and the combined fit reduces the allowed parameter space.
@@
     \caption{Model posterior plots (95\% confidence region) for the results with the physical synchrotron model and the data for GRB120711A.
-Left panel shows the results for the SPI alone fit compared to the combined fit and the right panel the GBM alone fit compared to the combined fit.
+The left panel shows the results for the SPI fit compared to the combined fit and the right panel shows the GBM fit compared to the combined fit.
 The combined fit reduces the allowed model space.}
@@
     \includegraphics[width=1\linewidth]{figures/fit_plot_high.pdf}
-    \caption{Data (for GRB120711A) and best fit model in count space for three of the SPI detectors and one of the NaI (BGO) detectors of GBM in the upper (lower) plot.
+    \caption{Data (for GRB120711A) and best-fit model in count space for three of the SPI detectors and one of the NaI (BGO) detectors of GBM  (upper  and lower plot, respectively).
 The spectral model for this fit was a physical synchrotron model.}
@@
 \label{conclusion}
-We have presented a new analysis method for GRBs detected by \textit{INTEGRAL}/SPI and the corresponding software package utilizing this method ({\tt PySPI}), which uses a proper forward-folding technique for each detector (see Sec.
+We present a new analysis method for GRBs detected by \textit{INTEGRAL}/SPI and the corresponding software package that uses this method.
+The {\tt PySPI} software uses a proper forward-folding technique for each detector (see Sec.
 \ref{pyspi}).
-To show that this improves the analysis of GRBs detected by SPI, we have analyzed GRB 120711A using the data from INTGRAL/SPI and \textit{Fermi}/GBM.
-The results for SPI with {\tt PySPI} are in agreement with those from the \textit{INTEGRAL} OSA software, but more constraining.
-Also, the resulting spectral shape for the fits with GBM and SPI data are in agreement and the relative calibration difference between SPI and GBM we conclude from the fits, is $\approx$ 10\% or less.
+To show that this improves the analysis of GRBs detected by SPI, we analysed GRB 120711A using the data from \textit{INTEGRAL}/SPI and \textit{Fermi}/GBM.
+The results for SPI with {\tt PySPI} are in agreement with those from the \textit{INTEGRAL} {\tt OSA} software, but provide better constraints.
+Also, the resulting spectral shape for the fits with GBM and SPI data are in agreement and the relative calibration difference between SPI and GBM ---which we conclude from the fits--- is $\approx$ 10\% or less.
 We show that the GBM as well as the SPI data for GRB 120711A can be fitted well with a physical synchrotron model and that combining the data in a simultaneous fit improves the parameter constraints.
 Consequently, SPI can play an important role in physical GRB model checking.
-%, if we apply a forward modelling method which is used in {\tt PySPI}, as described in Sec. \ref{pyspi}.
-
-The next steps will be the analysis of all GRBs detected by SPI with different physical models and {\tt PySPI}, to check if some of these models can be rejected with the SPI data.
-This will be covered in a future work.
-% thomas Generally {\tt PySPI} can improve the scientific output from SPI for GRBs significantly.
-Due to a new analysis method, that folds the source model directly into the data space of every SPI detector with the full response of the individual detectors, the results are more constraining than the results with the official analysis software.
+The next steps will entail an analysis of all GRBs detected by SPI with different physical models and {\tt PySPI} to check whether or not some of these models can be rejected with the SPI data.
+This will be covered in a future paper.
 
 \begin{acknowledgement}
+We thank {\v{Z}}.
+Bo{\v{s}}njak for quickly responding to our inquery about the details of data handling in \citet{Bosnjak-2014}.
 BB acknowledges support from the German Aerospace Center (Deutsches Zentrum f\"ur Luft- und Raumfahrt, DLR) under FKZ 50 0R 1913.
@@
 \bibliography{bib}
+
+%\newpage
 \begin{appendix}
+%\onecolumn
+  \section{Localising GRB 120711A}
 
-  \section{Localizing GRB 120711A}
+  It is also possible to localise GRBs with PySPI.
+To localise, we vary the spectrum parameters and the location of the source at the same time in one fit.
+For this, {\tt PySPI} has a fast response generator that uses the base response simulation grid to generate the response for any given source position quickly.
+Figure \ref{fig:localization} shows the localisation we get if we fit the location and use a Band function as spectral model.
+We also marked the position of the GRB measured by \textit{Swift}/XRT, which shows that the result with the SPI data is in agreement with the \textit{Swift}/XRT observation \citep{GCN_swift}.
+For this fit, we only used the energies up to 600 keV to avoid the PSD energy region.
 
-  \BB{It is also possible to localize GRBs with PySPI.
-To localize we vary the spectrum parameters and the location of the source at the same time in one fit.
-For this, PySPi has a fast response generator, that uses the base response simulation grid to generate the response for any given source position quickly.
-Fig.
-\ref{fig:localization} shows the localization we get if we fit the location and use a Band function as spectral model.
-We also marked the position of the GRB measured by Swift/XRT, which shows that the result with the SPI data is in agreement with the Swift/XRT observation \citep{GCN_swift}.
-For this fit we only used the energies up to 600 keV, to avoid the PSD energy region.}
-
-  \begin{figure}
+  \begin{figure}[ht]
   \begin{centering}
-    \includegraphics[width=1\linewidth]{figures/loc.pdf}
-    \caption{Localization of GRB120711A with PySPI with contours giving the statistical only 1 and 2 sigma areas.
-We estimate an additional systematic error of $\approx$ 0.5 degree because that is the resolution of the grid points in the response simulation.
+    \includegraphics[width=0.7\linewidth]{figures/loc.pdf}
+    \caption{Localisation of GRB120711A with PySPI.
+Contours show the statistical only 1- and 2-sigma credible regions.
+We estimate an additional systematic error of $\approx$ 0.5 degrees because that is the resolution of the grid points in the response simulation.
 The dashed lines mark the position observed by Swift/XRT \citep{GCN_swift}.}
@@
 \onecolumn
-  \section{Model Checking Plots}
+  \section{Model checking plots}
   \label{appendix}
   In this section we show a selection of the PPC- and QQ-plots for the simultaneous synchrotron fit to the SPI and GBM data for GRB120711A.
-The green and purple shaded area are the one and two sigma contours.
-In the PPC plots the dark yellow curve is the detected count spectrum and in the QQ plots the expected 1:1 relation between the cumulative model and observed counts.
 
@@
       \caption{PPC (left) and QQ (right) plot for the GBM detector n0.
-The green and purple shaded area are the one and two sigma contours.
-In the PPC plots the dark yellow curve is the detected count spectrum and in the QQ plots the expected 1:1 relation between the cumulative model and observed counts.}
+The green and purple shaded areas are the one- and two-sigma contours.
+In the PPC plots, the dark yellow curve is the detected count spectrum, and in the QQ plots it shows the expected 1:1 relation between the cumulative model and observed counts.}
       \label{fig:n0_model_check}
@@
       \caption{PPC (left) and QQ (right) plot for the GBM detector b0.
-The green and purple shaded area are the one and two sigma contours.
-In the PPC plots the dark yellow curve is the detected count spectrum and in the QQ plots the expected 1:1 relation between the cumulative model and observed counts.}
+The green and purple shaded area are the one- and two-sigma contours.
+The dark yellow curve has the same signification as in Fig.
+B.1.
+for the two plots.}
       \label{fig:b0_model_check}
@@
       \includegraphics[width=0.45\linewidth]{figures/low_13_qq.pdf}
-      \caption{PPC (left) and QQ (right) plot for the low energy range of SPI detector 13 (all single events).
-In the PPC plots the dark yellow curve is the detected count spectrum and in the QQ plots the expected 1:1 relation between the cumulative model and observed counts.}
+      \caption{PPC (left) and QQ (right) plot for the low energy range of SPI detector 13 (all single events). The dark
+yellow curve has the same signification as in Fig. B.1. for the two plots.}
       \label{fig:low_13_model_check}
@@
       \includegraphics[width=0.45\linewidth]{figures/psd_13_qq.pdf}
-      \caption{PPC (left) and QQ (right) plot for the middle energy range of SPI detector 13 (only PSD events).
-In the PPC plots the dark yellow curve is the detected count spectrum and in the QQ plots the expected 1:1 relation between the cumulative model and observed counts.}
+      \caption{PPC (left) and QQ (right) plot for the middle energy range of SPI detector 13 (only PSD events). The dark
+yellow curve has the same signification as in Fig. B.1. for the two plots.}
       \label{fig:psd_13_model_check}
